### 2022-05-30 Bubble-deformation.tex
Add files via upload

%  -----------------------------------------------------------------------------
%  -----------------------------------------------------------------------------
%  Numerical simulation of bubble deformation and breakup under simple linear 
%  shear flows
%  
%  Authors: Mitsuhiro Ohta, Tetsuya Ueta, Yozo Toei, Edwin Jimenez, and
%           Mark Sussman
%  
%  Modified: 22 May 2022
%  -----------------------------------------------------------------------------
%  -----------------------------------------------------------------------------

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
 showkeys,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
 prfluids,
 onecolumn
%prfluids,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\graphicspath{{figures/}}
\setlength{\tabcolsep}{12pt} % Modifies table column separation.

% MATH -------------------------------------------------------------------------
\newcommand{\Hea}{\mathcal{H}}
\newcommand{\opI}{\mathcal{I}}

\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
%\newcommand{\Real}[1]{\text{Re}\left\{#1\right\}}
%\newcommand{\Imag}[1]{\text{Im}\left\{#1\right\}}

\newcommand{\eps}{\epsilon}
\newcommand{\veps}{\varepsilon}
\newcommand{\ep}{\varepsilon}
\newcommand{\ome}{\omega}

\newcommand{\del}{\partial}
%\newcommand{\Bdy}{\del\Dom}
%\newcommand{\dive}{\nabla\cdot}
%\newcommand{\divS}{\text{div}_{\Bdy}}

\newcommand{\vv}{\mathbf}
\newcommand{\bmD}{\vv{D}}
\newcommand{\bmg}{\vv{g}}
\newcommand{\bmI}{\vv{I}}
\newcommand{\bmu}{\vv{u}}

\newcommand{\LWH}{L\times W \times H}

%\newcommand{\twoFigWidth}{0.485}

\newcommand{\lwh}[3]{L(#1R)\times W(#2R) \times H(#3R)}
%\newcommand{\dist}[1]{\text{dist}\left(#1\right)}
%\newcommand{\jump}[1]{\left[#1\right]_{-}^{+}}
%\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
%\newcommand{\abs}[1]{\left\vert#1\right\vert}
%\newcommand{\floor}[1]{\left\lfloor#1\right\rfloor}
%\newcommand{\ceil}[1]{\left\lceil#1\right\rceil}
%
%\newcommand{\vnu}{\boldsymbol\nu}
%\DeclareMathOperator*{\argmax}{arg\,max}
%\DeclareMathOperator*{\argmin}{arg\,min}

%  -----------------------------------------------------------------------------
\begin{document}

%\preprint{APS/123-QED}

%\title{Manuscript Title:\\with Forced Linebreak}% Force line breaks with \\
%\thanks{A footnote to the article title}%
\title{Numerical simulation of bubble deformation \\
       and breakup under simple linear shear flows}

\author{Mitsuhiro Ohta}
 \altaffiliation[Also in the ]{Department of Mechanical Engineering, Graduate School 
                 of Advanced Technology and Science,
                 Tokushima University}%Lines break automatically or can be forced with \\
  \email{m-ohta@tokushima-u.ac.jp}
\affiliation{
  Department of Mechanical Science, Graduate School of Technology, Industrial and Social Sciences,
  Tokushima University,\\
  2-1 Minamijyousanjima-cho,Tokushima 770-8506, Japan}
\author{Tetsuya Ueta}
\affiliation{
   Department of Mechanical Engineering, Graduate School of Advanced Technology and Science,\\
  Tokushima University, 2-1 Minamijyousanjima-cho,Tokushima 770-8506, Japan}
\author{Yozo Toei}
 %\email{Second.Author@institution.edu}
\affiliation{%
 %Authors' institution and/or address\\
 %This line break forced with \textbackslash\textbackslash
 High Performance Plastics Company, Sekisui Chemical Co., Ltd.,\\
 2-1 Hyakuyama, Mishimagun Shimamoto-cho, Osaka 618-0021, Japan
}%

%\collaboration{MUSO Collaboration}%\noaffiliation

\author{Edwin Jimenez}  
\affiliation{Department of Computing and Mathematical Sciences, MC 305-16 
             California Institute of Technology, Pasadena, CA 91125, USA
}%

\author{Mark Sussman}  
\affiliation{
  Department of Mathematics,
  Florida State University,
  Tallahassee, FL 32306, USA
}%

%\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
Numerical simulations for the deformation and breakup of a bubble in liquids
undergoing simple linear shear flow are presented.  Computational results are
obtained using a hydrodynamic scheme with formal second-order accuracy based on
a coupled level set/volume-of-fluid (CLSVOF) method.  To verify our numerical
algorithms, and to compare with previous results, we also present simulation
results for the well-known case of drop deformation and rupture.  The numerical
results reveal that the shear-induced bubble deformation and breakup process
differs significantly from that of the analogous drop system under similar flow
conditions.  The first distinguishing factor for bubble breakup is that the
magnitude of shear flow necessary for rupture is much larger than that in the
drop system case.  In other words, a larger Reynolds number is necessary to
induce bubble breakup.  The second distinct feature of the bubble system versus
the drop system is that the bubble does not maintain a stable deformed shape as
the parameters of the system approach the critical ``breakup'' Reynolds number.
It is asserted that the differences in morphology for a bubble undergoing
breakup, versus a drop in the same process, can be attributed to the density
and viscosity ratio of the corresponding two-phase flow systems.  The critical
conditions for bubble breakup with respect to the Reynolds and capillary
numbers are determined for several cases.
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
%                              %display desired
\keywords{Bubble deformation, bubble breakup, shear flow, CFD}

\maketitle

%\tableofcontents

%  -----------------------------------------------------------------------------
\section{Introduction}
%  -----------------------------------------------------------------------------

%
% Note: There were missing references in the .bib file for the following cite tags: 
%       WanMacReni02, OlaSinSak09, ZhaBag11, BayMor11, and Ren08-1. 
%       (Edwin, April 29, 2022)
%
The study of the deformation and breakup of a drop in immiscible viscous
liquids undergoing simple linear shear flow has been investigated extensively
due to its fundamental importance in connection with emulsion and materials
processing, mixing and reaction devices. The pioneering experimental work
of this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34},
and the subsequent theoretical and experimental progress up to the 1980s and
1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.  By the
2000s, progress in computational fluid dynamics (CFD) techniques and increased
access to powerful computing resources led to a surge of research focused on
direct simulations of this problem.  In particular, detailed computational
investigations based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were
presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,
KhiRenCri03,Ren06,Ren07,Ren08-2}.  Since then, the literature on computational
studies on the deformation and breakup of a single or several drops in shear
flow has continued to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06,
BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16,
HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques
have been developed to tackle this problem, including boundary-integral
approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06,
KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and interface-tracking
level set methods \cite{SusSmeOsh94}.

In contrast, and to the best of our knowledge, few computational studies on
bubble deformation and breakup in shear flow have been conducted
\cite{WanShiZha15}.  This type of bubble dynamics in shear flow is also of
critical importance to further our understanding of a variety of scientific and
engineering processes.  In this article, we present computational studies of
shear-driven deformation and breakup of a bubble in insoluble viscous liquids.
The physical properties that distinguish bubble and drop studies are expressed in
terms of the density ratio $\lambda = \rho_b / \rho_m$ and the viscosity ratio
$\eta = \mu_b / \mu_m$, where $\rho$ is the fluid density, $\mu$ is the
viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or
``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble
viscous liquid, the density ratio $\lambda \simeq 0$ and the viscosity ratio
$\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible
viscous liquid take $\lambda =1$ and $\eta \simeq 1$.

In this work we focus on identifying critical flow states numerically, in terms
of dimensionless quantities, that specify the extreme conditions at which a
bubble or drop in shear flow first transitions from deformation to breakup.  An
advantage of studying shear-driven bubble deformation and breakup
computationally, rather than experimentally, is that we can easily modify fluid
physical properties to ascertain the sensitivity of deformation and breakup to
physical parameters.  In our computations, the time-evolution of the boundary
between gas and liquid is tracked with a coupled level set/volume-of-fluid
(CLSVOF) interface capturing algorithm \cite{SusPuc00}.  We focus on
determining critical physical conditions in which the breakup of a bubble
occurs in shear flow because it is important to identify the parameter regimes
in which a relatively simple system transitions from stable to unstable.
Specifically, we identify the critical Reynolds number $Re_{c}$ corresponding
to the bubble breakup onset condition as a function of the Capillary number
$Ca$.  Although the $Re_{c}$ for drop breakup was reported previously
\cite{LiRenRen00}, in this work we determine, for the first time, the critical
Reynolds number that leads to \emph{bubble} breakup.  Additionally, our
computational studies reveal characteristics that distinguish the deformation
and breakup processes of a drop versus those of a bubble.

%  -----------------------------------------------------------------------------
\section{Problem Description}
%  -----------------------------------------------------------------------------

Figure~\ref{fig:SchemAndGrid}(a) shows a schematic of the computational system
for our studies of a bubble (or drop) in shear flow.  The computational domain
consists of a three-dimensional rectangular domain of $L(x)$ (length) $\times$
$W(y)$ (width) $\times$ $H(z)$ (height).  The size of $L(x)$, $W(y)$ and $H(z)$
was determined after consideration of numerical result sensitivity to domain
size; numerical studies of domain-size dependence are presented in
Section~\ref{sec:DomGrdSize}.  All computational results that follow were
obtained from numerical solutions of the three-dimensional governing equations
for gas-liquid/liquid-liquid flows.  Computations are initialized with a
spherical bubble set at the center of the domain that is then subjected to a
linear shear flow generated by the motion of the top and bottom plates, which 
have constant velocity $+V$ and $-V$, respectively.  In the interior of the
domain, the initial velocity condition is assumed to be a simple linear profile
and periodic boundary conditions are imposed along the $x$ and $y$ directions.
Common dimensionless physical parameters used to describe gas-liquid or
liquid-liquid two-phase flows include the Reynolds ($Re$), Weber ($We$) (or
$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers, and the density ratio $\lambda$
and viscosity ratio $\eta$.  For comparison with previous drop studies, we set
$\lambda=1$ and, since in this case the effect of gravity is not considered, we
may ignore the Froude number $Fr$.  As a result, (for $\lambda=1$) the
following dimensionless physical parameters are used to describe the problem of
drop or bubble deformation/breakup in shear flow
%
\begin{eqnarray}\label{dimensonless}
  Re = \frac{\rho_{b}UR}{\mu_{b}}, \quad
  Ca = \frac{\mu_{b}U}{\sigma}, \quad
  \eta = \frac{\mu_{b}}{\mu_{m}}
\end{eqnarray} 
%
where $R$ is the drop or bubble radius, $\sigma$ denotes the surface tension,
and $U$ is the velocity scale. For the problem of shear-induced drop
deformation and breakup, the velocity is set to $U = \mathit{\Gamma} R$, where
the shear-rate $\mathit{\Gamma} = 2V/H$.  As mentioned in the introduction,
most previous drop studies set $\eta = 1$. Thus, for comparison, in this case
we will set $\lambda = \eta = 1$ (and also neglect the effect of gravity so
that $g=0$). On the other hand, in our computations for a bubble, we set the
density and viscosity of air to $\rho_{b}$ = 1.2 kg/m$^{3}$ and $\mu_{b}$ = 1.8
$\times$ $10^{-5}$ Pa$\cdot$s, and we take the density ratio $\lambda$ = 1.2
$\times$ $10^{-3}$ and the viscosity ratio $\eta$ $<$ 1.0 $\times$ $10^{-3}$.
For consistency with previous studies, we will computationally examine the
deformation and breakup of a bubble in simple linear shear flow under as a
function of $Re$ and $Ca$ numbers.  In particular, for a certain $Ca$ value, we
focus on determining the critical value $Re_{c}$ that corresponds to the threshold
for breakup.

%  -----------------------------------------------------------------------------
\section{Numerical Analysis}
%  -----------------------------------------------------------------------------
% 
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{SchematicAndGrid}
  \caption{(a) Computational domain schematic for a bubble or drop in shear 
           flow and (b) (\textit{upper panel}) a two-level adaptive mesh 
           refinement (AMR) grid schematic with an actual computational 
           example (\textit{lower panel}) of bubble deformation in simple linear 
           shear flow on the same grid system.}
  \label{fig:SchemAndGrid}
\end{figure}
%

\subsection{Numerical method and governing equations}
%  -----------------------------------------------------------------------------
Numerical results were obtained using the interface-tracking CLSVOF method,
which is based on a fixed grid finite difference algorithm.  In our studies,
two-phase fluid flow is comprised of air and a viscous Newtonian liquid. A
single set of three-dimensional equations governs the motion of both fluids,
which are taken to be incompressible, and consists of the continuity equation
and the Navier-Stokes equations with surface tension forces:
%
\begin{align}
  \nabla\cdot\bmu &=0  \label{divu} \\
  \frac{\partial\bmu}{\partial t}+(\bmu\cdot\nabla)\bmu &=
  \frac{1}{\rho}\nabla\cdot(-p\bmI+2\mu\bmD)+\bmg-
  \frac{\sigma\kappa}{\rho}\nabla \Hea  \label{nseqn}
\end{align}
%
%%
%\begin{eqnarray}
%\nabla\cdot\bmu=0  \label{divu} %\\
%\end{eqnarray}
%%
%\begin{eqnarray}
%\frac{\partial\bmu}{\partial t}+(\bmu\cdot\nabla)\bmu=
%\frac{1}{\rho}\nabla\cdot(-p\bmI+2\mu\bmD)+\bmg-
%\frac{\sigma\kappa}{\rho}\nabla H  \label{nseqn}
%\end{eqnarray}
%
where $\bmu$ is the velocity vector, $t$ represents time, $p$ is the pressure,
$\bmI$ is the unit tensor, $\bmD$ is the rate of deformation tensor
($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$
is the viscosity, $\kappa$ is the interfacial curvature, and $\Hea(\phi)$ is
the Heaviside function as a function of the level set (LS) function $\phi$. The
singular term (last term) in the right hand side of equation~\eqref{nseqn} is a
body force due to surface tension and is equivalent to specifying that the jump
in the normal stress is equal to $\sigma\kappa$.  The interfacial curvature
$\kappa$ is computed with second order accuracy directly from the
volume-of-fluid (VOF) function using the height function technique.  We remark
that we get the same results if we were to compute $\kappa$ directly from the
LS function using the ``level set'' height function technique.

Since $\rho$ and $\mu$ are taken to be constant in each fluid, with a jump at
the interface, they can be expressed in terms of the Heaviside function,
%
\begin{eqnarray}\label{rhomu}
  \rho=\rho_{\rm m}\Hea+\rho_{\rm b}(1-\Hea), \qquad 
  \mu=\mu_{\rm m}\Hea+\mu_{\rm b}(1-\Hea).
\end{eqnarray}
%
The subscripts ``b'' and ``m'' refer to ``drop or bubble'' and ``matrix fluid'',
respectively.  The Heaviside function, $\Hea(\phi)$, is defined as follows:
%
\begin{equation}\label{heavyeqn}
  \Hea(\phi) = \begin{cases}
               1 & \phi \geq 0 \\
               0 & \phi <0 
               \end{cases}
\end{equation}
%
To represent the free surface with the CLSVOF method, we must evolve the solution
to both the VOF equation for $F$ and the LS equation for $\phi$:
%
%\begin{subequations}\label{eq:clsvof}
\begin{align}\label{eq:clsvof}
  \frac{\partial F}{\partial t}+(\bmu\cdot\nabla)F = 0, \qquad 
  \frac{\partial \phi}{\partial t}+(\bmu\cdot\nabla)\phi = 0. 
\end{align}
%\end{subequations}
%
In all computations the discretized variables $p$, $\phi$ and $F$ are located at
cell centers and the discrete variable $\bmu$ is located at cell face centers.
Our computations are performed using an overall second-order accurate
hydrodynamic scheme.  The spatial discretization uses second-order accurate,
slope limited, upwind techniques for the nonlinear advective terms.  The
velocity and pressure fields are computed using an implicit pressure projection
procedure.

To make efficient use of computational resources, our numerical simulations
utilize an adaptive hierarchy of grids based on a dynamic adaptive mesh
refinement (AMR) technique~\cite{SusAlmBelColHowWel99}.  Adaptive grids are
dynamically adjusted based on the location of a deforming gas-liquid interface.
In the AMR technique the grid resolution is increased in regions near the
interface while a coarser grid is used where the flow is relatively steady.
The upper panel of Figure~\ref{fig:SchemAndGrid}(b) displays a schematic view
of the hierarchical grid structure and the lower panel corresponds to an actual
computational example for bubble deformation in simple linear shear flow.  In
general, the mesh hierarchy is composed of different levels of refinement
ranging from coarsest $\ell=0$ (``level-0") to finest
$\ell=\ell_{\textrm{max}}$ (``level-$\ell_{\textrm{max}}$").  The refinement
ratio of one grid size ($\Delta x=\Delta y=\Delta z$) to the next finer level
is two so that $\Delta x^{\ell+1}=0.5\Delta x^{\ell}$.  All computations in
this study used an AMR system with a maximum prescribed level
$\ell_{\textrm{max}} = 1$ (as illustrated in the upper panel of
Figure~\ref{fig:SchemAndGrid}(b)).  In our adaptive mesh refinement algorithm,
the velocity in coarse grid cells that neighbor fine grid cells is interpolated
from the coarse grid using bilinear interpolation in order to initialize
``ghost'' fine cells. Thus, the bilinear interpolation procedure produces
interpolated fine grid data as a linear combination of the coarse grid data.

\subsection{Validation of numerical method}
%  -----------------------------------------------------------------------------
Numerical studies are presented to verify the accuracy of our computational
methods.  First, we compare quantitatively against the steady-state drop
deformation results reported by Li et al.~\cite{LiRenRen00}.  The shape of a
deformed drop in simple linear shear flow is described in terms of the Taylor
deformation parameter $De=(a-b)/(a+b)$, where $a$ and $b$ are the major and
minor axes of the deformed drop.  For consistency, we perform numerical
simulations using CLSVOF over the same computational domain and grid size used
in~\cite{LiRenRen00}, which has dimensions $\lwh{8}{4}{8}$ (recall that $R$ is
the bubble/drop radius) and a level-0 grid size $\Delta x=\Delta y=\Delta
z=R/8$; our two-level AMR grid structure also uses a finer level-1 grid size
$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  Numerical
results are listed in Table~\ref{tab:DeComparison} for $De$ as a function of
$Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
the VOF method used in \cite{LiRenRen00}, and also with our CLSVOF algorithm.
Table~\ref{tab:DeComparison} indicates that our numerical results are in good
agreement with previous computations for drop deformation and breakup.
%
\begin{table}[tbh]
\caption{Comparison of the Taylor deformation parameter $De$ as a function 
         of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$).}
\label{tab:DeComparison}
%\footnotesize
\center
\begin{tabular}{ c  c  c  c  c }
\hline
\hline
Reynolds number                      & 0.1     & 0.5     & 0.6     & 0.75      \\
$De$(Li et al. (\cite{LiRenRen00}))  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
$De$(Our study)                      & 0.3960  & 0.4570  & 0.4758  & Breakup   \\
\hline
\hline
\end{tabular}
\end{table}
%
\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{DropBreakComparison}
  \caption{Comparison with results reported in~\cite{RenCri01-2} (shown in boxes) 
           for drop breakup in shear flow. (Reprinted with permission from 
           reference~\cite{RenCri01-2}. Copyright 2001, AIP Publishing). Results
           obtained with our CLSVOF algorithm are shown outside boxes. The onset
           of drop breakup is demonstrated for (a) $Re=10$, $Ca=0.16$,
           (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.}
  \label{fig:DropBreakComp}
\end{figure}
%

Next, we present a comparison with numerical results for drop breakup reported
in~\cite{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop
breakup with pinch-off behavior for three $Re$ and $Ca$ conditions and with
constant values of $\lambda = \eta = 1$ for all cases.  The three cases that we
consider correspond to (a) $Re = 10, \, Ca = 0.16$, (b) $Re = 12, \, Ca =
0.1753$, and (c) $Re = 15, \, Ca = 0.196$, and which are illustrated in
Figures~\ref{fig:DropBreakComp}(a)-(c), respectively.  The results reported
in~\cite{RenCri01-2}, which were obtained with a VOF method, are shown inside
boxes while results obtained with our CLSVOF approach are displayed outside
boxes.  In the computations presented in~\cite{RenCri01-2}, the dimensions
$W=4R$ and $H=8R$ were fixed, while $L$ was changed depending on $Re$ and $Ca$
conditions, and the grid size was set to $\Delta x=\Delta y=\Delta z=R/8$.  To
compare with their results, we performed simulations with the CLSVOF method
over a two-level AMR computational domain of the same dimensions and the same
(level-0) discretization; we set the finer level-1 grid size $\Delta x^{\ell=1}
= \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  The results shown in
Figure~\ref{fig:DropBreakComp} verify that our numerical approach can reproduce
the same drop breakup behavior presented in~\cite{RenCri01-2}.  Slight
differences between the results can be attributed to the increased resolution
used our study in the level-1 grid around the elongated drop.  The numerical
validation studies performed in this section demonstrate that our numerical
method is capable of accurately simulating shear-induced drop deformation and
breakup.

\subsection{Consideration of domain and grid sizes}\label{sec:DomGrdSize}
%  -----------------------------------------------------------------------------
The computational domain size used in numerical studies can affect the behavior
of drop deformation and breakup.  Referring to
Figure~\ref{fig:SchemAndGrid}(a), with an appropriately large domain length $L$
and a fixed width $W=4R$, the effect of the height $H$ on drop behavior was
examined in~\cite{LiRenRen00} for Stokes flows and various $Ca$ conditions and
in~\cite{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.  Other related studies
investigated drop breakup sensitivity~\cite{RenCri01-1} and drop deformation
sensitivity~\cite{RenCriLi02} with respect to the entire domain size.

Here we investigate the drop dynamics sensitivity to domain size around the
critical Reynolds number $Re_{c}=0.75$.  Specifically, we consider domain size
sensitivity for the condition of $Re=0.75$, $Ca=0.3$, and $\lambda = \eta = 1$,
which is a condition used in the comparison studies of the previous section.
As shown in Table~\ref{tab:DeComparison}, the drop breaks up for the condition
of $Re=0.75$ and $Ca=0.3$ with a domain size of $\lwh{8}{4}{8}$.  Results for
domain size sensitivity for six domain systems, all of which use a level-1 grid
size $\Delta x^{\ell=1} = \Delta y^{\ell=1}= \Delta z^{\ell=1} = R/16$, are
tabulated in Table~\ref{tab:DomComparison}. Note that the domain size used in
the comparison study (Table~\ref{tab:DeComparison}) corresponds to System 1.
%
\begin{table}[tbh]
\caption{Comparison of the Taylor deformation parameter $De$ as a function of
         domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).}
\label{tab:DomComparison}
%\footnotesize
\center
\begin{tabular}{ c  c  c}
\hline
\hline
System      & Domain size ($\LWH$)         & $De$    \\
System 1    & $8R  \times 4R  \times 8R$   & Breakup \\
System 2    & $12R \times 4R  \times 8R$   & Breakup \\
System 3    & $8R  \times 4R  \times 6R$   & 0.541   \\
System 4    & $8R  \times 6R  \times 6R$   & 0.466   \\
System 5    & $8R  \times 8R  \times 8R$   & 0.460   \\
System 6    & $8R  \times 16R \times 16R$  & 0.460   \\
\hline
\hline
\end{tabular}
\end{table}
%

The results in Table~\ref{tab:DomComparison} suggest that drop deformation is
promoted when we use a domain size with $W=4R$.  In contrast, the drop does not
break up and becomes stable with a deformed shape if we set $L$ large enough
and $W \geq 6R$ and $H \geq 6R$.  Since the value of $De$ for the domain size
$\lwh{8}{6}{6}$ differs by only $1.3\%$ with the value for the domain size of
$\lwh{8}{16}{16}$, in the results that follow we set the width to $W=6R$ and the
height to $H=6R$ to minimize the number of computational grid nodes along those
directions.  To determine the critical Reynolds number $Re_c$ (with $Ca=0.3$),
we consider a domain size of $\lwh{24}{6}{6}$, and we find that the drop
reaches a stable state with deformation parameter $De=0.549$ for $Re=1.0$,
while a value of $Re=1.1$ leads to drop breakup.
% 
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{DeEvolution}
  \caption{Time evolution of the deformation parameter $De$ versus a dimensionless
           time $T = \mathit{\Gamma} t$ for a bubble, obtained 
           with two grid systems at different resolutions. Both systems use a 
           two-level AMR grid with a uniform 
           finest-level grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = 
           \Delta z ^{\ell=1}$. The evolution of $De$ using the first system, where
           $\Delta x^{\ell=1} = R/16$, is shown in black and it predicts that 
           bubble breakup occurs at a Reynolds number $Re=35$. 
           Results with the second system, shown in red, use $\Delta x^{\ell=1} 
           = R/24$, and they predict that breakup occurs at $Re=34$.}
  \label{fig:DeEvolution}
\end{figure}
%

The numerical results presented in this and the previous section used a
finest-level grid size set to $\Delta x^{\ell=1}(= \Delta y^{\ell=1}= \Delta
z^{\ell=1})=R/16$. To verify the adequacy of this grid resolution, we present
grid refinement results for a bubble breakup simulation with $Ca=1.0$, which
corresponds to the most deformable and stretchable bubble case considered in
our numerical studies. We use two different grid systems, one with $\Delta
x^{\ell=1}=R/16$ and another with $\Delta x^{\ell=1}=R/24$, to determine
$Re_c$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the
deformation parameter $De$ over time for the two grid systems; the $x$-axis is
a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $De$.
The results show that bubble breakup occurs at $Re_c = 35$ for the grid system
with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta
x^{\ell=1}=R/24$ predicts a critical value of $Re_c = 34$. Although there is
only a relatively small difference ($\sim 3\%$) between the critical Reynolds
numbers, and the time evolution of $De$ for the two grid systems is consistent
in both cases, the computational time using the grid system with
$\Delta x^{\ell=1}=R/24$ was more than 6 times longer than the one based on the
coarser system with $\Delta x^{\ell=1}=R/16$.  We note that in our search for
$Re_c$, we considered a wide range of values of $Ca$ and we found it necessary
to use a large $L$ ($\sim 24R$) since for certain shear flows the bubble can
stretch significantly without breaking up.  Nevertheless, for the conditions
presented in this section, the results indicate that our numerical approach,
even with a finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of
accurately reproducing bubble deformation and breakup without sacrificing any
essential dynamical features.

%  -----------------------------------------------------------------------------
\section{Results and Discussion}
%  -----------------------------------------------------------------------------

\subsection{Drop deformation and breakup}\label{sec:DropBreak}
%  -----------------------------------------------------------------------------
% 
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{DropBreakEvol}
  \caption{Time evolution of drop deformation and breakup in shear flow at the
           condition of $Ca=0.3$ with (a) $Re=1.0$ and (b) $Re=1.1$.}
  \label{fig:DropBreak}
\end{figure}
%
To illustrate the differences in deformation and breakup between a drop and a
bubble around critical conditions, we first present numerical results for drop
deformation.  The time evolution of drop deformation and breakup in simple
linear shear flow for two conditions is shown in Figure~\ref{fig:DropBreak};
the first case, shown in Figure~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and
$Re=1.0$, while the second case, depicted in Figure~\ref{fig:DropBreak}(a),
uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the
case with $Re=1.0$, the drop gradually deforms and finally attains a stable
deformed state with $De$= 0.549.  Over the same domain, for the case with
$Re=1.1$, the ``mother'' drop elongates over time and the volume at the ends of
the deforming drop expands; that is, both ends of the drop become bulb-shaped.
As time progresses, particularly over the time interval $48.4 \leq T \leq
55.2$, a thread-bridge forms between the bulbar ends and the thread-bridge
becomes thinner.  Finally, at around the dimensionless time $T\sim 56.7$, the
mother drop breaks up, forming two ``daughter'' drops through the pinch off;
one satellite drop is also generated between the pinched off daughter drops.

\subsection{Bubble deformation and breakup}
%  -----------------------------------------------------------------------------
% 
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{BubbleBreakCa0p3Re92}
  \caption{Time evolution of bubble deformation in shear flow at the
           condition of $Ca=0.3$ and $Re=92$.}
  \label{fig:BubbleBreakCa0p3Re92}
\end{figure}
%
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{BubbleBreakCa0p3Re93}
  \caption{Time evolution of bubble deformation in shear flow at the
           condition of $Ca=0.3$ and $Re=93$.}
  \label{fig:BubbleBreakCa0p3Re93}
\end{figure}
%
Next we present numerical results that illustrate the conditions that lead to
bubble deformation without breakup as well as conditions where the bubble
deforms and ultimately breaks up.  The time evolution of shear-induced bubble
deformation without breakup at the condition of $Ca=0.3$ and $Re=92$ is
depicted in Figure~\ref{fig:BubbleBreakCa0p3Re92} and the bubble breakup
process with flow condition of $Ca=0.3$ and $Re=93$ is illustrated in
Figure~\ref{fig:BubbleBreakCa0p3Re93}.  The results indicate that the critical
Reynolds number is approximately $Re_c = 93$ (with $Ca=0.3$).  A comparison
with the drop breakup dynamics presented in Section~\ref{sec:DropBreak} and the
corresponding processes for bubble deformation and breakup exhibit very
distinct features.  First, we note that a relatively large shear force
magnitude is required for bubble breakup ($\lambda$ = $\eta$ = 1.0 $\times$
$10^{-3}$) compared with the case of the drop ($\lambda$ = $\eta$ = 1). Then,
for the same value of $Ca=0.3$, the critical Reynolds number for the bubble is
around 85 times larger than that for the drop.  Focusing on the bubble dynamics
with no-breakup (Figure~\ref{fig:BubbleBreakCa0p3Re92}), the results show that
the bubble is largely elongated in the $x$-direction at the early stages ($T
\leq 24.3$) of bubble deformation, but the bubble does not develop the
bulb-like shape (large volume areas) at both ends present in the drop
deformation process.  It is also evident that the ends of the deforming bubble
develop cusped shapes under the influence of the strong shear flow.  A
noteworthy feature for the non-breaking bubble is that it does not settle into
a deformed stable state as in the case of drop deformation presented in
Figure~\ref{fig:DropBreak}(a).  After an initial elongation process, the bubble
enters a shrinking phase ($T = 27.8$) where the doglegged shape formed at the
center of the bubble returns to a smaller deformed shape ($T = 34.4$) that is
similar to its earlier shape ($T=3.47$).  However, when we compare the early
deformed bubble shape at $T = 3.47$ with the shape at $T = 34.4$, it is clear
that the shapes are not identical.  Following the shrinking phase, the bubble
begins to stretch again ($T = 38.2$) and the bubble oscillates between its
elongated shape and shortened geometry.

%
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{BubBreakCa0p3Re93Detail}
  \caption{Detail of bubble breakup process in shear flow at the condition
           of $Ca=0.3$ and $Re=93$.}
  \label{fig:BubBreakCa0p3Re93Detail}
\end{figure}
%
For the case of bubble breakup (Figure~\ref{fig:BubbleBreakCa0p3Re93}), we
observe that the deformation process is the almost same as the no-breakup case
until the doglegged shape is formed at $T \sim 27.4$. The bubble finally breaks
during the time interval $27.7 \leq T \leq 29.5$.  For a closer examination of
the bubble breakup process, a detailed panel of cross-sectional slices in the
$xz$-plane through the bubble shape center is presented in
Figure~\ref{fig:BubBreakCa0p3Re93Detail}.  The images displayed in
Figure~\ref{fig:BubBreakCa0p3Re93Detail}, which are taken at shorter time
intervals than those shown in Fig.~\ref{fig:BubbleBreakCa0p3Re93}, reveal that
the bubble breaks up into two daughter bubbles due to the pinch off at the
thread-bridge part of the doglegged shape during the shrinking process ($T =
28.5 \sim 28.8$).  After breaking up, the two daughter bubbles migrate to the
center: the left daughter bubble moves toward the right-side of the domain and
the right daughter bubble moves to the left side (see results for $T = 29.5
\sim 35.1$ in Figure~\ref{fig:BubbleBreakCa0p3Re93} and for $T = 28.8 \sim
30.9$ in Figure~\ref{fig:BubBreakCa0p3Re93Detail}).  The two daughter bubbles
then momentarily congregate near the domain center ($T = 35.1$ in
Figure~\ref{fig:BubbleBreakCa0p3Re93}), before they slowly start to separate:
the left daughter bubble moves to the left and the right daughter bubble moves
to the right ($T = 46.2$ in Figure~\ref{fig:BubbleBreakCa0p3Re93}).  The
results clearly demonstrate that the bubble breakup process is markedly
different from the analogous drop breakup process.

\subsection{Velocity field outside and inside the breaking bubble}
%  -----------------------------------------------------------------------------
%
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{BubbleFieldCa0p3Re93}
  \caption{Fluid velocity field outside and inside the breaking bubble in
           shear flow at the condition $Ca=0.3$ and $Re=93$.}
  \label{fig:BubbleFieldCa0p3Re93}
\end{figure}
%
In this section, we consider the fluid flow velocity field outside and inside
the bubble during the shear-induced breakup process.
Figure~\ref{fig:BubbleFieldCa0p3Re93} shows the velocity fields outside and
inside the bubble at cross-sectional slices in the $xz$-plane for a flow
condition of $Ca = 0.3$ and $Re = 93$.  Regions around the bubble where there
is a higher density of velocity vectors correspond to the level-1 grid portion
of the AMR structure.  The simulation results show that the velocity field
inside the bubble is particularly distinct from the surrounding flow field in
the exterior of the bubble.  The cross-sections at $T=12.2$ and $T=18.1$, taken
during the elongation phase, show how shear forces at the lower and upper
halves of the bubble act along the bottom and top surfaces, respectively, to
deform the interface.  Near the left and right edges of the bubble, inward
interior flows (that point toward the bubble center) begin to develop.  Strong
shearing forces in the exterior near the bottom-left-end and top-right-end of
the bubble interact with the interior flow field through the boundary to create
cusped shapes at the bottom-left and top-right ends of the bubble while the
interface is laterally elongated in the $x$-direction.  During the shrinking
process, which occurs for $23.6 \leq T \leq 27.8$, inward flows within the
bubble extend over a wider region and are no longer localized near the bubble
edges.  Then, we observe that circulating flows form at the thread-bridge part
of the doglegged bubble shape over the time interval $[25.7, 27.8]$.  During
the breakup process ($T \sim 28.8$), higher-intensity inward flows are formed
inside the bubble, near the pinch off region, that are naturally larger than
the surrounding interior flows and which are inextricably associated with the
bubble migration illustrated in Figs.~\ref{fig:BubbleBreakCa0p3Re93}
and~\ref{fig:BubBreakCa0p3Re93Detail}.  As time proceeds further ($T =  46.2$),
distinct inward flows are formed inside the daughter bubbles; the bubbles then
begin their migration toward the side walls.  Considering the left daughter
bubble, for example, we see that the mechanism responsible for this movement
results from larger shear forces acting on the bottom-left end than those in
the top-left end.

\subsection{Effect of surface tension on bubble deformation and breakup}
%  -----------------------------------------------------------------------------
%
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{BubbleDeformCa0p8Re42}
  \caption{Time evolution of bubble deformation in shear flow at the 
           condition of $Ca=0.8$ and $Re=42$.}
  \label{fig:BubDefCa0p8Re42}
\end{figure}
%
\begin{figure}%[h!]
  \centering
  \includegraphics[width=\textwidth]{BubbleBreakCa0p8Re43}
  \caption{Time evolution of bubble deformation in shear flow at the 
           condition of $Ca=0.8$ and $Re=43$.}
  \label{fig:BubBrkCa0p8Re43}
\end{figure}
%
%It means that the effect of the surface tension for the condition of $Ca = 0.8$
%is smaller than that for the condition of $Ca = 0.3$.
%
In previous sections, we considered numerical simulations of bubble deformation
and breakup with a Capillary number $Ca = 0.3$.  Here, we examine similar
bubble dynamics with $Ca = 0.8$ and we also investigate the effect of
interfacial tension on bubble deformation and breakup.  Using $Ca=0.8$ for both
cases, Figures~\ref{fig:BubDefCa0p8Re42} and~\ref{fig:BubBrkCa0p8Re43} present
the time evolution of shear-induced bubble deformation and breakup with $Re=42$
and $Re=43$, respectively.  We note that the bubble critical Reynolds number is
around $Re_{c} \approx 43$, whereas $Re_{c} \approx 0$ for the corresponding
case of the drop with $\lambda$ = $\eta$ = 1 (see e.g.~\cite{LiRenRen00}).
Note that $Re_{c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca
= 0.3$ since the bubble at $Ca = 0.8$ is more elastic due to the weaker effect
of surface tension in this case.  The results shown in
Figs.~\ref{fig:BubDefCa0p8Re42} and~\ref{fig:BubBrkCa0p8Re43} indicate that the
bubble deformation and breakup process for the condition of $Ca = 0.8$ is
analogous to that for $Ca = 0.3$.  For the case of bubble deformation without
breakup (Fig.~\ref{fig:BubDefCa0p8Re42}), the bubble initially assumes a long
elongated shape along the $x$-direction at around $T=24.3$. The bubble then
enters a compression stage over the time interval $[31.3,41.2]$ and
subsequently starts to elongate again at $T = 45.8$.  On the other hand, for
the case of bubble breakup (Fig.~\ref{fig:BubBrkCa0p8Re43}), an initial
elongation phase is followed by a doglegged shape formation at $T=33.7$.  After
that, the bubble ruptures from the thread-bridge part of the doglegged shape
and two daughter bubbles are produced ($T = 35.8$).  The two daughter bubbles
formed after breakup move to the central area ($T = 49.7$) as in the case of
$Ca = 0.8$ and $Re = 93$, but the two bubbles eventually coalesce in a region
approximately centered in the computational domain ($T = 55.6$).  We note that
in a real experimental setting, bubbles may coalesce after breaking up due to
slight deviations of flow conditions and states.  Although the process of
bubble deformation and breakup for flow conditions with $Ca = 0.3$ and $Ca =
0.8$ are similar, a pronounced difference is that the bubble for $Ca = 0.8$ is
more elongated and slender than that for $Ca = 0.3$ due to the smaller effect
of surface tension for $Ca = 0.8$.

Table~\ref{tab:CaRecComparison} lists columns of Capillary number and critical
Reynolds number pairs for shear-induced bubble breakup for a variety of flow
conditions.  The results indicate that sufficiently large shear forces are
required for bubble breakup even for large Capillary numbers; the combined
effects of very small density and viscosity ratios ($\lambda$ = $\eta$ = 1.0
$\times$ $10^{-3}$) act synergistically in deformation and breakup processes.
%
\begin{table}[tbh]
\caption{Critical Reynolds number corresponding to Capillary number}
\label{tab:CaRecComparison}
\footnotesize
\center
\begin{tabular}{ c  c  c  c  c }
\hline
\hline
Capillary number $Ca$            & 0.3  & 0.5  & 0.8  & 1.0  \\
Critical Reynolds number $Re_c$  & 93   & 67   & 43   & 35   \\
\hline
\hline
\end{tabular}
\end{table}

%  -----------------------------------------------------------------------------
\section{Conclusions}
%  -----------------------------------------------------------------------------
The bubble deformation and breakup process in simple linear shear flow liquid
was explored numerically using the CLSVOF computational method.  In this study,
the critical Reynolds number $Re_{c}$, at which bubble breakup first occurs,
was determined for several flow conditions, and the differences between bubble
deformation and breakup were compared with the well-known analogous process of
drop deformation and breakup.

Numerical results revealed significant differences between bubble deformation
and breakup and the corresponding drop dynamics.  For case of bubble, it was
discovered that much stronger shear flows are necessary to induce interface
breakup compared with a drop immersed in a similar flow field.  That is, a much
larger Reynolds number flow is required in order to induce bubble breakup.  The
behavior of bubble breakup was very similar through the $Ca$ number range
considered in our computations: the bubble underwent a similar breakup
mechanism in which rupture occurred at a thread-bridge part that followed a
doglegged shape formation stage.  In bubble deformation without breakup, near
$Re_{c}$, the bubble did not maintain a stable deformed shape, in contrast to
drop deformation near the critical Reynolds number.  The bubble exhibited
pronounced underdamped behavior: the bubble oscillated between elongating and
shrinking motions for non-rupturing flow conditions.

We attribute the large differences in morphology for the bubble undergoing
breakup, compared with the drop, to the density and viscosity ratio.  The
density and viscosity ratio remarkably impacts on bubble/drop deformation and
breakup.  The bubble deformation and breakup is subject to a synergistic
coupling of the density and viscosity ratio, and whose effect will be examined
separately in future work.

%\bibliography{apssamp}% Produces the bibliography via BibTeX.
\bibliography{references}

%  -----------------------------------------------------------------------------
%  -----------------------------------------------------------------------------
\end{document}
%
% ****** End of file apssamp.tex ******

### 2022-05-30 figures/pdf2png.sh

@@ -1,0 +1,12 @@
+#!/bin/sh
+#-------------------------------------------------------------------------------
+# Modified: 24 May 2022
+#-------------------------------------------------------------------------------
+
+PDFNAME=Fig11
+PNGNAME=BubbleBreakCa0p8Re43
+
+convert -density 300 -flatten -resize 2048x1540 ${PDFNAME}.pdf -quality 100 ${PNGNAME}.png
+
+#-------------------------------------------------------------------------------
+#-------------------------------------------------------------------------------

### 2022-12-23 Bubble-deformation.tex
Add files via upload

@@
 %  
-%  Modified: 22 May 2022
+%  Modified: 22 December 2022
 %  -----------------------------------------------------------------------------
@@
 
-In contrast, and to the best of our knowledge, few computational studies on
-bubble deformation and breakup in shear flow have been conducted
-\cite{WanShiZha15}.  This type of bubble dynamics in shear flow is also of
-critical importance to further our understanding of a variety of scientific and
-engineering processes.  In this article, we present computational studies of
-shear-driven deformation and breakup of a bubble in insoluble viscous liquids.
-The physical properties that distinguish bubble and drop studies are expressed in
-terms of the density ratio $\lambda = \rho_b / \rho_m$ and the viscosity ratio
-$\eta = \mu_b / \mu_m$, where $\rho$ is the fluid density, $\mu$ is the
-viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or
-``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble
-viscous liquid, the density ratio $\lambda \simeq 0$ and the viscosity ratio
-$\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible
-viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
+In contrast, few computational studies on bubble deformation and breakup in
+shear flow have been conducted \cite{WanShiZha15}.  This type of bubble
+dynamics in shear flow is also of critical importance for a variety of
+scientific and engineering processes, particularly high performance plastics
+applications that motivated this work.  In this article, we present
+computational studies of shear-driven deformation and breakup of a bubble in
+insoluble viscous liquids.  The physical properties that distinguish bubble and
+drop studies are expressed in terms of the density ratio $\lambda = \rho_b /
+\rho_m$ and the viscosity ratio $\eta = \mu_b / \mu_m$, where $\rho$ is the
+fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote
+the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a
+bubble in an insoluble viscous liquid, the density ratio $\lambda \simeq 0$ and
+the viscosity ratio $\eta \simeq 0$, whereas most studies dealing with a drop
+in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
 
@@
 of dimensionless quantities, that specify the extreme conditions at which a
-bubble or drop in shear flow first transitions from deformation to breakup.  An
-advantage of studying shear-driven bubble deformation and breakup
-computationally, rather than experimentally, is that we can easily modify fluid
-physical properties to ascertain the sensitivity of deformation and breakup to
-physical parameters.  In our computations, the time-evolution of the boundary
-between gas and liquid is tracked with a coupled level set/volume-of-fluid
-(CLSVOF) interface capturing algorithm \cite{SusPuc00}.  We focus on
-determining critical physical conditions in which the breakup of a bubble
-occurs in shear flow because it is important to identify the parameter regimes
-in which a relatively simple system transitions from stable to unstable.
-Specifically, we identify the critical Reynolds number $Re_{c}$ corresponding
-to the bubble breakup onset condition as a function of the Capillary number
-$Ca$.  Although the $Re_{c}$ for drop breakup was reported previously
-\cite{LiRenRen00}, in this work we determine, for the first time, the critical
-Reynolds number that leads to \emph{bubble} breakup.  Additionally, our
-computational studies reveal characteristics that distinguish the deformation
-and breakup processes of a drop versus those of a bubble.
+bubble or drop in shear flow first transitions from deformation to breakup.
+We validate our numerical methods through comparisons with previous
+shear-driven drop dynamics results and we also examine the effect of drop
+deformation and breakup sensitivity on domain and grid size.  An advantage of
+studying shear-driven bubble deformation and breakup computationally, rather
+than experimentally, is that we can easily modify fluid physical properties to
+ascertain the sensitivity of deformation and breakup to physical parameters.
+In our computations, the time-evolution of the boundary between gas and liquid
+is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
+capturing algorithm \cite{SusPuc00}.  We focus on determining critical physical
+conditions in which the breakup of a bubble occurs in shear flow because it is
+important to identify the parameter regimes in which a relatively simple system
+transitions from stable to unstable.  Specifically, we identify the critical
+Reynolds number $Re_{c}$ corresponding to the bubble breakup onset condition as
+a function of the Capillary number $Ca$.  Although the $Re_{c}$ for drop
+breakup was reported previously \cite{LiRenRen00}, in this work we determine,
+for the first time, the critical Reynolds number that leads to \emph{bubble}
+breakup.  Additionally, our computational studies reveal characteristics that
+distinguish the deformation and breakup processes of a drop versus those of a
+bubble.
 
@@
            example (\textit{lower panel}) of bubble deformation in simple linear 
-           shear flow on the same grid system.}
+           shear flow.}
   \label{fig:SchemAndGrid}
@@
 which is based on a fixed grid finite difference algorithm.  In our studies,
-two-phase fluid flow is comprised of air and a viscous Newtonian liquid. A
-single set of three-dimensional equations governs the motion of both fluids,
-which are taken to be incompressible, and consists of the continuity equation
-and the Navier-Stokes equations with surface tension forces:
+two-phase fluid flow is comprised of air and a viscous Newtonian liquid.  The
+Heaviside function, $\Hea(\phi)$, which is defined as
+%
+\begin{equation}\label{heavyeqn}
+  \Hea(\phi) = \begin{cases}
+               1 & \phi \geq 0 \\
+               0 & \phi <0 
+               \end{cases}
+\end{equation}
+%
+will be used below to distinguish each of the two fluids.  A single set of
+three-dimensional equations governs the motion of both fluids, which are taken
+to be incompressible, and consists of the continuity equation and the
+Navier-Stokes equations with surface tension forces:
 %
@@
 ($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$
-is the viscosity, $\kappa$ is the interfacial curvature, and $\Hea(\phi)$ is
-the Heaviside function as a function of the level set (LS) function $\phi$. The
-singular term (last term) in the right hand side of equation~\eqref{nseqn} is a
-body force due to surface tension and is equivalent to specifying that the jump
-in the normal stress is equal to $\sigma\kappa$.  The interfacial curvature
-$\kappa$ is computed with second order accuracy directly from the
-volume-of-fluid (VOF) function using the height function technique.  We remark
-that we get the same results if we were to compute $\kappa$ directly from the
-LS function using the ``level set'' height function technique.
+is the viscosity, $\kappa$ is the interfacial curvature, and the Heaviside
+function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$. The
+singular Heaviside gradient term in the right hand side of
+equation~\eqref{nseqn} is a body force due to surface tension and is equivalent
+to specifying that the jump in the normal stress is equal to
+$\sigma\kappa$~\cite{TanguyEtAl2007}.  The interfacial curvature $\kappa$ is
+computed with second order accuracy directly from the volume-of-fluid (VOF)
+function using the height function technique.  We remark that we get the same
+results if we were to compute $\kappa$ directly from the LS function using the
+``level set'' height function technique.
 
@@
 %
-The subscripts ``b'' and ``m'' refer to ``drop or bubble'' and ``matrix fluid'',
-respectively.  The Heaviside function, $\Hea(\phi)$, is defined as follows:
-%
-\begin{equation}\label{heavyeqn}
-  \Hea(\phi) = \begin{cases}
-               1 & \phi \geq 0 \\
-               0 & \phi <0 
-               \end{cases}
-\end{equation}
-%
-To represent the free surface with the CLSVOF method, we must evolve the solution
-to both the VOF equation for $F$ and the LS equation for $\phi$:
+The subscripts ``b'' and ``m'' refer to ``drop or bubble'' and ``matrix
+fluid'', respectively. To represent the free surface with the CLSVOF method, we
+must evolve the solution to both the VOF equation for $F$ and the LS equation
+for $\phi$:
 %
@@
 hydrodynamic scheme.  The spatial discretization uses second-order accurate,
-slope limited, upwind techniques for the nonlinear advective terms.  The
+slope-limited, upwind techniques for the nonlinear advective terms.  The
 velocity and pressure fields are computed using an implicit pressure projection
@@
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter $De$ as a function 
-         of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$).}
+\caption{Comparison of the Taylor deformation parameter $De$ for a drop as a function 
+         of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$). In all cases, the domain 
+         size is $\lwh{8}{4}{8}$, where $R$ is the drop radius.
+         CLSVOF method computations used a two-level AMR computational domain 
+         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
+         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
+         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 \label{tab:DeComparison}
@@
   \caption{Comparison with results reported in~\cite{RenCri01-2} (shown in boxes) 
-           for drop breakup in shear flow. (Reprinted with permission from 
+           for drop breakup in shear flow.  (The computational domain
+           dimensions $W=4R$ and $H=8R$ were fixed, while $L$ was changed depending 
+           on $Re$ and $Ca$ conditions, and the grid size was set to 
+           $\Delta x=\Delta y=\Delta z=R/8$.  Reprinted with permission from 
            reference~\cite{RenCri01-2}. Copyright 2001, AIP Publishing). Results
-           obtained with our CLSVOF algorithm are shown outside boxes. The onset
-           of drop breakup is demonstrated for (a) $Re=10$, $Ca=0.16$,
-           (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.}
+           obtained with our CLSVOF algorithm, corresponding to each case in
+           reference~\cite{RenCri01-2}, are shown outside boxes.  The
+           CLSVOF method used a two-level AMR computational domain 
+           with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
+           = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
+           $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$. 
+           The onset of drop breakup is demonstrated for (a) $Re=10$,
+           $Ca=0.16$, (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.
+           For all three $Re$ and $Ca$ conditions, $\lambda = \eta = 1$.}
   \label{fig:DropBreakComp}
@@
 Next, we present a comparison with numerical results for drop breakup reported
-in~\cite{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop
-breakup with pinch-off behavior for three $Re$ and $Ca$ conditions and with
-constant values of $\lambda = \eta = 1$ for all cases.  The three cases that we
-consider correspond to (a) $Re = 10, \, Ca = 0.16$, (b) $Re = 12, \, Ca =
-0.1753$, and (c) $Re = 15, \, Ca = 0.196$, and which are illustrated in
+in~\cite{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop breakup
+with pinch-off behavior for three $Re$ and $Ca$ conditions and with constant
+values of $\lambda = \eta = 1$ for all cases.  The three cases that we consider
+correspond to (a) $Re = 10, \, Ca = 0.16$, (b) $Re = 12, \, Ca = 0.1753$, and
+(c) $Re = 15, \, Ca = 0.196$, and which are illustrated in
 Figures~\ref{fig:DropBreakComp}(a)-(c), respectively.  The results reported
@@
 over a two-level AMR computational domain of the same dimensions and the same
-(level-0) discretization; we set the finer level-1 grid size $\Delta x^{\ell=1}
-= \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  The results shown in
+level-0 discretization: $\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta
+z^{\ell=0} = R/8$; we set the finer level-1 grid size $\Delta x^{\ell=1} =
+\Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  The results shown in
 Figure~\ref{fig:DropBreakComp} verify that our numerical approach can reproduce
@@
 sensitivity~\cite{RenCriLi02} with respect to the entire domain size.
-
-Here we investigate the drop dynamics sensitivity to domain size around the
-critical Reynolds number $Re_{c}=0.75$.  Specifically, we consider domain size
-sensitivity for the condition of $Re=0.75$, $Ca=0.3$, and $\lambda = \eta = 1$,
-which is a condition used in the comparison studies of the previous section.
-As shown in Table~\ref{tab:DeComparison}, the drop breaks up for the condition
-of $Re=0.75$ and $Ca=0.3$ with a domain size of $\lwh{8}{4}{8}$.  Results for
-domain size sensitivity for six domain systems, all of which use a level-1 grid
-size $\Delta x^{\ell=1} = \Delta y^{\ell=1}= \Delta z^{\ell=1} = R/16$, are
-tabulated in Table~\ref{tab:DomComparison}. Note that the domain size used in
-the comparison study (Table~\ref{tab:DeComparison}) corresponds to System 1.
 %
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter $De$ as a function of
-         domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).}
+\caption{Comparison of the Taylor deformation parameter $De$ for a drop as a function of
+         domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).
+         CLSVOF method computations used a two-level AMR computational domain 
+         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
+         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
+         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 \label{tab:DomComparison}
@@
 %
+
+Here we investigate the drop dynamics sensitivity to domain size around the
+critical Reynolds number $Re_{c}=0.75$.  Specifically, we consider domain size
+sensitivity for the condition of $Re=0.75$, $Ca=0.3$, and $\lambda = \eta = 1$,
+which is a condition used in the comparison studies of the previous section.
+As shown in Table~\ref{tab:DeComparison}, the drop breaks up for the condition
+of $Re=0.75$ and $Ca=0.3$ with a domain size of $\lwh{8}{4}{8}$.  Results for
+domain size sensitivity for six domain systems, all of which use a level-1 grid
+size $\Delta x^{\ell=1} = \Delta y^{\ell=1}= \Delta z^{\ell=1} = R/16$, are
+tabulated in Table~\ref{tab:DomComparison}. Note that the domain size used in
+the comparison study (Table~\ref{tab:DeComparison}) corresponds to System 1.
 
@@
 with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta
-x^{\ell=1}=R/24$ predicts a critical value of $Re_c = 34$. Although there is
-only a relatively small difference ($\sim 3\%$) between the critical Reynolds
-numbers, and the time evolution of $De$ for the two grid systems is consistent
-in both cases, the computational time using the grid system with
-$\Delta x^{\ell=1}=R/24$ was more than 6 times longer than the one based on the
-coarser system with $\Delta x^{\ell=1}=R/16$.  We note that in our search for
-$Re_c$, we considered a wide range of values of $Ca$ and we found it necessary
-to use a large $L$ ($\sim 24R$) since for certain shear flows the bubble can
-stretch significantly without breaking up.  Nevertheless, for the conditions
-presented in this section, the results indicate that our numerical approach,
-even with a finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of
+x^{\ell=1}=R/24$ predicts a critical value of $Re_c = 34$.  Note that although
+the time evolution of $De$ for the two grid systems is consistent for both
+resolutions (the predicted critical Reynolds numbers differ by $\sim 3\%$), the
+computational time using the grid system with $\Delta x^{\ell=1}=R/24$ was more
+than 6 times longer than the one based on the coarser system with $\Delta
+x^{\ell=1}=R/16$.  We remark that in our search for $Re_c$, we considered a
+wide range of values of $Ca$ and we found it necessary to use a large $L$
+($\sim 24R$) since for certain shear flows the bubble can stretch significantly
+without breaking up.  Nevertheless, for the conditions presented in this
+section, the results indicate that our numerical approach, even with a
+finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of
 accurately reproducing bubble deformation and breakup without sacrificing any
@@
 \begin{table}[tbh]
-\caption{Critical Reynolds number corresponding to Capillary number}
+\caption{Shear-induced bubble breakup for various flow conditions described in terms
+         of column pairs of critical Reynolds numbers and corresponding Capillary numbers.}
 \label{tab:CaRecComparison}

### 2022-12-23 Bubble-deformation.tex
up to validataion part

@@
 direct simulations of this problem.  In particular, detailed computational
-investigations based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were
+investigations of drop breakup, 
+based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were
 presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,
@@
 bubble or drop in shear flow first transitions from deformation to breakup.
-We validate our numerical methods through comparisons with previous
+We validate our numerical method through comparisons with previous
 shear-driven drop dynamics results and we also examine the effect of drop
@@
 Reynolds number $Re_{c}$ corresponding to the bubble breakup onset condition as
-a function of the Capillary number $Ca$.  Although the $Re_{c}$ for drop
+a function of the Capillary number $Ca$.  The critical Reynolds number, 
+$Re_{c}$, for drop
 breakup was reported previously \cite{LiRenRen00}, in this work we determine,

### 2022-12-23 Bubble-deformation.tex
added more to the captions; added references to the intro

@@
 a coupled level set/volume-of-fluid (CLSVOF) method.  To verify our numerical
-algorithms, and to compare with previous results, we also present simulation
-results for the well-known case of drop deformation and rupture.  The numerical
+algorithm, and to provide a basis for comparison, we also present simulation
+results which compare with previous, more popular, simulations  
+of drop deformation and rupture.  The numerical
 results reveal that the shear-induced bubble deformation and breakup process
@@
 shear flow have been conducted \cite{WanShiZha15}.  This type of bubble
-dynamics in shear flow is also of critical importance for a variety of
-scientific and engineering processes, particularly high performance plastics
-applications that motivated this work.  In this article, we present
+dynamics in shear flow is of critical importance for a variety of
+scientific and engineering processes. We refer the reader to the 
+following experimental studies relating to bubble deformation in foaming
+processes, microfluidic devices, and micro bubbles in the blood 
+circulation system,
+\cite{CHU2019108,muller2008single,bento2018deformation,drenckhan2015science}.
+In particular, it is the study of bubble deformation as it pertains
+to high performance plastics applications which motivates this work.  
+In this article, we present
 computational studies of shear-driven deformation and breakup of a bubble in
@@
 density and viscosity of air to $\rho_{b}$ = 1.2 kg/m$^{3}$ and $\mu_{b}$ = 1.8
-$\times$ $10^{-5}$ Pa$\cdot$s, and we take the density ratio $\lambda$ = 1.2
-$\times$ $10^{-3}$ and the viscosity ratio $\eta$ $<$ 1.0 $\times$ $10^{-3}$.
+$\times$ $10^{-5}$ Pa$\cdot$s, and we take the 
+density ratio 
+%%$\lambda$ = 1.2 $\times$ $10^{-3}$ 
+$\lambda$ = 1.0 $\times$ $10^{-3}$ 
+and the 
+viscosity ratio 
+%%$\eta$ $<$ 1.0 $\times$ $10^{-3}$.
+$\eta$ $=$ 1.0 $\times$ $10^{-3}$.
 For consistency with previous studies, we will computationally examine the
-deformation and breakup of a bubble in simple linear shear flow under as a
-function of $Re$ and $Ca$ numbers.  In particular, for a certain $Ca$ value, we
-focus on determining the critical value $Re_{c}$ that corresponds to the threshold
+deformation and breakup of a bubble in simple linear shear flow as a
+function of $Re$ and $Ca$ numbers.  In particular, 
+for a certain $Ca$ value, we
+focus on determining the critical value 
+$Re_{c}$ that corresponds to the threshold
 for breakup.
@@
 Numerical results were obtained using the interface-tracking CLSVOF method,
-which is based on a fixed grid finite difference algorithm.  In our studies,
-two-phase fluid flow is comprised of air and a viscous Newtonian liquid.  The
+which is based on a fixed grid finite volume algorithm.  In our studies,
+the two-phase fluid flow is comprised of air and a 
+viscous Newtonian liquid.  The
 Heaviside function, $\Hea(\phi)$, which is defined as
@@
 singular Heaviside gradient term in the right hand side of
-equation~\eqref{nseqn} is a body force due to surface tension and is equivalent
+equation~\eqref{nseqn} is a body force representing the surface tension force
+and is equivalent
 to specifying that the jump in the normal stress is equal to
@@
 computed with second order accuracy directly from the volume-of-fluid (VOF)
-function using the height function technique.  We remark that we get the same
+function using the height function technique~\cite{sussman2003second}.  
+We remark that we get the same
 results if we were to compute $\kappa$ directly from the LS function using the
@@
 refinement (AMR) technique~\cite{SusAlmBelColHowWel99}.  Adaptive grids are
-dynamically adjusted based on the location of a deforming gas-liquid interface.
+dynamically adjusted based on the location of the 
+deforming gas-liquid interface.
 In the AMR technique the grid resolution is increased in regions near the
@@
 
-\subsection{Validation of numerical method}
+\subsection{Validation of the numerical method}
 %  -----------------------------------------------------------------------------
-Numerical studies are presented to verify the accuracy of our computational
-methods.  First, we compare quantitatively against the steady-state drop
+Numerical studies reported in this section
+are presented in order to verify the accuracy of our computational
+method.  First, we compare quantitatively against the steady-state drop
 deformation results reported by Li et al.~\cite{LiRenRen00}.  The shape of a
@@
 differences between the results can be attributed to the increased resolution
-used our study in the level-1 grid around the elongated drop.  The numerical
+used in our study in the level-1 grid around the elongated drop.  The numerical
 validation studies performed in this section demonstrate that our numerical
@@
   \includegraphics[width=\textwidth]{DeEvolution}
-  \caption{Time evolution of the deformation parameter $De$ versus a dimensionless
+  \caption{Time evolution of the deformation parameter $De$ versus 
+   a dimensionless
    time $T = \mathit{\Gamma} t$ for a bubble, obtained 
@@
    Results with the second system, shown in red, use $\Delta x^{\ell=1} 
-           = R/24$, and they predict that breakup occurs at $Re=34$.}
+   = R/24$, and they predict that breakup occurs at $Re=34$.  The capillary
+   number corresponding to these results is $Ca=1.0$.
+   ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$)}
   \label{fig:DeEvolution}
@@
   \caption{Time evolution of drop deformation and breakup in shear flow at the
-           condition of $Ca=0.3$ with (a) $Re=1.0$ and (b) $Re=1.1$.}
+           condition of $Ca=0.3$ with (a) $Re=1.0$ and (b) $Re=1.1$.  The
+	   ``drop'' critical Reynolds number corresponding to $Ca=0.3$ is
+	   $1.0<Re_{c}<1.1$.
+	   ($\lambda$ = $\eta$ = 1.0)}
   \label{fig:DropBreak}
@@
   \caption{Time evolution of bubble deformation in shear flow at the
-           condition of $Ca=0.3$ and $Re=92$.}
+           condition of $Ca=0.3$ and $Re=92$.  
+	   The ``bubble'' 
+	   critical Reynolds number corresponding to $Ca=0.3$ is
+	   $92<Re_{c}<93$.
+           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   }
   \label{fig:BubbleBreakCa0p3Re92}
@@
   \caption{Time evolution of bubble deformation in shear flow at the
-           condition of $Ca=0.3$ and $Re=93$.}
+           condition of $Ca=0.3$ and $Re=93$.
+	   The ``bubble'' 
+	   critical Reynolds number corresponding to $Ca=0.3$ is
+	   $92<Re_{c}<93$.
+           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   }
   \label{fig:BubbleBreakCa0p3Re93}
@@
 distinct features.  First, we note that a relatively large shear force
-magnitude is required for bubble breakup ($\lambda$ = $\eta$ = 1.0 $\times$
-$10^{-3}$) compared with the case of the drop ($\lambda$ = $\eta$ = 1). Then,
+magnitude is required for bubble breakup 
+($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+compared with the case of the drop ($\lambda$ = $\eta$ = 1). Then,
 for the same value of $Ca=0.3$, the critical Reynolds number for the bubble is
@@
   \caption{Detail of bubble breakup process in shear flow at the condition
-           of $Ca=0.3$ and $Re=93$.}
+           of $Ca=0.3$ and $Re=93$.
+	   The ``bubble'' 
+	   critical Reynolds number corresponding to $Ca=0.3$ is
+	   $92<Re_{c}<93$.
+           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   }
   \label{fig:BubBreakCa0p3Re93Detail}
@@
   \caption{Fluid velocity field outside and inside the breaking bubble in
-           shear flow at the condition $Ca=0.3$ and $Re=93$.}
+           shear flow at the condition $Ca=0.3$ and $Re=93$.
+	   The ``bubble'' 
+	   critical Reynolds number corresponding to $Ca=0.3$ is
+	   $92<Re_{c}<93$.
+           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   }
   \label{fig:BubbleFieldCa0p3Re93}
@@
   \caption{Time evolution of bubble deformation in shear flow at the 
-           condition of $Ca=0.8$ and $Re=42$.}
+           condition of $Ca=0.8$ and $Re=42$.
+	   The ``bubble'' 
+	   critical Reynolds number corresponding to $Ca=0.8$ is
+	   $42<Re_{c}<43$.
+           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   }
   \label{fig:BubDefCa0p8Re42}
@@
   \caption{Time evolution of bubble deformation in shear flow at the 
-           condition of $Ca=0.8$ and $Re=43$.}
+           condition of $Ca=0.8$ and $Re=43$.
+	   The ``bubble'' 
+	   critical Reynolds number corresponding to $Ca=0.8$ is
+	   $42<Re_{c}<43$.
+           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   }
   \label{fig:BubBrkCa0p8Re43}
@@
 around $Re_{c} \approx 43$, whereas $Re_{c} \approx 0$ for the corresponding
-case of the drop with $\lambda$ = $\eta$ = 1 (see e.g.~\cite{LiRenRen00}).
+case of the drop with 
+$\lambda$ = $\eta$ = 1 (see e.g.~\cite{LiRenRen00}).
 Note that $Re_{c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca
@@
 required for bubble breakup even for large Capillary numbers; the combined
-effects of very small density and viscosity ratios ($\lambda$ = $\eta$ = 1.0
-$\times$ $10^{-3}$) act synergistically in deformation and breakup processes.
+effects of very small density and viscosity ratios 
+($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+act synergistically in deformation and breakup processes.
 %
 \begin{table}[tbh]
-\caption{Shear-induced bubble breakup for various flow conditions described in terms
-         of column pairs of critical Reynolds numbers and corresponding Capillary numbers.}
+\caption{Shear-induced bubble breakup for various flow 
+	conditions described in terms
+        of column pairs of critical Reynolds numbers and 
+	corresponding Capillary numbers.
+        ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	}
 \label{tab:CaRecComparison}

### 2022-12-24 Bubble-deformation.tex
data is in cen, will make plot tomorrow morning

@@
 As time progresses, particularly over the time interval $48.4 \leq T \leq
-55.2$, a thread-bridge forms between the bulbar ends and the thread-bridge
+55.2$, a thread-bridge forms between the bulbous ends and the thread-bridge
 becomes thinner.  Finally, at around the dimensionless time $T\sim 56.7$, the
@@
 	   critical Reynolds number corresponding to $Ca=0.3$ is
-	   $92<Re_{c}<93$.
+	   $92<Re_{c}<93$.  In contrast to the drop deformation case,
+           when $Re$ is slightly below $Re_{c}$
+           (See Figure \ref{fig:DropBreak} $Re=1.0$ for the drop case), 
+           the bubble shape will
+           not reach a steady shape, instead the bubble shape alternates
+           between the shapes ``slightly stretched'' ($T=3.47$),
+           fully stretched and ``doglegged'' ($T=27.8$) and ``almost''
+           back to the original ``slightly stretched'' case 
+           ($T=34.4$). 
            ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
@@
 
-Table~\ref{tab:CaRecComparison} lists columns of Capillary number and critical
-Reynolds number pairs for shear-induced bubble breakup for a variety of flow
+Table~\ref{tab:CaRecComparison} 
+lists, for representative $Ca$ values,
+the corresponding critical Reynolds number, $Re_{c}$, for shear-induced 
+bubble breakup for a variety of flow
 conditions.  The results indicate that sufficiently large shear forces are
-required for bubble breakup even for large Capillary numbers; the combined
+required for bubble breakup even for large Capillary numbers. The combined
 effects of very small density and viscosity ratios 
@@
 act synergistically in deformation and breakup processes.
+We conducted a linear least squares best fit analysis (linear vs. 
+power law vs. exponential models) of the data that we 
+list in Table~\ref{tab:CaRecComparison} and have found that the following
+exponential model is the best fit:
+%  Re = \frac{\rho_{b}UR}{\mu_{b}}, \quad
+%  Ca = \frac{\mu_{b}U}{\sigma}, \quad
+\begin{eqnarray}
+Re_{c}=4.9 e^{-1.41 (Ca)} \label{bestfit}
+\end{eqnarray}
+In Figure~\ref{fig:CaRecFit} we plot our best fit curve and make the
+hypothesis that a given $(Ca,Re)$ pair will result in bubble break up
+if the point $(Ca,Re)$ is above the critical curve.
+
 %

### 2022-12-24 Bubble-deformation.tex
data ready to be plotted
predicted variance of computed data very small

@@
 computational studies of shear-driven deformation and breakup of a bubble in
-insoluble viscous liquids.  The physical properties that distinguish bubble and
+insoluble viscous liquids.  
+Studying bubble break-up via computation rather
+than experiments simplifies the process of setting a combination of
+precise simple shear flow conditions, low $Ca$ conditions, low density ratio, 
+and low viscosity ratios.
+The physical properties that distinguish bubble and
 drop studies are expressed in terms of the density ratio $\lambda = \rho_b /
@@
 \begin{eqnarray}
-Re_{c}=4.9 e^{-1.41 (Ca)} \label{bestfit}
+Re_{c}=138.3 e^{-1.41 (Ca)} \label{bestfit}
 \end{eqnarray}
+(\ref{bestfit}) was derived from the linear least squares best fit
+of the log of $Re_{c}$:
+\begin{eqnarray}
+	\log(Re_{c})=4.9-1.41 (Ca)  \label{bestfitraw}
+\end{eqnarray}
+%% variance for X^T X c = b
+%% (S/(n-m)) (X^T X)^{-1}
+%% standard deviation: sqrt(2.1E-3)=.05 and sqrt(4.2E-3)=0.06
+The predicted variances for the parameters 
+``$4.9$'' and ``$-1.41$'' which appear in (\ref{bestfitraw}) are
+$2.1E-3$ and $4.2E-3$ respectively.  In other words, even with just
+four data points, we have computed a reasonable best fit curve.
+
 In Figure~\ref{fig:CaRecFit} we plot our best fit curve and make the
@@
 \end{table}
+
+%% variance for X^T X c = b
+%% (S/(n-m)) (X^T X)^{-1}
+\begin{figure}%[h!]
+  \centering
+  \includegraphics[width=\textwidth]{critical_Reynolds_Number_label}
+  \caption{A plot of the critical Reynolds number versus Capillary number
+	for the data listed in Table \ref{tab:CaRecComparison}.  The
+	linear least squares best fit for the $\log(Re_{c})$ is
+	$\log(Re_{c})=4.9-1.41(Ca)$ (i.e. $Re_{c}=138.3 e^{-1.41 Ca}$)
+	with a predicted variance
+	for the parameters ``$4.9$'' and ``$-1.41$'' being
+	$2.1E-3$ and $4.2E-3$ respectively.  Even for the
+	given data that we computed, it is suggested that 
+	a ``bubble break-up map''
+	can be derived, in which for the conditions that
+	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$ and $0<Ca<1$, one
+	can predict whether a given $(Ca,Re)$ pair will result in shear
+	induced bubble break-up or not.  
+	   }
+  \label{fig:CaRecFit}
+\end{figure}
+%
 

### 2022-12-24 Bubble-deformation.tex
n-m

@@
 %% (S/(n-m)) (X^T X)^{-1}
-%% standard deviation: sqrt(2.1E-3)=.05 and sqrt(4.2E-3)=0.06
+%% standard deviation: sqrt(4.2E-3)=.07 and sqrt(8.4E-3)=0.09
 The predicted variances for the parameters 
 ``$4.9$'' and ``$-1.41$'' which appear in (\ref{bestfitraw}) are
-$2.1E-3$ and $4.2E-3$ respectively.  In other words, even with just
+$4.2E-3$ and $8.4E-3$ respectively.  In other words, even with just
 four data points, we have computed a reasonable best fit curve.
@@
 	for the parameters ``$4.9$'' and ``$-1.41$'' being
-	$2.1E-3$ and $4.2E-3$ respectively.  Even for the
+	$4.2E-3$ and $8.4E-3$ respectively.  Even for the
 	given data that we computed, it is suggested that 

### 2022-12-26 Bubble-deformation.tex
incorporated Fig12 from Mitsuhiro, added mathematical description of the ICs and BCs

@@
 and periodic boundary conditions are imposed along the $x$ and $y$ directions.
+Mathematically, the initial and boundary conditions are described as
+follows:
+\begin{eqnarray}
+	\phi(x,y,z,0)=\sqrt{(x-\frac{L}{2})^{2}+(y-\frac{W}{2})^{2}+
+	(z-\frac{H}{2})^{2}}-R \label{IC_BC} \\
+	\bmu(x,y,z,0)=\left( \begin{array}{c}
+		\frac{2V}{H}(z-\frac{H}{2}) \\ 0 \\ 0 
+	\end{array} \right) \nonumber \\
+	\phi(x+L,y,z,t)=\phi(x,y,z,t) \hspace{20pt}
+	\phi(x,y+W,z,t)=\phi(x,y,z,t) \nonumber \\
+	\bmu(x,y,H,t)=\left( \begin{array}{c}
+		                V \\ 0 \\ 0 
+	\end{array} \right)  \hspace{20pt}
+	\bmu(x,y,0,t)=\left( \begin{array}{c}
+		                -V \\ 0 \\ 0 
+	\end{array} \right)  \nonumber \\
+	\bmu(x+L,y,z,t)=\bmu(x,y,z,t) \hspace{20pt} 
+	\bmu(x,y+W,z,t)=\bmu(x,y,z,t). \nonumber
+\end{eqnarray}
+$\phi(x,y,z,t)$ is a material indicator function which is positive 
+in the ``matrix'' fluid and negative in the bubble (or drop) fluid.
+$\bmu(x,y,z,t)$ is the velocity.
+
 Common dimensionless physical parameters used to describe gas-liquid or
@@
 hypothesis that a given $(Ca,Re)$ pair will result in bubble break up
-if the point $(Ca,Re)$ is above the critical curve.
+if the point $(Ca,Re)$ is above the critical curve, 
+$0.3<Ca<1$, and the initial/boundary conditions are given
+by (\ref{IC_BC}).
 
@@
   \centering
-  \includegraphics[width=\textwidth]{critical_Reynolds_Number_label}
+  \includegraphics[width=\textwidth]{Fig12-Critical-Re}
   \caption{A plot of the critical Reynolds number versus Capillary number
@@
 	can be derived, in which for the conditions that
-	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$ and $0<Ca<1$, one
+	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$, $0.3<Ca<1$, and
+        the initial/boundary conditions are given by (\ref{IC_BC}),	
+	one
 	can predict whether a given $(Ca,Re)$ pair will result in shear

### 2022-12-27 Bubble-deformation.tex
figures/Fig11-Critical-Re1_cubic.jpg

@@
 	\bmu(x+L,y,z,t)=\bmu(x,y,z,t) \hspace{20pt} 
-	\bmu(x,y+W,z,t)=\bmu(x,y,z,t). \nonumber
+	\bmu(x,y+W,z,t)=\bmu(x,y,z,t) \nonumber
 \end{eqnarray}
@@
 the corresponding critical Reynolds number, $Re_{c}$, for shear-induced 
-bubble breakup for a variety of flow
-conditions.  The results indicate that sufficiently large shear forces are
-required for bubble breakup even for large Capillary numbers. The combined
-effects of very small density and viscosity ratios 
-($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
-act synergistically in deformation and breakup processes.
-We conducted a linear least squares best fit analysis (linear vs. 
-power law vs. exponential models) of the data that we 
-list in Table~\ref{tab:CaRecComparison} and have found that the following
-exponential model is the best fit:
-%  Re = \frac{\rho_{b}UR}{\mu_{b}}, \quad
-%  Ca = \frac{\mu_{b}U}{\sigma}, \quad
-\begin{eqnarray}
-Re_{c}=138.3 e^{-1.41 (Ca)} \label{bestfit}
-\end{eqnarray}
-(\ref{bestfit}) was derived from the linear least squares best fit
-of the log of $Re_{c}$:
-\begin{eqnarray}
-	\log(Re_{c})=4.9-1.41 (Ca)  \label{bestfitraw}
-\end{eqnarray}
-%% variance for X^T X c = b
-%% (S/(n-m)) (X^T X)^{-1}
-%% standard deviation: sqrt(4.2E-3)=.07 and sqrt(8.4E-3)=0.09
-The predicted variances for the parameters 
-``$4.9$'' and ``$-1.41$'' which appear in (\ref{bestfitraw}) are
-$4.2E-3$ and $8.4E-3$ respectively.  In other words, even with just
-four data points, we have computed a reasonable best fit curve.
-
-In Figure~\ref{fig:CaRecFit} we plot our best fit curve and make the
-hypothesis that a given $(Ca,Re)$ pair will result in bubble break up
-if the point $(Ca,Re)$ is above the critical curve, 
-$0.3<Ca<1$, and the initial/boundary conditions are given
-by (\ref{IC_BC}).
+bubble breakup.  The data in 
+Table~\ref{tab:CaRecComparison} 
+corresponds to $\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$, $0.3<Ca<1$, and
+the initial/boundary conditions are given by (\ref{IC_BC}).
+The results in 
+Table~\ref{tab:CaRecComparison}
+indicate that sufficiently large shear forces are
+required for bubble breakup even for large Capillary numbers. 
+In Figure~\ref{fig:CaRecFit} we plot the cubic interpolant of the
+data given in 
+Table~\ref{tab:CaRecComparison}
+and make the
+hypothesis that given a new data point, $(Ca,Re)$, 
+shear induced bubble break up
+will occur if the point $(Ca,Re)$ is above the given critical curve, 
+and the bubble will not break if the $(Ca,Re)$ pair is below the 
+critical curve.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{Fig12-Critical-Re}
+  \includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
   \caption{A plot of the critical Reynolds number versus Capillary number
-	for the data listed in Table \ref{tab:CaRecComparison}.  The
-	linear least squares best fit for the $\log(Re_{c})$ is
-	$\log(Re_{c})=4.9-1.41(Ca)$ (i.e. $Re_{c}=138.3 e^{-1.41 Ca}$)
-	with a predicted variance
-	for the parameters ``$4.9$'' and ``$-1.41$'' being
-	$4.2E-3$ and $8.4E-3$ respectively.  Even for the
-	given data that we computed, it is suggested that 
-	a ``bubble break-up map''
-	can be derived, in which for the conditions that
+	for the data listed in Table~\ref{tab:CaRecComparison}.  
 	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$, $0.3<Ca<1$, and
-        the initial/boundary conditions are given by (\ref{IC_BC}),	
-	one
-	can predict whether a given $(Ca,Re)$ pair will result in shear
+        the initial/boundary conditions are given by (\ref{IC_BC}).
+	Given a new data point, $(Ca,Re)$, one
+	can reliably predict whether the 
+	given $(Ca,Re)$ pair will result in shear
 	induced bubble break-up or not.  

### 2023-07-16 Reply-Reviewer1_EdwinEdited_26Jun2023.tex
trying to emphasize only the most salient properties

%  -----------------------------------------------------------------------------
%  Modified: 26 June 2023
%  -----------------------------------------------------------------------------
\documentclass{letter}

 \date{\today}

\begin{document}
\begin{letter}{
Physical Review Fluids\\
Professor Eric S. G. Shaqfeh, Editor\\}

\opening{Dear Prof. Shaqfeh,}

Please find enclosed the revised version of our manuscript (FZ10233):
``Numerical Simulation of Bubble Deformation and Breakup under Simple Linear Shear Flows''
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

%% REVIEWER 1 and REVIEWER 2 COMMENTS HAVE TO BE SEPARATE.
Changes made in response to comments of Reviewer 1: 
\begin{enumerate}
\item

\textsf
{This is an excellent manuscript and I recommend acceptance.\\
The main results are figure 11 where the boundary between bubbles that break up
and those that do not is plotted in the Ca-Re plane. If possible, it would be
interesting it the authors could include also the boundary for drops.  As the
authors point out, the main difference between bubbles and drops are the ratios
of the material properties.  It would be interesting to see in more detail how
the breakup modes and the boundary between breakup and no breakup depends on
those. My guess is that the viscosity ratio is more important than the density
ratio.}
\vspace{5 mm}

Response: \\
We really appreciate your compliment.

We have added a drop critical curve with $\lambda$ (density ratio) =1 and
$\eta$ (viscosity ratio) = 1 to Fig. 11.  Also, we have mentioned the
difference between both critical curves.

Additionally, we have examined the effect of $\lambda$ and $\eta$ on drop
breakup for the following combinations of $\lambda$ and $\eta$:
\\
\begin{tabbing}
 \hspace{55mm} \= \hspace{10mm} \kill
 \hspace{5mm} 1. $\lambda$ = 1.0, $\eta$ =1.0 (done) \> 2. $\lambda \simeq 0.0$, $\eta \simeq 0.0$ (this study) \\ 
 \hspace{5mm} 3. $\lambda$ = 1.0, $\eta \simeq 0.0$ \> 4. $\lambda$ = 1.0, $\eta$ =0.1 \\
 \hspace{5mm} 5. $\lambda$ = 0.1, $\eta$ =1.0 \> 6. $\lambda$ = 0.1, $\eta$ =0.1  \\
 \hspace{5mm} 7. $\lambda$ = 1.0, $\eta$ =100 \> 8. $\lambda$ = 1.0, $\eta$ =1000 \\
\end{tabbing}

Although computations for all these conditions have not been completed, we have
found out that the effect of the viscosity ratio on drop deformation is larger
than that of the density ratio, as the reviewer expected.  We will also present
our research on the effect of density and viscosity ratios on a future journal
paper.
\par\noindent

\end{enumerate}

\closing{On behalf of the authors,}
Mitsuhiro Ohta

\end{letter}
\end{document}

### 2023-07-16 Reply-Reviewer2_EdwinEdited_26Jun2023.tex
trying to emphasize only the most salient properties

%  -----------------------------------------------------------------------------
%  Modified: 26 June 2023
%  -----------------------------------------------------------------------------
\documentclass{letter}

 \date{\today}

\usepackage{color}

\begin{document}
\begin{letter}{
Physical Review Fluids\\
Professor Eric S. G. Shaqfeh, Editor\\}

\opening{Dear Prof. Shaqfeh,}

Please find enclosed the revised version of our manuscript (FZ10233):
``Numerical Simulation of Bubble Deformation and Breakup under Simple Linear Shear Flows''
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

%% REVIEWER 1 and REVIEWER 2 COMMENTS HAVE TO BE SEPARATE.
Changes made in response to comments of Reviewer 2: 
\begin{enumerate}

\item
\textsf
{Page 3: The CLSVOF method is not an interface tracking one (in such methods
the interface is calculated simultaneously with the velocity and pressure
fields), but an interface capturing method (in such methods the interface is
reconstructed after the velocity field is calculated at each time step).
Although this is a matter of nomenclature, using the wrong name can be
confusing because the interface tracking algorithms, such as ALE, are
completely different from CLSVOF.}
\vspace{3 mm}

Response: \\
We agree with the reviewer's opinion. We have changed the ``interface tracking''
wording to ``interface capturing method''.
\\
Please see the 1st line from the top in ``III. A. Numerical method and governing equations''.
\\

\par\noindent
\item
\textsf
{Page 3: The definitions of the dimensionless numbers, Re, and Ca, are not
appropriate.  These numbers are defined here using the properties of air (the
dispersed material), whereas in the related references, which are used for
validation, they are defined using the properties of the continuous phase.
This is not so important in the validation tests where viscosity and density
ratios between the two phases are set equal to one, but it is important for the
new results. In general, the deformation of the inclusion is caused by the
forces exerted on it by the fluid in the matrix, and even more so when the
inclusion is just an air bubble, which has negligible density and viscosity.
Moreover, the capillary number is the ratio of viscous forces over capillarity
and the Reynolds number is the ratio of inertia over viscous forces, and the
viscous forces are negligible for air in comparison to viscous forces in the
liquid.}
\vspace{3 mm}

Response: \\
Thank you very much for your suggestion.  We have modified the definitions of
$Re$ and $Ca$ because we had typos in the definitions of $Re$ and $Ca$.  The
computations presented were performed using $Re$ and $Ca$ defined by the
density and the viscosity of the surrounding liquid.
\\
Please see Eq.(2).
\\

\par\noindent
\item
\textsf
{Page 3: The direction of gravity is not specified. Is it acting along the
z-direction? If so, see point \#9 below.  If not, in what direction does it
act? In other studies, an air bubble was considered under the action of both
gravity and velocity gradient in the same direction, ref. [3] and [4].
Interesting variations arise from the occurrence of a lift force on a
deformable bubble. Again, these additional works need to be cited and
discussed.}
\vspace{3 mm}

Response: \\
We have added the direction of gravity in Fig. 1. Regarding the setting of
gravity in this study, we will describe it in our response for Question \#9. 
\\

\par\noindent
\item
\textsf
{Page 4, top: “The singular Heaviside gradient term in the right hand side of
equation (5) is a body force...”. Although this term arises along with gravity
as a body force, in fact, it presumably acts only on the fluid/fluid
interface.}
\vspace{3 mm}

Response: \\
Following to reviewer's comment, we have provided an additional explanation
``The surface tension force expressed by the singular Heaviside gradient term
acts only on the gas-liquid interface.''
\\
Please see the 5th line from the top of Page 4.
\\

\par\noindent
\item
\textsf
{Page 4: Eq. (7a) determines the evolution of F, but the need to introduce F in
addition to the colour function required by VOF (which is determined by eq.
(7b)) is not discussed. F was not even mentioned before eq. (7). The authors
should also reference previous works where the need for this distinction has
been explained.}
\vspace{3 mm}

Response: \\
We agree with reviewer's comment. We have added details of the CLSVOF method at
the beginning of Section ``A. Numerical method and governing equations.''
\\

\par\noindent
\item
\textsf
{Page 5: ``The results shown in Figure 2 verify that our numerical approach can
reproduce the same drop breakup behavior presented in [8].'' The comparison is
only qualitative, not quantitative. One can readily see several differences in
all three cases presented.  The comparison could be improved either by
superimposing the plots or even better by extracting numerical values for the
velocity field or the drop shape. The latter may be more involved, which makes
addressing issue \#7 below even more important.}
\vspace{3 mm}

Response: \\
Though there are differences between previous studies and our study, 
we think a major cause of differences is attributable to the grid size (Renardy: $\Delta x =R/8$, our study: Renardy: $\Delta x =R/16$) 
as we mentioned in the paper.
As a quantitative comparison (regarding Question \#9), we have added a
comparison for bubble deformation to Fig. 3.  We confirmed the validity of our
computations with regard to bubble deformation.\\
{\color{blue}  Mark: I am still computing bubble deformation for an additional comparison}
\\

\par\noindent
\item
\textsf
Page 6: It is well-known that interface capturing methods have drawbacks in
terms of accuracy, which in this problem could lead to uncertainty or
inaccuracy concerning the breakup conditions and the related bubble shapes.
Indeed, the topological changes may affect the small characteristic size of the
filament formed by the distorted drop or bubble, when it becomes comparable
with the grid size. For instance, in their study of two bubbles rising in line
(using VOF and Basilisk as a solver), Zang and Magnaudet, ref. [5], found that
refinement up to R/272 (i.e. the local grid size is 272 times smaller than the
bubble radius) is required in the proximity of the interface to properly
capture the topological changes of millimetric bubbles, since only then the
characteristic size of the grid is smaller than the average film thickness in
typical coalescence conditions. Instead, the authors use R/24 local grid size
at the most. Moreover, the Adaptive Mesh Refinement (AMR) technique is usually
employed for 3-4 consecutive levels of refinement, at least. In the present
work, only two levels of refinement have been used, why? The mesh convergence
study seems quite incomplete.  A more complete study with figures to verify it
should be included in an appendix concerning the mesh and time step
independence of the results. The type of time discretization used is not
stated; is it explicit and which algorithm is used?
\vspace{3 mm}

Response: \\
First, we would like to emphasize to the reviewer that very long
computational times are required for drop/bubble deformation and breakup in
shear flow. For bubble simulations, in particular, even longer computational
times are needed because the time step is much smaller than that for the drop.
In our study, time steps smaller than values determined theoretically from
various time-step constraints were used: the time step was $O(10^{-4}$) s for
the drop and $O(10^{-5}$) s for the bubble.  In addition, it is especially difficult to
solve stably two-phase flows with $\lambda$ (density ratio) $\simeq 0$ and
$\eta$ (viscosity ratio) $\simeq 0$. In some cases, computational times
over a month long were required.  To overcome the problem of very long
computational times, various computational countermeasures were employed in
past studies. For example, in Renardy's study (Phys. Fluids, 2000) a domain
size with $W$ (width ($y$-directional length)) = 2$D$ ($D$: diameter of
drop/bubble) was employed to reduce the number of computational grid
points.  As shown in Table I\hspace{-1.2pt}I in this study, using a width of $W =
2D$ accentuates drop deformation. Regarding the grid size, relatively coarse
discretizations have been used in recent studies: $\Delta x =R/48$ (Komrakova et al.,
CES, 2015), $\Delta x =2R/15, R/15, R/25, R/30$ (Hernandez and Rangel, Comput.
Fluids, 2017), $\Delta x =R/15$ (Amania et al., CES, 2019), $\Delta x =R/30$
(Zhang et al., CES, 2021).

\medskip

Komrakova et al. (CES, 2015) and Zhang et al. (CES, 2021) used a LBM method for
two-phase flows, Hernandez and Rangel (Comput. Fluid., 2017) used a VOF method
and Amania et al. (CES, 2019) applied a level set method to computations.
Although Komrakova et al. (CES, 2015) set a higher grid resolution ($\Delta x
=R/48$, which corresponds to $R$=48 lattice units in the LBM method), they
performed computations over a quarter of the full domain, which is inappropriate
for high $Re$ conditions.  In the study by Hernandez and Rangel (Comput.
Fluids, 2017), it was shown that the grid resolution should be $\Delta x \leq
R/15$ for approximately a 5\% error. Zhang et al. (CES, 2021) used a higher grid
resolution ($R$=60 lattice units), but the height of the computational domain was
$4R$ for 3D-computations.  Additionally, the LBM method (Komrakova et al.,
CES(2015), Zhang et al., CES(2021)) allows the use of higher grid resolutions
due to shorter computational times that result from not solving the continuity
equation simultaneously; the decreased computational times come at the
expense of diminished accuracy.

Our simulations were performed under stringent computational settings, in terms
of domain sizes and grid resolutions, selected to guarantee a minimum accuracy
in our numerical results.  The critical $Re$ numbers found from the bubble
simulations presented in this study will provide a minimum standard for future
studies.  Anticipating future increased computational resources and the
development of new numerical algorithms, we have added the following comment:
Additional grid refinements may be desirable to perform further accuracy
evaluations for bubble deformation and breakup. \\ (see the last line at the
section “B.  Validation of the numerical method”, Page 5) Regarding the
refinement level of AMR, the use of 3-4 consecutive refinement levels is not
always preferred.  A small refinement level is rather suitable in terms of
stable computations and we found that our mesh setting for this purpose was
reasonable.
{\color{blue}  Mark: please  write the type of time discretization.}
\\

\par\noindent
\item
\textsf
{\color{red} Several experimental studies concerning bubbles in shear flow
exist (for example, ref. [6]) so alternatively one could compare the numerical
results with experiments and avoid the comparison with other numerical results,
which are older and may not have achieved convergence due to lack of access to
the software and hardware we have today.}
\vspace{3 mm}

Response: \\
{\color{blue}  Mark: I am still computing bubble deformation for an additional comparison}
\\

\par\noindent
\item
\textsf
{The following is the most disturbing issue with this study: It is fine to
examine conditions leading to bubble breakup or other flow instabilities, but
the range of parameter values investigated must correspond to existing
materials and achievable flow conditions.  The authors have given the governing
equations in dimensional form and defined dimensionless numbers incorrectly as
stated in point \#2, but also assigned them values that may not be physically
relevant. Moreover, the bubble size is nowhere stated.................\\
Finally, the Reynolds number of the channel in this case would be: $Re_{\rm
channel} \simeq 6000$.  This high value of Re corresponds to turbulence
conditions.................}
\vspace{3 mm}

Response: \\
As we have stated in response to your comment \#2, correct dimensionless
numbers based on the density and the viscosity of the surrounding liquid were
used in real computations.  Regarding physical properties and conditions in our
computations, we will give you an example for the case of $Ca$ = 0.3 and $Re$
=93.\\

Physical properties (a silicone oil has a very similar physical properties with these values.):\\
\quad $\rho_{\rm m}$ (density of liquid) = 1000 kg/m$^3$, $\mu_{\rm m}$ (viscosity of liquid) = 0.2 Pa$\cdot$s,
$\sigma$ (surface tension) = 0.025 N/m, $R$ (bubble radius) = 5.0 mm.\\
From ${\it \Gamma}$ = $2V/H$ = $2V/6R$, \  $V$ = 3${\it \Gamma} R$ = $\frac{3\sigma Ca}{\mu_{\rm m}} $ = 1.1 m/s.
Also, we obtain $Fr$ (Froude number) = $\frac{{\it \Gamma}R}{\sqrt {gR}}$ = 1.7. \\
In this flow system, the effect of gravity may not be completely negligible. However, in our computations, 
we set $g = 0$ because we wanted to clearly manifest only the effect of density and viscosity ratios. 
From another perspective, it can be said that we investigated phenomena in space.
At the end of the Problem Description section, we added a detailed explanation about physical properties and conditions.

Also, regarding the channel $Re$ number, we obtain $Re_{\rm channel} =
\frac{\rho_{\rm m}2VH}{\mu_{\rm m}}$ = 3300 for a simple linear shear-flow.  As
expected, $Re_{\rm channel} = 3300$ falls within turbulence conditions for
simple linear shear-flow of a single phase fluid.  It is important to note that
the generation of turbulence is suppressed and turbulent eddy dissipation
becomes large if bubbles exist in fluid flows. However, as far as we know,
there are no conclusive results on turbulence in a simple linear shear-flow
which includes bubbles.  We predict that the generation of turbulence is
considerably suppressed when bubbles occupy a significant portion of the
flow in a channel, as in this study. At present, we believe that our
computations based on the assumption of laminar flows are reasonable and not
unrealistic.\\

\par\noindent
\item
\textsf
{Page 9, Fig. 5 and related discussion: It is quite strange that the bubble
does not reach a final steady shape, but seems to expand, contract and then
expand again. Here, it is even more important to verify that the simulations
have converged (via mesh and time refinement) and to extend them much further
in time to determine if this periodic motion will prevail or finally lead to a
steady state.}
\vspace{3 mm}

Response: \\
Regarding Question \#12, we have made a new figure for the case of $Re$ = 50
and $Ca$ = 0.3.  As is obvious from the new figure, bubble reaches a final
steady shape, when the condition of $Re$ number is much smaller than the
critical $Re$ number ($Re_{\rm c}$). The results show that the bubble is largely
elongated and contracts to a doglegged shape when the $Re$ number is close to
$Re_{\rm c}$)..........\\
{\color{blue}  Mark: I will add these discussions after making a new figure.}

Moreover, the main object of this study is to find $Re_{\rm c}$; we have plans
for examining bubble periodic deformation with expansion and contraction in
future work.  In ongoing and upcoming work, we will examine the effect of
$\lambda$ and $\eta$ on drop breakup for some combinations of $\lambda$ and
$\eta$ as follows: 
\\
\begin{tabbing}
 \hspace{55mm} \= \hspace{10mm} \kill
 \hspace{5mm} 1. $\lambda$ = 1.0, $\eta$ =1.0 (done) \> 2. $\lambda \simeq 0.0$, $\eta \simeq 0.0$ (this study) \\ 
 \hspace{5mm} 3. $\lambda$ = 1.0, $\eta \simeq 0.0$ \> 4. $\lambda$ = 1.0, $\eta$ =0.1 \\
 \hspace{5mm} 5. $\lambda$ = 0.1, $\eta$ =1.0 \> 6. $\lambda$ = 0.1, $\eta$ =0.1  \\
 \hspace{5mm} 7. $\lambda$ = 1.0, $\eta$ =100 \> 8. $\lambda$ = 1.0, $\eta$ =1000 \\
\end{tabbing}
After we complete the study of the effect of $\lambda$ and $\eta$, we will work
on periodic bubble deformation with expansion and contraction.  Due to
prohibitely long computation times, additional computing resources and improved
numerical algorithms are necessary to simulate multiple periodic cycles in
bubble expansion and contraction.\\

\par\noindent
\item
\textsf
{ Page 13: Fig. 11, which distinguishes the two areas of bubble breakup against
just bubble deformation, presents only 4 points and a curve connecting them,
although this is an important physical result. Several more points must be
included in it to reach a definitive conclusion.}
\vspace{3 mm}

Response: \\
We appreciate the reviewer's opinion, but it is important to keep in mind that
at the start of our study there were no guiding initial results that indicated
even potential values for critical Reynolds numbers for a bubble. The critical
Reynolds numbers found and presented were obtained after extensive and
expensive computations.  After lengthy computations, we were able to determine
the bubble $Re_{\rm c}$ number for 4 $Ca$ numbers.  Nevertheless, we believe
that a bubble breakup critical curve drawn based on 4 points will be useful for
low $Ca$ numbers.  Following the suggestion from the reviewer 1, we have added
a drop breakup critical curve ($\lambda$ = $\eta$ =1.0) to Fig. 11.  The
difference in $Re_{\rm c}$ number between the bubble and the drop is clearer in
the new Fig. 11.  But, the reviewer's opinion is appropriate, and we have added
the following supplementary statement: In future work, we will determine the $Re_{\rm c}$
for a variety of high $Ca$ numbers to construct a detailed critical curve for a wider
range of $Ca$ numbers.\\

\par\noindent
\item
\textsf
{\color{red}  End of conclusions section: ........................
These phrases state the obvious, the densities and viscosities are different between drops and bubbles and, therefore, they cause different dynamics. 
Instead, it is imperative that the authors give the different physics that the property differences generate. 
To this end, they should examine thoroughly and in every detail the velocity and stress fields in each arrangement. 
This may require additional figures and text, but it must be done. Without this examination and its conclusions, this study is more appropriate for a 
Journal on numerical methods in fluid flows than a physical review Journal. This is the second most important issue with this presentation}
\vspace{3 mm}

Response: \\
{\color{blue}  Mark: I have finished an additional computation for showing property differences, and I am making a new figure.}
\\

\end{enumerate}

Less important issues
\begin{enumerate}

\item
\textsf
{Page 2: The symbols for the domain length, width and height are L(x), W(y) and H(z), the variables in parenthesis indicate the direction related 
to the lengths L, W, and H. However, these are geometric parameters, and could be confused with functions, in the way they are given by the 
authors here and elsewhere in the text.\\
}
\vspace{5 mm}

Response: \\
We agree with reviewer's comment. We deleted $(x), (y), (z)$ and will simply
express the domain length, width and height as $L, W, H$.\\

\par\noindent
\item
\textsf
{Page 6: “... depicted in Figure 4(a), uses Ca = 0:3 and Re = 1:1.” It should be Figure 4(b).\\
}
\vspace{5 mm}

Response: \\
We've fixed the error.\\

\par\noindent
\item
\textsf
{Page 8: “... process is the almost same...” should be “... process is almost the same...”.\\
}
\vspace{5 mm}

Response: \\
We've fixed the typo.\\

\par\noindent
\item
\textsf
{The authors could cite another relevant paper where a similar analysis was undertaken [10]. 
The main difference is that the present computations are fully 3D, while in this suggested study shear 
flow until breakup is examined of a 2D bubble. Nevertheless, there are some similarities 
that should be recognized. The present work is more accurate and extensive.\\
}
\vspace{5 mm}

Response: \\
The paper by Wei et al. is now cited in the Introduction.\\

\par\noindent
\item
\textsf
{The authors should use D instead of De as the symbol for the parameter introduced by Taylor to 
determine the extent for bubble deformation, because De stands for the Deborah number.\\
}
\vspace{5 mm}

Response: \\
We have changed the symbol from $De$ to $D$ as suggested.\\

\end{enumerate}

\closing{On behalf of the authors,}
Mitsuhiro Ohta

\end{letter}
\end{document}

### 2023-07-17 Bubble-deformation.tex
edit paper

@@
 
-\usepackage{graphicx}% Include figure files
+\usepackage[dvipdfmx]{graphicx}% Include figure files
+%\usepackage{graphicx}% Include figure files
 \usepackage{dcolumn}% Align table columns on decimal point
 \usepackage{bm}% bold math
+\usepackage{comment}
+\usepackage{color}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 \newcommand{\vv}{\mathbf}
+\newcommand{\bmV}{\vv{V}}
 \newcommand{\bmD}{\vv{D}}
@@
 based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were
-presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,
-KhiRenCri03,Ren06,Ren07,Ren08-2}.  Since then, the literature on computational
+presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.  
+Since then, the literature on computational
 studies on the deformation and breakup of a single or several drops in shear
@@
 approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06,
-KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and interface-tracking
+KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and 
+{\color{red} interface-capturing }
 level set methods \cite{SusSmeOsh94}.
 
-In contrast, few computational studies on bubble deformation and breakup in
-shear flow have been conducted \cite{WanShiZha15}.  This type of bubble
-dynamics in shear flow is of critical importance for a variety of
+{\color{red} In contrast, only a few computational studies on bubble deformation and breakup in
+shear flow can be found \cite{WeiQiaXu12,WanShiZha15}. 
+In these previous studies, the dynamics of bubble 
+deformation in shear flow has mainly been exmained.}
+{\color{blue} What distinguishes our work from that in 
+\cite{WeiQiaXu12,WanShiZha15}?}
+This type of bubble dynamics in shear flow is of critical importance for a variety of
 scientific and engineering processes. We refer the reader to the 
@@
 processes, microfluidic devices, and micro bubbles in the blood 
-circulation system,
-\cite{CHU2019108,muller2008single,bento2018deformation,drenckhan2015science}.
+circulation system,\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.
 In particular, it is the study of bubble deformation as it pertains
@@
 The physical properties that distinguish bubble and
-drop studies are expressed in terms of the density ratio $\lambda = \rho_b /
-\rho_m$ and the viscosity ratio $\eta = \mu_b / \mu_m$, where $\rho$ is the
+drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} /
+\rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the
 fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote
 the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a
-bubble in an insoluble viscous liquid, the density ratio $\lambda \simeq 0$ and
-the viscosity ratio $\eta \simeq 0$, whereas most studies dealing with a drop
+bubble in an insoluble viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, 
+whereas most studies dealing with a drop
 in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
@@
 is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
-capturing algorithm \cite{SusPuc00}.  We focus on determining critical physical
+capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.  
+We focus on determining critical physical
 conditions in which the breakup of a bubble occurs in shear flow because it is
@@
 transitions from stable to unstable.  Specifically, we identify the critical
-Reynolds number $Re_{c}$ corresponding to the bubble breakup onset condition as
-a function of the Capillary number $Ca$.  The critical Reynolds number, 
-$Re_{c}$, for drop
-breakup was reported previously \cite{LiRenRen00}, in this work we determine,
-for the first time, the critical Reynolds number that leads to \emph{bubble}
+Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
+a function of the Capillary number ($Ca$). 
+The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
+reported previously by \cite{LiRenRen00}.
+{\color{red} In previous studies on the motion of bubble deformation
+in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, 
+only findings for bubble defomation under very low $Re$ 
+number conditions have been reported.}
+{\color{blue} What were the $Re$ conditions considered by 
+\cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions 
+considered in our paper?}
+In this work we determine, for the first time, the critical Reynolds number that leads to \emph{bubble}
 breakup.  Additionally, our computational studies reveal characteristics that
-distinguish the deformation and breakup processes of a drop versus those of a
-bubble.
+distinguish the deformation and breakup processes of a drop versus those of a bubble.
 
@@
 for our studies of a bubble (or drop) in shear flow.  The computational domain
-consists of a three-dimensional rectangular domain of $L(x)$ (length) $\times$
-$W(y)$ (width) $\times$ $H(z)$ (height).  The size of $L(x)$, $W(y)$ and $H(z)$
+consists of a three-dimensional rectangular domain of $L$ (length) $\times$
+$W$ (width) $\times$ $H$ (height).  The size of $L$, $W$ and $H$
 was determined after consideration of numerical result sensitivity to domain
@@
 for gas-liquid/liquid-liquid flows.  Computations are initialized with a
-spherical bubble set at the center of the domain that is then subjected to a
+spherical bubble {\color{red} (or drop) of radius $R$ = 5 mm set at the 
+center of the computational domain.   The bubble (or drop) is then 
+subjected to a
 linear shear flow generated by the motion of the top and bottom plates, which 
-have constant velocity $+V$ and $-V$, respectively.  In the interior of the
+have constant velocity $+V$ and $-V$, respectively.}  In the interior of the
 domain, the initial velocity condition is assumed to be a simple linear profile
@@
 liquid-liquid two-phase flows include the Reynolds ($Re$), Weber ($We$) (or
-$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers, and the density ratio $\lambda$
-and viscosity ratio $\eta$.  For comparison with previous drop studies, we set
-$\lambda=1$ and, since in this case the effect of gravity is not considered, we
-may ignore the Froude number $Fr$.  As a result, (for $\lambda=1$) the
+$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers.  Gas-Liquid and 
+Liquid-Liquid two-phase flow problems are also determined by the
+density ratio $\lambda$ and the viscosity ratio $\eta$.  
+In the present study, the effect of gravity is not considered so
+that we ignore the effect of the $Fr$ number.
+
+When comparing with previous drop studies, we fix
+$\lambda=1$.  As a result, (for $\lambda=1$) the
 following dimensionless physical parameters are used to describe the problem of
-drop or bubble deformation/breakup in shear flow
+drop deformation/breakup in shear flow
 %
 \begin{eqnarray}\label{dimensonless}
-  Re = \frac{\rho_{b}UR}{\mu_{b}}, \quad
-  Ca = \frac{\mu_{b}U}{\sigma}, \quad
-  \eta = \frac{\mu_{b}}{\mu_{m}}
+  Re = \frac{\rho_{\rm {\color{red}m}}UR}{\mu_{\rm {\color{red}m}}}, \quad
+  Ca = \frac{\mu_{\rm {\color{red}m}}U}{\sigma}, \quad
+  \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}}
 \end{eqnarray}
 %
-where $R$ is the drop or bubble radius, $\sigma$ denotes the surface tension,
-and $U$ is the velocity scale. For the problem of shear-induced drop
-deformation and breakup, the velocity is set to $U = \mathit{\Gamma} R$, where
-the shear-rate $\mathit{\Gamma} = 2V/H$.  As mentioned in the introduction,
-most previous drop studies set $\eta = 1$. Thus, for comparison, in this case
-we will set $\lambda = \eta = 1$ (and also neglect the effect of gravity so
-that $g=0$). On the other hand, in our computations for a bubble, we set the
-density and viscosity of air to $\rho_{b}$ = 1.2 kg/m$^{3}$ and $\mu_{b}$ = 1.8
-$\times$ $10^{-5}$ Pa$\cdot$s, and we take the 
-density ratio 
-%%$\lambda$ = 1.2 $\times$ $10^{-3}$ 
-$\lambda$ = 1.0 $\times$ $10^{-3}$ 
-and the 
-viscosity ratio 
-%%$\eta$ $<$ 1.0 $\times$ $10^{-3}$.
-$\eta$ $=$ 1.0 $\times$ $10^{-3}$.
-For consistency with previous studies, we will computationally examine the
+$U$ is the velocity scale and $\sigma$ denotes the surface tension. 
+For the problem of shear-induced drop deformation and breakup, 
+the velocity is set to 
+$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  
+As mentioned in the introduction, most previous drop studies set 
+$\eta = 1$\cite{?}. 
+Thus, for comparison with previous drop deformation and breakup problems,
+we set $\lambda = \eta = 1$ (and also neglect the 
+effect of gravity so that $g=0$). On the other hand, in 
+our computations for bubble deformation, 
+we set the density and viscosity of air to be
+$\rho_{\rm b}$ = 1.2 kg/m$^{3}$ and $\mu_{\rm b} = 1.8
+\times 10^{-5}$ Pa$\cdot$s respectively.
+We emphasize that for consistency with previous studies, 
+{\color{blue} cite some of these previous studies which examine deformation
+and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
+we computationally examine the
 deformation and breakup of a bubble in simple linear shear flow as a 
-function of $Re$ and $Ca$ numbers.  In particular, 
-for a certain $Ca$ value, we
-focus on determining the critical value 
-$Re_{c}$ that corresponds to the threshold
-for breakup.
+function of the $Re$ and $Ca$ numbers. 
+{\color{red} That is to say, by setting $g=0$, we are isolating the
+effect of only varying $Re$ and $Ca$ on bubble 
+deformation and breakup.  In our controlled study, we determine 
+the critical $Re_{\rm c}$ versus $Ca$ curve 
+in which $Re_{\rm c}$ corresponds to the threshold of 
+bubble (or drop) breakup.  
+We determine the
+critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the
+density ratio and viscosity ratio. }
+
+{\color{red} In our computations, the density of the matrix fluid 
+is fixed at
+$\rho_{\rm m}$ = 1000 kg/m$^3$.  The surface tension at the bubble (drop)
+interface is $\sigma =2.5 \times 10^{-2}$ N/m.
+The values of $Re$ and $Ca$ in our simulations are controlled by
+changing the values of $\mu_{\rm m}$ and $V$.
+For studying bubble deformation and break-up, 
+the density and viscosity ratios satisfy 
+$\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.}
 
@@
 % 
+%\begin{comment} 
 \begin{figure}%[h!]
@@
 \end{figure}
+%\end{comment}
 %
@@
 %  -----------------------------------------------------------------------------
-Numerical results were obtained using the interface-tracking CLSVOF method,
-which is based on a fixed grid finite volume algorithm.  In our studies,
+Numerical results were obtained using the {\color{red} interface capturing} 
+Coupled Level Set and Volume of Fluid (CLSVOF) 
+method \cite{SusPuc00,SUSSMAN2007469},
+which is based on a fixed grid finite volume algorithm.  
+{\color{red}The CLSVOF method is a robust  numerical  technique  
+that  combines  some  of  the  advantages  of 
+the Volume of Fluid (VOF) method (\cite{HirNic81}) 
+and the Level Set (LS) (\cite{SusSmeOsh94}) method
+while overcoming their weaknesses. 
+In the VOF method,  the Volume Fraction function, $F$, is used to 
+represent the interface. The values of $F$ correspond 
+to the volume fraction of liquid in a given computational cell. 
+In other words, $F = 0$ when a computational cell contains 
+only gas and $F = 1$ when a computational cell contains only liquid. 
+If $0 < F < 1$, then a computational cell contains 
+the gas-liquid interface. The VOF method has a great advantage 
+over the LS method in that accurate algorithms for 
+advecting $F$ can be applied
+so that mass/volume is conserved up to machine precision
+while still maintaining a sharp representation of the interface. 
+On the other hand, the disadvantage of the VOF method in comparison
+to the LS method 
+is that tangled and difficult reconstruction procedures are required 
+for determining the slope of the piecewise linear VOF reconstructed interface.
+In the LS method, the signed distance function $\phi$ (LS function) 
+is used to track the interface. The interface is implicitly 
+represented by the set of points in which $\phi = 0$. 
+Liquid and gas regions are defined as $\phi > 0$ in the 
+liquid and $\phi < 0$ in the gas, respectively.  
+One of the advantages of the LS method is that one can track and represent 
+smoothly the interface, but the LS method has the disadvantage 
+that mass/volume is not explicitly conserved. 
+In the CLSVOF method, the coupling between the LS function 
+and the VOF function occurs when computing the normal of the reconstructed 
+interface in the VOF calculation process and also when assigning 
+the LS function with the exact signed normal distance to the reconstructed 
+interface in the LS calculation process. That is to say, the 
+piecewise linear approximation (the volume-of-fluid reconstruction step) 
+for the 
+VOF method is determined using the unit normal vector ($\bm n$) 
+estimated from information of the LS function. By taking 
+advantage of both 
+methods, the evolution of the liquid–gas interface location can be
+computationally captured in such a way so that volume/mass is preserved
+to machine precision and at the same time,
+the interface normals and the surface tension force 
+(which is proportional
+to the interface curvature) can be straightforwardly derived from the
+smooth level set function. }
+
+In our studies,
 the two-phase fluid flow is comprised of air and a 
-viscous Newtonian liquid.  The
-Heaviside function, $\Hea(\phi)$, which is defined as
+viscous Newtonian liquid.  
+The Heaviside function, $\Hea(\phi)$, which is defined as
 %
@@
 function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$. The
-singular Heaviside gradient term in the right hand side of
-equation~\eqref{nseqn} is a body force representing the surface tension force
-and is equivalent
-to specifying that the jump in the normal stress is equal to
-$\sigma\kappa$~\cite{TanguyEtAl2007}.  The interfacial curvature $\kappa$ is
+singular Heaviside gradient term in the right hand side of equation~\eqref{nseqn} is a body 
+force representing the surface tension force and is equivalent to specifying that the jump 
+in the normal stress is equal to
+$\sigma\kappa$~\cite{TanguyEtAl2007}. 
+{\color{red} The surface tension force expressed 
+by the singular Heaviside gradient term acts only on the 
+gas-liquid interface. 
+The sharp interface ``Ghost Fluid Method'' \cite{kang2000boundary}
+is used to discretize the gradient of the Heaviside function as it 
+appears in the surface tension force term.  This force, upon discretization,
+is only non-zero across cells in which the level set function changes
+sign. }
+
+The interfacial curvature $\kappa$ is
 computed with second order accuracy directly from the volume-of-fluid (VOF)
-function using the height function technique~\cite{sussman2003second}.  
+function using the height function technique~\cite{Sus03,SUSSMAN2007469}.  
 We remark that we get the same
@@
 procedure.
+
+{\color{red}
+The temporal discretization of our numerical method is an operator split
+projection method as described by \cite{SUSSMAN2007469}.  An outline of 
+our method is as follows (see \cite{SUSSMAN2007469}, section 4, for more 
+details): }
+\begin{description}
+\item[Step 1. CLSVOF interface advection]
+ \begin{eqnarray*}
+ \phi^{n+1}=\phi^{n}-\Delta t[\bmu\cdot\nabla\phi]^{n} \\
+ F^{n+1}=F^{n}-\Delta t[\bmu\cdot\nabla F]^{n} 
+ \end{eqnarray*}
+\item[Step 2. Nonlinear advective force terms]
+ \begin{eqnarray*}
+ {\cal A}=[\bmu\cdot\nabla\bmu]^{n}
+ \end{eqnarray*}
+\item[Step 3. Viscosity force]
+ \begin{eqnarray*}
+ \frac{\bmu^{\ast}-\bmu^{n}}{\Delta t}=-{\cal A}+g\vec{z}-
+  [\nabla p/\rho]^{n}+\frac{1}{2}\frac{
+    \nabla\cdot(2\mu\bmD^{n})+ 
+    \nabla\cdot(2\mu\bmD^{\ast})}{\rho}
+ \end{eqnarray*}
+\item[Step 4. Pressure projection]
+ \begin{eqnarray*}
+ \bmV=\bmu^{n}+\Delta t(-{\cal A}+g\vec{z}+
+   \frac{1}{2}\frac{
+    \nabla\cdot(2\mu\bmD^{n})+ 
+    \nabla\cdot(2\mu\bmD^{\ast})}{\rho})
+ \end{eqnarray*}
+ \begin{eqnarray*}
+ \nabla\cdot\frac{\nabla p}{\rho}=\frac{1}{\Delta t}\nabla\cdot\bmV
+ \end{eqnarray*}
+ \begin{eqnarray*}
+ \bmu^{n+1}=\bmV-\Delta t \frac{\nabla p}{\rho}
+ \end{eqnarray*}
+\end{description}
 
@@
 deformed drop in simple linear shear flow is described in terms of the Taylor
-deformation parameter $De=(a-b)/(a+b)$, where $a$ and $b$ are the major and
+deformation parameter {\color{red} $D$}=$(a-b)/(a+b)$, 
+where $a$ and $b$ are the major and
 minor axes of the deformed drop.  For consistency, we perform numerical
@@
 $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  Numerical
-results are listed in Table~\ref{tab:DeComparison} for $De$ as a function of
+results are listed in Table~\ref{tab:DeComparison} for {\color{red} $D$} 
+as a function of
 $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
@@
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter $De$ for a drop as a function 
+\caption{Comparison of the Taylor deformation parameter {\color{red} $D$} 
+for a drop as a function 
          of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$). In all cases, the domain 
@@
 Reynolds number                      & 0.1     & 0.5     & 0.6     & 0.75      \\
-$De$(Li et al. (\cite{LiRenRen00}))  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
-$De$(Our study)                      & 0.3960  & 0.4570  & 0.4758  & Breakup   \\
+{\color{red} $D$}(Li et al. (\cite{LiRenRen00}))  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
+{\color{red} $D$}(Our study)                      & 0.3960  & 0.4570  & 0.4758  & Breakup   \\
 \hline
@@
 %
+%\begin{comment} 
 \begin{figure}[h!]
@@
 \end{figure}
+%\end{comment} 
 %
@@
 differences between the results can be attributed to the increased resolution
-used in our study in the level-1 grid around the elongated drop.  The numerical
-validation studies performed in this section demonstrate that our numerical
-method is capable of accurately simulating shear-induced drop deformation and
-breakup.
+used in our study in the level-1 grid around the elongated drop.  
+{\color{red} The numerical
+validation studies performed in this section and the following section
+demonstrate that our numerical
+method can reliably determine the transition regions at which shear-induced
+bubble or drop deformation leads to breakup.  We remark that in the next
+section, we demonstrate that we can expect an error of $\%3$ for predicting
+the transition to break-up.  The analysis in this section and the
+following also demonstrate that the error is reduced by a factor of 2 each
+time the grid is refined by a factor of 2. Also, we refer the
+reader to \cite{ohta2011robust} in which we apply our 
+CLSVOF method for bubble formation
+problems. }
 
@@
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter $De$ for a drop as a function of
+\caption{Comparison of the Taylor deformation parameter {\color{red} $D$} for a drop as a function of
          domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).
@@
 \hline
-System      & Domain size ($\LWH$)         & $De$    \\
+System      & Domain size ($\LWH$)         & {\color{red} $D$}    \\
 System 1    & $8R  \times 4R  \times 8R$   & Breakup \\
@@
 Here we investigate the drop dynamics sensitivity to domain size around the
-critical Reynolds number $Re_{c}=0.75$.  Specifically, we consider domain size
+critical Reynolds number $Re_{\rm c}=0.75$.  Specifically, we consider domain size
 sensitivity for the condition of $Re=0.75$, $Ca=0.3$, and $\lambda = \eta = 1$,
@@
 break up and becomes stable with a deformed shape if we set $L$ large enough
-and $W \geq 6R$ and $H \geq 6R$.  Since the value of $De$ for the domain size
+and $W \geq 6R$ and $H \geq 6R$.  Since the value of {\color{red} $D$} for the domain size
 $\lwh{8}{6}{6}$ differs by only $1.3\%$ with the value for the domain size of
@@
 height to $H=6R$ to minimize the number of computational grid nodes along those
-directions.  To determine the critical Reynolds number $Re_c$ (with $Ca=0.3$),
+directions.  To determine the critical Reynolds number $Re_{\rm c}$ (with $Ca=0.3$),
 we consider a domain size of $\lwh{24}{6}{6}$, and we find that the drop
-reaches a stable state with deformation parameter $De=0.549$ for $Re=1.0$,
+reaches a stable state with deformation parameter {\color{red} $D$}=0.549 for $Re=1.0$,
 while a value of $Re=1.1$ leads to drop breakup.
 % 
+%\begin{comment} 
 \begin{figure}%[h!]
@@
   \includegraphics[width=\textwidth]{DeEvolution}
-  \caption{Time evolution of the deformation parameter $De$ versus 
+  \caption{Time evolution of the deformation parameter {\color{red} $D$} versus 
    a dimensionless
@@
    finest-level grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = 
-   \Delta z ^{\ell=1}$. The evolution of $De$ using the first system, where
+   \Delta z ^{\ell=1}$. The evolution of {\color{red} $D$} using the first system, where
    $\Delta x^{\ell=1} = R/16$, is shown in black and it predicts that 
@@
    number corresponding to these results is $Ca=1.0$.
-   ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$)}
+   ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$)}
   \label{fig:DeEvolution}
 \end{figure}
+%\end{comment} 
 %
@@
 x^{\ell=1}=R/16$ and another with $\Delta x^{\ell=1}=R/24$, to determine
-$Re_c$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the
-deformation parameter $De$ over time for the two grid systems; the $x$-axis is
-a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $De$.
-The results show that bubble breakup occurs at $Re_c = 35$ for the grid system
+$Re_{\rm c}$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the
+deformation parameter {\color{red} $D$} over time for the two grid systems; the $x$-axis is
+a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is {\color{red} $D$}.
+The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system
 with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta
-x^{\ell=1}=R/24$ predicts a critical value of $Re_c = 34$.  Note that although
-the time evolution of $De$ for the two grid systems is consistent for both
+x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  Note that although
+the time evolution of {\color{red} $D$} for the two grid systems is consistent for both
 resolutions (the predicted critical Reynolds numbers differ by $\sim 3\%$), the
@@
 than 6 times longer than the one based on the coarser system with $\Delta
-x^{\ell=1}=R/16$.  We remark that in our search for $Re_c$, we considered a
+x^{\ell=1}=R/16$.  We remark that in our search for $Re_{\rm c}$, we considered a
 wide range of values of $Ca$ and we found it necessary to use a large $L$
@@
 	   ``drop'' critical Reynolds number corresponding to $Ca=0.3$ is
-	   $1.0<Re_{c}<1.1$.
+	   $1.0<Re_{\rm c}<1.1$.
 	   ($\lambda$ = $\eta$ = 1.0)}
@@
 the first case, shown in Figure~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and
-$Re=1.0$, while the second case, depicted in Figure~\ref{fig:DropBreak}(a),
+$Re=1.0$, while the second case, depicted in Figure~\ref{fig:DropBreak}({\color{red}b}),
 uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the
 case with $Re=1.0$, the drop gradually deforms and finally attains a stable
-deformed state with $De$= 0.549.  Over the same domain, for the case with
+deformed state with {\color{red} $D$}= 0.549.  Over the same domain, for the case with
 $Re=1.1$, the ``mother'' drop elongates over time and the volume at the ends of
@@
 	   critical Reynolds number corresponding to $Ca=0.3$ is
-	   $92<Re_{c}<93$.  In contrast to the drop deformation case,
-           when $Re$ is slightly below $Re_{c}$
+	   $92<Re_{\rm c}<93$.  In contrast to the drop deformation case,
+           when $Re$ is slightly below $Re_{\rm c}$
            (See Figure \ref{fig:DropBreak} $Re=1.0$ for the drop case), 
@@
            ($T=34.4$). 
-           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+           ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
 	   }
@@
 \end{figure}
-%
+%\end{comment} 
+%
+%\begin{comment}
 \begin{figure}%[h!]
@@
 	   critical Reynolds number corresponding to $Ca=0.3$ is
-	   $92<Re_{c}<93$.
-           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   $92<Re_{\rm c}<93$.
+           ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
 	   }
@@
 Figure~\ref{fig:BubbleBreakCa0p3Re93}.  The results indicate that the critical
-Reynolds number is approximately $Re_c = 93$ (with $Ca=0.3$).  A comparison
+Reynolds number is approximately $Re_{\rm c}$ = 93 (with $Ca=0.3$).  A comparison
 with the drop breakup dynamics presented in Section~\ref{sec:DropBreak} and the
@@
 magnitude is required for bubble breakup 
-($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
 compared with the case of the drop ($\lambda$ = $\eta$ = 1). Then,
@@
 %
+%\begin{comment} 
 \begin{figure}%[h!]
@@
 \end{figure}
+%\end{comment} 
 %
 For the case of bubble breakup (Figure~\ref{fig:BubbleBreakCa0p3Re93}), we
-observe that the deformation process is the almost same as the no-breakup case
+observe that the deformation process is almost {\color{red}the} same as the no-breakup case
 until the doglegged shape is formed at $T \sim 27.4$. The bubble finally breaks
@@
 %
+%egin{comment} 
 \begin{figure}%[h!]
@@
 %
+%egin{comment}
 \begin{figure}%[h!]
@@
 	   critical Reynolds number corresponding to $Ca=0.8$ is
-	   $42<Re_{c}<43$.
-           ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+	   $42<Re_{\rm c}<43$.
+           ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
 	   }
@@
 \end{figure}
-%
+%\end{comment} 
+%
+%egin{comment} 
 \begin{figure}%[h!]
@@
 and $Re=43$, respectively.  We note that the bubble critical Reynolds number is
-around $Re_{c} \approx 43$, whereas $Re_{c} \approx 0$ for the corresponding
+around $Re_{\rm c} \approx 43$, whereas $Re_{\rm c} \approx 0$ for the corresponding
 case of the drop with 
 $\lambda$ = $\eta$ = 1 (see e.g.~\cite{LiRenRen00}).
-Note that $Re_{c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca
+Note that $Re_{\rm c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca
 = 0.3$ since the bubble at $Ca = 0.8$ is more elastic due to the weaker effect
@@
 lists, for representative $Ca$ values,
-the corresponding critical Reynolds number, $Re_{c}$, for shear-induced 
+the corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced 
 bubble breakup.  The data in 
 Table~\ref{tab:CaRecComparison} 
-corresponds to $\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$, $0.3<Ca<1$, and
+corresponds to $\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
 the initial/boundary conditions are given by (\ref{IC_BC}).
-The results in 
-Table~\ref{tab:CaRecComparison}
-indicate that sufficiently large shear forces are
-required for bubble breakup even for large Capillary numbers. 
-In Figure~\ref{fig:CaRecFit} we plot the cubic interpolant of the
-data given in 
-Table~\ref{tab:CaRecComparison}
-and make the
-hypothesis that given a new data point, $(Ca,Re)$, 
-shear induced bubble break up
-will occur if the point $(Ca,Re)$ is above the given critical curve, 
-and the bubble will not break if the $(Ca,Re)$ pair is below the 
-critical curve.
+The results in Table~\ref{tab:CaRecComparison}
+indicate that sufficiently large shear forces are required for bubble breakup even for large Capillary numbers. 
+In Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in Table~\ref{tab:CaRecComparison} and 
+make the hypothesis that given a new data point, $(Ca,Re)$,  shear induced bubble break up will occur if the point $(Ca,Re)$ 
+is above the given critical curve, and the bubble will not break if the $(Ca,Re)$ pair is below the critical curve.
+{\color {red} For comparison purpose, a drop critical curve with $\lambda =\eta = 1$ is also indicated in Fig.~\ref{fig:CaRecFit}.
+From Fig.~\ref{fig:CaRecFit}, it is recognized that the difference between both critical curves is 
+Hereafter, we will settle $Re_{\rm c}$ numbers for the condition of 
+high $Ca$ numbers to determine a general critical curve 
+for a wide range of $Ca$ numbers.}
+{\color{blue} it seems like the above passage is still a work in progress?}
 
@@
 	corresponding Capillary numbers.
-        ($\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$) 
+        ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
 	}
@@
 Capillary number $Ca$            & 0.3  & 0.5  & 0.8  & 1.0  \\
-Critical Reynolds number $Re_c$  & 93   & 67   & 43   & 35   \\
+Critical Reynolds number $Re_{\rm c}$  & 93   & 67   & 43   & 35   \\
 \hline
@@
 %% (S/(n-m)) (X^T X)^{-1}
+%egin{comment} 
 \begin{figure}%[h!]
@@
 	for the data listed in Table~\ref{tab:CaRecComparison}.  
-	$\lambda$ = $\eta$ = 1.0 $\times$ $10^{-3}$, $0.3<Ca<1$, and
+	$\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
         the initial/boundary conditions are given by (\ref{IC_BC}).
@@
 was explored numerically using the CLSVOF computational method.  In this study,
-the critical Reynolds number $Re_{c}$, at which bubble breakup first occurs,
+the critical Reynolds number $Re_{\rm c}$, at which bubble breakup first occurs,
 was determined for several flow conditions, and the differences between bubble
@@
 doglegged shape formation stage.  In bubble deformation without breakup, near
-$Re_{c}$, the bubble did not maintain a stable deformed shape, in contrast to
+$Re_{\rm c}$, the bubble did not maintain a stable deformed shape, in contrast to
 drop deformation near the critical Reynolds number.  The bubble exhibited

### 2023-12-29 Reply-Reviewer2.tex
paper updates

--- 2023-07-16 Reply-Reviewer2_EdwinEdited_26Jun2023.tex
@@
 %  -----------------------------------------------------------------------------
-%  Modified: 26 June 2023
+%  Modified: 17 December 2023
 %  -----------------------------------------------------------------------------
@@
 \\
-Please see the 1st line from the top in ``III. A. Numerical method and governing equations''.
+Please see the 1st line from the top in ``I\hspace{-1.2pt}I\hspace{-1.2pt}I. A. Numerical method and governing equations''.
 \\
@@
 Though there are differences between previous studies and our study, 
-we think a major cause of differences is attributable to the grid size (Renardy: $\Delta x =R/8$, our study: Renardy: $\Delta x =R/16$) 
-as we mentioned in the paper.
-As a quantitative comparison (regarding Question \#9), we have added a
-comparison for bubble deformation to Fig. 3.  We confirmed the validity of our
-computations with regard to bubble deformation.\\
-{\color{blue}  Mark: I am still computing bubble deformation for an additional comparison}
+we think a major cause of differences is attributable to the grid size 
+(Renardy: $\Delta x =R/8$, our study: Renardy: $\Delta x =R/16$) as we 
+mentioned in the paper.
+{\color{red}
+%As a quantitative comparison (regarding Question \#8), we have newly made a
+%comparison for bubble deformation as Table I\hspace{-1.2pt}I. 
+We present a new quantitative comparison, in terms of the Taylor deformation
+parameter $D$ as a function of $Ca$, in Table I\hspace{-1.2pt}I for bubble
+deformation.  Note that it took several months to obtain additional
+computational results for bubble deformation.  Comparisons of our results
+against past studies (summarized in Table I\hspace{-1.2pt}I) support the
+validity of our bubble deformation computations.
+%We confirmed the validity of our computations about bubble deformation.
+}
 \\
@@
 $\eta$ (viscosity ratio) $\simeq 0$. In some cases, computational times
-over a month long were required.  To overcome the problem of very long
+over a few months long were required.  To overcome the problem of very long
 computational times, various computational countermeasures were employed in
@@
 drop/bubble) was employed to reduce the number of computational grid
-points.  As shown in Table I\hspace{-1.2pt}I in this study, using a width of $W =
+points.  As shown in Table I\hspace{-1.2pt}I\hspace{-1.2pt}I in this study, using a width of $W =
 2D$ accentuates drop deformation. Regarding the grid size, relatively coarse
@@
 \medskip
-
 Komrakova et al. (CES, 2015) and Zhang et al. (CES, 2021) used a LBM method for
@@
 Additional grid refinements may be desirable to perform further accuracy
-evaluations for bubble deformation and breakup. \\ (see the last line at the
-section “B.  Validation of the numerical method”, Page 5) Regarding the
-refinement level of AMR, the use of 3-4 consecutive refinement levels is not
+evaluations for bubble deformation and breakup.  (see the last line at the
+section “C. Consideration of domain and grid sizes”, Page 9)
+
+Regarding the refinement level of AMR, the use of 3-4 consecutive refinement levels is not
 always preferred.  A small refinement level is rather suitable in terms of
@@
 reasonable.
-{\color{blue}  Mark: please  write the type of time discretization.}
+
+{\color{red}
+We briefly described the type of time discretization, the temporal discretization, 
+and the algorithm of our numerical method. Also, we have added information 
+on our paper as a reference to obtain more details about the numerical method used in 
+this study.}
 \\
@@
 Response: \\
-{\color{blue}  Mark: I am still computing bubble deformation for an additional comparison}
+{\color{red} 
+%As a quantitative comparison, we have newly made a comparison for bubble 
+%deformation as Table I\hspace{-1.2pt}I:
+We added a new quantitative comparison for bubble deformation in Table
+I\hspace{-1.2pt}I to verify the validity of our computational results; in the
+table we compare against the experimental results of Muller-Fischer et al.
+(Experiments in fluids, 2008) and Rust and Manga (Journal of Colloid and
+Interface Science, 2002). The new numerical results for bubble deformation
+indicate that our computations are consistent with past studies.
+%We believe that the effectivity of our computations could be proved for bubble deformation.
+}
 \\
@@
 Response: \\
-Regarding Question \#12, we have made a new figure for the case of $Re$ = 50
-and $Ca$ = 0.3.  As is obvious from the new figure, bubble reaches a final
-steady shape, when the condition of $Re$ number is much smaller than the
-critical $Re$ number ($Re_{\rm c}$). The results show that the bubble is largely
-elongated and contracts to a doglegged shape when the $Re$ number is close to
-$Re_{\rm c}$)..........\\
-{\color{blue}  Mark: I will add these discussions after making a new figure.}
-
-Moreover, the main object of this study is to find $Re_{\rm c}$; we have plans
-for examining bubble periodic deformation with expansion and contraction in
-future work.  In ongoing and upcoming work, we will examine the effect of
+{\color{red}  
+Regarding Question \#12, we have made a new figure (shear stress profile) for
+the case of $Re$ = 50 and $Ca$ = 0.3.  In the case of $Re$ = 50, the bubble
+finally settles into a steady deformed shape. Additionally, we observed a
+steady deformed bubble at the $Re$ = 70 (not presented in this paper).  As
+discussed in detail in the new Section~I\hspace{-1.2pt}V.C, in the limit, as the value of $Re$
+approaches the critical $Re_{\rm c}$ condition, the bubble does not maintain
+its deformed state but instead alternates in an elongation and contraction
+process.  
+%It can be expected the bubble will be in a steady deformed state when the 
+%condition of $Re$ number is smaller than the critical $Re$ number ($Re_{\rm c}$),  
+%whereas the bubble is largely elongated and contracts to a doglegged 
+%shape when the $Re$ number is close to $Re_{\rm c}$.\\
+} Moreover, the main object of this study is to find $Re_{\rm c}$; we have
+plans for examining bubble periodic deformation with expansion and contraction
+in future work.  In ongoing and upcoming work, we will examine the effect of
 $\lambda$ and $\eta$ on drop breakup for some combinations of $\lambda$ and
@@
 low $Ca$ numbers.  Following the suggestion from the reviewer 1, we have added
-a drop breakup critical curve ($\lambda$ = $\eta$ =1.0) to Fig. 11.  The
-difference in $Re_{\rm c}$ number between the bubble and the drop is clearer in
-the new Fig. 11.  But, the reviewer's opinion is appropriate, and we have added
-the following supplementary statement: In future work, we will determine the $Re_{\rm c}$
-for a variety of high $Ca$ numbers to construct a detailed critical curve for a wider
-range of $Ca$ numbers.\\
+a drop breakup critical curve ($\lambda$ = $\eta$ =1.0) to Fig. 12 (former Fig. 11).  
+The difference in $Re_{\rm c}$ number between the bubble and the drop is clearer in
+the new Fig. 12.  But, the reviewer's opinion is appropriate. 
+In future work, we will determine the $Re_{\rm c}$ for a variety of high $Ca$ numbers 
+to construct a detailed critical curve for a wider range of $Ca$ numbers.\\
 
@@
 Response: \\
-{\color{blue}  Mark: I have finished an additional computation for showing property differences, and I am making a new figure.}
+{\color{red}
+We agree with reviewer's comment. In response, we have added two new images of the
+shear stress profile for a bubble for two $Re$ conditions in Fig. 8.
+A discussion of the new results, in terms of the shear stresses acting on the
+bubble at the two different conditions, is given in Section~I\hspace{-1.2pt}V.C. 
+}
 \\

### 2023-12-29 Bubble-deformation.tex
paper updates

@@
 %  
-%  Modified: 22 December 2022
+%  Modified: 17 December 2023
 %  -----------------------------------------------------------------------------
@@
 Numerical simulations for the deformation and breakup of a bubble in liquids
-undergoing simple linear shear flow are presented.  Computational results are
+undergoing simple linear shear flow are presented.  Numerical results are
 obtained using a hydrodynamic scheme with formal second-order accuracy based on
@@
 due to its fundamental importance in connection with emulsion and materials
-processing, mixing and reaction devices. The pioneering experimental work
-of this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34},
+processing, mixing and reaction devices. The pioneering experimental work of
+this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34},
 and the subsequent theoretical and experimental progress up to the 1980s and
@@
 direct simulations of this problem.  In particular, detailed computational
-investigations of drop breakup, 
-based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were
-presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.  
-Since then, the literature on computational
-studies on the deformation and breakup of a single or several drops in shear
-flow has continued to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06,
-BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16,
+investigations of drop breakup, based on a Volume-of-Fluid (VOF) method
+\cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2,
+RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.  Since then, the literature on
+computational studies on the deformation and breakup of a single or several
+drops in shear flow has continued to grow \cite{CriGuiAlfBlaLoe03,
+InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08,
+CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16,
 HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques
@@
 approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06,
-KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and 
-{\color{red} interface-capturing }
-level set methods \cite{SusSmeOsh94}.
-
-{\color{red} In contrast, only a few computational studies on bubble deformation and breakup in
-shear flow can be found \cite{WeiQiaXu12,WanShiZha15}. 
-In these previous studies, the dynamics of bubble 
-deformation in shear flow has mainly been exmained.}
-{\color{blue} What distinguishes our work from that in 
-\cite{WeiQiaXu12,WanShiZha15}?}
-This type of bubble dynamics in shear flow is of critical importance for a variety of
-scientific and engineering processes. We refer the reader to the 
+KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and {\color{red}
+interface-capturing} level set methods \cite{SusSmeOsh94}.  {\color{red} In
+contrast, only a few computational studies on bubble deformation and breakup in
+shear flow can be found \cite{WeiQiaXu12,WanShiZha15}.  In these previous
+studies, the dynamics of bubble deformation in shear flow has mainly been
+examined.} {\color{blue} Concerning bubble breakup, Wei et
+al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup
+process under the condition of $Ca$ (Capillary number) = 35.}
+% {\color{blue} What distinguishes our work from that in
+% \cite{WeiQiaXu12,WanShiZha15}?}
+This type of bubble dynamics in shear flow is of critical importance for a
+variety of scientific and engineering processes. We refer the reader to the
 following experimental studies relating to bubble deformation in foaming
-processes, microfluidic devices, and micro bubbles in the blood 
-circulation system,\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.
-In particular, it is the study of bubble deformation as it pertains
-to high performance plastics applications which motivates this work.  
-In this article, we present
-computational studies of shear-driven deformation and breakup of a bubble in
-insoluble viscous liquids.  
-Studying bubble break-up via computation rather
-than experiments simplifies the process of setting a combination of
+processes, microfluidic devices, and micro bubbles in the blood circulation
+system,\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.
+In particular, it is the study of bubble deformation as it pertains to high
+performance plastics applications which motivates this work.  In this article,
+we present computational studies of shear-driven deformation and breakup of a
+bubble in insoluble viscous liquids.  Studying bubble break-up via computation
+rather than experiments simplifies the process of setting a combination of
 precise simple shear flow conditions, low $Ca$ conditions, low density ratio,
-and low viscosity ratios.
-The physical properties that distinguish bubble and
-drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} /
-\rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the
-fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote
-the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a
-bubble in an insoluble viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, 
-whereas most studies dealing with a drop
-in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
+and low viscosity ratios.  The physical properties that distinguish bubble and
+drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm
+b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$,
+where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts
+``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'',
+respectively.  For a bubble in an insoluble viscous liquid, $\lambda \simeq 0$
+and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible
+viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
 
@@
 Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
-a function of the Capillary number ($Ca$). 
+a function of $Ca$. 
 The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
@@
 {\color{red} In previous studies on the motion of bubble deformation
-in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, 
-only findings for bubble defomation under very low $Re$ 
-number conditions have been reported.}
-{\color{blue} What were the $Re$ conditions considered by 
-\cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions 
-considered in our paper?}
-In this work we determine, for the first time, the critical Reynolds number that leads to \emph{bubble}
-breakup.  Additionally, our computational studies reveal characteristics that
+in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble defomation under very low 
+$Re$ number conditions ({\color{blue} $Re \ll 1$}) have been reported.}
+%{\color{blue} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
+In this work we determine, for the first time, the critical Reynolds number ({\color{blue} $Re \gg 1$}) 
+that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
 distinguish the deformation and breakup processes of a drop versus those of a bubble.
@@
 
-When comparing with previous drop studies, we fix
-$\lambda=1$.  As a result, (for $\lambda=1$) the
-following dimensionless physical parameters are used to describe the problem of
-drop deformation/breakup in shear flow
+When comparing with previous drop studies, we fix $\lambda=1$.  As a result,
+(for $\lambda=1$) the following dimensionless physical parameters are used to
+describe the problem of drop deformation/breakup in shear flow
 %
@@
 %
-$U$ is the velocity scale and $\sigma$ denotes the surface tension. 
-For the problem of shear-induced drop deformation and breakup, 
-the velocity is set to 
-$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  
-As mentioned in the introduction, most previous drop studies set 
-$\eta = 1$\cite{?}. 
-Thus, for comparison with previous drop deformation and breakup problems,
-we set $\lambda = \eta = 1$ (and also neglect the 
-effect of gravity so that $g=0$). On the other hand, in 
-our computations for bubble deformation, 
-we set the density and viscosity of air to be
-$\rho_{\rm b}$ = 1.2 kg/m$^{3}$ and $\mu_{\rm b} = 1.8
-\times 10^{-5}$ Pa$\cdot$s respectively.
-We emphasize that for consistency with previous studies, 
-{\color{blue} cite some of these previous studies which examine deformation
-and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
-we computationally examine the
-deformation and breakup of a bubble in simple linear shear flow as a 
-function of the $Re$ and $Ca$ numbers. 
-{\color{red} That is to say, by setting $g=0$, we are isolating the
-effect of only varying $Re$ and $Ca$ on bubble 
-deformation and breakup.  In our controlled study, we determine 
-the critical $Re_{\rm c}$ versus $Ca$ curve 
-in which $Re_{\rm c}$ corresponds to the threshold of 
-bubble (or drop) breakup.  
-We determine the
-critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the
-density ratio and viscosity ratio. }
-
-{\color{red} In our computations, the density of the matrix fluid 
-is fixed at
+$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
+problem of shear-induced drop deformation and breakup, the velocity is set to
+$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
+mentioned in the introduction, most previous drop studies set $\eta =
+1$\cite{?}.  Thus, for comparison with previous drop deformation and breakup
+problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
+so that $g=0$). On the other hand, in our computations for bubble deformation,
+we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$
+and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize
+that for consistency with previous studies (\cite{LiRenRen00, RusMan02,
+MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
+%{\color{blue} cite some of these previous studies which examine deformation
+%and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
+we computationally examine the deformation and breakup of a bubble in simple
+linear shear flow as a function of the $Re$ and $Ca$ numbers.  {\color{red}
+That is to say, by setting $g=0$, we are isolating the effect of only varying
+$Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we
+determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$
+corresponds to the threshold of bubble (or drop) breakup.  We determine the
+critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density
+ratio and viscosity ratio. }
+
+{\color{red} In our computations, the density of the matrix fluid is fixed at
 $\rho_{\rm m}$ = 1000 kg/m$^3$.  The surface tension at the bubble (drop)
-interface is $\sigma =2.5 \times 10^{-2}$ N/m.
-The values of $Re$ and $Ca$ in our simulations are controlled by
-changing the values of $\mu_{\rm m}$ and $V$.
-For studying bubble deformation and break-up, 
-the density and viscosity ratios satisfy 
-$\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.}
+interface is $\sigma =2.5 \times 10^{-2}$ N/m.  The values of $Re$ and $Ca$ in
+our simulations are controlled by changing the values of $\mu_{\rm m}$ and $V$.
+For studying bubble deformation and break-up, the density and viscosity ratios
+satisfy $\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.}
 
@@
 Numerical results were obtained using the {\color{red} interface capturing}
-Coupled Level Set and Volume of Fluid (CLSVOF) 
-method \cite{SusPuc00,SUSSMAN2007469},
-which is based on a fixed grid finite volume algorithm.  
-{\color{red}The CLSVOF method is a robust  numerical  technique  
-that  combines  some  of  the  advantages  of 
-the Volume of Fluid (VOF) method (\cite{HirNic81}) 
-and the Level Set (LS) (\cite{SusSmeOsh94}) method
-while overcoming their weaknesses. 
-In the VOF method,  the Volume Fraction function, $F$, is used to 
-represent the interface. The values of $F$ correspond 
-to the volume fraction of liquid in a given computational cell. 
-In other words, $F = 0$ when a computational cell contains 
-only gas and $F = 1$ when a computational cell contains only liquid. 
-If $0 < F < 1$, then a computational cell contains 
-the gas-liquid interface. The VOF method has a great advantage 
-over the LS method in that accurate algorithms for 
-advecting $F$ can be applied
-so that mass/volume is conserved up to machine precision
-while still maintaining a sharp representation of the interface. 
-On the other hand, the disadvantage of the VOF method in comparison
-to the LS method 
-is that tangled and difficult reconstruction procedures are required 
-for determining the slope of the piecewise linear VOF reconstructed interface.
-In the LS method, the signed distance function $\phi$ (LS function) 
-is used to track the interface. The interface is implicitly 
-represented by the set of points in which $\phi = 0$. 
-Liquid and gas regions are defined as $\phi > 0$ in the 
-liquid and $\phi < 0$ in the gas, respectively.  
-One of the advantages of the LS method is that one can track and represent 
-smoothly the interface, but the LS method has the disadvantage 
-that mass/volume is not explicitly conserved. 
-In the CLSVOF method, the coupling between the LS function 
-and the VOF function occurs when computing the normal of the reconstructed 
-interface in the VOF calculation process and also when assigning 
-the LS function with the exact signed normal distance to the reconstructed 
-interface in the LS calculation process. That is to say, the 
-piecewise linear approximation (the volume-of-fluid reconstruction step) 
-for the 
-VOF method is determined using the unit normal vector ($\bm n$) 
-estimated from information of the LS function. By taking 
-advantage of both 
-methods, the evolution of the liquid–gas interface location can be
-computationally captured in such a way so that volume/mass is preserved
-to machine precision and at the same time,
-the interface normals and the surface tension force 
-(which is proportional
-to the interface curvature) can be straightforwardly derived from the
-smooth level set function. }
+Coupled Level Set and Volume of Fluid (CLSVOF) method
+\cite{SusPuc00,SUSSMAN2007469}, which is based on a fixed grid finite volume
+algorithm.  {\color{red}The CLSVOF method is a robust  numerical  technique
+that  combines  some  of  the  advantages  of the Volume of Fluid (VOF) method
+(\cite{HirNic81}) and the Level Set (LS) (\cite{SusSmeOsh94}) method while
+overcoming their weaknesses.  In the VOF method,  the Volume Fraction function,
+$F$, is used to represent the interface. The values of $F$ correspond to the
+volume fraction of liquid in a given computational cell.  In other words, $F =
+0$ when a computational cell contains only gas and $F = 1$ when a computational
+cell contains only liquid.  If $0 < F < 1$, then a computational cell contains
+the gas-liquid interface. The VOF method has a great advantage over the LS
+method in that accurate algorithms for advecting $F$ can be applied so that
+mass/volume is conserved up to machine precision while still maintaining a
+sharp representation of the interface.  On the other hand, the disadvantage of
+the VOF method in comparison to the LS method is that tangled and difficult
+reconstruction procedures are required for determining the slope of the
+piecewise linear VOF reconstructed interface.  In the LS method, the signed
+distance function $\phi$ (LS function) is used to track the interface. The
+interface is implicitly represented by the set of points in which $\phi = 0$.
+Liquid and gas regions are defined as $\phi > 0$ in the liquid and $\phi < 0$
+in the gas, respectively.  One of the advantages of the LS method is that one
+can track and represent smoothly the interface, but the LS method has the
+disadvantage that mass/volume is not explicitly conserved.  In the CLSVOF
+method, the coupling between the LS function and the VOF function occurs when
+computing the normal of the reconstructed interface in the VOF calculation
+process and also when assigning the LS function with the exact signed normal
+distance to the reconstructed interface in the LS calculation process. That is
+to say, the piecewise linear approximation (the volume-of-fluid reconstruction
+step) for the VOF method is determined using the unit normal vector ($\bm n$)
+estimated from information of the LS function. By taking advantage of both
+methods, the evolution of the liquid-gas interface location can be
+computationally captured in such a way so that volume/mass is preserved to
+machine precision and at the same time, the interface normals and the surface
+tension force (which is proportional to the interface curvature) can be
+straightforwardly derived from the smooth level set function. }
 
@@
 method.  First, we compare quantitatively against the steady-state drop
-deformation results reported by Li et al.~\cite{LiRenRen00}.  The shape of a
+deformation results reported by Li et al. \cite{LiRenRen00}.  The shape of a
 deformed drop in simple linear shear flow is described in terms of the Taylor
 deformation parameter {\color{red} $D$}=$(a-b)/(a+b)$, 
-where $a$ and $b$ are the major and
-minor axes of the deformed drop.  For consistency, we perform numerical
-simulations using CLSVOF over the same computational domain and grid size used
-in~\cite{LiRenRen00}, which has dimensions $\lwh{8}{4}{8}$ (recall that $R$ is
+where $a$ and $b$ are the major and minor axes of the deformed drop.  
+For consistency, we perform numerical simulations using CLSVOF over the same
+computational domain and grid size used in~\cite{LiRenRen00}, which has dimensions 
+$\lwh{8}{4}{8}$ (recall that $R$ is
 the bubble/drop radius) and a level-0 grid size $\Delta x=\Delta y=\Delta
@@
 results are listed in Table~\ref{tab:DeComparison} for {\color{red} $D$} 
-as a function of
-$Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
+as a function of $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
 the VOF method used in \cite{LiRenRen00}, and also with our CLSVOF algorithm.
@@
 \end{table}
-%
+
+%Testing author name~\citeauthor{MulTobDreFisWin08}
+
+%% Ohta
+{\color{blue} Next, we examine the validation of our computational method
+intended for the bubble deformation in simple linear shear flow reported by
+Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
+al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
+deformation under the condition of $Re \approx 0$. In this study, using the
+computational domain with $\lwh{12}{6}{6}$ and the finer grid size with $\Delta
+x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$, computations were
+performed for the condition of $Ca = 0.96$ and  1.63 with $Re \approx 0$ ($Re =
+5.0 \times 10^{-4}$),  $\lambda = 1.2 \times 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$
+according to experimental conditions by Muller-Fischer et al.
+\cite{MulTobDreFisWin08}.  Comparison of our numerical results and previous
+experimental results (\cite{MulTobDreFisWin08}) are tabulated in
+Table~\ref{tab:DeComparisonRe=0}.  Additionally, in
+Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
+condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by Rust and
+Manga (\cite{RusMan02}). These experimental values by Rust and Manga
+(\cite{RusMan02}) were obtained from the graph showing the relation of $D$ vs
+$Re$ (\cite{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
+numerical results predicted larger values of $D$ than experimental ones
+reported by Muller-Fischer et al.~\cite{MulTobDreFisWin08}. Nevertheless, we
+found that our numerical results are very close to the experimental results by
+Rust and Manga (\cite{RusMan02}), which emphasizes the intrinsic difficulties
+associated with experimental investigations of bubble dynamics, even in simple
+linear shear flow.  These comparisons suggest that our computational method is
+effective and robust at reproducing bubble dynamics in simple linear shear
+flow.}
+
+%%
+\begin{table}[tbh]
+{\color{blue}
+\caption{Comparison of  {\color{red} $D$} for a bubble as a function 
+         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). In all cases, the domain 
+         size is $\lwh{12}{6}{6}$.
+         CLSVOF computations used a two-level AMR computational domain 
+         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
+         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
+         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
+ }
+\label{tab:DeComparisonRe=0}
+%\footnotesize
+\center
+\begin{tabular}{ c  c  c  c  c }
+\hline
+\hline
+Capillary number                                                                 & 0.96   &  1.63       \\
+{$D$}(Muller-Fischer et al. (\cite{MulTobDreFisWin08}))   & 0.37   &   0.58     \\
+{$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
+{$D$}(Our study)                                              & 0.63   &   0.76     \\
+\hline
+\hline
+\end{tabular}
+\end{table}
+%%
+
+%%%%
 %\begin{comment} 
@@
 
-Next, we present a comparison with numerical results for drop breakup reported
+Finally, we present a comparison with numerical results for drop breakup reported
 in~\cite{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop breakup
@@
 used in our study in the level-1 grid around the elongated drop.
-{\color{red} The numerical
-validation studies performed in this section and the following section
-demonstrate that our numerical
-method can reliably determine the transition regions at which shear-induced
-bubble or drop deformation leads to breakup.  We remark that in the next
-section, we demonstrate that we can expect an error of $\%3$ for predicting
-the transition to break-up.  The analysis in this section and the
-following also demonstrate that the error is reduced by a factor of 2 each
-time the grid is refined by a factor of 2. Also, we refer the
-reader to \cite{ohta2011robust} in which we apply our 
-CLSVOF method for bubble formation
-problems. }
+
+{\color{red} The numerical validation studies performed in this section and the
+following section demonstrate that our numerical method can reliably determine
+the transition regions at which shear-induced bubble or drop deformation leads
+to breakup.  We remark that in the next section, we demonstrate that we can
+expect an error of $3\%$ for predicting the transition to break-up.  The
+analysis in this section and the following also demonstrate that the error is
+reduced by a factor of 2 each time the grid is refined by a factor of 2. Also,
+we refer the reader to \cite{ohta2011robust} in which we apply our CLSVOF
+method for bubble formation problems.}
 
@@
 essential dynamical features.
+{\color{red} Additional grid refinements may be desirable to perform further 
+accuracy evaluations for bubble deformation and breakup.}
 
@@
 
+%% Ohta
+{\color{blue} 
+\subsection{Shear stress acting on the bubble}
+%  -----------------------------------------------------------------------------
+%
+%\begin{comment} 
+\begin{figure}%[h!]
+  \centering
+  \includegraphics[width=\textwidth]{ShearStress}
+  \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for two Reynolds 
+           numbers under the condition of $Ca = 0.3$. The left image shows the 
+           shear stress profile at $Re=50$ and the right image at $Re=93$.
+	   }
+  \label{fig:ShearStress}
+\end{figure}
+%\end{comment} 
+%
+In the previous section, the appearance of bubble deformation and breakup was
+discussed. It is expected that a large deformation and breakup of the bubble
+are closely related to the state of shear stress acting on the bubble.
+Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble,
+for two Reynolds numbers under the condition of $Ca = 0.3$.  The shear stress
+profile on the left corresponds to the case of $Re = 50$ and the right side
+shows the shear stress profile for the case of $Re = 93$.  The normalized shear
+stress $\tau^{\ast} = \tau / \tau_{0}$ is defined as a ratio of the local shear
+stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress
+$\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  In this study, for a given $Ca$
+condition, the same value of $\tau_{0}$ is used regardless of $Re$. For the
+case of $Re = 50$, the bubble reaches a deformed stable state.  As observed in
+previous sections, when the value of $Re$ is slightly below the critical $Re$
+condition, the bubble does not settle into a deformed stable state but instead
+alternates in an elongation and contraction process.  In comparison, the right
+image in Fig.~\ref{fig:ShearStress} shows a higher shear stress profile near
+the bubble endpoints for the case of $Re = 93$ as it undergoes an elongation
+state in the process toward breakup.  The value of the maximum shear stress for
+the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ and the maximum shear stress
+for the case of $Re = 93$ at the moment shown in Fig.~\ref{fig:ShearStress} has
+the value of $\tau ^{\ast} \approx 8$.  The shear stress profile of in
+Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from $\tau
+^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions
+with $\tau ^{\ast} \geqq 6$ are illustrated in red.  As can be seen in the
+figure, the strongest shear stresses are concentrated on the ends of the bubble
+for both $Re$ conditions.  This indicates that the strong shear stresses acting
+on the ends of the bubble are responsible for much of the bubble stretching.
+It is important to note that the magnitude of the shear stress acting on the
+ends of the bubble for the case of $Re = 93$ is much larger than that for the
+case of $Re = 50$.  On the other hand, the shear stress inside the bubble was
+very small relative to that of the matrix fluid due to very small density and
+viscosity of the bubble.  Since the force of strong shear stresses acting on
+the ends of the bubble is difficult to transfer across the interface, as a
+consequence, a sufficiently large $Re$ condition is required for large bubble
+deformations.  }
+
 \subsection{Velocity field outside and inside the breaking bubble}
@@
 %
-%egin{comment} 
+%\begin{comment} 
 \begin{figure}%[h!]
@@
 %
-%egin{comment}
+%\begin{comment} 
 \begin{figure}%[h!]
@@
 
-Table~\ref{tab:CaRecComparison} 
-lists, for representative $Ca$ values,
-the corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced 
-bubble breakup.  The data in 
-Table~\ref{tab:CaRecComparison} 
-corresponds to $\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
-the initial/boundary conditions are given by (\ref{IC_BC}).
-The results in Table~\ref{tab:CaRecComparison}
-indicate that sufficiently large shear forces are required for bubble breakup even for large Capillary numbers. 
-In Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in Table~\ref{tab:CaRecComparison} and 
-make the hypothesis that given a new data point, $(Ca,Re)$,  shear induced bubble break up will occur if the point $(Ca,Re)$ 
-is above the given critical curve, and the bubble will not break if the $(Ca,Re)$ pair is below the critical curve.
-{\color {red} For comparison purpose, a drop critical curve with $\lambda =\eta = 1$ is also indicated in Fig.~\ref{fig:CaRecFit}.
-From Fig.~\ref{fig:CaRecFit}, it is recognized that the difference between both critical curves is 
-Hereafter, we will settle $Re_{\rm c}$ numbers for the condition of 
-high $Ca$ numbers to determine a general critical curve 
-for a wide range of $Ca$ numbers.}
-{\color{blue} it seems like the above passage is still a work in progress?}
-
-%
+Table~\ref{tab:CaRecComparison} lists, for representative $Ca$ values, the
+corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced bubble
+breakup.  The data in Table~\ref{tab:CaRecComparison} corresponds to $\lambda =
+1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and the
+initial/boundary conditions are given by (\ref{IC_BC}).  The results in
+Table~\ref{tab:CaRecComparison} indicate that sufficiently large shear forces
+are required for bubble breakup even for large Capillary numbers.  In
+Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in
+Table~\ref{tab:CaRecComparison} and make the hypothesis that given a new data
+point, $(Ca,Re)$,  shear induced bubble break up will occur if the point
+$(Ca,Re)$ is above the given critical curve, and the bubble will not break if
+the $(Ca,Re)$ pair is below the critical curve.  {\color {red} For comparison,
+a critical curve for the drop with $\lambda =\eta = 1$ is also indicated in
+Fig.~\ref{fig:CaRecFit}.  The inclusion of breakup and no-breakup critical
+curves, for both the drop and the bubble, will facilitate future identification
+of $Re_{\rm c}$ numbers---and thus a more complete general critical curve---for
+a wide range of high $Ca$ numbers.  }
+%{\color{blue} it seems like the above passage is still a work in progress?}
+% Yes. I have been suspending computations for bubbles because I have been focussing on non-Newtonian cases, but I have a plan for restarting again.
+
 \begin{table}[tbh]
@@
 %% (S/(n-m)) (X^T X)^{-1}
-%egin{comment} 
+%\begin{comment} 
 \begin{figure}%[h!]
   \centering
-  \includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
+  %\includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
+  \includegraphics[width=\textwidth]{CaRecFit}
   \caption{A plot of the critical Reynolds number versus Capillary number

### 2023-12-31 Reply-Reviewer2.tex
paper mods

@@
 \begin{enumerate}
-
+%%1
 \item
@@
 
+%%2
 \par\noindent
@@
 
+%%3
 \par\noindent
@@
 Response: \\
-We have added the direction of gravity in Fig. 1. Regarding the setting of
-gravity in this study, we will describe it in our response for Question \#9. 
+We have added the direction of gravity in Fig. 1 ($z$ direction);
+albeit, we prescribe zero gravity in our simulations.  The rationale
+for setting gravity equal to zero is given in more detail in our response
+to item 9.  Essentially the purpose of this study is to do a controlled
+study of the effects of the density and viscosity ratios.  We can isolate
+the dependencies on these two ratios by prescribing zero gravity.  We now
+reference [3] and [4].
 \\
 
+%%4
 \par\noindent
@@
 
+%%5
 \par\noindent
@@
 
+%%6
 \par\noindent
@@
 
+%%7
 \par\noindent
@@
 
+%%8
 \par\noindent
@@
 
+%%9
 \par\noindent
@@
 In this flow system, the effect of gravity may not be completely negligible. However, in our computations, 
-we set $g = 0$ because we wanted to clearly manifest only the effect of density and viscosity ratios. 
-From another perspective, it can be said that we investigated phenomena in space.
+we set $g = 0$ because we wanted to clearly isolate only the effects of 
+the density and viscosity ratios. 
+From another perspective, it can be said that we investigated 
+phenomena in space.
 At the end of the Problem Description section, we added a detailed explanation about physical properties and conditions.

### 2023-12-31 Bubble-deformation.tex
paper mods

@@
 %
-The study of the deformation and breakup of a drop in immiscible viscous
+The study of the deformation {\em and breakup} of a drop in immiscible viscous
 liquids undergoing simple linear shear flow has been investigated extensively
@@
 KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and {\color{red}
-interface-capturing} level set methods \cite{SusSmeOsh94}.  {\color{red} In
-contrast, only a few computational studies on bubble deformation and breakup in
-shear flow can be found \cite{WeiQiaXu12,WanShiZha15}.  In these previous
-studies, the dynamics of bubble deformation in shear flow has mainly been
-examined.} {\color{blue} Concerning bubble breakup, Wei et
+interface-capturing} level set methods \cite{SusSmeOsh94}.  {\color{red} 
+In contrast, few computational studies on bubble 
+deformation {\em and breakup} can be found.  
+We remark that there has been a 
+number of articles on the study of lift of {\em slightly}
+deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
+We reiterate though, that for bubble deformation {\em and breakup} in
+shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15}.  
+In these previous
+studies, the dynamics (e.g. rotation angle) of bubble deformation 
+in shear flow was mainly examined.} 
+{\color{blue} Concerning bubble breakup, Wei et
 al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup
@@
 % \cite{WeiQiaXu12,WanShiZha15}?}
-This type of bubble dynamics in shear flow is of critical importance for a
+Bubble dynamics in shear flow, {\em including breakup},
+is of critical importance for a
 variety of scientific and engineering processes. We refer the reader to the
@@
 performance plastics applications which motivates this work.  In this article,
-we present computational studies of shear-driven deformation and breakup of a
+we present computational studies of shear-driven deformation 
+{\em and breakup} of a
 bubble in insoluble viscous liquids.  Studying bubble break-up via computation
@@
 mentioned in the introduction, most previous drop studies set $\eta =
-1$\cite{?}.  Thus, for comparison with previous drop deformation and breakup
+1$ (e.g. \cite{LiRenRen00}).  
+Thus, for comparison with previous drop deformation and breakup
 problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
@@
   \frac{1}{\rho}\nabla\cdot(-p\bmI+2\mu\bmD)+\bmg-
-  \frac{\sigma\kappa}{\rho}\nabla \Hea  \label{nseqn}
+  \frac{\sigma\kappa}{\rho}\nabla \Hea  
+  \label{nseqn}
 \end{align}
@@
  \end{eqnarray*}
-\item[Step 4. Pressure projection]
+\item[Step 4. Pressure projection and ghost fluid surface tension algorithm]
  \begin{eqnarray*}
@@
     \nabla\cdot(2\mu\bmD^{\ast})}{\rho})
+ \end{eqnarray*}
+ \begin{eqnarray*}
+ \bmV=\bmV-
+   \Delta t \frac{\sigma\kappa(\phi^{n+1})}{\rho}\nabla \Hea(\phi^{n+1}) 
  \end{eqnarray*}

### 2024-01-01 Reply-Reviewer2.tex
Need to reference Zhang Ni and Magnaudet

@@
 Response: \\
-We agree with the reviewer's opinion. We have changed the ``interface tracking''
+We agree with the reviewer. We have changed the ``interface tracking''
 wording to ``interface capturing method''.
@@
 Response: \\
-Thank you very much for your suggestion.  We have modified the definitions of
-$Re$ and $Ca$ because we had typos in the definitions of $Re$ and $Ca$.  The
-computations presented were performed using $Re$ and $Ca$ defined by the
+Thank you very much for catching this.  We have modified the definitions of
+$Re$ and $Ca$ accordingly; it was an accident that we had previously 
+defined these quantities in terms of the dispersed material.
+The computations presented were performed using $Re$ and $Ca$ defined by the
 density and the viscosity of the surrounding liquid.
@@
 for setting gravity equal to zero is given in more detail in our response
-to item 9.  Essentially the purpose of this study is to do a controlled
-study of the effects of the density and viscosity ratios.  We can isolate
-the dependencies on these two ratios by prescribing zero gravity.  We now
-reference [3] and [4].
+to item 9.  The purpose of our study is to do controlled
+numerical experiments on the effects of the density and 
+viscosity ratios.  We can isolate
+the dependencies on these two ratios by prescribing zero gravity.  Although
+[3] and [4] do not address the transition to break-up, they address a very
+much related aspect to bubble motion in shear flow, so now we cite them in
+the introduction.
 \\
@@
 Though there are differences between previous studies and our study, 
-we think a major cause of differences is attributable to the grid size 
+we think a major cause of the discrepancies is attributable to the grid size 
 (Renardy: $\Delta x =R/8$, our study: Renardy: $\Delta x =R/16$) as we 

### 2024-01-01 Bubble-deformation.tex
Need to reference Zhang Ni and Magnaudet

@@
   \caption{(a) Computational domain schematic for a bubble or drop in shear 
-           flow and (b) (\textit{upper panel}) a two-level adaptive mesh 
-           refinement (AMR) grid schematic with an actual computational 
-           example (\textit{lower panel}) of bubble deformation in simple linear 
-           shear flow.}
+           flow.  Gravity is set to zero in our computations in order to isolate
+           the effects of density and viscosity ratios.  
+           (b) (\textit{upper panel}) a two-level adaptive mesh 
+           refinement (AMR) grid schematic corresponding to one of our
+           simulations;
+           (\textit{lower panel}) snapshot of bubble deformation 
+           in simple linear shear flow.}
   \label{fig:SchemAndGrid}
@@
 \begin{description}
+\item[Timestep $\Delta t$] The timestep is governed by the CFL condition and
+  surface tension (section 5.7 of \cite{SUSSMAN2007469}):
+ \begin{eqnarray*}
+ \Delta t < \min_{i,j,k} \left( \frac{\Delta x}{2|U^{n}|},
+   \frac{1}{2}\sqrt{\frac{\rho^{L}}{8\pi\sigma}}\Delta x^{3/2}\right)
+ \end{eqnarray*}
+
 \item[Step 1. CLSVOF interface advection]

### 2024-03-30 Bubble-deformation.tex
incorporating new results

@@
 %% Ohta
-{\color{blue} Next, we examine the validation of our computational method
-intended for the bubble deformation in simple linear shear flow reported by
+{\color{blue} Next, we examine the validation of our computational method in which
+we compare with the ``bubble deformation in simple linear shear flow'' 
+results reported by
 Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
 al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
-deformation under the condition of $Re \approx 0$. In this study, using the
-computational domain with $\lwh{12}{6}{6}$ and the finer grid size with $\Delta
-x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$, computations were
-performed for the condition of $Ca = 0.96$ and  1.63 with $Re \approx 0$ ($Re =
-5.0 \times 10^{-4}$),  $\lambda = 1.2 \times 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$
-according to experimental conditions by Muller-Fischer et al.
-\cite{MulTobDreFisWin08}.  Comparison of our numerical results and previous
+deformation under the condition of $Re \approx 0$. In our study, using the
+computational domain with $\lwh{12}{6}{6}$ and the finer grid sizes with 
+(i)
+$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$, and
+(ii)
+$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/24$, 
+computations were
+performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
+with $Re \approx 0$ ($Re =
+5.0 \times 10^{-4}$),  
+$\lambda = 1.2 \times 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.
+The parameters that we have prescribed are consistent with the 
+experimental conditions by Muller-Fischer et al.
+\cite{MulTobDreFisWin08}.  
+Comparisons of our numerical results and previous
 experimental results (\cite{MulTobDreFisWin08}) are tabulated in
-Table~\ref{tab:DeComparisonRe=0}.  Additionally, in
+Table~\ref{tab:DeComparisonRe=0}.  
+Additionally, in
 Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
@@
 \caption{Comparison of  {\color{red} $D$} for a bubble as a function 
-         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). In all cases, the domain 
+         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
+	 In all cases, the domain 
          size is $\lwh{12}{6}{6}$.
@@
 {$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
-{$D$}(Our study)                                              & 0.63   &   0.76     \\
+{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.76     \\
+{$D$}(Our study $\Delta x^{\ell=1}=R/24$)  & 0.63   &   0.75     \\
 \hline
@@
   \centering
-  \includegraphics[width=\textwidth]{DeEvolution}
-  \caption{Time evolution of the deformation parameter {\color{red} $D$} versus 
-   a dimensionless
+%  \includegraphics[width=\textwidth]{DeEvolution}
+  \includegraphics[width=\textwidth]{Fig3-Comparison-of-De-New}
+  \caption{Time evolution of the deformation 
+   parameter {\color{red} $D$} versus 
+   dimensionless
    time $T = \mathit{\Gamma} t$ for a bubble, obtained 
-   with two grid systems at different resolutions. Both systems use a 
-   two-level AMR grid with a uniform 
-   finest-level grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = 
-   \Delta z ^{\ell=1}$. The evolution of {\color{red} $D$} using the first system, where
+   with three grid systems at different resolutions. All three resolutions 
+   use a two-level AMR grid with an effective fine resolution  
+   grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = 
+   \Delta z ^{\ell=1}$. 
+   The evolution of {\color{red} $D$} using the first system, where
+   $\Delta x^{\ell=1} = R/8$, is shown in blue and it predicts that 
+   bubble breakup occurs at a Reynolds number $Re=33$.
+   The evolution of {\color{red} $D$} using the second system, where
    $\Delta x^{\ell=1} = R/16$, is shown in black and it predicts that 
    bubble breakup occurs at a Reynolds number $Re=35$.
-   Results with the second system, shown in red, use $\Delta x^{\ell=1} 
+   Results with the third system, shown in red, use $\Delta x^{\ell=1} 
    = R/24$, and they predict that breakup occurs at $Re=34$.  The capillary
@@
 corresponds to the most deformable and stretchable bubble case considered in
-our numerical studies. We use two different grid systems, one with $\Delta
-x^{\ell=1}=R/16$ and another with $\Delta x^{\ell=1}=R/24$, to determine
+our numerical studies. We use three different grid systems, 
+(i) $\Delta x^{\ell=1}=R/8$,
+(ii) $\Delta x^{\ell=1}=R/16$,
+and 
+(iii) $\Delta x^{\ell=1}=R/24$, in order to determine
 $Re_{\rm c}$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the
-deformation parameter {\color{red} $D$} over time for the two grid systems; the $x$-axis is
-a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is {\color{red} $D$}.
+deformation parameter {\color{red} $D$} over time for the three grid systems; 
+the $x$-axis is
+a dimensionless time defined by $T=\mathit{\Gamma} t$ 
+and the $y$-axis is {\color{red} $D$}.
 The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system
 with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta
-x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  Note that although
-the time evolution of {\color{red} $D$} for the two grid systems is consistent for both
-resolutions (the predicted critical Reynolds numbers differ by $\sim 3\%$), the
+x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  
+For the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is too
+coarse in order to capture the proper break-up time, albeit the critical
+Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid resolution
+cases.
+Note that although
+the time evolution of {\color{red} $D$} for the two finer resolution
+systems ($R/16$ and $R/24$) is consistent between the two,
+(the predicted critical Reynolds numbers differ by $\sim 3\%$), the
 computational time using the grid system with $\Delta x^{\ell=1}=R/24$ was more

### 2024-03-31 Reply-Reviewer2.tex
updating paper and reviewer 2 responses

@@
 Please find enclosed the revised version of our manuscript (FZ10233):
-``Numerical Simulation of Bubble Deformation and Breakup under Simple Linear Shear Flows''
+``Numerical Simulation of Bubble Deformation and Breakup under 
+Simple Linear Shear Flows''
 We thank the reviewers for their comments and thoughts regarding improvement 
@@
 Response: \\
-Though there are differences between previous studies and our study, 
-we think a major cause of the discrepancies is attributable to the grid size 
-(Renardy: $\Delta x =R/8$, our study: Renardy: $\Delta x =R/16$) as we 
-mentioned in the paper.
-{\color{red}
-%As a quantitative comparison (regarding Question \#8), we have newly made a
-%comparison for bubble deformation as Table I\hspace{-1.2pt}I. 
-We present a new quantitative comparison, in terms of the Taylor deformation
-parameter $D$ as a function of $Ca$, in Table I\hspace{-1.2pt}I for bubble
-deformation.  Note that it took several months to obtain additional
-computational results for bubble deformation.  Comparisons of our results
-against past studies (summarized in Table I\hspace{-1.2pt}I) support the
-validity of our bubble deformation computations.
-%We confirmed the validity of our computations about bubble deformation.
-}
+We agree that there are ``small'' differences between the previous
+study by Renardy and Cristini [8] and our present study.  We claim
+that the major cause of the differences is that Renardy and
+Cristini [8] used a grid size of 
+$\Delta x=R/8$ 
+whereas in our case,
+the effective fine grid resolution had a grid size of 
+$\Delta x=R/16$.  We have made this more clear in the Figure 2 caption. 
+\par\noindent
+Also we have made quantitative comparisons for the Taylor deformation
+parameter $D$ in Table I (drop deformation) and our newly added Table II 
+(bubble deformation).  Note that it took 8 months to compute the results
+reported in our newly added Table II.  
+Comparisons of our results
+against past studies 
+(summarized in Tables I and II)
+support the
+validity of our bubble (and drop) deformation computations.
 \\

### 2024-03-31 Reply-Reviewer2.tex
cited Zhang et al, put in the explanation, getting close

@@
 Response: \\
-We agree that there are ``small'' differences between the previous
+We agree that there are several differences between the previous
 study by Renardy and Cristini [8] and our present study.  We claim
@@
 \par\noindent
-Also we have made quantitative comparisons for the Taylor deformation
-parameter $D$ in Table I (drop deformation) and our newly added Table II 
+We have made {\em quantitative} comparisons for the Taylor deformation
+parameter $D$ in Table I (drop deformation).  In the revision, we have
+added another table with {\em quantitative} comparisons.  Please
+refer to our newly added Table II 
 (bubble deformation).  Note that it took 8 months to compute the results
-reported in our newly added Table II.  
+reported in our new Table II.  
 Comparisons of our results

### 2024-03-31 Bubble-deformation.tex
cited Zhang et al, put in the explanation, getting close

@@
 {\color{red} In previous studies on the motion of bubble deformation
-in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble defomation under very low 
+in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low 
 $Re$ number conditions ({\color{blue} $Re \ll 1$}) have been reported.}
@@
   \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
+	\hspace{20pt} m=\mbox{matrix fluid}
 \end{eqnarray}
@@
 %% Ohta
-{\color{blue} Next, we examine the validation of our computational method in which
+{\color{blue} Next, we examine the validation of our 
+computational method in which
 we compare with the ``bubble deformation in simple linear shear flow'' 
@@
 al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
-deformation under the condition of $Re \approx 0$. In our study, using the
-computational domain with $\lwh{12}{6}{6}$ and the finer grid sizes with 
-(i)
-$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$, and
-(ii)
-$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/24$, 
-computations were
+deformation under the condition of $Re \approx 0$. 
+In our study, we computed
+the bubble deformation on a 
+computational domain with dimensions
+$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid 
+size was
+$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
+Computations were
 performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
-with $Re \approx 0$ ($Re =
-5.0 \times 10^{-4}$),  
-$\lambda = 1.2 \times 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.
+with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  
+$\lambda = 1.2 \times 10^{-3}$ and  
+$\eta \leq 1.2 \times 10^{-6}$.
 The parameters that we have prescribed are consistent with the 
@@
 {$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
-{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.76     \\
-{$D$}(Our study $\Delta x^{\ell=1}=R/24$)  & 0.63   &   0.75     \\
+{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.75     \\
+% 8 months compute time.
 \hline
@@
   \includegraphics[width=\textwidth]{DropBreakComparison}
-  \caption{Comparison with results reported in~\cite{RenCri01-2} (shown in boxes) 
-           for drop breakup in shear flow.  (The computational domain
-           dimensions $W=4R$ and $H=8R$ were fixed, while $L$ was changed depending 
-           on $Re$ and $Ca$ conditions, and the grid size was set to 
-           $\Delta x=\Delta y=\Delta z=R/8$.  Reprinted with permission from 
-           reference~\cite{RenCri01-2}. Copyright 2001, AIP Publishing). Results
+  \caption{Comparison with results reported 
+	in~\cite{RenCri01-2} 
+	(shown in boxes) 
+        for drop breakup in shear flow.  
+	In~\cite{RenCri01-2},
+	the computational domain
+        dimensions were 
+	$W=4R$, $H=8R$, and $L$ was varied depending 
+        on the $Re$ and $Ca$ conditions.  The
+	grid size 
+	in~\cite{RenCri01-2} 
+	was set to 
+        $\Delta x=\Delta y=\Delta z=R/8$.  
+	Reprinted with permission from 
+        reference~\cite{RenCri01-2}. 
+	Copyright 2001, AIP Publishing. 
+	Results
         obtained with our CLSVOF algorithm, corresponding to each case in
@@
         CLSVOF method used a two-level AMR computational domain 
-           with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
-           = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
+        with a level-0 discretization 
+	$\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$ 
+	and a level-1 discretization
         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$. 
@@
 \subsection{Consideration of domain and grid sizes}\label{sec:DomGrdSize}
-%  -----------------------------------------------------------------------------
+%  ------------------------------------------------------------------------
+
+\subsubsection{Selecting the appropriate domain size}
+
 The computational domain size used in numerical studies can affect the behavior
@@
 %
+
+\subsubsection{Selecting the appropriate grid size}
+
+{ \color{red}
+The grid size and adaptive meshing strategy that we adopt is chosen
+in order to answer the research question as to the conditions which determine
+whether a bubble in shear flow
+will break-up or not.  In such a case, we must accurately capture the 
+balance of forces with respect to the (non-local) force exerted from the 
+wall driven 
+flow acting against the interfacial
+surface tension force.  By nature of the research question, 
+the accuracy of the transition
+point for break-up depends intimately on the 
+largest Taylor Deformation parameter $D$
+that is supported by the grid (see e.g. Figures \ref{fig:ShearStress} and
+\ref{fig:BubBrkCa0p8Re43}).  
+As we report here, we have found that as
+long as the grid size is fine enough to support a Taylor Deformation parameter
+$D<0.95$, then the transition region 
+(see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit}) will be captured
+with a tolerance of three percent.  The simulation time becomes impractical
+if we were to try to further improve the tolerance.  A smaller tolerance
+would necessitate a longer supported Deformation
+parameter $D$ which would in turn necessitate a higher aspect ratio
+computational domain, increased droplet surface area at break-up,
+increased number of time steps, and higher resolution for representing the
+drop/bubble at its thinnest point.
+
+We make the distinction between our present research, and the research found
+in the work of Zang, Ni, 
+and Magnaudet\cite{zhang2021three,zhang2022three} on predicting the
+conditions for bubble mergers.  Even in the most extreme cases for
+mergers, the largest Deformation parameter never exceeds
+$0.4$ in \cite{zhang2021three}.  In summary, our gridding requirements 
+necessitate grid points distributed relatively evenly throughout the 
+computational domain when a bubble is stretched to a $0.9$ aspect ratio,
+whereas in \cite{zhang2021three} the gridding strategy necessitates 
+a localized strategy.
+
+}
 
@@
   \includegraphics[width=\textwidth]{ShearStress}
-  \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for two Reynolds 
+  \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for 
+	two Reynolds 
         numbers under the condition of $Ca = 0.3$. The left image shows the 
@@
 	for the data listed in Table~\ref{tab:CaRecComparison}.  
-	$\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
+	$\lambda = 1.2 \times 10^{-3}$, 
+	$\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and
         the initial/boundary conditions are given by (\ref{IC_BC}).
@@
 	given $(Ca,Re)$ pair will result in shear
-	induced bubble break-up or not.  
+	induced bubble break-up or not.  Note, for the ``Drop delineation
+	curve,'' $\lambda=\eta=1$.
 	   }

### 2024-04-01 Reply-Reviewer2.tex
reply to reviewer2

@@
 Response: \\
-First, we would like to emphasize to the reviewer that very long
-computational times are required for drop/bubble deformation and breakup in
-shear flow. For bubble simulations, in particular, even longer computational
-times are needed because the time step is much smaller than that for the drop.
-In our study, time steps smaller than values determined theoretically from
-various time-step constraints were used: the time step was $O(10^{-4}$) s for
-the drop and $O(10^{-5}$) s for the bubble.  In addition, it is especially difficult to
-solve stably two-phase flows with $\lambda$ (density ratio) $\simeq 0$ and
-$\eta$ (viscosity ratio) $\simeq 0$. In some cases, computational times
-over a few months long were required.  To overcome the problem of very long
-computational times, various computational countermeasures were employed in
-past studies. For example, in Renardy's study (Phys. Fluids, 2000) a domain
-size with $W$ (width ($y$-directional length)) = 2$D$ ($D$: diameter of
-drop/bubble) was employed to reduce the number of computational grid
-points.  As shown in Table I\hspace{-1.2pt}I\hspace{-1.2pt}I in this study, using a width of $W =
-2D$ accentuates drop deformation. Regarding the grid size, relatively coarse
-discretizations have been used in recent studies: $\Delta x =R/48$ (Komrakova et al.,
-CES, 2015), $\Delta x =2R/15, R/15, R/25, R/30$ (Hernandez and Rangel, Comput.
-Fluids, 2017), $\Delta x =R/15$ (Amania et al., CES, 2019), $\Delta x =R/30$
-(Zhang et al., CES, 2021).
+\par\noindent
+In response to the question ``In the present
+work, only two levels of refinement have been used, why?'', we added the 
+following text to our revision, (under the heading ``selecting the 
+appropriate grid size'')
+\par\noindent
 
-\medskip
-Komrakova et al. (CES, 2015) and Zhang et al. (CES, 2021) used a LBM method for
-two-phase flows, Hernandez and Rangel (Comput. Fluid., 2017) used a VOF method
-and Amania et al. (CES, 2019) applied a level set method to computations.
-Although Komrakova et al. (CES, 2015) set a higher grid resolution ($\Delta x
-=R/48$, which corresponds to $R$=48 lattice units in the LBM method), they
-performed computations over a quarter of the full domain, which is inappropriate
-for high $Re$ conditions.  In the study by Hernandez and Rangel (Comput.
-Fluids, 2017), it was shown that the grid resolution should be $\Delta x \leq
-R/15$ for approximately a 5\% error. Zhang et al. (CES, 2021) used a higher grid
-resolution ($R$=60 lattice units), but the height of the computational domain was
-$4R$ for 3D-computations.  Additionally, the LBM method (Komrakova et al.,
-CES(2015), Zhang et al., CES(2021)) allows the use of higher grid resolutions
-due to shorter computational times that result from not solving the continuity
-equation simultaneously; the decreased computational times come at the
-expense of diminished accuracy.
+{ \color{red}
+The grid size and adaptive meshing strategy that we adopt is chosen
+in order to answer the research question as to the conditions which determine
+whether a bubble in shear flow
+will break-up or not.  In such a case, we must accurately capture the 
+balance of forces with respect to the (non-local) force exerted from the 
+wall driven 
+flow acting against the interfacial
+surface tension force.  By nature of the research question, 
+the accuracy of the transition
+point for break-up depends on the 
+largest Taylor Deformation parameter $D$
+that is supported by the grid (see e.g. Figures 8 and 11).  
+As we report here, we have found that as
+long as the grid size is fine enough to support a Taylor Deformation parameter
+$D<0.95$, then the transition region 
+(see Figures 3 and 12) will be captured
+with a tolerance of three percent.  The simulation time becomes impractical
+if we were to try to further improve the tolerance.  A smaller tolerance
+would necessitate a longer supported Deformation
+parameter $D$ which would in turn necessitate a higher aspect ratio
+computational domain, increased droplet surface area at break-up,
+increased number of time steps, and higher resolution for representing the
+drop/bubble at its thinnest point.
 
-Our simulations were performed under stringent computational settings, in terms
-of domain sizes and grid resolutions, selected to guarantee a minimum accuracy
-in our numerical results.  The critical $Re$ numbers found from the bubble
-simulations presented in this study will provide a minimum standard for future
-studies.  Anticipating future increased computational resources and the
-development of new numerical algorithms, we have added the following comment:
-Additional grid refinements may be desirable to perform further accuracy
-evaluations for bubble deformation and breakup.  (see the last line at the
-section “C. Consideration of domain and grid sizes”, Page 9)
+We make the distinction between our present research, and the research found
+in the work of Zang, Ni, 
+and Magnaudet[47,48] on predicting the
+conditions for bubble mergers.  Even in the most extreme cases for
+mergers, the largest Deformation parameter never exceeds
+$0.4$ in [47].  In summary, our gridding requirements 
+necessitate grid points distributed relatively evenly throughout the 
+computational domain when a bubble is stretched to a $0.9$ Deformation,
+whereas in \cite{zhang2021three} the gridding strategy necessitates 
+a more localized strategy.
 
-Regarding the refinement level of AMR, the use of 3-4 consecutive refinement levels is not
-always preferred.  A small refinement level is rather suitable in terms of
-stable computations and we found that our mesh setting for this purpose was
-reasonable.
+}
 
-{\color{red}
-We briefly described the type of time discretization, the temporal discretization, 
-and the algorithm of our numerical method. Also, we have added information 
-on our paper as a reference to obtain more details about the numerical method used in 
-this study.}
-\\
+\par\noindent
+In response to the enquiry ``The mesh convergence
+study seems quite incomplete.  A more complete study with figures to verify it
+should be included in an appendix concerning the mesh and time step
+independence of the results.'', we have modified Figure 3 to report results
+for three different grid resolutions.  Figure 3 illustrates that we
+capture the proper break-up time as the grid is refined, and at the point
+where the critical Reynolds' number is prescribed.  In Figure 3,
+we point out that the time step was $O(10^{-5}$)s for the 
+elongating bubble! ($\Delta x=R/16$) Further refinements reduce the
+time step according to the surface tension time step constraint
+(see section III(A)).  We now report in the revision the temporal
+discretization of our method along with the timestep constraint.
+Since surface tension is discretized explicitly in time, the
+surface tension time step constraint is much more restrictive than
+the classical CFL time step constraint of $\Delta x/U$.
+(again see section IIIA).
 

### 2024-04-01 Bubble-deformation.tex
reply to reviewer2

@@
 the accuracy of the transition
-point for break-up depends intimately on the 
+point for break-up depends on the 
 largest Taylor Deformation parameter $D$
@@
 necessitate grid points distributed relatively evenly throughout the 
-computational domain when a bubble is stretched to a $0.9$ aspect ratio,
+computational domain when a bubble is stretched to a $D=0.9$ Deformation,
 whereas in \cite{zhang2021three} the gridding strategy necessitates 
-a localized strategy.
-
+a more localized strategy.
 }
@@
 z^{\ell=1})=R/16$. To verify the adequacy of this grid resolution, we present
-grid refinement results for a bubble breakup simulation with $Ca=1.0$, which
+rid refinement results for a bubble breakup simulation with $Ca=1.0$, which
 corresponds to the most deformable and stretchable bubble case considered in
@@
 essential dynamical features.
-{\color{red} Additional grid refinements may be desirable to perform further 
-accuracy evaluations for bubble deformation and breakup.}
 

### 2024-04-01 Reply-Reviewer2.tex
reply to reviewer 2 complete

@@
 flow acting against the interfacial
-surface tension force.  By nature of the research question, 
-the accuracy of the transition
-point for break-up depends on the 
+surface tension force.   
+The accuracy of the ``Critical Reynolds Number''
+depends on the 
 largest Taylor Deformation parameter $D$
@@
 $D<0.95$, then the transition region 
+(i.e. ``Critical Reynolds number'')
 (see Figures 3 and 12) will be captured
 with a tolerance of three percent.  The simulation time becomes impractical
-if we were to try to further improve the tolerance.  A smaller tolerance
-would necessitate a longer supported Deformation
+if we were to try to further improve the ``critical Reynolds number''
+accuracy.  
+A smaller tolerance
+would necessitate a larger supported Deformation
 parameter $D$ which would in turn necessitate a higher aspect ratio
@@
 computational domain when a bubble is stretched to a $0.9$ Deformation,
-whereas in \cite{zhang2021three} the gridding strategy necessitates 
+whereas in [47] the gridding strategy necessitates 
 a more localized strategy.
@@
 stated in point \#2, but also assigned them values that may not be physically
-relevant. Moreover, the bubble size is nowhere stated.................\\
+relevant. Moreover, the bubble size is nowhere stated.  \\
 Finally, the Reynolds number of the channel in this case would be: $Re_{\rm
 channel} \simeq 6000$.  This high value of Re corresponds to turbulence
-conditions.................}
+conditions.}
 \vspace{3 mm}
@@
 =93.\\
-
-Physical properties (a silicone oil has a very similar physical properties with these values.):\\
-\quad $\rho_{\rm m}$ (density of liquid) = 1000 kg/m$^3$, $\mu_{\rm m}$ (viscosity of liquid) = 0.2 Pa$\cdot$s,
+\par\noindent
+Physical properties 
+(a silicone oil has a very similar physical properties with these values):\\
+\quad $\rho_{\rm m}$ (density of liquid) = 1000 kg/m$^3$, 
+$\mu_{\rm m}$ (viscosity of liquid) = 0.2 Pa$\cdot$s,
 $\sigma$ (surface tension) = 0.025 N/m, $R$ (bubble radius) = 5.0 mm.\\
-From ${\it \Gamma}$ = $2V/H$ = $2V/6R$, \  $V$ = 3${\it \Gamma} R$ = $\frac{3\sigma Ca}{\mu_{\rm m}} $ = 1.1 m/s.
-Also, we obtain $Fr$ (Froude number) = $\frac{{\it \Gamma}R}{\sqrt {gR}}$ = 1.7. \\
-In this flow system, the effect of gravity may not be completely negligible. However, in our computations, 
+From ${\it \Gamma}$ = $2V/H$ = $2V/6R$, \  
+$V$ = 3${\it \Gamma} R$ = $\frac{3\sigma Ca}{\mu_{\rm m}} $ = 1.1 m/s.
+Also, we obtain $Fr$ (Froude number) = 
+$\frac{{\it \Gamma}R}{\sqrt {gR}}$ = 1.7. \\
+In this flow system, the effect of gravity may not be completely 
+negligible. However, in our computations, 
 we set $g = 0$ because we wanted to clearly isolate only the effects of 
@@
 phenomena in space.
-At the end of the Problem Description section, we added a detailed explanation about physical properties and conditions.
+At the end of the Problem Description section, 
+we added a detailed explanation about physical properties and conditions.
 
@@
 
+%%10
 \par\noindent
@@
 {\color{red}  
-Regarding Question \#12, we have made a new figure (shear stress profile) for
-the case of $Re$ = 50 and $Ca$ = 0.3.  In the case of $Re$ = 50, the bubble
-finally settles into a steady deformed shape. Additionally, we observed a
-steady deformed bubble at the $Re$ = 70 (not presented in this paper).  As
-discussed in detail in the new Section~I\hspace{-1.2pt}V.C, in the limit, as the value of $Re$
-approaches the critical $Re_{\rm c}$ condition, the bubble does not maintain
-its deformed state but instead alternates in an elongation and contraction
-process.  
-%It can be expected the bubble will be in a steady deformed state when the 
-%condition of $Re$ number is smaller than the critical $Re$ number ($Re_{\rm c}$),  
-%whereas the bubble is largely elongated and contracts to a doglegged 
-%shape when the $Re$ number is close to $Re_{\rm c}$.\\
-} Moreover, the main object of this study is to find $Re_{\rm c}$; we have
-plans for examining bubble periodic deformation with expansion and contraction
-in future work.  In ongoing and upcoming work, we will examine the effect of
-$\lambda$ and $\eta$ on drop breakup for some combinations of $\lambda$ and
-$\eta$ as follows: 
-\\
-\begin{tabbing}
- \hspace{55mm} \= \hspace{10mm} \kill
- \hspace{5mm} 1. $\lambda$ = 1.0, $\eta$ =1.0 (done) \> 2. $\lambda \simeq 0.0$, $\eta \simeq 0.0$ (this study) \\ 
- \hspace{5mm} 3. $\lambda$ = 1.0, $\eta \simeq 0.0$ \> 4. $\lambda$ = 1.0, $\eta$ =0.1 \\
- \hspace{5mm} 5. $\lambda$ = 0.1, $\eta$ =1.0 \> 6. $\lambda$ = 0.1, $\eta$ =0.1  \\
- \hspace{5mm} 7. $\lambda$ = 1.0, $\eta$ =100 \> 8. $\lambda$ = 1.0, $\eta$ =1000 \\
-\end{tabbing}
-After we complete the study of the effect of $\lambda$ and $\eta$, we will work
-on periodic bubble deformation with expansion and contraction.  Due to
-prohibitely long computation times, additional computing resources and improved
-numerical algorithms are necessary to simulate multiple periodic cycles in
-bubble expansion and contraction.\\
-
+We have made a new figure (Figure 8: shear stress profile) for
+the cases of 
+(i) $Re$ = 50 and $Ca$ = 0.3, and
+(ii) $Re$ = 93 and $Ca$ = 0.3.
+Our new Figure 8 is a part of our new 
+Section~I\hspace{-1.2pt}V.C.  The purpose of this new material
+is to gain further insight on the unsteady dynamics of bubble
+elongation.  What we discovered was that for the Reynolds
+number sufficiently below the critical value, a relatively quick
+unsteady elongation period gives way to a steady state (with no
+break up).  On
+the otherhand for Reynolds number {\em close} to the critical Reynolds
+number, there is a prolonged, unsteady, elongation period, in which
+periodic motion is observed and the deformation parameter $D$ is close 
+to one.  It is agreed, that the ``vacillating''
+behavior cannot last forever, ultimately (perhaps stochastically!),
+the bubble will either settle down or break.  We assert that regardless
+of the outcome, this vacillating behaviour will always occur
+in close proximity to the critical Reynolds' number.  In otherwords,
+regardless of the outcome, we claim that one is assured of being within 
+3 percent of the critical Reynolds number (see Figure 3).  In fact,
+we hypothesize that there will {\em always} be ``vacillating'' behavior
+if one is sufficiently close to the critical Reynolds number.  i.e.
+given an almost infinite supply of computational resources, as one hones
+in closer and closer to the critical Reynolds number, a ``tug of war''
+will be observed between the surface tension force trying to pull the
+bubble together versus the wall driven shear stress trying to pull the
+bubble apart.  This discussion
+is added to the paper.
+}
+%%11
 \par\noindent
@@
 expensive computations.  After lengthy computations, we were able to determine
-the bubble $Re_{\rm c}$ number for 4 $Ca$ numbers.  Nevertheless, we believe
-that a bubble breakup critical curve drawn based on 4 points will be useful for
-low $Ca$ numbers.  Following the suggestion from the reviewer 1, we have added
-a drop breakup critical curve ($\lambda$ = $\eta$ =1.0) to Fig. 12 (former Fig. 11).  
-The difference in $Re_{\rm c}$ number between the bubble and the drop is clearer in
-the new Fig. 12.  But, the reviewer's opinion is appropriate. 
-In future work, we will determine the $Re_{\rm c}$ for a variety of high $Ca$ numbers 
-to construct a detailed critical curve for a wider range of $Ca$ numbers.\\
+the bubble $Re_{\rm c}$ number for 4 $Ca$ numbers.  We believe
+that a bubble breakup critical curve drawn based on 4 points will be 
+useful for low $Ca$ numbers.  Following the suggestion from the 
+other reviewer (reviewer 1), 
+we have added
+a drop breakup critical curve ($\lambda$ = $\eta$ =1.0) 
+to Fig. 12 (formerly Fig. 11).  
+The difference in $Re_{\rm c}$ number between the bubble and 
+the drop is clearer in
+the new Fig. 12.  
+In future work, we will determine the $Re_{\rm c}$ for a 
+variety of high $Ca$ numbers 
+in order to construct a detailed critical curve 
+for a wider range of $Ca$ numbers.\\
 
+%%12
 \par\noindent
@@
 \textsf
-{\color{red}  End of conclusions section: ........................
+{\color{red}  End of conclusions section: .........
 These phrases state the obvious, the densities and viscosities are different between drops and bubbles and, therefore, they cause different dynamics. 
@@
 {\color{red}
-We agree with reviewer's comment. In response, we have added two new images of the
+We agree with reviewer's comment. In response, we have added 
+two new images of the
 shear stress profile for a bubble for two $Re$ conditions in Fig. 8.
-A discussion of the new results, in terms of the shear stresses acting on the
-bubble at the two different conditions, is given in Section~I\hspace{-1.2pt}V.C. 
+A discussion of the new results, in terms of the 
+shear stresses acting on the
+bubble at the two different conditions, 
+is given in Section~I\hspace{-1.2pt}V.C. 
 }

### 2024-04-01 Bubble-deformation.tex
reply to reviewer 2 complete

@@
 flow acting against the interfacial
-surface tension force.  By nature of the research question, 
-the accuracy of the transition
-point for break-up depends on the 
+surface tension force.  
+The accuracy of the ``Critical Reynolds Number''
+depends on the 
 largest Taylor Deformation parameter $D$
-that is supported by the grid (see e.g. Figures \ref{fig:ShearStress} and
+that is supported by the grid 
+(see e.g. Figures \ref{fig:ShearStress} and
 \ref{fig:BubBrkCa0p8Re43}).  
@@
 $D<0.95$, then the transition region 
+(i.e. ``Critical Reynolds number'')
 (see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit}) will be captured
 with a tolerance of three percent.  The simulation time becomes impractical
-if we were to try to further improve the tolerance.  A smaller tolerance
-would necessitate a longer supported Deformation
+if we were to try to further improve the ``critical Reynolds number''
+accuracy.  
+A smaller tolerance
+would necessitate a larger supported Deformation
 parameter $D$ which would in turn necessitate a higher aspect ratio
@@
 are closely related to the state of shear stress acting on the bubble.
-Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble,
-for two Reynolds numbers under the condition of $Ca = 0.3$.  The shear stress
+Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble
+for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds
+number equal to 50 and 93.  
+The shear stress
 profile on the left corresponds to the case of $Re = 50$ and the right side
-shows the shear stress profile for the case of $Re = 93$.  The normalized shear
-stress $\tau^{\ast} = \tau / \tau_{0}$ is defined as a ratio of the local shear
-stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress
-$\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  In this study, for a given $Ca$
-condition, the same value of $\tau_{0}$ is used regardless of $Re$. For the
-case of $Re = 50$, the bubble reaches a deformed stable state.  As observed in
-previous sections, when the value of $Re$ is slightly below the critical $Re$
-condition, the bubble does not settle into a deformed stable state but instead
-alternates in an elongation and contraction process.  In comparison, the right
-image in Fig.~\ref{fig:ShearStress} shows a higher shear stress profile near
-the bubble endpoints for the case of $Re = 93$ as it undergoes an elongation
-state in the process toward breakup.  The value of the maximum shear stress for
-the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ and the maximum shear stress
-for the case of $Re = 93$ at the moment shown in Fig.~\ref{fig:ShearStress} has
-the value of $\tau ^{\ast} \approx 8$.  The shear stress profile of in
-Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from $\tau
-^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions
-with $\tau ^{\ast} \geqq 6$ are illustrated in red.  As can be seen in the
-figure, the strongest shear stresses are concentrated on the ends of the bubble
-for both $Re$ conditions.  This indicates that the strong shear stresses acting
+shows the shear stress profile for the case of $Re = 93$.  
+The normalized shear
+stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a 
+ratio of the local shear
+stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ 
+and the apparent shear stress
+$\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  
+In this study, for a given $Ca$ condition, the same 
+value of $\tau_{0}$ is used regardless of $Re$. 
+\par\noindent
+For the
+case of $Re = 50$, the bubble reaches a deformed stable state.  
+\par\noindent
+As observed in
+previous sections, when the value of $Re$ is slightly below the 
+critical $Re$ condition, the bubble does not settle into a deformed 
+stable state but instead alternates in an elongation and contraction process.  
+In comparison to the $Re=50$ case on the left, the right
+image in Fig.~\ref{fig:ShearStress} ($Re=93$)
+shows a higher shear stress profile near
+the bubble endpoints as it undergoes an elongation
+state in the process toward breakup.  
+The value of the maximum shear stress for
+the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ 
+and the maximum shear stress
+for the case of $Re = 93$ at the moment 
+shown in Fig.~\ref{fig:ShearStress} has
+the value of $\tau ^{\ast} \approx 8$.  
+The shear stress profile in
+Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from 
+$\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, 
+shear stress regions
+with $\tau ^{\ast} \geqq 6$ are illustrated in red.  
+As can be seen in the
+figure, the strongest shear stresses are concentrated on the 
+ends of the bubble for both $Re$ conditions.  
+This indicates that the strong shear stresses acting
 on the ends of the bubble are responsible for much of the bubble stretching.
@@
 ends of the bubble for the case of $Re = 93$ is much larger than that for the
-case of $Re = 50$.  On the other hand, the shear stress inside the bubble was
+case of $Re = 50$.
+
+We also observe that the shear stress {\em inside} the bubble was
 very small relative to that of the matrix fluid due to very small density and
@@
 consequence, a sufficiently large $Re$ condition is required for large bubble
-deformations.  }
+deformations.  
+\par\noindent
+In summary, what we discover is that for the Reynolds
+number sufficiently below the critical value, a relatively quick
+unsteady elongation period gives way to a steady state (with no
+break up).  On
+the otherhand for Reynolds number {\em close} to the critical Reynolds
+number, there is a prolonged, unsteady, elongation period, in which
+periodic motion is observed and the deformation parameter $D$ is close 
+to one.  The ``vacillating''
+behavior cannot last forever, ultimately (perhaps stochastically!),
+the bubble will either settle down or break.  We assert that regardless
+of the outcome, this vacillating behaviour will always occur
+in close proximity to the critical Reynolds' number.  In otherwords,
+regardless of the outcome, we claim, using the grid resolution of
+$R/16$, that one is assured of being within 
+3 percent of the critical Reynolds number (see Figure \ref{fig:DeEvolution}).  
+In fact,
+we hypothesize that there will {\em always} be ``vacillating'' behavior
+if one is sufficiently close to the critical Reynolds number.  i.e.
+given an almost infinite supply of computational resources, as one hones
+in closer and closer to the critical Reynolds number, a ``tug of war''
+will be observed between the surface tension force trying to pull the
+bubble together versus the wall driven shear stress trying to pull the
+bubble apart.
+
+}
 

### 2024-04-03 Bubble-deformation.tex
change blue to red, fix caption bug

@@
 %\usepackage{graphicx}% Include figure files
+\usepackage{caption}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 in shear flow was mainly examined.} 
-{\color{blue} Concerning bubble breakup, Wei et
+{\color{red} Concerning bubble breakup, Wei et
 al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup
 process under the condition of $Ca$ (Capillary number) = 35.}
-% {\color{blue} What distinguishes our work from that in
+% {\color{red} What distinguishes our work from that in
 % \cite{WeiQiaXu12,WanShiZha15}?}
@@
 in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low 
-$Re$ number conditions ({\color{blue} $Re \ll 1$}) have been reported.}
-%{\color{blue} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
-In this work we determine, for the first time, the critical Reynolds number ({\color{blue} $Re \gg 1$}) 
+$Re$ number conditions ({\color{red} $Re \ll 1$}) have been reported.}
+%{\color{red} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
+In this work we determine, for the first time, the critical Reynolds 
+number ({\color{red} $Re \gg 1$}) 
 that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
@@
 MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
-%{\color{blue} cite some of these previous studies which examine deformation
+%{\color{red} cite some of these previous studies which examine deformation
 %and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
@@
 %% Ohta
-{\color{blue} Next, we examine the validation of our 
+{\color{red} Next, we examine the validation of our 
 computational method in which
@@
 \begin{table}[tbh]
-{\color{blue}
+\captionsetup{labelfont={color=red},font={color=red}}
+
 \caption{Comparison of  {\color{red} $D$} for a bubble as a function 
@@
          $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
- }
+
 \label{tab:DeComparisonRe=0}
@@
 x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  
-For the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is too
+For the $\Delta x^{\ell=1}=R/8$ results, it is clear 
+that the $R/8$ resolution is too
 coarse in order to capture the proper break-up time, albeit the critical
-Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid resolution
+Reynolds' number, $Re_{\rm c}$ = 33, was still close to the 
+finer grid resolution
 cases.
@@
 %% Ohta
-{\color{blue} 
+{\color{red} 
 \subsection{Shear stress acting on the bubble}
@@
 a wide range of high $Ca$ numbers.  }
-%{\color{blue} it seems like the above passage is still a work in progress?}
+%{\color{red} it seems like the above passage is still a work in progress?}
 % Yes. I have been suspending computations for bubbles because I have been focussing on non-Newtonian cases, but I have a plan for restarting again.

### 2024-07-25 Bubble-deformation.tex
updated figure and caption justification
using grammarly

@@
 %  
-%  Modified: 17 December 2023
-%  -----------------------------------------------------------------------------
-%  -----------------------------------------------------------------------------
-
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.2 distribution.
-%   Version 4.2a of REVTeX, December 2014
-%
-%   Copyright (c) 2014 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.2
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
-\documentclass[%
- reprint,
- showkeys,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps,
- prfluids,
- onecolumn
-%prfluids,
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-2}
-
-\usepackage[dvipdfmx]{graphicx}% Include figure files
+%  Modified: 26 April 2023
+%  -----------------------------------------------------------------------------
+%  -----------------------------------------------------------------------------
+%% 
+%% Copyright 2007-2020 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%% 
+%% Template article for Elsevier's document class `elsarticle'
+%% with harvard style bibliographic references
+
+%\documentclass[preprint,12pt,authoryear]{elsarticle}
+\documentclass[review]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times,authoryear]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
+%% \documentclass[final,3p,times,authoryear]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
+%% \documentclass[final,5p,times,authoryear]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+\usepackage{lineno}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+\usepackage{latexsym}
+\usepackage{amsfonts}
+\usepackage{amsbsy}
+%\usepackage{psfrag}
+\usepackage{subfigure}
+\usepackage{mathtools}
+\usepackage{graphicx}
+
+% Following three lines are needed for this document.
+% If you are not loading colors or url, then these are
+% not required.
+\usepackage{url}
+\usepackage{xcolor}
+\definecolor{newcolor}{rgb}{.8,.349,.1}
+
+%\graphicspath{{figures/}}
+\graphicspath{{Figure/}}
+
+%\usepackage[dvipdfmx]{graphicx}% Include figure files
 %\usepackage{graphicx}% Include figure files
-\usepackage{caption}
-\usepackage{dcolumn}% Align table columns on decimal point
+%\usepackage{caption}
+%\usepackage{dcolumn}% Align table columns on decimal point
 \usepackage{bm}% bold math
-\usepackage{comment}
+%\usepackage{comment}
 \usepackage{color}
+%\usepackage{ragged2e}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
-\graphicspath{{figures/}}
-\setlength{\tabcolsep}{12pt} % Modifies table column separation.
+%\graphicspath{{figures/}}
+%\setlength{\tabcolsep}{12pt} % Modifies table column separation.
 
@@
 
+\journal{Chemical Engineering Journal}
+
 %  -----------------------------------------------------------------------------
@@
 
-%\preprint{APS/123-QED}
-
-%\title{Manuscript Title:\\with Forced Linebreak}% Force line breaks with \\
-%\thanks{A footnote to the article title}%
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for theassociated footnote;
+%% use the fnref command within \author or \affiliation for footnotes;
+%% use the fntext command for theassociated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for theassociated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \affiliation{organization={},
+%%            addressline={}, 
+%%            city={},
+%%            postcode={}, 
+%%            state={},
+%%            country={}}
+%% \fntext[label3]{}
+
 \title{Numerical simulation of bubble deformation \\
@@
 
-\author{Mitsuhiro Ohta}
- \altaffiliation[Also in the ]{Department of Mechanical Engineering, Graduate School 
-                 of Advanced Technology and Science,
-                 Tokushima University}%Lines break automatically or can be forced with \\
-  \email{m-ohta@tokushima-u.ac.jp}
-\affiliation{
-  Department of Mechanical Science, Graduate School of Technology, Industrial and Social Sciences,
-  Tokushima University,\\
-  2-1 Minamijyousanjima-cho,Tokushima 770-8506, Japan}
-\author{Tetsuya Ueta}
-\affiliation{
-   Department of Mechanical Engineering, Graduate School of Advanced Technology and Science,\\
-  Tokushima University, 2-1 Minamijyousanjima-cho,Tokushima 770-8506, Japan}
-\author{Yozo Toei}
- %\email{Second.Author@institution.edu}
-\affiliation{%
- %Authors' institution and/or address\\
- %This line break forced with \textbackslash\textbackslash
- High Performance Plastics Company, Sekisui Chemical Co., Ltd.,\\
- 2-1 Hyakuyama, Mishimagun Shimamoto-cho, Osaka 618-0021, Japan
-}%
+\author[1,2]{Mitsuhiro Ohta\corref{cor1}} 
+\cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
+\address[1]{
+  organization={Department of Mechanical Science, Graduate School of Technology, 
+                Industrial and Social Sciences, Tokushima University},
+  addressline={2-1 Minamijyousanjima-cho},
+  state={Tokushima 770-8506}, 
+  country={Japan}}
+\address[2]{
+  organization={Department of Mechanical Engineering, Graduate School of Technology, 
+                Industrial and Social Sciences, Tokushima University},
+  addressline={2-1 Minamijyousanjima-cho},
+  state={Tokushima 770-8506}, 
+  country={Japan}}
+
+\author[2]{Tetsuya Ueta}
+\author[3]{Yozo Toei}
+
+\address[3]{
+  organization={High Performance Plastics Company, Sekisui Chemical Co., Ltd.},
+  addressline={2-1 Hyakuyama, Mishimagun Shimamoto-cho},
+  state={Osaka 618-0021}, 
+  country={Japan}}
 
@@
 
-\author{Edwin Jimenez}  
-\affiliation{Department of Computing and Mathematical Sciences, MC 305-16 
-             California Institute of Technology, Pasadena, CA 91125, USA
-}%
-
-\author{Mark Sussman}  
-\affiliation{
-  Department of Mathematics,
-  Florida State University,
-  Tallahassee, FL 32306, USA
-}%
+\author[4]{Edwin Jimenez}  
+\address[4]{
+  organization={Spectral Numerical, LLC},
+  addressline={1942 Broadway St., STE 314C},
+  city={Boulder},
+  state={CO 80302},
+  country={USA}}
+
+\author[5]{Mark Sussman}  
+\address[5]{
+  organization={Department of Mathematics, Florida State University},
+  city={Tallahassee},
+  state={FL 32306},
+  country={USA}}
 
@@
 
-\date{\today}% It is always \today, today,
+%\date{\today}% It is always \today, today,
              %  but any date may be explicitly specified
@@
 \begin{abstract}
-Numerical simulations for the deformation and breakup of a bubble in liquids
-undergoing simple linear shear flow are presented.  Numerical results are
-obtained using a hydrodynamic scheme with formal second-order accuracy based on
-a coupled level set/volume-of-fluid (CLSVOF) method.  To verify our numerical
-algorithm, and to provide a basis for comparison, we also present simulation
-results which compare with previous, more popular, simulations  
-of drop deformation and rupture.  The numerical
-results reveal that the shear-induced bubble deformation and breakup process
-differs significantly from that of the analogous drop system under similar flow
-conditions.  The first distinguishing factor for bubble breakup is that the
-magnitude of shear flow necessary for rupture is much larger than that in the
-drop system case.  In other words, a larger Reynolds number is necessary to
-induce bubble breakup.  The second distinct feature of the bubble system versus
-the drop system is that the bubble does not maintain a stable deformed shape as
-the parameters of the system approach the critical ``breakup'' Reynolds number.
-It is asserted that the differences in morphology for a bubble undergoing
-breakup, versus a drop in the same process, can be attributed to the density
-and viscosity ratio of the corresponding two-phase flow systems.  The critical
-conditions for bubble breakup with respect to the Reynolds and capillary
-numbers are determined for several cases.
+Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.
+Numerical results are obtained using a hydrodynamic scheme with formal second-order accuracy based on a coupled level set/volume-of-fluid (CLSVOF) method.
+To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.
+The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.
+The first distinguishing factor for bubble breakup is that the magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case.
+In other words, a larger Reynolds number is needed to induce bubble breakup.
+The second distinct feature of the bubble system versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the critical ``breakup'' Reynolds number.
+It is asserted that the differences in morphology for a bubble undergoing breakup versus a drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.
+The critical conditions for bubble breakup with respect to the Reynolds and capillary numbers are determined for several cases.
 \end{abstract}
 
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-%                              %display desired
-\keywords{Bubble deformation, bubble breakup, shear flow, CFD}
-
-\maketitle
+\begin{keyword}
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+%\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
+%% Keywords
+Bubble deformation\sep bubble breakup\sep shear flow\sep CFD
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
+
+%\maketitle
 
@@
 %
-The study of the deformation {\em and breakup} of a drop in immiscible viscous
-liquids undergoing simple linear shear flow has been investigated extensively
-due to its fundamental importance in connection with emulsion and materials
-processing, mixing and reaction devices. The pioneering experimental work of
-this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34},
-and the subsequent theoretical and experimental progress up to the 1980s and
-1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.  By the
-2000s, progress in computational fluid dynamics (CFD) techniques and increased
-access to powerful computing resources led to a surge of research focused on
-direct simulations of this problem.  In particular, detailed computational
-investigations of drop breakup, based on a Volume-of-Fluid (VOF) method
-\cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2,
-RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.  Since then, the literature on
-computational studies on the deformation and breakup of a single or several
-drops in shear flow has continued to grow \cite{CriGuiAlfBlaLoe03,
-InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08,
-CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16,
-HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques
-have been developed to tackle this problem, including boundary-integral
-approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06,
-KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and {\color{red}
-interface-capturing} level set methods \cite{SusSmeOsh94}.  {\color{red} 
-In contrast, few computational studies on bubble 
-deformation {\em and breakup} can be found.  
-We remark that there has been a 
-number of articles on the study of lift of {\em slightly}
-deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
-We reiterate though, that for bubble deformation {\em and breakup} in
-shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15}.  
-In these previous
-studies, the dynamics (e.g. rotation angle) of bubble deformation 
-in shear flow was mainly examined.} 
-{\color{red} Concerning bubble breakup, Wei et
-al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup
-process under the condition of $Ca$ (Capillary number) = 35.}
-% {\color{red} What distinguishes our work from that in
-% \cite{WeiQiaXu12,WanShiZha15}?}
-Bubble dynamics in shear flow, {\em including breakup},
-is of critical importance for a
-variety of scientific and engineering processes. We refer the reader to the
-following experimental studies relating to bubble deformation in foaming
-processes, microfluidic devices, and micro bubbles in the blood circulation
-system,\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.
-In particular, it is the study of bubble deformation as it pertains to high
-performance plastics applications which motivates this work.  In this article,
-we present computational studies of shear-driven deformation 
-{\em and breakup} of a
-bubble in insoluble viscous liquids.  Studying bubble break-up via computation
-rather than experiments simplifies the process of setting a combination of
-precise simple shear flow conditions, low $Ca$ conditions, low density ratio,
-and low viscosity ratios.  The physical properties that distinguish bubble and
-drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm
-b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$,
-where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts
-``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'',
-respectively.  For a bubble in an insoluble viscous liquid, $\lambda \simeq 0$
-and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible
-viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
-
-In this work we focus on identifying critical flow states numerically, in terms
-of dimensionless quantities, that specify the extreme conditions at which a
-bubble or drop in shear flow first transitions from deformation to breakup.
-We validate our numerical method through comparisons with previous
-shear-driven drop dynamics results and we also examine the effect of drop
-deformation and breakup sensitivity on domain and grid size.  An advantage of
-studying shear-driven bubble deformation and breakup computationally, rather
-than experimentally, is that we can easily modify fluid physical properties to
-ascertain the sensitivity of deformation and breakup to physical parameters.
-In our computations, the time-evolution of the boundary between gas and liquid
-is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface
-capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.  
-We focus on determining critical physical
-conditions in which the breakup of a bubble occurs in shear flow because it is
-important to identify the parameter regimes in which a relatively simple system
-transitions from stable to unstable.  Specifically, we identify the critical
-Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as
-a function of $Ca$. 
-The critical Reynolds number, $Re_{\rm c}$, for drop breakup was 
-reported previously by \cite{LiRenRen00}.
-{\color{red} In previous studies on the motion of bubble deformation
-in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low 
-$Re$ number conditions ({\color{red} $Re \ll 1$}) have been reported.}
-%{\color{red} What were the $Re$ conditions considered by \cite{RusMan02, MulTobDreFisWin08} and what are the $Re$ conditions considered in our paper?}
-In this work we determine, for the first time, the critical Reynolds 
-number ({\color{red} $Re \gg 1$}) 
-that leads to \emph{bubble} breakup.  Additionally, our computational studies reveal characteristics that
-distinguish the deformation and breakup processes of a drop versus those of a bubble.
+Bubble dynamics in shear flow, {\em including breakup}, is critically important for various scientific and engineering processes.
+We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, and microbubbles in the blood circulation system,\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.  This article presents computational studies of shear-driven deformation {\em and breakup} of a bubble in insoluble viscous liquids.  Studying bubble break-up via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ conditions, low-density ratio (1:1000), and low viscosity ratios (1:100).  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
+
+In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme conditions at which a bubble in shear flow first transitions from deformation to breakup.
+We validate our numerical method by examining the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.
+An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties to ascertain the sensitivity of deformation and breakup to physical parameters.
+In our computations, the time-evolution of the boundary between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.
+We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify the parameter regimes in which a relatively simple system transitions from stable to unstable.
+Specifically, we ascertain the critical Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.
+
+In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
+In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to \emph{bubble} breakup.
+Additionally, our computational studies reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
+
+We remark that there have been a number of articles on the study of lift of {\em slightly} deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
+We reiterate, though, that for bubble deformation {\em and breakup} in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15}.
+These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.
+Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup process under the condition of $Ca$ (Capillary number) = 35.
+
+To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop.
+We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the simpler drop problem.
+For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
+
+The study of the deformation {\em and breakup} of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.
+The pioneering experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.
+By the 2000s, progress in computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused on direct simulations of this problem.
+In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.
+Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.
 
@@
 for our studies of a bubble (or drop) in shear flow.  The computational domain
-consists of a three-dimensional rectangular domain of $L$ (length) $\times$
-$W$ (width) $\times$ $H$ (height).  The size of $L$, $W$ and $H$
-was determined after consideration of numerical result sensitivity to domain
-size; numerical studies of domain-size dependence are presented in
+consists of a three-dimensional rectangular domain of $L$ (length) $\times$ $W$
+(width) $\times$ $H$ (height).  The size of $L$, $W$ and $H$ was determined
+after consideration of numerical result sensitivity to domain size; numerical
+studies of domain-size dependence are presented in
 Section~\ref{sec:DomGrdSize}.  All computational results that follow were
@@
 for gas-liquid/liquid-liquid flows.  Computations are initialized with a
-spherical bubble {\color{red} (or drop) of radius $R$ = 5 mm set at the 
-center of the computational domain.   The bubble (or drop) is then 
-subjected to a
-linear shear flow generated by the motion of the top and bottom plates, which 
-have constant velocity $+V$ and $-V$, respectively.}  In the interior of the
-domain, the initial velocity condition is assumed to be a simple linear profile
-and periodic boundary conditions are imposed along the $x$ and $y$ directions.
-Mathematically, the initial and boundary conditions are described as
-follows:
+spherical bubble (or drop) of radius $R$ = 5 mm set at the center of the
+computational domain.   The bubble (or drop) is then subjected to a linear
+shear flow generated by the motion of the top and bottom plates, which have
+constant velocity $+V$ and $-V$, respectively.  In the interior of the domain,
+the initial velocity condition is assumed to be a simple linear profile and
+periodic boundary conditions are imposed along the $x$ and $y$ directions.
+Mathematically, the initial and boundary conditions are described as follows:
+%
 \begin{eqnarray}
@@
 \end{eqnarray}
-$\phi(x,y,z,t)$ is a material indicator function which is positive 
-in the ``matrix'' fluid and negative in the bubble (or drop) fluid.
-$\bmu(x,y,z,t)$ is the velocity.
+%
+$\phi(x,y,z,t)$ is a material indicator function which is positive in the
+``matrix'' fluid and negative in the bubble (or drop) fluid.  $\bmu(x,y,z,t)$
+is the velocity.
 
@@
 liquid-liquid two-phase flows include the Reynolds ($Re$), Weber ($We$) (or
-$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers.  Gas-Liquid and 
-Liquid-Liquid two-phase flow problems are also determined by the
-density ratio $\lambda$ and the viscosity ratio $\eta$.  
-In the present study, the effect of gravity is not considered so
-that we ignore the effect of the $Fr$ number.
+$Ca$ (= $We/Re$)) and Froude ($Fr$) numbers.  Gas-Liquid and Liquid-Liquid
+two-phase flow problems are also determined by the density ratio $\lambda$ and
+the viscosity ratio $\eta$.  In the present study, the effect of gravity is not
+considered so that we ignore the effect of the $Fr$ number.
 
@@
 \begin{eqnarray}\label{dimensonless}
-  Re = \frac{\rho_{\rm {\color{red}m}}UR}{\mu_{\rm {\color{red}m}}}, \quad
-  Ca = \frac{\mu_{\rm {\color{red}m}}U}{\sigma}, \quad
+  Re = \frac{\rho_{\rm m}UR}{\mu_{\rm m}}, \quad
+  Ca = \frac{\mu_{\rm m}U}{\sigma}, \quad
   \eta = \frac{\mu_{\rm b}}{\mu_{\rm m}} 
@@
 $U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
-mentioned in the introduction, most previous drop studies set $\eta =
-1$ (e.g. \cite{LiRenRen00}).  
-Thus, for comparison with previous drop deformation and breakup
-problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity
-so that $g=0$). On the other hand, in our computations for bubble deformation,
-we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$
-and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We emphasize
-that for consistency with previous studies (\cite{LiRenRen00, RusMan02,
-MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), 
-%{\color{red} cite some of these previous studies which examine deformation
-%and breakup of a bubble or drop as a function of the $Re$ and $Ca$ numbers.}
-we computationally examine the deformation and breakup of a bubble in simple
-linear shear flow as a function of the $Re$ and $Ca$ numbers.  {\color{red}
-That is to say, by setting $g=0$, we are isolating the effect of only varying
-$Re$ and $Ca$ on bubble deformation and breakup.  In our controlled study, we
-determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$
-corresponds to the threshold of bubble (or drop) breakup.  We determine the
-critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density
-ratio and viscosity ratio. }
-
-{\color{red} In our computations, the density of the matrix fluid is fixed at
-$\rho_{\rm m}$ = 1000 kg/m$^3$.  The surface tension at the bubble (drop)
-interface is $\sigma =2.5 \times 10^{-2}$ N/m.  The values of $Re$ and $Ca$ in
-our simulations are controlled by changing the values of $\mu_{\rm m}$ and $V$.
-For studying bubble deformation and break-up, the density and viscosity ratios
-satisfy $\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.}
+mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.
+\cite{LiRenRen00}).  Thus, for comparison with previous drop deformation and
+breakup problems, we set $\lambda = \eta = 1$ (and also neglect the effect of
+gravity so that $g=0$). On the other hand, in our computations for bubble
+deformation, we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2
+kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We
+emphasize that for consistency with previous studies (\cite{LiRenRen00,
+RusMan02, MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), we
+computationally examine the deformation and breakup of a bubble in simple
+linear shear flow as a function of the $Re$ and $Ca$ numbers.  That is to say,
+by setting $g=0$, we are isolating the effect of only varying $Re$ and $Ca$ on
+bubble deformation and breakup.  In our controlled study, we determine the
+critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$ corresponds to
+the threshold of bubble (or drop) breakup.  We determine the critical $Re_{\rm
+c}$ versus $Ca$ curve for strategic pairs of the density ratio and viscosity
+ratio.
+
+In our computations, the density of the matrix fluid is fixed at $\rho_{\rm m}$
+= 1000 kg/m$^3$.  The surface tension at the bubble (drop) interface is $\sigma
+=2.5 \times 10^{-2}$ N/m.  The values of $Re$ and $Ca$ in our simulations are
+controlled by changing the values of $\mu_{\rm m}$ and $V$.  For studying
+bubble deformation and break-up, the density and viscosity ratios satisfy
+$\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.
 
@@
 \begin{figure}%[h!]
-  \centering
-  \includegraphics[width=\textwidth]{SchematicAndGrid}
+  \includegraphics[width=\textwidth]{1-SchematicAndGrid}
   \caption{(a) Computational domain schematic for a bubble or drop in shear 
@@
 %  -----------------------------------------------------------------------------
-Numerical results were obtained using the {\color{red} interface capturing}
+Numerical results were obtained using the interface capturing
 Coupled Level Set and Volume of Fluid (CLSVOF) method
 \cite{SusPuc00,SUSSMAN2007469}, which is based on a fixed grid finite volume
-algorithm.  {\color{red}The CLSVOF method is a robust  numerical  technique
+algorithm.  The CLSVOF method is a robust  numerical  technique
 that  combines  some  of  the  advantages  of the Volume of Fluid (VOF) method
@@
 tension force (which is proportional to the interface curvature) can be
-straightforwardly derived from the smooth level set function. }
+straightforwardly derived from the smooth level set function.
 
@@
 function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$. The
-singular Heaviside gradient term in the right hand side of equation~\eqref{nseqn} is a body 
-force representing the surface tension force and is equivalent to specifying that the jump 
-in the normal stress is equal to
-$\sigma\kappa$~\cite{TanguyEtAl2007}. 
-{\color{red} The surface tension force expressed 
-by the singular Heaviside gradient term acts only on the 
-gas-liquid interface. 
-The sharp interface ``Ghost Fluid Method'' \cite{kang2000boundary}
-is used to discretize the gradient of the Heaviside function as it 
-appears in the surface tension force term.  This force, upon discretization,
-is only non-zero across cells in which the level set function changes
-sign. }
+singular Heaviside gradient term in the right hand side of
+equation~\eqref{nseqn} is a body force representing the surface tension force
+and is equivalent to specifying that the jump in the normal stress is equal to
+$\sigma\kappa$~\cite{TanguyEtAl2007}.  The surface tension force expressed by
+the singular Heaviside gradient term acts only on the gas-liquid interface.
+The sharp interface ``Ghost Fluid Method'' \cite{kang2000boundary} is used to
+discretize the gradient of the Heaviside function as it appears in the surface
+tension force term.  This force, upon discretization, is only non-zero across
+cells in which the level set function changes sign.
 
@@
 
-{\color{red}
 The temporal discretization of our numerical method is an operator split
@@
 our method is as follows (see \cite{SUSSMAN2007469}, section 4, for more 
-details): }
+details):
 \begin{description}
@@
 deformed drop in simple linear shear flow is described in terms of the Taylor
-deformation parameter {\color{red} $D$}=$(a-b)/(a+b)$, 
+deformation parameter $D$=$(a-b)/(a+b)$, 
 where $a$ and $b$ are the major and minor axes of the deformed drop.  
@@
 $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  Numerical
-results are listed in Table~\ref{tab:DeComparison} for {\color{red} $D$} 
+results are listed in Table~\ref{tab:DeComparison} for $D$ 
 as a function of $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
@@
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter {\color{red} $D$} 
-for a drop as a function 
+\caption{Comparison of the Taylor deformation parameter $D$ for a drop as a function 
          of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$). In all cases, the domain 
@@
 Reynolds number                      & 0.1     & 0.5     & 0.6     & 0.75      \\
-{\color{red} $D$}(Li et al. (\cite{LiRenRen00}))  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
-{\color{red} $D$}(Our study) & 0.3960  & 0.4570  & 0.4758  & Breakup   \\
+$D$(Li et al. (\cite{LiRenRen00}))  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
+$D$(Our study) & 0.3960  & 0.4570  & 0.4758  & Breakup   \\
 \hline
@@
 %% Ohta
-{\color{red} Next, we examine the validation of our 
-computational method in which
-we compare with the ``bubble deformation in simple linear shear flow'' 
-results reported by
+Next, we examine the validation of our computational method in which we compare
+with the ``bubble deformation in simple linear shear flow'' results reported by
 Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
 al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
-deformation under the condition of $Re \approx 0$. 
-In our study, we computed
-the bubble deformation on a 
-computational domain with dimensions
-$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid 
-size was
-$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
-Computations were
-performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ 
-with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  
-$\lambda = 1.2 \times 10^{-3}$ and  
-$\eta \leq 1.2 \times 10^{-6}$.
-The parameters that we have prescribed are consistent with the 
-experimental conditions by Muller-Fischer et al.
-\cite{MulTobDreFisWin08}.  
-Comparisons of our numerical results and previous
-experimental results (\cite{MulTobDreFisWin08}) are tabulated in
-Table~\ref{tab:DeComparisonRe=0}.  
-Additionally, in
+deformation under the condition of $Re \approx 0$.  In our study, we computed
+the bubble deformation on a computational domain with dimensions
+$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid size
+was $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
+Computations were performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$
+with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  $\lambda = 1.2 \times
+10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.  The parameters that we have
+prescribed are consistent with the experimental conditions by Muller-Fischer et
+al.  \cite{MulTobDreFisWin08}.  Comparisons of our numerical results and
+previous experimental results (\cite{MulTobDreFisWin08}) are tabulated in
+Table~\ref{tab:DeComparisonRe=0}.  Additionally, in
 Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
@@
 effective and robust at reproducing bubble dynamics in simple linear shear
-flow.}
+flow.
 
@@
 \begin{table}[tbh]
-\captionsetup{labelfont={color=red},font={color=red}}
-
-\caption{Comparison of  {\color{red} $D$} for a bubble as a function 
+\caption{Comparison of  $D$ for a bubble as a function 
          of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
@@
   \centering
-  \includegraphics[width=\textwidth]{DropBreakComparison}
+  \includegraphics[width=\textwidth]{2-DropBreakComparison}
   \caption{Comparison with results reported 
@@
 
-{\color{red} The numerical validation studies performed in this section and the
+The numerical validation studies performed in this section and the
 following section demonstrate that our numerical method can reliably determine
@@
 we refer the reader to \cite{ohta2011robust} in which we apply our CLSVOF
-method for bubble formation problems.}
+method for bubble formation problems.
 
@@
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter {\color{red} $D$} for a drop as a function of
+\caption{Comparison of the Taylor deformation parameter $D$ for a drop as a function of
          domain size ($Re=0.75$, $Ca=0.3$, $\lambda = \eta = 1$).
@@
 \hline
-System      & Domain size ($\LWH$)         & {\color{red} $D$}    \\
+System      & Domain size ($\LWH$)         & $D$     \\
 System 1    & $8R  \times 4R  \times 8R$   & Breakup \\
@@
 break up and becomes stable with a deformed shape if we set $L$ large enough
-and $W \geq 6R$ and $H \geq 6R$.  Since the value of {\color{red} $D$} for the domain size
+and $W \geq 6R$ and $H \geq 6R$.  Since the value of $D$ for the domain size
 $\lwh{8}{6}{6}$ differs by only $1.3\%$ with the value for the domain size of
@@
 we consider a domain size of $\lwh{24}{6}{6}$, and we find that the drop
-reaches a stable state with deformation parameter {\color{red} $D$}=0.549 for $Re=1.0$,
+reaches a stable state with deformation parameter $D$=0.549 for $Re=1.0$,
 while a value of $Re=1.1$ leads to drop breakup.
@@
 %  \includegraphics[width=\textwidth]{DeEvolution}
-  \includegraphics[width=\textwidth]{Fig3-Comparison-of-De-New}
+  \includegraphics[width=\textwidth]{3-Comparison-of-De-New}
   \caption{Time evolution of the deformation 
-   parameter {\color{red} $D$} versus 
-   dimensionless
+   parameter $D$ versus dimensionless
    time $T = \mathit{\Gamma} t$ for a bubble, obtained 
@@
    \Delta z ^{\ell=1}$. 
-   The evolution of {\color{red} $D$} using the first system, where
+   The evolution of $D$ using the first system, where
    $\Delta x^{\ell=1} = R/8$, is shown in blue and it predicts that 
    bubble breakup occurs at a Reynolds number $Re=33$.
-   The evolution of {\color{red} $D$} using the second system, where
+   The evolution of $D$ using the second system, where
    $\Delta x^{\ell=1} = R/16$, is shown in black and it predicts that 
@@
 
-{ \color{red}
-The grid size and adaptive meshing strategy that we adopt is chosen
-in order to answer the research question as to the conditions which determine
-whether a bubble in shear flow
-will break-up or not.  In such a case, we must accurately capture the 
-balance of forces with respect to the (non-local) force exerted from the 
-wall driven 
-flow acting against the interfacial
-surface tension force.  
-The accuracy of the ``Critical Reynolds Number''
-depends on the 
-largest Taylor Deformation parameter $D$
-that is supported by the grid 
-(see e.g. Figures \ref{fig:ShearStress} and
-\ref{fig:BubBrkCa0p8Re43}).  
-As we report here, we have found that as
-long as the grid size is fine enough to support a Taylor Deformation parameter
-$D<0.95$, then the transition region 
-(i.e. ``Critical Reynolds number'')
-(see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit}) will be captured
-with a tolerance of three percent.  The simulation time becomes impractical
-if we were to try to further improve the ``critical Reynolds number''
-accuracy.  
-A smaller tolerance
-would necessitate a larger supported Deformation
-parameter $D$ which would in turn necessitate a higher aspect ratio
-computational domain, increased droplet surface area at break-up,
+The grid size and adaptive meshing strategy that we adopt is chosen in order to
+answer the research question as to the conditions which determine whether a
+bubble in shear flow will break-up or not.  In such a case, we must accurately
+capture the balance of forces with respect to the (non-local) force exerted
+from the wall driven flow acting against the interfacial surface tension force.
+The accuracy of the ``Critical Reynolds Number'' depends on the largest Taylor
+Deformation parameter $D$ that is supported by the grid (see e.g. Figures
+\ref{fig:ShearStress} and \ref{fig:BubBrkCa0p8Re43}).  As we report here, we
+have found that as long as the grid size is fine enough to support a Taylor
+Deformation parameter $D<0.95$, then the transition region (i.e. ``Critical
+Reynolds number'') (see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit})
+will be captured with a tolerance of three percent.  The simulation time
+becomes impractical if we were to try to further improve the ``critical
+Reynolds number'' accuracy.  A smaller tolerance would necessitate a larger
+supported Deformation parameter $D$ which would in turn necessitate a higher
+aspect ratio computational domain, increased droplet surface area at break-up,
 increased number of time steps, and higher resolution for representing the
@@
 
-We make the distinction between our present research, and the research found
-in the work of Zang, Ni, 
-and Magnaudet\cite{zhang2021three,zhang2022three} on predicting the
-conditions for bubble mergers.  Even in the most extreme cases for
-mergers, the largest Deformation parameter never exceeds
-$0.4$ in \cite{zhang2021three}.  In summary, our gridding requirements 
-necessitate grid points distributed relatively evenly throughout the 
-computational domain when a bubble is stretched to a $D=0.9$ Deformation,
-whereas in \cite{zhang2021three} the gridding strategy necessitates 
-a more localized strategy.
-}
+We make the distinction between our present research, and the research found in
+the work of Zang, Ni, and Magnaudet\cite{zhang2021three,zhang2022three} on
+predicting the conditions for bubble mergers.  Even in the most extreme cases
+for mergers, the largest Deformation parameter never exceeds $0.4$ in
+\cite{zhang2021three}.  In summary, our gridding requirements necessitate grid
+points distributed relatively evenly throughout the computational domain when a
+bubble is stretched to a $D=0.9$ Deformation, whereas in \cite{zhang2021three}
+the gridding strategy necessitates a more localized strategy.
 
@@
 corresponds to the most deformable and stretchable bubble case considered in
-our numerical studies. We use three different grid systems, 
-(i) $\Delta x^{\ell=1}=R/8$,
-(ii) $\Delta x^{\ell=1}=R/16$,
-and 
-(iii) $\Delta x^{\ell=1}=R/24$, in order to determine
-$Re_{\rm c}$.  Figure~\ref{fig:DeEvolution} shows the time evolution of the
-deformation parameter {\color{red} $D$} over time for the three grid systems; 
-the $x$-axis is
-a dimensionless time defined by $T=\mathit{\Gamma} t$ 
-and the $y$-axis is {\color{red} $D$}.
-The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system
-with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta
-x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  
-For the $\Delta x^{\ell=1}=R/8$ results, it is clear 
-that the $R/8$ resolution is too
-coarse in order to capture the proper break-up time, albeit the critical
-Reynolds' number, $Re_{\rm c}$ = 33, was still close to the 
-finer grid resolution
-cases.
-Note that although
-the time evolution of {\color{red} $D$} for the two finer resolution
-systems ($R/16$ and $R/24$) is consistent between the two,
+our numerical studies. We use three different grid systems, (i) $\Delta
+x^{\ell=1}=R/8$, (ii) $\Delta x^{\ell=1}=R/16$, and (iii) $\Delta
+x^{\ell=1}=R/24$, in order to determine $Re_{\rm c}$.
+Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation
+parameter $D$ over time for the three grid systems; the $x$-axis is a
+dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $D$.
+The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid
+system with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with
+$\Delta x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  For
+the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is
+too coarse in order to capture the proper break-up time, albeit the critical
+Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid
+resolution cases.  Note that although the time evolution of $D$ for the two
+finer resolution systems ($R/16$ and $R/24$) is consistent between the two,
 (the predicted critical Reynolds numbers differ by $\sim 3\%$), the
@@
 than 6 times longer than the one based on the coarser system with $\Delta
-x^{\ell=1}=R/16$.  We remark that in our search for $Re_{\rm c}$, we considered a
-wide range of values of $Ca$ and we found it necessary to use a large $L$
+x^{\ell=1}=R/16$.  We remark that in our search for $Re_{\rm c}$, we considered
+a wide range of values of $Ca$ and we found it necessary to use a large $L$
 ($\sim 24R$) since for certain shear flows the bubble can stretch significantly
@@
   \centering
-  \includegraphics[width=\textwidth]{DropBreakEvol}
+  \includegraphics[width=\textwidth]{4-DropBreakEvol}
   \caption{Time evolution of drop deformation and breakup in shear flow at the
@@
 the first case, shown in Figure~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and
-$Re=1.0$, while the second case, depicted in Figure~\ref{fig:DropBreak}({\color{red}b}),
+$Re=1.0$, while the second case, depicted in Figure~\ref{fig:DropBreak}(b),
 uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the
 case with $Re=1.0$, the drop gradually deforms and finally attains a stable
-deformed state with {\color{red} $D$}= 0.549.  Over the same domain, for the case with
+deformed state with $D$= 0.549.  Over the same domain, for the case with
 $Re=1.1$, the ``mother'' drop elongates over time and the volume at the ends of
@@
   \centering
-  \includegraphics[width=\textwidth]{BubbleBreakCa0p3Re92}
+  \includegraphics[width=\textwidth]{5-BubbleBreakCa0p3Re92}
   \caption{Time evolution of bubble deformation in shear flow at the
@@
   \centering
-  \includegraphics[width=\textwidth]{BubbleBreakCa0p3Re93}
+  \includegraphics[width=\textwidth]{6-BubbleBreakCa0p3Re93}
   \caption{Time evolution of bubble deformation in shear flow at the
@@
   \centering
-  \includegraphics[width=\textwidth]{BubBreakCa0p3Re93Detail}
+  \includegraphics[width=\textwidth]{7-BubBreakCa0p3Re93Detail}
   \caption{Detail of bubble breakup process in shear flow at the condition
@@
 For the case of bubble breakup (Figure~\ref{fig:BubbleBreakCa0p3Re93}), we
-observe that the deformation process is almost {\color{red}the} same as the no-breakup case
+observe that the deformation process is almost the same as the no-breakup case
 until the doglegged shape is formed at $T \sim 27.4$. The bubble finally breaks
@@
 %% Ohta
-{\color{red} 
+
 \subsection{Shear stress acting on the bubble}
@@
   \centering
-  \includegraphics[width=\textwidth]{ShearStress}
+  \includegraphics[width=\textwidth]{8-ShearStress}
   \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for 
@@
 are closely related to the state of shear stress acting on the bubble.
-Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble
-for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds
-number equal to 50 and 93.  
-The shear stress
-profile on the left corresponds to the case of $Re = 50$ and the right side
-shows the shear stress profile for the case of $Re = 93$.  
-The normalized shear
-stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a 
-ratio of the local shear
-stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ 
-and the apparent shear stress
-$\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  
-In this study, for a given $Ca$ condition, the same 
+Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble for
+two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds number equal
+to 50 and 93.  The shear stress profile on the left corresponds to the case of
+$Re = 50$ and the right side shows the shear stress profile for the case of $Re
+= 93$.  The normalized shear stress, $\tau^{\ast} = \tau / \tau_{0}$, is
+defined as a ratio of the local shear stress $\tau = \mu_{\rm
+m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress $\tau_{0} = \mu_{\rm
+m}$$\mathit{\Gamma}$.  In this study, for a given $Ca$ condition, the same
 value of $\tau_{0}$ is used regardless of $Re$. 
 \par\noindent
-For the
-case of $Re = 50$, the bubble reaches a deformed stable state.  
+For the case of $Re = 50$, the bubble reaches a deformed stable state.  
 \par\noindent
@@
 
-We also observe that the shear stress {\em inside} the bubble was
-very small relative to that of the matrix fluid due to very small density and
-viscosity of the bubble.  Since the force of strong shear stresses acting on
-the ends of the bubble is difficult to transfer across the interface, as a
-consequence, a sufficiently large $Re$ condition is required for large bubble
-deformations.  
+We also observe that the shear stress {\em inside} the bubble was very small
+relative to that of the matrix fluid due to very small density and viscosity of
+the bubble.  Since the force of strong shear stresses acting on the ends of the
+bubble is difficult to transfer across the interface, as a consequence, a
+sufficiently large $Re$ condition is required for large bubble deformations.  
 \par\noindent
@@
 break up).  On
-the otherhand for Reynolds number {\em close} to the critical Reynolds
+the other hand for Reynolds number {\em close} to the critical Reynolds
 number, there is a prolonged, unsteady, elongation period, in which
@@
 of the outcome, this vacillating behaviour will always occur
-in close proximity to the critical Reynolds' number.  In otherwords,
+in close proximity to the critical Reynolds' number.  In other words,
 regardless of the outcome, we claim, using the grid resolution of
@@
 
-}
-
 \subsection{Velocity field outside and inside the breaking bubble}
@@
   \centering
-  \includegraphics[width=\textwidth]{BubbleFieldCa0p3Re93}
+  \includegraphics[width=\textwidth]{9-BubbleFieldCa0p3Re93}
   \caption{Fluid velocity field outside and inside the breaking bubble in
@@
   \centering
-  \includegraphics[width=\textwidth]{BubbleDeformCa0p8Re42}
+  \includegraphics[width=\textwidth]{10-BubbleDeformCa0p8Re42}
   \caption{Time evolution of bubble deformation in shear flow at the 
@@
   \centering
-  \includegraphics[width=\textwidth]{BubbleBreakCa0p8Re43}
+  \includegraphics[width=\textwidth]{11-BubbleBreakCa0p8Re43}
   \caption{Time evolution of bubble deformation in shear flow at the 
@@
 $(Ca,Re)$ is above the given critical curve, and the bubble will not break if
-the $(Ca,Re)$ pair is below the critical curve.  {\color {red} For comparison,
+the $(Ca,Re)$ pair is below the critical curve.  For comparison,
 a critical curve for the drop with $\lambda =\eta = 1$ is also indicated in
@@
 of $Re_{\rm c}$ numbers---and thus a more complete general critical curve---for
-a wide range of high $Ca$ numbers.  }
+a wide range of high $Ca$ numbers.
 %{\color{red} it seems like the above passage is still a work in progress?}
-% Yes. I have been suspending computations for bubbles because I have been focussing on non-Newtonian cases, but I have a plan for restarting again.
+%Yes. I have been suspending computations for bubbles because I have been
+%focussing on non-Newtonian cases, but I have a plan for restarting again.
 
@@
   %\includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
-  \includegraphics[width=\textwidth]{CaRecFit}
+  \includegraphics[width=\textwidth]{12-CaRecFit}
   \caption{A plot of the critical Reynolds number versus Capillary number
@@
 %\bibliography{apssamp}% Produces the bibliography via BibTeX.
+\bibliographystyle{elsarticle-harv} 
 \bibliography{references}

### 2024-11-04 Revised-paper/Reply/Reply-Reviewer1.tex
significance and novelty

%  -----------------------------------------------------------------------------
%  Modified:October 2024
%  -----------------------------------------------------------------------------
\documentclass{letter}

 \date{\today}

\usepackage{color}

\begin{document}
\begin{letter}{
Chemical Engineering Science\\
Professor Wei Ge, Editor\\}

\opening{Dear Prof. Ge,}

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 1: \begin{enumerate}
%%1
\item
\textsf
{Abstract, hightlights, and introduction are written in a way that confuses the reader: the text jumps back and forth between bubbles and drops as well as shear flows and other flow configurations. Then it suddenly moves to lift and deformation rather than breakup. Finally a number of random applications are mentioned without any relation to bubble breakup. The authors should clearly state what their contrbution is from the outset. The reader will not go on until the end to figure that out by himself. The use of shorter paragraphs each addressing a single issue is very helpful.}
\vspace{3 mm}

Response: \\
In the revision, we made many improvements to the grammar and structure so that the reader can follow in a much more efficient manner. \\
\\

%%2
\item
\textsf
{Method: The use of only 2 levels of grid refinement appears odd. For an accurate representation of the flow near the interface a very fine mesh is typically needed. Only 32 cells over the bubble diameter is hardly sufficient ot get accurate results as corroborated by the mediorce agreement of the presented simulation results with the experimental data used for validation. Two more levels of grid refinement are likely needed to resolved the flow near the bubble while farther away some coarsening may be possible. Optimizing the grid is imperative in a situaltion like the considerd one due to the strong deformation of the bubble which high curvature of the interface and the singular nature of the breakup event. Fully capturing the breakup, which represents a topological singularity, is impossible without a subgrid scale model.}
\vspace{3 mm}

Response: \\
The grid size and adaptive meshing strategy we adopted are chosen to answer the research question as to the conditions that determine 
whether a bubble in shear flow will break up.  
In such a case, we must accurately capture the balance of forces concerning the (non-local) force exerted from the wall-driven 
flow acting against the interfacial surface tension force.

The accuracy of the ``Critical Reynolds Number'' depends on the largest Taylor Deformation parameter $D$ supported by the grid.  
As we report here, we have found that as long as the grid size is fine enough to support a Taylor Deformation parameter $D<0.95$, 
then the transition region (i.e., ``Critical Reynolds number'') (see Figures 3 and 12) will be captured with a tolerance of three percent.

Figure 3 illustrates that we capture the proper break-up time as the grid is refined and at the point where the critical Reynolds
number is prescribed. In Figure 3, we point out that the time step was $O(10^{-5}$)s for the elongating bubble ($\Delta x=R/16$).
Further refinements reduce the time step according to the surface tension time step constraint. 
The simulation time would become impractical if we tried to improve the accuracy of the ``critical Reynolds number'' further.  
(For example, in the present study, the computation took more than one year for an experiment with $Re$ = 0.0 and $Ca$ = 1.63 
(M\"{u}ller-Fischer et al. (2008)).
A smaller tolerance would necessitate a larger  supported Deformation parameter $D$, which would, in turn, necessitate a 
higher aspect ratio computational domain, increased droplet surface area at break-up, increased number of time steps, and 
higher resolution for representing the drop/bubble at its thinnest point. \\
\\

%%3
\par\noindent
\item
\textsf
{Results: Mostly just pictures are shown from which little is to be learned. The only results of which future use can be expected is the regime map in Fig. 12. Bu this is also only qualitative and based on very few data points. More combinations of Ca and Re should be provided and a quantitative fit to the regime boundary be obtained. Moreover only two values of density and viscosity ratio equal to 1 and ~0.001 are used. An investigation of intermediate values would be straight forward and would allow to provide also models for the influence of these obviously important parameters. In particular it should be clarified whether the difference in behavior is more due to the density ration or more due to the viscosity ratio. Also it needs to be investigated how small these ratios need to be for the gas phase properties to be considered as negligibly small. For the practically important case of air bubbles in water the viscosity ratio is 0.02, an order of magnitude larger than considered in the paper. Whether this can already be considered negligible or not remains unclear.}
\vspace{3 mm}

Response: \\
		We cannot understand this criticism in the context of the referee's previous comment.  They are contradictory statements.  In the previous comment, the referee complains that we have lack of results, and in this section the referee complains that our results are superfluous.  Every Figure that we show strategically informs the reader about the tensile strength properties of a bubble in wall driven shear flow.  All the results that we report are novel and significant tion, and in the present comment, the referee complains about our results which clearly highlight why this problem is so hard, and why it is unreasonable to ask for more.  Already the presented results that we present regarding the ``tensile strength'' of a {\em bubble} in the presence of driven walls
We believe the figures and computational results presented in this study are very valuable to developing the study of drop/bubble deformation and breakup.
The following points were especially presented and revealed in this paper for the first time. \\
\begin{enumerate}
\item The behavior of the bubble deformation process around critical $Re$ conditions with $Ca$ = 0.3  $\sim$ 1.0 has been presented for the first time.
\item The behavior of the bubble breakup process at critical $Re$ conditions with $Ca$ = 0.3  $\sim$ 1.0 has been presented for the first time.
\item The value of critical $Re$ numbers was found for $Ca$ = 0.3  $\sim$ 1.0 for the first time.
\item  We showed that most previous computational studies overestimated drop deformation and breakup because most previous studies used a domain size with $W$ (width ($y$directional length)) =4$R$. Drop deformation is promoted when using a domain size with $W=4R$. 
\item The difference in the deformation and breakup between the bubble and the drop with $\lambda = 1$ and $\eta = 1$ was clearly shown.
\item Shear-induced bubble/drop breakup critical curves were obtained. 
\end{enumerate}

Regarding the effect of $\lambda$ and $\eta$, ongoingly we have examining the effect of $\lambda$ and $\eta$ on drop breakup for following 
combinations of $\lambda$ and $\eta$:

\begin{tabbing}
 \hspace{55mm} \= \hspace{10mm} \kill
 \hspace{5mm} 1. $\lambda$ = 1.0, $\eta$ =1.0 (done) \> 2. $\lambda \simeq 0.0$, $\eta \simeq 0.0$ (this study) \\ 
 \hspace{5mm} 3. $\lambda$ = 1.0, $\eta \simeq 0.0$ (done) \> 4. $\lambda$ = 1.0, $\eta$ =0.01 \\
 \hspace{5mm} 5. $\lambda$ = 1.0, $\eta \simeq 0.1$ \> 6. $\lambda$ = 0.1, $\eta \simeq 0.0$ (done) \\
 \hspace{5mm} 7. $\lambda$ = 0.1, $\eta$ =0.01 \> 8. $\lambda = 0.1$, $\eta$ =0.1  \\
 \hspace{5mm} 9. $\lambda$ = 0.1, $\eta$ =1.0 (done) \> 10. $\lambda$ = 1.0, $\eta$ =10  \\
 \hspace{5mm} 11. $\lambda$ = 1.0, $\eta$ =100 \> 12. $\lambda$ = 1.0, $\eta$ =1000 \\
\end{tabbing}

Since it takes a very long computational time to obtain results for the effect of $\lambda$ and $\eta$ on drop deformation and breakup, 
all computations for these conditions have not been finished. We will also present the fruits of research on the effect of density and 
viscosity ratios in the next papers. \\
\\

%%4
\par\noindent
\item
\textsf
{The effect of gravity is neglected which potentially obliterates the results. It is not at all clear that the effect of the shear flow can be separated from that of gravity without rendering the results meaningless for any practical application. Even when one wants to do so it needs to be considered that the bubbles will be deformed into an ellipsoidal shape. Then at least the influence of initial condition has to be checked in order to ensure that the results make any sense. \\}
\vspace{3 mm}

Response: \\
In our computations, we set $g = 0$ because we wanted to clearly isolate only the effects of the density and viscosity ratios and 
wanted to compare previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$.
When the gravity is considered, we obtain $Fr$ (Froude number) $\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$ = 1.7 ($Re$ = 93 and $Ca$ = 0.3) 
and 1.9 ($Re = 43$ and $Ca$ = 0.8). \\
Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
However, bubbles for both conditions reach the breakup at $t$ = about 0.5 s. 
($V$ (moving wall speed) had about 1.1 $\sim$ 1.3 m/s for the range of $Ca$ and $Re$ in our computaions.)
Therefore, the effect of gravity (bubble rise motion) is expected to be negligible to the behavior of bubble deformation and breakup 
around critical $Re$ number conditions. Our computational results will provide fundamental knowledge and findings for practical applications.
In the revised paper, we have described these explanations.\\
\\
Please see lines 123 to 130.
\\

%%5
\par\noindent
\item
\textsf
{Language and writing (examples):\\
line 191 and following: "Timestep $\Delta t$" appears out of any context. So do "Step 1." to "Step 4".\\
line 232: ""bubble deformation in simple linear shear flow" results" is impossible language. \\}
\vspace{3 mm}

Response: \\
We carefully checked the paper and modified poor English writing, expressions, etc.\\
\textcolor{red}
{
Mark and Edwin: Please modify these sentences at line 191 and line 232. (line198 and 242 in the revised paper.)\\
}
\\
Please confirm lines  198 to 
\\

\end{enumerate}

\closing{On behalf of the authors,}
Mitsuhiro Ohta

\end{letter}
\end{document}

### 2024-11-04 Revised-paper/Reply/Reply-Reviewer2.tex
significance and novelty

%  -----------------------------------------------------------------------------
%  Modified:October 2024
%  -----------------------------------------------------------------------------
\documentclass{letter}

 \date{\today}

\usepackage{color}

\begin{document}
\begin{letter}{
Chemical Engineering Science\\
Professor Wei Ge, Editor\\}

\opening{Dear Prof. Ge,}

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 2: \begin{enumerate}
%%1
\item
\textsf
{Why are there several words in italics in the Introduction section and some other parts?}
\vspace{3 mm}

Response: \\
The italic format was used to emphasize words, But the italic format was removed in the revised 
paper because words in italic format are confusing expressions.\\

%%2
\item
\textsf
{Page 2 Line 14: There should be an "and" before "Renardy"}
\vspace{3 mm}

Response: \\
We appreciate the reviewer's suggestion. The description of the applicable part disappeared 
in the revised paper because we have completely modified the ``Introduction".\\
\\
Please see the ``Introduction".
\\

%%3
\par\noindent
\item
\textsf
{The authors mentioned several DNS methods in the Introduction section while choosing the CLSVOF method in this work. What are the reasons?}
\vspace{3 mm}

Response: \\
As explained in the ``Numerical Analysis", the CLSVOF method couples both the level set and VOF methods and can 
take advantage of both methodologies. 
Consequently,  the CLSVOF method is superior to other interface-capturing/interface-tracking methods. 
This is the reason we selected the CLSVOF method. We only referred to several interface-capturing/interface-tracking 
method methods in introducing previous studies.\\
\\

%%4
\par\noindent
\item
\textsf
{Why can the effect of gravity be disregarded in this work?\\}
\vspace{3 mm}

Response: \\
In our computations, we set $g = 0$ because we wanted to isolate only the effects of the density and viscosity ratios and 
wanted to compare previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$. 
Also, in the revised paper, a brief discussion of the potential influence of gravity (Froude number) on bubble breakup dynamics 
has been added according to another reviewer's suggestion.\\
\\
Please see lines 123 to 130.
\\

%%5
\par\noindent
\item
\textsf
{Page 9: The results of D are compared with those in other literature. 
What are the underlying causes of these differences? It is also noticed that different literatures are used for different verification steps.
Why not use the same literature for verification?}
\vspace{3 mm}

Response: \\
Table 1 shows the comparison of the deformation parameter $D$ (Li et al., Physics of Fluids, Vol.12, 269–282, 2000) for a drop as a function of 
$Re$ ($Ca$ = 0.3, $\lambda =1$ and $\eta = 1$).
The $D$ computationally obtained by Li et al. (2000) is regarded as a benchmark problem in this field. First, we compared the $D$ by Li et al. (2000) 
with our computational results. Also, In Fig. 2,  we compared the appearance of drop breakup (Renardy and Cristini, 
Physics of Fluids, Vol.13, 2161–2164, 2001) with our computational results.
On the other hand, regarding quantitative physical quantities on bubble deformation and breakup, only experimental results for $D$ exist under 
the condition of $Re \simeq 0$.
Thus, As shown in Table 2, we performed the comparison of the deformation parameter $D$ for a bubble as a function of  $Ca$ 
($Re \simeq 0$, $\lambda  \simeq 0$ and $\eta  \simeq 0$). In the experiments, obtaining precise experimental data will be difficult because 
the dynamic motion of a bubble in a highly viscous liquid in an experimental device needs to be accurately set.
We don't know the cause of the difference between both experimental results, but our numerical results were close to those of Rust and 
Manga (Journal of Colloid and 
Interface Science, Vol. 249, 476– 480 2002). For your reference, computations for bubble deformation with the condition of $Re \simeq 0$ 
were hard tasks and a very long computational time (one year) was needed. \\
\\

%%6
\par\noindent
\item
\textsf
{Page 14: What are the units of the variable T?.}
\vspace{3 mm}

Response: \\
$T$ is the dimensionless time defined by $T$ =$\mathit{\Gamma} t$. \\
\\
Please confirm line 354.
\\

%%7
\par\noindent
\item
\textsf
{Figure 4: Drop deformation and breakup are compared under conditions with $Re$ = 1.0 and 1.1. When $Re$ = 1.0, the simulation ends at $T$ = 35.0, and it is stated that drops will not break up. When $R$ = 1.1, the drop also does not break up at $T$ = 35.0. It breaks up at $T$ = 56.7. What about also showing the status of drop under $Re$ = 1.0 at $T$ = 56.7? It might be a more reasonable comparison.}
\vspace{3 mm}

Response: \\
We agree with the reviewer's suggestion. We added results at $T$ = 40.1, 50.0, and 56.7 to the drop status for $Re$ = 1.0 in Fig. 4.
As can be seen from new Fig. 4, a drop remains a stable deformed state after $T$ = 35.0. In the revised paper, such a comment was added.\\
\\
Please confirm lines 380 to 381.
\\

%%8
\par\noindent
\item
\textsf
{Figures 5 - 9: I am curious about the way that the selection of the Ts. Why are they not unified in these five figures?.}
\vspace{3 mm}

Response: \\
Regarding Figs. 5 and 6, we compared bubble dynamics for $Re$ = 92 (Fig. 5) with that for $Re$ = 93 (Fig. 5) at almost the same $T$.
But, we found a mistake in Fig. 5: we replaced the figure with $T$ = 17.4 with the figure with $T$ = 12.2.
In the same way, we replaced the figure with $T$ = 24.3 with the figure with $T$ = 17.0 in Fig. 10. \\

Fig. 7 shows the detailed bubble breakup process. Giving the highest priority to show the detailed bubble breakup process, we selected 
results with $T$ independently of $T$ set in Figs. 5 and 6.\\

Fig. 8 shows the shear stress profile around a bubble for two Reynolds numbers ($Re$ = 50 and 93). In Fig. 8, the shear stress for the 
$Re$ = 50 condition was drawn around the bubble after the bubble attained a stable deformed state.
The shear stress for the case of $Re$ = 93 was depicted when the bubble sufficiently elongated ($T$ = 14.9).
We wanted to compare the maximum shear stress value at both $Re$ conditions. \\
In the revised paper, these explanations for Fig. 8 were added.\\

As for Fig. 9, we drew velocity fields around bubbles corresponding to Fig. 7.\\
\\

%%9
\par\noindent
\item
\textsf
{Page 16 Line 395: Why does the bubble not develop the bulb-like shape like the drop?.}
\vspace{3 mm}

Response: \\
In the breakup of the drop with $\lambda =1$ and $\eta = 1$ (Fig. 4), the drop starts to break at the center of the drop without 
the elongation in the first place because the drop easily breaks under the low $Re$ number. 
Consequently, the drop breakup is seemingly developed with a bulb-like shape because the liquid bridge between two mother 
drops is formed in the breakup process.
On the other hand, in the case of the bubble, very large shear forces are required to deform the bubble because $\lambda \simeq 0$ 
and $\eta \simeq 0$.
Thus, the bubble undergoing large shear forces is largely stretched along the direction of the shear flow, and the very long 
elongated bubble is finally formed. 
Accordingly, the bubble breaks up without the bulb-like shape. In the revised paper, we added these considerations.\\
\\
Please see lines 408 to 413.
\\

%%10
\par\noindent
\item
\textsf
{Page 17 Line 424: What are the possible reasons that the bubble breakup process is different from the drop breakup process?}
\vspace{3 mm}

Response: \\
As mentioned above (Answer 9), the effect of $\lambda$ and $\eta$ on the breakup process is large, and especially $\eta$ is 
a dominant factor for the breakup process. 
The shear stress is defined by $\tau = \mu$$\dot{\gamma}$ ($\dot{\gamma}$: the shear-rate (the velocity gradient)).
As is obvious from this equation, since the viscosity of a gas is much less than that of a liquid($\eta \simeq 0$), so a very large velocity 
gradient needs to be achieved to realize $\tau$ that makes the bubble largely deformed.
As a result, the bubble undergoing large shear forces (velocity gradients) is largely stretched along the direction of the shear flow, and
the appearance of the bubble breakup becomes quite different from that of a drop 
Therefore, to be exact, the bubble breakup process is different from the drop breakup with $\lambda = 1$ and $\eta =1$.  
We added "with $\lambda = 1$ and $\eta =1$" to the revised paper.
Ongoingly, we have been examining the effect of $\lambda$ and $\eta$ on drop breakup, and it is confirmed that large shear forces 
are required to deform the drop when $\lambda = 1$ and $\eta \simeq 0$ and the drop breaks up by way of forming the long 
elongated shape. 
Also, we have referred to the effect of the viscosity ratio on the deformation and breakup of the drop in the revised paper.\\
\\
Please see lines 440 to 442.
\\

%%11
\par\noindent
\item
\textsf
{Section 4.4: What about the velocity field of the breaking drop? In the previous text and figures, it does not seem similar to that of the breaking bubble.}
\vspace{3 mm}

Response: \\
Detailed velocity fields of the deforming and/or breaking drop have already been presented in some literature.
So, we have not shown the velocity fields of the deforming and/or breaking drop here.
The behavior of a breakup influences the velocity fields for the drop and the bubble, so the velocity fields between the drop 
and the bubble is not similar.
In the revised paper, we added these explanations.  \\
\\
Please see lines 497 to 501.
\\

%%12
\par\noindent
\item
\textsf
{Is there any correlation that can be summarized between Rec and Ca?}
\vspace{3 mm}

Response: \\
We need to additionally investigate $Re_{\rm c}$ for a wider $Ca$ number condition to consider correlation between $Re_{\rm c}$ and $Ca$,
but we predict that a correlation with $Re_{\rm c}$ as a function of $Ca$ for predicting the bubble breakup can be formulated.\\
\\

\end{enumerate}

\closing{On behalf of the authors,}
Mitsuhiro Ohta

\end{letter}
\end{document}

### 2024-11-04 Revised-paper/Reply/Reply-Reviewer3.tex
significance and novelty

%  -----------------------------------------------------------------------------
%  Modified:October 2024
%  -----------------------------------------------------------------------------
\documentclass{letter}

 \date{\today}

\usepackage{color}

\begin{document}
\begin{letter}{
Chemical Engineering Science\\
Professor Wei Ge, Editor\\}

\opening{Dear Prof. Ge,}

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 3: \begin{enumerate}
%%1
\item
\textsf
{The manuscript needs extensive revision for language and grammar.}
\vspace{3 mm}

Response: \\
We carefully checked English writing and grammar.\\

%%2
\item
\textsf
{Discuss more your results.}
\vspace{3 mm}

Response: \\
We additionally developed a discussion for our results.\\
\\
Please see the red characters in the ``Results and Discussion".
\\

%%3
\par\noindent
\item
\textsf
{Improve your figures.}
\vspace{3 mm}

Response: \\
We are confused about the reviewer's comment because the reviewer did not provide which figures to improve.
We carefully checked all the figures and improved Figs. 4, 5, and 10.\\
\\

%%4
\par\noindent
\item
\textsf
{What is the novelty of your study?\\
Discuss about other studies on numerical simulation of bubble deformation. How your study differs?\\
Improve Introduction section.\\}
\vspace{3 mm}

Response: \\
We have referred to and explained previous studies about bubble deformation and breakup in the ``Introduction".
Besides, we have stated the novelty of this study and the difference between this study and previous studies.
In previous experimental studies on the motion of bubble deformation in a simple shear flow, only bubble deformation under very 
low $Re$ number conditions ($Re \ll 1$) have been examined.  
Meanwhile, only a few studies have been reported for the numerical simulation of bubble deformation and breakup in a simple shear flow.
These previous studies mainly examined the dynamics of bubble deformation in a shear flow.
Concerning bubble breakup, Wei et al. (2012) presented only one numerical result for a bubble breakup process under 
the condition of $Ca$ (capillary number) = 35.  
In this study, we first determined the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup for $Ca = 0.3 \sim 1.0$.
This is the largest novelty in this study.
Additionally, our study revealed characteristics that distinguish a drop's deformation and breakup processes from a bubble.\\
In the revised paper, we have completely modified the ``Introduction".  \\
\\
Please see the ``Introduction".
\\

%%4
\par\noindent
\item
\textsf
{The conclusions are not supported by the results and discussion.}
\vspace{3 mm}

Response: \\
We carefully checked The ``Conclusions", and believe the results and discussion properly support our conclusions.\\
We have made a minor alteration to the  ``Conclusions".\\
\\
Please see the ``Conclusions".
\\

\end{enumerate}

\closing{On behalf of the authors,}
Mitsuhiro Ohta

\end{letter}
\end{document}

### 2024-11-04 Revised-paper/Reply/Reply-Reviewer4.tex
significance and novelty

%  -----------------------------------------------------------------------------
%  Modified:October 2024
%  -----------------------------------------------------------------------------
\documentclass{letter}

 \date{\today}

\usepackage{color}

\begin{document}
\begin{letter}{
Chemical Engineering Science\\
Professor Wei Ge, Editor\\}

\opening{Dear Prof. Ge,}

Please find enclosed the revised version of our manuscript (CES-D-24-01867):
``Numerical Simulation of Bubble Deformation and Breakup under 
Simple Linear Shear Flows''.
We thank the reviewers for their comments and thoughts regarding improvement 
of our paper. We believe that we have addressed all of the reviewers’ 
concerns; the changes are itemized in detail below.

\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  Also, changes are hi-lighted in red.
\par\noindent

Changes made in response to comments of Reviewer 4: 
\begin{enumerate}
%%1
\item
\textsf
{The investigated ranges of density ratio ($\lambda$) and viscosity ratio ($\eta$) could be expanded to encompass lower values, which 
would be applicable to various gas-liquid systems, including molten metal processes and slurry bubble columns.}
\vspace{3 mm}

Response: \\
Thank you for your kind comments. 
In the revised paper, we have completely modified the ``Introduction" and stated the target and applicable processes of this study.\\
\\
Please see the ``Introduction".
\\

%%2
\par\noindent
\item
\textsf
{Additional details regarding the computational tools/code and algorithms employed would enhance the reproducibility of the 
results presented in this study.}
\vspace{3 mm}

Response: \\
Thank you very much for your suggestions.  We have additionally referred to our papers (following three papers) 
performed based on the computational code with the same algorithm.

\begin{enumerate}
\item [1.] M. Ohta, T. Furukawa, Y. Yoshida, M. Sussman,\\
A Three-Dimensional Numerical Study on the Dynamics and Deformation of a Bubble Rising in a Hybrid Carreau and FENE-CR Modeled Polymeric Liquid, 
Journal of Non-Newtonian Fluid Mechanics, Vol.265, pp.66-78 (2019).\\
\item [2.] M. Ohta, Y. Akama, Y. Yoshida, \\
M. Sussman, Influence of the Viscosity Ratio on Drop Dynamics and Breakup for a Drop Rising in an Immiscible Low-Viscous Liquid,\\
Journal of Fluid Mechanics, Vol.752, pp.383-409 (2014).\\
\item [3.]  M. Ohta, M. Sussman, \\
The Buoyancy-Driven Motion of a Single Skirted Bubble or Drop Rising through a Viscous Liquid, \\
Physics of Fluids, Vol.24, 112101 (18pp) (2012).\\
\end{enumerate}
Please see lines 223 to 227.
\\

%%3
\par\noindent
\item
\textsf
{The authors should elucidate the rationale behind constraining the viscosity ratio to values below $10^{-3}$.}
\vspace{3 mm}

Response: \\
In the paper, we already described physical properties (density, viscosity, surface tension) set in the computations:\\
\\
Bubble: $\rho_{\rm b}$ = 1.2 kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5} $ Pa$\cdot$s\\
Liquid:  $\rho_{\rm m}$ = 1000 kg/m$^{3}$ and $\mu_{\rm m}$ = a changeable value corresponding to $Ca$ [Pa$\cdot$s]\\
Surface tension : $\sigma =2.5 \times 10^{-2}$ N/m. \\
Then, $\mu_{\rm m}$ had $2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s and
$V$ had about 1.1 $\sim$ 1.3 m/s for the range of $Ca$ and $Re$ in our computaions.\\
When $\mu_{\rm m}$ = $2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s, we have $\eta < 1.0 \times 10^{-3}$.\\
We have added the range of $\mu_{\rm m}$ and $V$ used in this study.\\
\\
Please see lines 119 to 120.
\\

%%4
\par\noindent
\item
\textsf
{While gravitational effects were not considered in this investigation, a brief discussion of the potential influence 
of the Froude number (Fr) on bubble breakup dynamics would provide valuable context.}
\vspace{3 mm}

Response: \\
We agree with the reviewer's comment.  \\
In our computations, we set $g = 0$ because we wanted to isolate only the effects of the density and viscosity ratios and 
wanted to compare previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$.
When the gravity is considered, we obtain $Fr$ (Froude number) $\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$ = 1.7 ($Re$ = 93 and $Ca$ = 0.3) 
and 1.9 ($Re = 43$ and $Ca$ = 0.8). \\
Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
However, bubbles for both conditions reach the breakup at $t$ = about 0.5 s. 
Accordingly, it is expected that the effect of gravity (bubble rise motion) can be negligible to the behavior of bubble deformation and breakup 
around critical $Re$ number conditions.
In the revised paper, we have described these explanations.\\
\\
Please see line 95 (the definiton of $Fr$) and lines 123 to 130.
\\

\end{enumerate}

\closing{On behalf of the authors,}
Mitsuhiro Ohta

\end{letter}
\end{document}

### 2024-11-04 Revised-paper/Highlights.tex
significance and novelty

%  -----------------------------------------------------------------------------
%  Modified:October 2024
%  -----------------------------------------------------------------------------
\documentclass{article}

\usepackage{color}

\begin{document}
Highlights\\

\begin{itemize}
\item The deformation and breakup of a bubble in liquids undergoing simple linear shear flow are computationally reproduced.

\item Shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.

\item The critical conditions for bubble breakup concerning the Reynolds and capillary numbers are determined.

\item The bubble oscillates between elongating and shrinking motions for non-rupturing flow conditions.

\end{itemize}

\end{document}

### 2024-11-04 Revised-paper/Paper/Bubble-deformation-Rev.tex
significance and novelty

--- 2024-07-25 Bubble-deformation.tex
@@
 %\documentclass[preprint,12pt,authoryear]{elsarticle}
-\documentclass[review]{elsarticle}
+\documentclass{elsarticle}
 
@@
 %% please give \usepackage{epsfig}
-
-\usepackage{lineno}
 
@@
 
-%\graphicspath{{figures/}}
-\graphicspath{{Figure/}}
+\graphicspath{{figures/}}
 
@@
 \usepackage{color}
+\usepackage{comment}
+% line numbers
+\usepackage{lineno}
 %\usepackage{ragged2e}
@@
 
-\journal{Chemical Engineering Journal}
+\journal{Chemical Engineering Science}
 
@@
 \cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
-\address[1]{
+\affiliation[1]{
   organization={Department of Mechanical Science, Graduate School of Technology, 
@@
   country={Japan}}
-\address[2]{
+\affiliation[2]{
   organization={Department of Mechanical Engineering, Graduate School of Technology, 
@@
 
-\address[3]{
+\affiliation[3]{
   organization={High Performance Plastics Company, Sekisui Chemical Co., Ltd.},
@@
 \author[4]{Edwin Jimenez}  
-\address[4]{
+\affiliation[4]{
   organization={Spectral Numerical, LLC},
@@
 \author[5]{Mark Sussman}  
-\address[5]{
+\affiliation[5]{
   organization={Department of Mathematics, Florida State University},
@@
 \begin{abstract}
+\textcolor{red}
+{
 Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.  
-Numerical results are obtained using a hydrodynamic scheme with formal second-order accuracy based on a coupled level set/volume-of-fluid (CLSVOF) method.
-To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.
-The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.
-The first distinguishing factor for bubble breakup is that the magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case.
-In other words, a larger Reynolds number is needed to induce bubble breakup.
-The second distinct feature of the bubble system versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the critical ``breakup'' Reynolds number.
-It is asserted that the differences in morphology for a bubble undergoing breakup versus a drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.
+Numerical results are obtained using a hydrodynamic scheme with formal second-order accuracy based on a coupled level 
+set/volume-of-fluid (CLSVOF) method.  To verify our numerical algorithm and provide a basis for comparison, we also 
+present simulation results that compare with previous, more popular, drop deformation and rupture simulations.  
+The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that 
+of the analogous drop system under similar flow conditions.  The first distinguishing factor for bubble breakup is that the 
+magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case. 
+In other words, a larger Reynolds number is needed to induce bubble breakup.  The second distinct feature of the bubble system 
+versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the 
+critical ``breakup'' Reynolds number.  It is asserted that the differences in morphology for a bubble undergoing breakup versus a 
+drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.
 The critical conditions for bubble breakup with respect to the Reynolds and capillary numbers are determined for several cases.  
+}
 \end{abstract}
@@
 
+%\maketitle
+
+%\tableofcontents
 \linenumbers
-
-%\maketitle
-
-%\tableofcontents
-
 %  -----------------------------------------------------------------------------
@@
 %
-Bubble dynamics in shear flow, {\em including breakup}, is critically important for various scientific and engineering processes.
-We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, and microbubbles in the blood circulation system,\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.  This article presents computational studies of shear-driven deformation {\em and breakup} of a bubble in insoluble viscous liquids.  Studying bubble break-up via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ conditions, low-density ratio (1:1000), and low viscosity ratios (1:100).  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
-
-In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme conditions at which a bubble in shear flow first transitions from deformation to breakup.
-We validate our numerical method by examining the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.
-An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties to ascertain the sensitivity of deformation and breakup to physical parameters.
-In our computations, the time-evolution of the boundary between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SUSSMAN2007469}.
-We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify the parameter regimes in which a relatively simple system transitions from stable to unstable.
-Specifically, we ascertain the critical Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.
-
-In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
-In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to \emph{bubble} breakup.
-Additionally, our computational studies reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
-
-We remark that there have been a number of articles on the study of lift of {\em slightly} deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
-We reiterate, though, that for bubble deformation {\em and breakup} in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15}.
+\textcolor{red}
+{
+Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes. 
+We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, 
+and microbubbles in the blood circulation system, \cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.  
+In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
+This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  
+Studying bubble break-up via computation rather than experiments simplifies the process of setting a combination of precise, simple shear 
+flow conditions, low $Ca$ conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish 
+bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity 
+ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' 
+denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ 
+and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.  
+%
+In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme 
+conditions at which a bubble in shear flow first transitions from deformation to breakup.  We validate our numerical method by examining 
+the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.  An advantage of studying shear-driven 
+bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties to 
+ascertain the sensitivity of deformation and breakup to physical parameters.  In our computations, the time-evolution of the boundary 
+between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.  
+We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify 
+the parameter regimes in which a relatively simple system transitions from stable to unstable.  Specifically, we ascertain the critical 
+Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.          
+%
+In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings 
+for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.  In this work, we determine, for the 
+first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.  Additionally, our computational studies 
+reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
+%
+We remark that there have been a number of articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.  
+We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15}.
 These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.
-Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup process under the condition of $Ca$ (Capillary number) = 35.
-
+Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup process under 
+the condition of $Ca$ (capillary number) = 35. \\ \indent
+%
 To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop.
-We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the simpler drop problem.
-For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
-
-The study of the deformation {\em and breakup} of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.
-The pioneering experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.
-By the 2000s, progress in computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused on direct simulations of this problem.
-In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.
-Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.
-
+We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the 
+simpler drop problem. For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
+%
+The study of the deformation and breakup of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated 
+extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.The pioneering 
+experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and 
+experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.  By the 2000s, progress in 
+computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused 
+on direct simulations of this problem.  In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) 
+method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}. 
+Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued 
+to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, 
+IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this 
+problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, 
+front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.
+\textcolor{blue} 
+{
+Thus, a lot of studies about the deformation and breakup of a drop in simple linear shear have been presented so far. In contrast, few
+ studies have been conducted on bubble deformation and breakup.
+ }
+}
 %  -----------------------------------------------------------------------------
@@
 two-phase flow problems are also determined by the density ratio $\lambda$ and
-the viscosity ratio $\eta$.  In the present study, the effect of gravity is not
-considered so that we ignore the effect of the $Fr$ number.
+the viscosity ratio $\eta$.  In the present study, in order to clearly isolate only the effects 
+of $\lambda$ and $\eta$, the effect of gravity is not considered ($g = 0$) so that 
+we ignore the effect of the $Fr$ number 
+\textcolor{red}
+{
+$\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$.
+}
 
@@
 mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.
-\cite{LiRenRen00}).  Thus, for comparison with previous drop deformation and
+\citet{LiRenRen00}).  Thus, for comparison with previous drop deformation and
 breakup problems, we set $\lambda = \eta = 1$ (and also neglect the effect of
@@
 kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We
-emphasize that for consistency with previous studies (\cite{LiRenRen00,
+emphasize that for consistency with previous studies (\citet{LiRenRen00,
 RusMan02, MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), we
@@
 =2.5 \times 10^{-2}$ N/m. The values of $Re$ and $Ca$ in our simulations are
-controlled by changing the values of $\mu_{\rm m}$ and $V$.  For studying
-bubble deformation and break-up, the density and viscosity ratios satisfy
+controlled by changing the values of $\mu_{\rm m}$ and $V$. 
+\textcolor{red}
+{
+Specifically, we set $\mu_{\rm m} = 2.0 \times 10^{-2} \sim 6.0 \times 10^{-2}$ Pa$\cdot$s and
+$V$ = about 1.1 $\sim$ 1.3 m/s.
+As a consequence, 
+}
+for studying bubble deformation and break-up, the density and viscosity ratios satisfy
 $\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.
 
+\textcolor{red}
+{
+For readers’ reference, we describe the effect of gravity here. When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.
+Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
+However, bubbles in our computations reach the breakup by way of deformation very quickly at $t$ = about 0.5 s. 
+Accordingly, it is expected that the effect of gravity (bubble rise motion) can be small for the behavior of bubble deformation and breakup 
+around critical $Re$ number conditions in our study.
+}
 %  -----------------------------------------------------------------------------
@@
 \begin{figure}%[h!]
-  \includegraphics[width=\textwidth]{1-SchematicAndGrid}
+%  \includegraphics[width=\textwidth]{1-SchematicAndGrid}
+  \centering
+  \includegraphics[scale=0.4]{Figure/1-SchematicAndGrid}
   \caption{(a) Computational domain schematic for a bubble or drop in shear 
@@
 Coupled Level Set and Volume of Fluid (CLSVOF) method
-\cite{SusPuc00,SUSSMAN2007469}, which is based on a fixed grid finite volume
+(\citet{SusPuc00,SusSmiHusOhtZhi07}), which is based on a fixed grid finite volume
 algorithm.  The CLSVOF method is a robust  numerical  technique
 that  combines  some  of  the  advantages  of the Volume of Fluid (VOF) method
-(\cite{HirNic81}) and the Level Set (LS) (\cite{SusSmeOsh94}) method while
+(\citet{HirNic81}) and the Level Set (LS) (\citet{SusSmeOsh94}) method while
 overcoming their weaknesses.  In the VOF method,  the Volume Fraction function,
@@
 and is equivalent to specifying that the jump in the normal stress is equal to
-$\sigma\kappa$~\cite{TanguyEtAl2007}.  The surface tension force expressed by
+$\sigma\kappa$ (\citet{TanguyEtAl2007}).  The surface tension force expressed by
 the singular Heaviside gradient term acts only on the gas-liquid interface.
-The sharp interface ``Ghost Fluid Method'' \cite{kang2000boundary} is used to
+The sharp interface ``Ghost Fluid Method'' (\citet{KanFedLiu00}) is used to
 discretize the gradient of the Heaviside function as it appears in the surface
@@
 computed with second order accuracy directly from the volume-of-fluid (VOF)
-function using the height function technique~\cite{Sus03,SUSSMAN2007469}.  
+function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).  
 We remark that we get the same
@@
 The temporal discretization of our numerical method is an operator split
-projection method as described by \cite{SUSSMAN2007469}.  An outline of 
-our method is as follows (see \cite{SUSSMAN2007469}, section 4, for more 
+projection method as described by \citet{SusSmiHusOhtZhi07}.  An outline of 
+our method is as follows (see \citet{SusSmiHusOhtZhi07}, section 4, for more 
 details):
@@
 \item[Timestep $\Delta t$] The timestep is governed by the CFL condition and
-  surface tension (section 5.7 of \cite{SUSSMAN2007469}):
+  surface tension (section 5.7 of \citet{SusSmiHusOhtZhi07}):
  \begin{eqnarray*}
@@
 utilize an adaptive hierarchy of grids based on a dynamic adaptive mesh
-refinement (AMR) technique~\cite{SusAlmBelColHowWel99}.  Adaptive grids are
+refinement (AMR) technique (\citet{SusAlmBelColHowWel99}).  Adaptive grids are
 dynamically adjusted based on the location of the 
@@
 %  -----------------------------------------------------------------------------
-Numerical studies reported in this section
-are presented in order to verify the accuracy of our computational
-method.  First, we compare quantitatively against the steady-state drop
-deformation results reported by Li et al. \cite{LiRenRen00}.  The shape of a
+\textcolor{red}
+{
+The effectiveness of our computational method has been demonstrated for the complicated rising motion of 
+single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19} .
+In this section, the accuracy of our computational method will be verified for the problem of shear-induced 
+deformation of a drop and bubble. 
+}
+First, we compare quantitatively against the steady-state drop
+deformation results reported by \citet{LiRenRen00}.  The shape of a
 deformed drop in simple linear shear flow is described in terms of the Taylor
@@
 For consistency, we perform numerical simulations using CLSVOF over the same
-computational domain and grid size used in~\cite{LiRenRen00}, which has dimensions 
+computational domain and grid size used in \citet{LiRenRen00}, which has dimensions 
 $\lwh{8}{4}{8}$ (recall that $R$ is
@@
 as a function of $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
-the VOF method used in \cite{LiRenRen00}, and also with our CLSVOF algorithm.
+the VOF method used in \citet{LiRenRen00}, and also with our CLSVOF algorithm.
 Table~\ref{tab:DeComparison} indicates that our numerical results are in good
@@
 Reynolds number                      & 0.1     & 0.5     & 0.6     & 0.75      \\
-$D$(Li et al. (\cite{LiRenRen00}))  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
+$D$(\citet{LiRenRen00})  & 0.3968  & 0.45    & 0.4768  & Breakup   \\
 $D$(Our study) & 0.3960  & 0.4570  & 0.4758  & Breakup   \\
@@
 with the ``bubble deformation in simple linear shear flow'' results reported by
-Muller-Fischer et al.~\cite{MulTobDreFisWin08}.  Muller-Fischer et
-al.~\cite{MulTobDreFisWin08} experimentally inquired into the bubble
+\citet{MulTobDreFisWin08}.  \citet{MulTobDreFisWin08} experimentally inquired into the bubble
 deformation under the condition of $Re \approx 0$.  In our study, we computed
@@
 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.  The parameters that we have
-prescribed are consistent with the experimental conditions by Muller-Fischer et
-al.  \cite{MulTobDreFisWin08}.  Comparisons of our numerical results and
-previous experimental results (\cite{MulTobDreFisWin08}) are tabulated in
+prescribed are consistent with the experimental conditions by  \citet{MulTobDreFisWin08}.  
+Comparisons of our numerical results and
+previous experimental results (\citet{MulTobDreFisWin08}) are tabulated in
 Table~\ref{tab:DeComparisonRe=0}.  Additionally, in
 Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
-condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by Rust and
-Manga (\cite{RusMan02}). These experimental values by Rust and Manga
-(\cite{RusMan02}) were obtained from the graph showing the relation of $D$ vs
-$Re$ (\cite{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
+condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by  \citet{RusMan02}. 
+These experimental values were obtained from the graph showing the relation of $D$ vs
+$Re$ (\citet{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
 numerical results predicted larger values of $D$ than experimental ones
-reported by Muller-Fischer et al.~\cite{MulTobDreFisWin08}. Nevertheless, we
+reported by \citet{MulTobDreFisWin08}. Nevertheless, we
 found that our numerical results are very close to the experimental results by
-Rust and Manga (\cite{RusMan02}), which emphasizes the intrinsic difficulties
+\citet{RusMan02}, which emphasizes the intrinsic difficulties
 associated with experimental investigations of bubble dynamics, even in simple
@@
 Capillary number & 0.96  & 1.63  \\
-{$D$}(Muller-Fischer et al. (\cite{MulTobDreFisWin08}))   & 0.37   &   0.58     \\
-{$D$}(Rust and Manga (\cite{RusMan02}))    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
-{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.75     \\
+{$D$}(\citet{MulTobDreFisWin08})   & 0.37   &   0.58     \\
+{$D$}(\citet{RusMan02})    & $0.71\pm 0.05$   &   $0.81\pm 0.02$     \\
+{$D$}(Our study $\Delta x^{\ell=1}=R/16$)  & 0.63   &   0.71     \\
 % 8 months compute time.
@@
   \centering
-  \includegraphics[width=\textwidth]{2-DropBreakComparison}
+%\includegraphics[width=\textwidth]{2-DropBreakComparison}
+  \includegraphics[scale=0.5]{Figure/2-DropBreakComparison}
   \caption{Comparison with results reported 
-	in~\cite{RenCri01-2} 
+	in~\citet{RenCri01-2} 
 	(shown in boxes) 
         for drop breakup in shear flow.  
-	In~\cite{RenCri01-2},
+	In~\citet{RenCri01-2},
 	the computational domain
@@
 	grid size 
-	in~\cite{RenCri01-2} 
+	in~\citet{RenCri01-2} 
 	was set to 
@@
 	Reprinted with permission from 
-        reference~\cite{RenCri01-2}. 
+        reference~\citet{RenCri01-2}. 
 	Copyright 2001, AIP Publishing. 
@@
         obtained with our CLSVOF algorithm, corresponding to each case in
-        reference~\cite{RenCri01-2}, are shown outside boxes.  The
+        reference~\citet{RenCri01-2}, are shown outside boxes.  The
         CLSVOF method used a two-level AMR computational domain 
@@
 Finally, we present a comparison with numerical results for drop breakup reported
-in~\cite{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop breakup
+in~\citet{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop breakup
 with pinch-off behavior for three $Re$ and $Ca$ conditions and with constant
@@
 Figures~\ref{fig:DropBreakComp}(a)-(c), respectively.  The results reported
-in~\cite{RenCri01-2}, which were obtained with a VOF method, are shown inside
+in~\citet{RenCri01-2}, which were obtained with a VOF method, are shown inside
 boxes while results obtained with our CLSVOF approach are displayed outside
-boxes.  In the computations presented in~\cite{RenCri01-2}, the dimensions
+boxes.  In the computations presented in~\citet{RenCri01-2}, the dimensions
 $W=4R$ and $H=8R$ were fixed, while $L$ was changed depending on $Re$ and $Ca$
@@
 Figure~\ref{fig:DropBreakComp} verify that our numerical approach can reproduce
-the same drop breakup behavior presented in~\cite{RenCri01-2}.  Slight
+the same drop breakup behavior presented in~\citet{RenCri01-2}.  Slight
 differences between the results can be attributed to the increased resolution
@@
 reduced by a factor of 2 each time the grid is refined by a factor of 2. Also,
-we refer the reader to \cite{ohta2011robust} in which we apply our CLSVOF
+we refer the reader to \citet{ohta2011robust} in which we apply our CLSVOF
 method for bubble formation problems.
@@
 and a fixed width $W=4R$, the effect of the height $H$ on drop behavior was
-examined in~\cite{LiRenRen00} for Stokes flows and various $Ca$ conditions and
-in~\cite{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.  Other related studies
-investigated drop breakup sensitivity~\cite{RenCri01-1} and drop deformation
-sensitivity~\cite{RenCriLi02} with respect to the entire domain size.
+examined in~\citet{LiRenRen00} for Stokes flows and various $Ca$ conditions and
+in~\citet{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.  Other related studies
+investigated drop breakup sensitivity (\citet{RenCri01-1}) and drop deformation
+sensitivity (\citet{RenCriLi02}) with respect to the entire domain size.
 %
@@
   \centering
-%  \includegraphics[width=\textwidth]{DeEvolution}
-  \includegraphics[width=\textwidth]{3-Comparison-of-De-New}
+% \includegraphics[width=\textwidth]{3-Comparison-of-De-New}
+  \includegraphics[scale=0.6]{Figure/3-Comparison-of-De-New}
   \caption{Time evolution of the deformation 
@@
 We make the distinction between our present research, and the research found in
-the work of Zang, Ni, and Magnaudet\cite{zhang2021three,zhang2022three} on
+the work of  \citet{zhang2021three,zhang2022three} on
 predicting the conditions for bubble mergers.  Even in the most extreme cases
 for mergers, the largest Deformation parameter never exceeds $0.4$ in
-\cite{zhang2021three}.  In summary, our gridding requirements necessitate grid
+\citet{zhang2021three}.  In summary, our gridding requirements necessitate grid
 points distributed relatively evenly throughout the computational domain when a
-bubble is stretched to a $D=0.9$ Deformation, whereas in \cite{zhang2021three}
+bubble is stretched to a $D=0.9$ Deformation, whereas in \citet{zhang2021three}
 the gridding strategy necessitates a more localized strategy.
@@
   \centering
-  \includegraphics[width=\textwidth]{4-DropBreakEvol}
+  \textcolor{red}
+{
+  \includegraphics[width=\textwidth]{Figure/4-DropBreakEvol}
   \caption{Time evolution of drop deformation and breakup in shear flow at the
@@
 	   ($\lambda$ = $\eta$ = 1.0)}
+ }
   \label{fig:DropBreak}
@@
 deformation.  The time evolution of drop deformation and breakup in simple
-linear shear flow for two conditions is shown in Figure~\ref{fig:DropBreak};
-the first case, shown in Figure~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and
-$Re=1.0$, while the second case, depicted in Figure~\ref{fig:DropBreak}(b),
+linear shear flow for two conditions is shown in Figure 4;
+%~\ref{fig:DropBreak};
+the first case, shown in Figure 4(a),
+%~\ref{fig:DropBreak}(a)
+uses $Ca=0.3$ and $Re=1.0$, while the second case, depicted in Figure 4(b),
+%~\ref{fig:DropBreak}(b),
 uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the
 case with $Re=1.0$, the drop gradually deforms and finally attains a stable
-deformed state with $D$= 0.549.  Over the same domain, for the case with
+deformed state. 
+\textcolor{red}
+{
+After $T$ = 35.0, the drop remains a stable deformed state with $D$= 0.549.
+}
+Over the same domain, for the case with
 $Re=1.1$, the ``mother'' drop elongates over time and the volume at the ends of
@@
   \centering
-  \includegraphics[width=\textwidth]{5-BubbleBreakCa0p3Re92}
+  \includegraphics[width=\textwidth]{Figure/5-BubbleBreakCa0p3Re92}
   \caption{Time evolution of bubble deformation in shear flow at the
@@
   \centering
-  \includegraphics[width=\textwidth]{6-BubbleBreakCa0p3Re93}
+  \includegraphics[width=\textwidth]{Figure/6-BubbleBreakCa0p3Re93}
   \caption{Time evolution of bubble deformation in shear flow at the
@@
 deformation process.  It is also evident that the ends of the deforming bubble
-develop cusped shapes under the influence of the strong shear flow.  A
-noteworthy feature for the non-breaking bubble is that it does not settle into
+develop cusped shapes under the influence of the strong shear flow.
+\textcolor{red}
+{
+In providing a more detailed description, very large shear forces are required to deform the bubble 
+because $\lambda \simeq 0$ and $\eta \simeq 0$.
+Thus, the bubble undergoing large shear forces at $T > 0$ is largely stretched long the shear flow direction, 
+and the very long elongated bubble with cusped shapes is formed. 
+Accordingly, the bubble finally breaks up through f the elongated shape without forming a bulb-like shape.
+}
+A noteworthy feature for the non-breaking bubble is that it does not settle into
 a deformed stable state as in the case of drop deformation presented in
@@
   \centering
-  \includegraphics[width=\textwidth]{7-BubBreakCa0p3Re93Detail}
+  \includegraphics[width=\textwidth]{Figure/7-BubBreakCa0p3Re93Detail}
   \caption{Detail of bubble breakup process in shear flow at the condition
@@
 results clearly demonstrate that the bubble breakup process is markedly
-different from the analogous drop breakup process.
+different from the analogous drop breakup process 
+\textcolor{red}
+{
+with $\lambda = 1$ and $\eta =1$. Note that the appearance of deformation and breakup of the drop
+will largely depend on the viscosity ratios.
+}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{8-ShearStress}
+% \includegraphics[width=\textwidth]{8-ShearStress}
+  \includegraphics[scale=0.4]{Figure/8-ShearStress}
   \caption{Normalized shear stress $\tau^{\ast}$ around a bubble for 
@@
 value of $\tau_{0}$ is used regardless of $Re$. 
-\par\noindent
-For the case of $Re = 50$, the bubble reaches a deformed stable state.  
-\par\noindent
-As observed in
-previous sections, when the value of $Re$ is slightly below the 
-critical $Re$ condition, the bubble does not settle into a deformed 
-stable state but instead alternates in an elongation and contraction process.  
-In comparison to the $Re=50$ case on the left, the right
-image in Fig.~\ref{fig:ShearStress} ($Re=93$)
-shows a higher shear stress profile near
-the bubble endpoints as it undergoes an elongation
+%\par\noindent
+For the case of $Re = 50$, the bubble reached a deformed stable state,
+%\par\noindent
+\textcolor{red}
+{
+and the shear stress profile around the bubble was drawn after the bubble attained a stable deformed state.
+}
+As observed in previous sections, when the value of $Re$ is slightly below the 
+critical $Re$ condition, the bubble does not settle into a deformed stable state but instead alternates in an elongation and 
+contraction process.  
+\textcolor{red}
+{
+The shear stress profile for the case of $Re$ = 93 was depicted when the bubble sufficiently elongated ($T$ = 14.9).
+}
+In comparison to the $Re=50$ case on the left, the right image in Fig.~\ref{fig:ShearStress} ($Re=93$) shows a higher 
+shear stress profile near the bubble endpoints as it undergoes an elongation
 state in the process toward breakup.
-The value of the maximum shear stress for
-the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ 
-and the maximum shear stress
-for the case of $Re = 93$ at the moment 
-shown in Fig.~\ref{fig:ShearStress} has
-the value of $\tau ^{\ast} \approx 8$.  
-The shear stress profile in
-Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from 
-$\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, 
-shear stress regions
+The value of the maximum shear stress for the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ 
+and the maximum shear stress for the case of $Re = 93$ at the moment 
+shown in Fig.~\ref{fig:ShearStress} has the value of $\tau ^{\ast} \approx 8$.  
+The shear stress profile in Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from 
+$\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions
 with $\tau ^{\ast} \geqq 6$ are illustrated in red.  
-As can be seen in the
-figure, the strongest shear stresses are concentrated on the 
+As can be seen in the figure, the strongest shear stresses are concentrated on the 
 ends of the bubble for both $Re$ conditions.  
-This indicates that the strong shear stresses acting
-on the ends of the bubble are responsible for much of the bubble stretching.
+This indicates that the strong shear stresses acting on the ends of the bubble are responsible 
+for much of the bubble stretching.
 It is important to note that the magnitude of the shear stress acting on the
@@
 
-We also observe that the shear stress {\em inside} the bubble was very small
+We also observe that the shear stress inside the bubble was very small
 relative to that of the matrix fluid due to very small density and viscosity of
@@
 unsteady elongation period gives way to a steady state (with no
-break up).  On
-the other hand for Reynolds number {\em close} to the critical Reynolds
+break up).  On the other hand for Reynolds number close to the critical Reynolds
 number, there is a prolonged, unsteady, elongation period, in which
 periodic motion is observed and the deformation parameter $D$ is close 
-to one.  The ``vacillating''
-behavior cannot last forever, ultimately (perhaps stochastically!),
+to one.  The ``vacillating'' behavior cannot last forever, ultimately (perhaps stochastically!),
 the bubble will either settle down or break.  We assert that regardless
@@
 In fact,
-we hypothesize that there will {\em always} be ``vacillating'' behavior
+we hypothesize that there will always be ``vacillating'' behavior
 if one is sufficiently close to the critical Reynolds number.  i.e.
@@
 %\begin{comment} 
-\begin{figure}%[h!]
+\begin{figure}[h!]
   \centering
-  \includegraphics[width=\textwidth]{9-BubbleFieldCa0p3Re93}
+  \includegraphics[width=\textwidth]{Figure/9-BubbleFieldCa0p3Re93}
   \caption{Fluid velocity field outside and inside the breaking bubble in
@@
 the bubble during the shear-induced breakup process.
+\textcolor{red}
+{
+Detailed velocity fields of the deforming and breaking drop have already been presented in 
+some references (\citet{LiRenRen00, RenCri01-1}).
+The velocity fields for the drop and the bubble will be influenced by the behavior of the 
+breakup process, so the velocity fields for the drop and the bubble are not similar
+}
 Figure~\ref{fig:BubbleFieldCa0p3Re93} shows the velocity fields outside and
@@
   \centering
-  \includegraphics[width=\textwidth]{10-BubbleDeformCa0p8Re42}
+  \includegraphics[width=\textwidth]{Figure/10-BubbleDeformCa0p8Re42}
   \caption{Time evolution of bubble deformation in shear flow at the 
@@
   \centering
-  \includegraphics[width=\textwidth]{11-BubbleBreakCa0p8Re43}
+  \includegraphics[width=\textwidth]{Figure/11-BubbleBreakCa0p8Re43}
   \caption{Time evolution of bubble deformation in shear flow at the 
@@
 In previous sections, we considered numerical simulations of bubble deformation
-and breakup with a Capillary number $Ca = 0.3$.  Here, we examine similar
+and breakup with a capillary number $Ca = 0.3$.  Here, we examine similar
 bubble dynamics with $Ca = 0.8$ and we also investigate the effect of
@@
 case of the drop with 
-$\lambda$ = $\eta$ = 1 (see e.g.~\cite{LiRenRen00}).
+$\lambda$ = $\eta$ = 1 (see e.g.~\citet{LiRenRen00}).
 Note that $Re_{\rm c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca
@@
 breakup (Fig.~\ref{fig:BubDefCa0p8Re42}), the bubble initially assumes a long
-elongated shape along the $x$-direction at around $T=24.3$. The bubble then
+elongated shape along the $x$-direction at around $T=17.0$. The bubble then
 enters a compression stage over the time interval $[31.3,41.2]$ and
@@
 Table~\ref{tab:CaRecComparison} indicate that sufficiently large shear forces
-are required for bubble breakup even for large Capillary numbers.  In
+are required for bubble breakup even for large capillary numbers.  In
 Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in
@@
         of column pairs of critical Reynolds numbers and 
-	corresponding Capillary numbers.
+	corresponding capillary numbers.
         ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
@@
   \centering
-  %\includegraphics[width=\textwidth]{Fig11-Critical-Re1_cubic}
-  \includegraphics[width=\textwidth]{12-CaRecFit}
-  \caption{A plot of the critical Reynolds number versus Capillary number
+% \includegraphics[width=\textwidth]{12-CaRecFit}
+  \includegraphics[scale=0.6]{Figure/12-CaRecFit}
+  \caption{A plot of the critical Reynolds number versus capillary number
 	for the data listed in Table~\ref{tab:CaRecComparison}.  
@@
 shrinking motions for non-rupturing flow conditions.
-
+\textcolor{red}
+{
+At the same time, bubble deformation under smaller $Re$ conditions ($< Re_{\rm c}$)
+becomes in a stable state.
+}
 We attribute the large differences in morphology for the bubble undergoing
@@
 \bibliographystyle{elsarticle-harv} 
-\bibliography{references}
+\bibliography{Bubble-deformation}
 

### 2024-11-12 Revised-paper/Paper/Bubble-deformation-Rev.tex
add 5 new references

@@
 Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.
-Numerical results are obtained using a hydrodynamic scheme with formal second-order accuracy based on a coupled level 
-set/volume-of-fluid (CLSVOF) method.  To verify our numerical algorithm and provide a basis for comparison, we also 
-present simulation results that compare with previous, more popular, drop deformation and rupture simulations.  
-The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that 
-of the analogous drop system under similar flow conditions.  The first distinguishing factor for bubble breakup is that the 
-magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case. 
-In other words, a larger Reynolds number is needed to induce bubble breakup.  The second distinct feature of the bubble system 
-versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the 
-critical ``breakup'' Reynolds number.  It is asserted that the differences in morphology for a bubble undergoing breakup versus a 
-drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.
+Numerical results are obtained using a projection method for incompressible two-phase flow in which the method represents interfaces using the sharp interface coupled level set and volume of fluid (CLSVOF) method.
+To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.
+The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.
+The first distinguishing factor for bubble breakup is that the magnitude of shear flow necessary for causing rupture is much larger than that in the drop system case.
+In other words, a larger Reynolds number is needed to induce bubble breakup.
+The second distinct feature of the bubble system versus the drop system is that the bubble does not maintain a stable deformed shape as the system parameters approach the critical ``breakup'' Reynolds number.
+It is asserted that the differences in morphology for a bubble undergoing breakup versus a drop in the same process can be attributed to the density and viscosity ratio of the corresponding two-phase flow systems.
 The critical conditions for bubble breakup with respect to the Reynolds and capillary numbers are determined for several cases.
@@
 We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, 
-and microbubbles in the blood circulation system, \cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15}.  
+microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814}.
 In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
@@
 We remark that there have been a number of articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.  
-We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15}.
+We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.
 These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.
-Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented only one numerical result for a bubble breakup process under 
-the condition of $Ca$ (capillary number) = 35. \\ \indent
+Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented one numerical result for a bubble breakup process under the condition of $Ca$ (capillary number) = 35.
+Sharifi et al\cite{AAMM-16-2} presented two results for bubble breakup corresponding to $Ca=7.5$ and $Ca=11.2$.
+We point out that all of the previous
+computational research on bubble deformation (and breakup) under shear driven 
+flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}  use the (explicit) Lattice Boltzmann method.
+For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method implicitly capture the velocity continuity condition and the normal stress boundary condition.
+We contend that a projection method (e.g.
+this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower)  method for our study rather than the Lattice Boltzmann method.
+Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07},  maintains the gas/liquid interface as sharp and by construction our method preserves mass and volume within a fraction of a percent.
+The results that we present in this article (see e.g.
+section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data and grid refinement studies.
+Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.
+\\ \indent
 %
@@
 
-\subsubsection{Selecting the appropriate grid size}
+\subsubsection{Selecting the appropriate grid size \label{convergence} }
 

### 2024-11-16 Revised-paper/Reply/Reply-Reviewer1.tex
go over response

@@
 Response: \\
-The grid size and adaptive meshing strategy we adopted are chosen to answer the research question as to the conditions that determine 
-whether a bubble in shear flow will break up.  
-In such a case, we must accurately capture the balance of forces concerning the (non-local) force exerted from the wall-driven 
-flow acting against the interfacial surface tension force.
+In the section entitled ``Selecting the appropriate grid size,'' we 
+report results of a grid refinement study for our simulation results on
+the threshold Reynolds number required for bubble break-up.  Based on
+our grid refinement study, we claim that our results are within three
+percent of the ``exact threshold'' assuming that we had access to an
+infinite amount of computing power.  So, now the reviewer is asking for
+more resolution in which we assert the reviewer request is totally 
+unreasonable given the present state of technology.
 
-The accuracy of the ``Critical Reynolds Number'' depends on the largest Taylor Deformation parameter $D$ supported by the grid.  
-As we report here, we have found that as long as the grid size is fine enough to support a Taylor Deformation parameter $D<0.95$, 
-then the transition region (i.e., ``Critical Reynolds number'') (see Figures 3 and 12) will be captured with a tolerance of three percent.
+As mentioned in our initial submission, and further emphasized in the revision,
+if we refine the grid one more time, the simulation time will be 
+lengthened by at least a factor 16! Why? (i) factor of 4 refinement 
+due to 4 times as many grid points in the ``interface zone''; (ii) factor of $2^{3/2}$
+refinement due to the surface tension stability time step constraint; (iii) factor of 2 refinement {\em OR MORE} because as one converges to the critical Reynolds number, the bubble oscillates, thus prolonging the ability to determine break-up versus no break-up.
+Furthermore the bubble is longer at this critical juncture, thereby necessitating a longer and higher aspect ratio computational domain.
+Further important notes: (a) we cannot just do adaptivity at the regions of high curvature because the resulting speed-up by using less grid points is offset by the further ill-conditioning of the matrix system in not having the interface wholly contained on the finest level.
+(b) The referee in their critism did not mention alternate published work; and for good reason!
+Our work is the first of its kind!
+In the revised introduction, we make it clear that previous work on bubble deformation (just two papers) are based on the Lattice Boltzmann method which is unacceptable for measuring the tensile strength properties of a bubble.
+(c) in our revised introduction, we make it clear why the bubble deformation problem is so much more difficult than the drop deformation problem.
+(and why ours is the FIRST to report on
+tensile stress thresholding)  We have added further references to the introduction which understate the importance of our research on the ``tensile strength'' properties of a bubble, and at the same time we have made it clear why both controlled experiments and numerical simulations are so difficult.
+In the Capillary and Reynolds number regime that we are interested in, experiments must be performed in microgravity, on the otherhand, computations are so much more difficult for the bubble case than the drop case because the density ratio is about
+1000 to one for the bubble case.
 
-Figure 3 illustrates that we capture the proper break-up time as the grid is refined and at the point where the critical Reynolds
-number is prescribed. In Figure 3, we point out that the time step was $O(10^{-5}$)s for the elongating bubble ($\Delta x=R/16$).
-Further refinements reduce the time step according to the surface tension time step constraint. 
-The simulation time would become impractical if we tried to improve the accuracy of the ``critical Reynolds number'' further.  
-(For example, in the present study, the computation took more than one year for an experiment with $Re$ = 0.0 and $Ca$ = 1.63 
+Finally, we note that in the present study, the computation took more than one year for an experiment with $Re$ = 0.0 and $Ca$ = 1.63 
 (M\"{u}ller-Fischer et al. (2008)).
@@
 higher aspect ratio computational domain, increased droplet surface area at break-up, increased number of time steps, and 
-higher resolution for representing the drop/bubble at its thinnest point. \\
+higher resolution for representing the drop/bubble at its thinnest point. 
+All this translates to the simulation taking over 16 years on a refined mesh.
 \\
@@
 Response: \\
-		We cannot understand this criticism in the context of the referee's previous comment.
-They are contradictory statements.
-In the previous comment, the referee complains that we have lack of results, and in this section the referee complains that our results are superfluous.
-Every Figure that we show strategically informs the reader about the tensile strength properties of a bubble in wall driven shear flow.
-All the results that we report are novel and significant tion, and in the present comment, the referee complains about our results which clearly highlight why this problem is so hard, and why it is unreasonable to ask for more.
-Already the presented results that we present regarding the ``tensile strength'' of a {\em bubble} in the presence of driven walls
-We believe the figures and computational results presented in this study are very valuable to developing the study of drop/bubble deformation and breakup.
-The following points were especially presented and revealed in this paper for the first time. \\
+As in our response to the previous comment, we believe it is unreasonable to report more results; specifically each new data point requires an additional year, and additional computers.
+As also mentioned in our response to point 2 above, and hilighted in our revised introduction,
+our work as it stands now is significant and novel.  We take the referee comments on as a challenge for future work.
+
+We remark that the significance of our article is the fact that we have 
+reported for the first time controlled tensile strength properties for a bubble in shear flow.  In addition, we have made the following noteworthy discoveries along the way:
 \begin{enumerate}
@@
 In our computations, we set $g = 0$ because we wanted to clearly isolate only the effects of the density and viscosity ratios and 
-wanted to compare previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$.
+wanted to compare with previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$.
 When the gravity is considered, we obtain $Fr$ (Froude number) $\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$ = 1.7 ($Re$ = 93 and $Ca$ = 0.3) 
@@
 ($V$ (moving wall speed) had about 1.1 $\sim$ 1.3 m/s for the range of $Ca$ and $Re$ in our computaions.)
-Therefore, the effect of gravity (bubble rise motion) is expected to be negligible to the behavior of bubble deformation and breakup 
-around critical $Re$ number conditions. Our computational results will provide fundamental knowledge and findings for practical applications.
+Therefore, the effect of gravity (bubble rise motion) is expected to be negligible when juxtaposed with the measured tensile strength properties of bubble deformation and breakup 
+around the critical $Re$ number conditions.
+Contrary to what the reviewer suggests, we believe that our computational results in which we only focus on the force balance between the driving shear flow and the bubble surface tension will provide fundamental knowledge and findings for practical applications.
 In the revised paper, we have described these explanations.\\

### 2024-11-16 Revised-paper/Paper/Bubble-deformation-Rev.tex
go over response

@@
 We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, 
-microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814}.
+microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble}.
 In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
 This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  
-Studying bubble break-up via computation rather than experiments simplifies the process of setting a combination of precise, simple shear 
-flow conditions, low $Ca$ conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish 
+Studying bubble break-up, vis a vis that of the drop, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear 
+flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish 
 bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity 
@@
 denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ 
-and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.  
+and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.  
 %
@@
 the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.  An advantage of studying shear-driven 
-bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties to 
-ascertain the sensitivity of deformation and breakup to physical parameters.  In our computations, the time-evolution of the boundary 
+bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties and external properties (e.g.
+the gravity force, in order to compare with the analogous drop case) in order to isolate
+the sensitivity of deformation and breakup to physical parameters.  In our computations, the time-evolution of the boundary 
 between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.  
@@
 In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings 
-for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.  In this work, we determine, for the 
+for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
+This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.
+In this work, we determine, for the
 first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.  Additionally, our computational studies 
@@
 flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}  use the (explicit) Lattice Boltzmann method.
-For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method implicitly capture the velocity continuity condition and the normal stress boundary condition.
+For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.
 We contend that a projection method (e.g.
@@
 Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.
+Finally, the larger the deformation parameter $D$, the longer we must make our computational domain (bigger domain aspect ratio!) thereby adversely effecting the condition number even more for carrying our the pressure projection.
 \\ \indent
 %
-To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop.
+To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop (for terrestrial experiments, when the density ratio of drop to matrix is very close to one!).
 We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the 
@@
  studies have been conducted on bubble deformation and breakup.
+We reiterate why there have been few studies regarding the ``tensile strength'' of bubbles.
+Experimentally, in the moderate to high Reynolds number regime, and low Capillary number regime, one is restricted to microgravity conditions.
+Computational experiments are difficult too.
+In order to accurately compute the tensile strength of a bubble, one must resort to a combination of
+parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).
  }

### 2024-11-16 Revised-paper/Reply/Reply-Reviewer1.tex
need to proofread the paper

@@
 infinite amount of computing power.  So, now the reviewer is asking for
-more resolution in which we assert the reviewer request is totally 
+more resolution in which we assert the reviewer request is 
 unreasonable given the present state of technology.
@@
 Further important notes: (a) we cannot just do adaptivity at the regions of high curvature because the resulting speed-up by using less grid points is offset by the further ill-conditioning of the matrix system in not having the interface wholly contained on the finest level.
-(b) The referee in their critism did not mention alternate published work; and for good reason!
+As well, a sufficiently fine mesh is all around the gas-liquid interface in order to properly simulate the force exerted from the wall to the bubble.
+(b) The referee in his/her critism of our work did not mention alternate published work; and for good reason!
 Our work is the first of its kind!
-In the revised introduction, we make it clear that previous work on bubble deformation (just two papers) are based on the Lattice Boltzmann method which is unacceptable for measuring the tensile strength properties of a bubble.
-(c) in our revised introduction, we make it clear why the bubble deformation problem is so much more difficult than the drop deformation problem.
-(and why ours is the FIRST to report on
-tensile stress thresholding)  We have added further references to the introduction which understate the importance of our research on the ``tensile strength'' properties of a bubble, and at the same time we have made it clear why both controlled experiments and numerical simulations are so difficult.
-In the Capillary and Reynolds number regime that we are interested in, experiments must be performed in microgravity, on the otherhand, computations are so much more difficult for the bubble case than the drop case because the density ratio is about
+In the revised introduction, we make it clear that previous work on bubble deformation (just two papers) are based on the Lattice Boltzmann method which is an unacceptable method for measuring the tensile strength properties of a bubble.
+(c) in our revised introduction, we make it clear why the bubble deformation problem is so much more difficult than the drop deformation problem and why our work is the FIRST to report on
+tensile stress thresholding.
+We have added further references to the introduction which understate the importance of our research on the ``tensile strength'' properties of a bubble, and at the same time we have made it clear why both controlled experiments and numerical simulations are so difficult.
+In the Capillary and Reynolds number regime that we are interested in, experiments (which isolate the effect of density ratio) must be performed in microgravity, on the otherhand, computations are so much more difficult for the bubble case than the drop case because the density ratio is about
 1000 to one for the bubble case.
@@
 Drop deformation is promoted when using a domain size with $W=4R$.
-\item The difference in the deformation and breakup between the bubble and the drop with $\lambda = 1$ and $\eta = 1$ was clearly shown.
+\item The difference in the deformation and breakup between the bubble ($\lambda<<1$) and the drop ($\lambda = 1$ and $\eta = 1$) was clearly shown.
 \item Shear-induced bubble/drop breakup critical curves were obtained. 
@@
 
-Regarding the effect of $\lambda$ and $\eta$, ongoingly we have examining the effect of $\lambda$ and $\eta$ on drop breakup for following 
+Regarding the effect of $\lambda$ and $\eta$, ongoingly we are examining the effect of $\lambda$ and $\eta$ on drop breakup for following 
 combinations of $\lambda$ and $\eta$:
@@
 \\
-Please see lines 123 to 130.
+Please see lines 133 to 139.
 \\
@@
 We carefully checked the paper and modified poor English writing, expressions, etc.\\
-\textcolor{red}
-{
-Mark and Edwin: Please modify these sentences at line 191 and line 232. (line198 and 242 in the revised paper.)\\
-}
-\\
-Please confirm lines  198 to 
-\\
 

### 2024-11-16 Revised-paper/Reply/Reply-Reviewer2.tex
need to proofread the paper

@@
 Response: \\
-As explained in the ``Numerical Analysis", the CLSVOF method couples both the level set and VOF methods and can 
-take advantage of both methodologies. 
-Consequently,  the CLSVOF method is superior to other interface-capturing/interface-tracking methods. 
-This is the reason we selected the CLSVOF method. We only referred to several interface-capturing/interface-tracking 
-method methods in introducing previous studies.\\
+The level set method, by itself, is not designed to directly conserve the
+volume of materials.
+The error is especially large at regions of high curvature.
+The lack of volume conservation can significantly alter the numerical predictions.
+On the other hand, the volume of fluid method, by itself, is not designed to accurately and robustly approximate the interface curvature.
+The surface tension force will be incorrectly calculated if the curvature is not accurately approximated.
+We have found that the CLSVOF method on the otherhand, in which we couple the two methods, is the optimal method.
+We have added further discussion to the paper.
+
+\\
 \\
@@
 In our computations, we set $g = 0$ because we wanted to isolate only the effects of the density and viscosity ratios and 
-wanted to compare previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$. 
+wanted to compare with previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$. 
 Also, in the revised paper, a brief discussion of the potential influence of gravity (Froude number) on bubble breakup dynamics 

### 2024-11-16 Revised-paper/Paper/Bubble-deformation-Rev.tex
need to proofread the paper

@@
 between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.
+The rationale for the CLSVOF method is that the hybrid method represents the (complex) gas-liquid interfaces with minimal volume loss (property of the volume-of-fluid method) and minimal error in the approximation of the surface tension force (property of the level set method).
 We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify 
@@
 this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower) method for our study rather than the Lattice Boltzmann method.
-Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07},  maintains the gas/liquid interface as sharp and by construction our method preserves mass and volume within a fraction of a percent.
+Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07},  maintains the gas/liquid interface as sharp, enables accurate approximation of the surface tension force,  and by construction the CLSVOF method preserves mass and volume within a fraction of a percent.
 The results that we present in this article (see e.g.
@@
 
-When comparing with previous drop studies, we fix $\lambda=1$.  As a result,
+When comparing with previous drop studies, we fix $\lambda=1$ for the drop cases.  As a result,
 (for $\lambda=1$) the following dimensionless physical parameters are used to
@@
 \begin{description}
-\item[Timestep $\Delta t$] The timestep is governed by the CFL condition and
+\item[All Steps. Timestep] 
+ \begin{eqnarray*}
+ \end{eqnarray*}
+  The timestep, $\Delta t$, is governed by the CFL condition and
   surface tension (section 5.7 of \citet{SusSmiHusOhtZhi07}):
@@
 of the hierarchical grid structure and the lower panel corresponds to an actual
-computational example for bubble deformation in simple linear shear flow.  In
+computational example corresponding to bubble deformation in simple linear shear flow.  In
 general, the mesh hierarchy is composed of different levels of refinement

### 2024-11-17 Revised-paper/Paper/Bubble-deformation-Rev.tex
grammar fixes

@@
 Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.
-Numerical results are obtained using a projection method for incompressible two-phase flow in which the method represents interfaces using the sharp interface coupled level set and volume of fluid (CLSVOF) method.
+Numerical results are obtained using a projection method for incompressible two-phase flow.
+The method represents interfaces using the sharp interface coupled level set and Volume-Of-Fluid (CLSVOF) method.
 To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.
@@
 %
-\textcolor{red}
-{
+\textcolor{red} {
 Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.
-We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, 
-microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble}.
-In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
-This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  
-Studying bubble break-up, vis a vis that of the drop, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear 
-flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish 
-bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity 
-ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' 
-denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ 
-and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.  
-%
-In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme 
-conditions at which a bubble in shear flow first transitions from deformation to breakup.  We validate our numerical method by examining 
-the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.  An advantage of studying shear-driven 
-bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties and external properties (e.g.
-the gravity force, in order to compare with the analogous drop case) in order to isolate
-the sensitivity of deformation and breakup to physical parameters.  In our computations, the time-evolution of the boundary 
-between gas and liquid is tracked with a coupled level set/volume-of-fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.
-The rationale for the CLSVOF method is that the hybrid method represents the (complex) gas-liquid interfaces with minimal volume loss (property of the volume-of-fluid method) and minimal error in the approximation of the surface tension force (property of the level set method).
-We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify 
-the parameter regimes in which a relatively simple system transitions from stable to unstable.  Specifically, we ascertain the critical 
-Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.          
-%
-In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings 
-for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
+We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
+}
+\par
+\textcolor{red} {
+This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
+}
+\par
+\textcolor{red} {
+In this work, we focus on identifying critical flow states numerically, in terms of dimensionless quantities, that specify the extreme conditions at which a bubble in shear flow first transitions from deformation to breakup.
+We validate our numerical method by examining the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.
+An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties and external properties (e.g.
+we can easily modify the gravity force, in order to compare with the analogous drop case or compare with microgravity conditions) in order to isolate the sensitivity of deformation and breakup to physical parameters.
+In our computations, the time-evolution of the boundary between gas and liquid is tracked with a Coupled-Level-Set and Volume-Of-Fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.
+The rationale for the CLSVOF method is that the hybrid method represents the (complex) gas-liquid interfaces with minimal volume loss (property of the Volume-Of-Fluid method) and minimal error in the approximation of the surface tension force (property of the Level-Set method).
+}
+\par
+\textcolor{red} {
+We focus on determining critical physical conditions in which the breakup of a bubble occurs in shear flow because it is important to identify the parameter regimes in which a relatively simple system transitions from stable to unstable.
+Specifically, we ascertain the critical Reynolds number ($Re_{\rm c}$) corresponding to the bubble breakup onset condition as a function of $Ca$.
+}
+\par
+In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
 This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.
-In this work, we determine, for the
-first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.  Additionally, our computational studies 
-reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
-%
+In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.
+Additionally, our computational studies reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.
+\par
+\textcolor{red} {
 We remark that there have been a number of articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
@@
 Sharifi et al\cite{AAMM-16-2} presented two results for bubble breakup corresponding to $Ca=7.5$ and $Ca=11.2$.
-We point out that all of the previous
-computational research on bubble deformation (and breakup) under shear driven 
-flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}  use the (explicit) Lattice Boltzmann method.
+We point out that all of the previous computational research on bubble deformation (and breakup) under shear driven flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2} use the (explicit) Lattice Boltzmann method.
 For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.
@@
 Finally, the larger the deformation parameter $D$, the longer we must make our computational domain (bigger domain aspect ratio!) thereby adversely effecting the condition number even more for carrying our the pressure projection.
-\\ \indent
-%
+}
+\par
+\textcolor{red} {
 To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop (for terrestrial experiments, when the density ratio of drop to matrix is very close to one!).
-We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the 
-simpler drop problem. For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
-%
-The study of the deformation and breakup of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated 
-extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.The pioneering 
-experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and 
-experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.  By the 2000s, progress in 
-computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused 
-on direct simulations of this problem.  In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) 
-method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}. 
-Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued 
-to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, 
-IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this 
-problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, 
-front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.
+We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the simpler drop problem.
+For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
+}
+\par
+\textcolor{red} {
+The study of the deformation and breakup of a drop in immiscible viscous liquids undergoing simple linear shear flow has been investigated extensively due to its fundamental importance to emulsion processes, materials processing, mixing, and reaction devices.
+The pioneering experimental work on this problem was performed by Taylor in the early 1930s \cite{Tay32, Tay34}, and the subsequent theoretical and experimental progress up to the 1980s and 1990s was reviewed in \cite{Ral84} and \cite{Sto94}, respectively.
+By the 2000s, progress in computational fluid dynamics (CFD) techniques and increased access to powerful computing resources led to a surge of research focused on direct simulations of this problem.
+In particular, detailed computational investigations of drop breakup, based on a Volume-of-Fluid (VOF) method \cite{HirNic81} were presented in \cite{LiRenRen00, RenCri01-1, RenCri01-2, RenCriLi02,KhiRenCri03,Ren06,Ren07,Ren08-2}.
+Since then, the literature on computational studies on the deformation and breakup of a single or several drops in shear flow has continued to grow \cite{CriGuiAlfBlaLoe03, InaTomOgi03,ZhaMikBan06, BazAndMei06, JanAnd08, CroGriSch10,KomShaEskDer14,KomShaEskDer15, IoaLiuZha16, HerRan17,AmaBalCasOli19, ZhaShuGuaYan21} and a variety of numerical techniques have been developed to tackle this problem, including boundary-integral approaches \cite{CriBlaLoe01, JanAnd07}, lattice Boltzmann methods \cite{Ina06, KomShaEskDer14}, front tracking schemes \cite{UnvTry92}, and interface-capturing level set methods \cite{SusSmeOsh94}.
+}
+\par
 \textcolor{blue} 
-{
-Thus, a lot of studies about the deformation and breakup of a drop in simple linear shear have been presented so far. In contrast, few
- studies have been conducted on bubble deformation and breakup.
+{ Thus, a lot of studies about the deformation and breakup of a drop in simple linear shear have been presented so far.
+In contrast, few studies have been conducted on bubble deformation and breakup.
 We reiterate why there have been few studies regarding the ``tensile strength'' of bubbles.
-Experimentally, in the moderate to high Reynolds number regime, and low Capillary number regime, one is restricted to microgravity conditions.
+Experimentally, if one wants to isolate the interplay of shearing force with the bubble surface tension force, in the moderate to high Reynolds number regime, and low Capillary number regime, one is restricted to microgravity conditions.
 Computational experiments are difficult too.
-In order to accurately compute the tensile strength of a bubble, one must resort to a combination of
-parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).
- }
+In order to accurately compute the tensile strength of a bubble, one must resort to a combination of parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).
 }
@@
 
-Figure~\ref{fig:SchemAndGrid}(a) shows a schematic of the computational system
-for our studies of a bubble (or drop) in shear flow.  The computational domain
-consists of a three-dimensional rectangular domain of $L$ (length) $\times$ $W$
-(width) $\times$ $H$ (height).  The size of $L$, $W$ and $H$ was determined
-after consideration of numerical result sensitivity to domain size; numerical
-studies of domain-size dependence are presented in
-Section~\ref{sec:DomGrdSize}.  All computational results that follow were
-obtained from numerical solutions of the three-dimensional governing equations
-for gas-liquid/liquid-liquid flows.  Computations are initialized with a
-spherical bubble (or drop) of radius $R$ = 5 mm set at the center of the
-computational domain.   The bubble (or drop) is then subjected to a linear
-shear flow generated by the motion of the top and bottom plates, which have
-constant velocity $+V$ and $-V$, respectively.  In the interior of the domain,
-the initial velocity condition is assumed to be a simple linear profile and
-periodic boundary conditions are imposed along the $x$ and $y$ directions.
+Figure~\ref{fig:SchemAndGrid}(a) shows a schematic of the computational system for our studies of a bubble (or drop) in shear flow.
+The computational domain consists of a three-dimensional rectangular domain with the dimensions of $L$ (length) $\times$ $W$ (width) $\times$ $H$ (height).
+The size of $L$, $W$ and $H$ was determined after consideration of the sensitivity of numerical results to the domain size; numerical studies of domain-size dependence are presented in Section~\ref{sec:DomGrdSize}.
+All computational results that follow were obtained from numerical solutions of the three-dimensional governing equations for gas-liquid/liquid-liquid flows.
+Computations are initialized with a spherical bubble (or drop) of radius $R$ = 5 mm set at the center of the computational domain.
+The bubble (or drop) is then subjected to a linear shear flow generated by the motion of the top and bottom plates, which have constant velocity $+V$ and $-V$, respectively.
+In the interior of the domain, the initial velocity condition is assumed to be a simple linear profile and periodic boundary conditions are imposed along the $x$ and $y$ directions.
 Mathematically, the initial and boundary conditions are described as follows:
@@
 two-phase flow problems are also determined by the density ratio $\lambda$ and
-the viscosity ratio $\eta$.  In the present study, in order to clearly isolate only the effects 
-of $\lambda$ and $\eta$, the effect of gravity is not considered ($g = 0$) so that 
-we ignore the effect of the $Fr$ number 
+the viscosity ratio $\eta$.
+In the present study, in order to clearly isolate the effects of $\lambda$ and $\eta$, and isolate the balance of the driving wall force with the bubble surface tension force, the effect of gravity is not considered ($g = 0$) so that we ignore the effect of the $Fr$ number
 \textcolor{red}
@@
 
-When comparing with previous drop studies, we fix $\lambda=1$ for the drop cases.  As a result,
-(for $\lambda=1$) the following dimensionless physical parameters are used to
-describe the problem of drop deformation/breakup in shear flow
+When comparing with previous drop studies, we fix $\lambda=1$ for the drop cases.
+As a result, (for $\lambda=1$) the following dimensionless physical parameters are used to describe the problem of drop deformation/breakup in shear flow:
 %
@@
 %
-$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the
-problem of shear-induced drop deformation and breakup, the velocity is set to
-$U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.  As
-mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.
-\citet{LiRenRen00}).  Thus, for comparison with previous drop deformation and
-breakup problems, we set $\lambda = \eta = 1$ (and also neglect the effect of
-gravity so that $g=0$). On the other hand, in our computations for bubble
-deformation, we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2
-kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.  We
-emphasize that for consistency with previous studies (\citet{LiRenRen00,
-RusMan02, MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), we
-computationally examine the deformation and breakup of a bubble in simple
-linear shear flow as a function of the $Re$ and $Ca$ numbers.  That is to say,
-by setting $g=0$, we are isolating the effect of only varying $Re$ and $Ca$ on
-bubble deformation and breakup.  In our controlled study, we determine the
-critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$ corresponds to
-the threshold of bubble (or drop) breakup.  We determine the critical $Re_{\rm
-c}$ versus $Ca$ curve for strategic pairs of the density ratio and viscosity
-ratio.
-
-In our computations, the density of the matrix fluid is fixed at $\rho_{\rm m}$
-= 1000 kg/m$^3$.  The surface tension at the bubble (drop) interface is $\sigma
-=2.5 \times 10^{-2}$ N/m. The values of $Re$ and $Ca$ in our simulations are
-controlled by changing the values of $\mu_{\rm m}$ and $V$. 
+$U$ is the velocity scale and $\sigma$ denotes the surface tension.
+For the problem of shear-induced drop deformation and breakup, the velocity is set to $U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.
+As mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.
+\citet{LiRenRen00}).
+Thus, for comparison with previous drop deformation and breakup problems, we set $\lambda = \eta = 1$ (and also neglect the effect of gravity so that $g=0$).
+On the other hand, in our computations for bubble deformation, we set the density and viscosity of air to be $\rho_{\rm b}$ = 1.2 kg/m$^{3}$ and $\mu_{\rm b} = 1.8 \times 10^{-5}$ Pa$\cdot$s respectively.
+We emphasize that for consistency with previous studies (\citet{LiRenRen00, RusMan02, MulTobDreFisWin08, KomShaEskDer14, AmaBalCasOli19}), we computationally examine the deformation and breakup of a bubble in simple linear shear flow as a function of the $Re$ and $Ca$ numbers.
+That is to say, by setting $g=0$, we are isolating the effect of only varying $Re$ and $Ca$ on bubble deformation and breakup.
+In our controlled study, we determine the critical $Re_{\rm c}$ versus $Ca$ curve in which $Re_{\rm c}$ corresponds to the threshold of bubble (or drop) breakup.
+We determine the critical $Re_{\rm c}$ versus $Ca$ curve for strategic pairs of the density ratio and viscosity ratio.
+\par
+In our computations, the density of the matrix fluid is fixed at $\rho_{\rm m}$ = 1000 kg/m$^3$.
+The surface tension at the bubble (drop) interface is $\sigma =2.5 \times 10^{-2}$ N/m.
+The values of $Re$ and $Ca$ in our simulations are controlled by changing the values of $\mu_{\rm m}$ and $V$.
 \textcolor{red}
@@
 $\lambda = 1.2 \times 10^{-3}$ and $\eta < 1.0 \times 10^{-3}$.
-
+\par
 \textcolor{red}
 {
-For readers’ reference, we describe the effect of gravity here. When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.
+For readers’ reference, we describe the effect of gravity here.
+When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.
 Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
 However, bubbles in our computations reach the breakup by way of deformation very quickly at $t$ = about 0.5 s.
-Accordingly, it is expected that the effect of gravity (bubble rise motion) can be small for the behavior of bubble deformation and breakup 
-around critical $Re$ number conditions in our study.
+Accordingly, it is expected that the effect of gravity (bubble rise motion) can be small for the behavior of bubble deformation and breakup around critical $Re$ number conditions in our study.
 }
@@
 %  -----------------------------------------------------------------------------
-Numerical results were obtained using the interface capturing
-Coupled Level Set and Volume of Fluid (CLSVOF) method
-(\citet{SusPuc00,SusSmiHusOhtZhi07}), which is based on a fixed grid finite volume
-algorithm.  The CLSVOF method is a robust  numerical  technique
-that  combines  some  of  the  advantages  of the Volume of Fluid (VOF) method
-(\citet{HirNic81}) and the Level Set (LS) (\citet{SusSmeOsh94}) method while
-overcoming their weaknesses.  In the VOF method,  the Volume Fraction function,
-$F$, is used to represent the interface. The values of $F$ correspond to the
-volume fraction of liquid in a given computational cell.  In other words, $F =
-0$ when a computational cell contains only gas and $F = 1$ when a computational
-cell contains only liquid.  If $0 < F < 1$, then a computational cell contains
-the gas-liquid interface. The VOF method has a great advantage over the LS
-method in that accurate algorithms for advecting $F$ can be applied so that
-mass/volume is conserved up to machine precision while still maintaining a
-sharp representation of the interface.  On the other hand, the disadvantage of
-the VOF method in comparison to the LS method is that tangled and difficult
-reconstruction procedures are required for determining the slope of the
-piecewise linear VOF reconstructed interface.  In the LS method, the signed
-distance function $\phi$ (LS function) is used to track the interface. The
-interface is implicitly represented by the set of points in which $\phi = 0$.
-Liquid and gas regions are defined as $\phi > 0$ in the liquid and $\phi < 0$
-in the gas, respectively.  One of the advantages of the LS method is that one
-can track and represent smoothly the interface, but the LS method has the
-disadvantage that mass/volume is not explicitly conserved.  In the CLSVOF
-method, the coupling between the LS function and the VOF function occurs when
-computing the normal of the reconstructed interface in the VOF calculation
-process and also when assigning the LS function with the exact signed normal
-distance to the reconstructed interface in the LS calculation process. That is
-to say, the piecewise linear approximation (the volume-of-fluid reconstruction
-step) for the VOF method is determined using the unit normal vector ($\bm n$)
-estimated from information of the LS function. By taking advantage of both
-methods, the evolution of the liquid-gas interface location can be
-computationally captured in such a way so that volume/mass is preserved to
-machine precision and at the same time, the interface normals and the surface
-tension force (which is proportional to the interface curvature) can be
-straightforwardly derived from the smooth level set function.
-
-In our studies,
-the two-phase fluid flow is comprised of air and a 
-viscous Newtonian liquid.  
-The Heaviside function, $\Hea(\phi)$, which is defined as
-%
+Numerical results were obtained using the interface capturing Coupled Level Set and Volume of Fluid (CLSVOF) method (\citet{SusPuc00,SusSmiHusOhtZhi07}), which is based on a fixed grid finite volume algorithm.
+The CLSVOF method is a robust  numerical  technique that  combines  some  of  the  advantages  of the Volume of Fluid (VOF) method (\citet{HirNic81}) and the Level Set (LS) (\citet{SusSmeOsh94}) method while overcoming their weaknesses.
+In the VOF method,  the Volume Fraction function, $F$, is used to represent the interface.
+The values of $F$ correspond to the volume fraction of liquid in a given computational cell.
+In other words, $F = 0$ when a computational cell contains only gas and $F = 1$ when a computational cell contains only liquid.
+If $0 < F < 1$, then a computational cell contains the gas-liquid interface.
+The VOF method has a great advantage over the LS method in that accurate algorithms for advecting $F$ can be applied so that mass/volume is conserved up to machine precision while still maintaining a sharp representation of the interface.
+On the other hand, the disadvantage of the VOF method in comparison to the LS method is that tangled and difficult reconstruction procedures are required for determining the slope of the piecewise linear VOF reconstructed interface.
+In the LS method, the signed distance function $\phi$ (LS function) is used to track the interface.
+The interface is implicitly represented by the set of points in which $\phi = 0$.
+Liquid and gas regions are defined as $\phi > 0$ in the liquid and $\phi < 0$ in the gas, respectively.
+One of the advantages of the LS method is that one can track and represent smoothly the interface, but the LS method has the disadvantage that mass/volume is not explicitly conserved.
+In the CLSVOF method, the coupling between the LS function and the VOF function occurs when computing the normal of the reconstructed interface in the VOF calculation process and also when assigning the LS function with the exact signed normal distance to the reconstructed interface in the LS calculation process.
+That is to say, the piecewise linear approximation (the volume-of-fluid reconstruction step) for the VOF method is determined using the unit normal vector ($\bm n$) estimated from information of the LS function.
+By taking advantage of both methods, the evolution of the liquid-gas interface location can be computationally captured in such a way so that volume/mass is preserved to machine precision and at the same time, the interface normals and the surface tension force (which is proportional to the interface curvature) can be straightforwardly derived from the smooth level set function.
+\par 
+In our studies, the two-phase fluid flow is comprised of air and a viscous Newtonian liquid.  The Heaviside function, $\Hea(\phi)$, which is defined as
 \begin{equation}\label{heavyeqn}
@@
 \end{equation}
-%
 will be used below to distinguish each of the two fluids.  A single set of
@@
 Navier-Stokes equations with surface tension forces:
-%
 \begin{align}
@@
 %
-where $\bmu$ is the velocity vector, $t$ represents time, $p$ is the pressure,
-$\bmI$ is the unit tensor, $\bmD$ is the rate of deformation tensor
-($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$
-is the viscosity, $\kappa$ is the interfacial curvature, and the Heaviside
-function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$. The
-singular Heaviside gradient term in the right hand side of
-equation~\eqref{nseqn} is a body force representing the surface tension force
-and is equivalent to specifying that the jump in the normal stress is equal to
-$\sigma\kappa$ (\citet{TanguyEtAl2007}).  The surface tension force expressed by
-the singular Heaviside gradient term acts only on the gas-liquid interface.
-The sharp interface ``Ghost Fluid Method'' (\citet{KanFedLiu00}) is used to
-discretize the gradient of the Heaviside function as it appears in the surface
-tension force term.  This force, upon discretization, is only non-zero across
-cells in which the level set function changes sign.
-
-The interfacial curvature $\kappa$ is
-computed with second order accuracy directly from the volume-of-fluid (VOF)
-function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).  
-We remark that we get the same
-results if we were to compute $\kappa$ directly from the LS function using the
-``level set'' height function technique.
+\par
+$\bmu$ is the velocity vector, $t$ represents time, $p$ is the pressure, $\bmI$ is the unit tensor, $\bmD$ is the rate of deformation tensor ($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$ is the viscosity, $\kappa$ is the interfacial curvature, and the Heaviside function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$.
+The singular Heaviside gradient term in the right hand side of equation~\eqref{nseqn} is a body force representing the surface tension force and is equivalent to specifying that the jump in the normal stress is equal to $\sigma\kappa$ (\citet{TanguyEtAl2007}).
+The surface tension force expressed by the singular Heaviside gradient term acts only on the gas-liquid interface.
+The sharp interface ``Ghost Fluid Method'' (\citet{KanFedLiu00}) is used to discretize the gradient of the Heaviside function as it appears in the surface tension force term.
+This force, upon discretization, is only non-zero across cells in which the level set function changes sign.
+\par
+The interfacial curvature $\kappa$ is computed with second order accuracy directly from the volume-of-fluid (VOF) function and the level set function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).
+We remark that we get the same results if we were to compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
 
@@
 %
-The subscripts ``b'' and ``m'' refer to ``drop or bubble'' and ``matrix
-fluid'', respectively. To represent the free surface with the CLSVOF method, we
-must evolve the solution to both the VOF equation for $F$ and the LS equation
-for $\phi$:
+The subscripts ``b'' and ``m'' refer to ``drop or bubble'' and ``matrix fluid'', respectively.
+To represent the free surface with the CLSVOF method, we must evolve the solution to both the VOF equation for $F$ and the LS equation for $\phi$:
 %
@@
 %
-In all computations the discretized variables $p$, $\phi$ and $F$ are located at
-cell centers and the discrete variable $\bmu$ is located at cell face centers.
-Our computations are performed using an overall second-order accurate
-hydrodynamic scheme.  The spatial discretization uses second-order accurate,
-slope-limited, upwind techniques for the nonlinear advective terms.  The
-velocity and pressure fields are computed using an implicit pressure projection
-procedure.
-
+In all computations, the discretized variables $p$, $\phi$ and $F$ are located at the cell centers and the discrete velocity variable $\bmu$ is located at cell face centers.
+Our computations are performed using an overall second-order accurate hydrodynamic scheme.
+The spatial discretization uses second-order accurate, slope-limited, upwind techniques for the nonlinear advective terms.
+The velocity and pressure fields are computed using an implicit pressure projection procedure.
+\par
 The temporal discretization of our numerical method is an operator split
@@
 \end{description}
-
-To make efficient use of computational resources, our numerical simulations
-utilize an adaptive hierarchy of grids based on a dynamic adaptive mesh
-refinement (AMR) technique (\citet{SusAlmBelColHowWel99}).  Adaptive grids are
-dynamically adjusted based on the location of the 
-deforming gas-liquid interface.
-In the AMR technique the grid resolution is increased in regions near the
-interface while a coarser grid is used where the flow is relatively steady.
-The upper panel of Figure~\ref{fig:SchemAndGrid}(b) displays a schematic view
-of the hierarchical grid structure and the lower panel corresponds to an actual
-computational example corresponding to bubble deformation in simple linear shear flow.  In
-general, the mesh hierarchy is composed of different levels of refinement
-ranging from coarsest $\ell=0$ (``level-0") to finest
-$\ell=\ell_{\textrm{max}}$ (``level-$\ell_{\textrm{max}}$").  The refinement
-ratio of one grid size ($\Delta x=\Delta y=\Delta z$) to the next finer level
-is two so that $\Delta x^{\ell+1}=0.5\Delta x^{\ell}$.  All computations in
-this study used an AMR system with a maximum prescribed level
-$\ell_{\textrm{max}} = 1$ (as illustrated in the upper panel of
-Figure~\ref{fig:SchemAndGrid}(b)).  In our adaptive mesh refinement algorithm,
-the velocity in coarse grid cells that neighbor fine grid cells is interpolated
-from the coarse grid using bilinear interpolation in order to initialize
-``ghost'' fine cells. Thus, the bilinear interpolation procedure produces
-interpolated fine grid data as a linear combination of the coarse grid data.
+To make efficient use of computational resources, our numerical simulations utilize an adaptive hierarchy of grids based on a dynamic adaptive mesh refinement (AMR) technique (\citet{SusAlmBelColHowWel99}).
+Adaptive grids are dynamically adjusted based on the location of the deforming gas-liquid interface.
+In the AMR technique, the grid resolution is increased in regions near the interface while a coarser grid is used where the flow is relatively steady.
+The upper panel of Figure~\ref{fig:SchemAndGrid}(b) displays a schematic view of the hierarchical grid structure and the lower panel corresponds to an actual computational example corresponding to bubble deformation in simple linear shear flow.
+In general, the mesh hierarchy is composed of different levels of refinement ranging from coarsest $\ell=0$ (``level-0") to finest $\ell=\ell_{\textrm{max}}$ (``level-$\ell_{\textrm{max}}$").
+The refinement ratio of one grid size ($\Delta x=\Delta y=\Delta z$) to the next finer level is two so that $\Delta x^{\ell+1}=0.5\Delta x^{\ell}$.
+All computations in this study used an AMR system with a maximum prescribed level $\ell_{\textrm{max}} = 1$ (as illustrated in the upper panel of Figure~\ref{fig:SchemAndGrid}(b)).
+In our adaptive mesh refinement algorithm, the velocity in the coarse grid cells that neighbor fine grid cells is interpolated from the coarse grid using bilinear interpolation in order to initialize ``ghost'' fine cells.
+Thus, the bilinear interpolation procedure produces interpolated fine grid data as a linear combination of the coarse grid data.
 
@@
 {
-The effectiveness of our computational method has been demonstrated for the complicated rising motion of 
-single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19} .
-In this section, the accuracy of our computational method will be verified for the problem of shear-induced 
-deformation of a drop and bubble. 
-}
-First, we compare quantitatively against the steady-state drop
-deformation results reported by \citet{LiRenRen00}.  The shape of a
-deformed drop in simple linear shear flow is described in terms of the Taylor
-deformation parameter $D$=$(a-b)/(a+b)$, 
-where $a$ and $b$ are the major and minor axes of the deformed drop.  
-For consistency, we perform numerical simulations using CLSVOF over the same
-computational domain and grid size used in \citet{LiRenRen00}, which has dimensions 
-$\lwh{8}{4}{8}$ (recall that $R$ is
-the bubble/drop radius) and a level-0 grid size $\Delta x=\Delta y=\Delta
-z=R/8$; our two-level AMR grid structure also uses a finer level-1 grid size
-$\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  Numerical
-results are listed in Table~\ref{tab:DeComparison} for $D$ 
-as a function of $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case, obtained with
-the VOF method used in \citet{LiRenRen00}, and also with our CLSVOF algorithm.
-Table~\ref{tab:DeComparison} indicates that our numerical results are in good
-agreement with previous computations for drop deformation and breakup.
+The effectiveness of our computational method has been demonstrated for the complicated rising motion of single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19}.
+In this section, the accuracy of our computational method will be verified for the problem of shear-induced deformation of a drop and bubble.
+}
+First, we compare quantitatively against the steady-state drop deformation results reported by \citet{LiRenRen00}.
+The shape of a deformed drop in simple linear shear flow is described in terms of the Taylor deformation parameter $D$=$(a-b)/(a+b)$, where $a$ and $b$ are the major and minor axes of the deformed drop respectively.
+For consistency, we perform numerical simulations using CLSVOF over the same computational domain and grid size used in \citet{LiRenRen00}, which has dimensions $\lwh{8}{4}{8}$ (recall that $R$ is the bubble/drop radius) and a level-0 grid size $\Delta x=\Delta y=\Delta z=R/8$; our two-level AMR grid structure also uses a finer level-1 grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
+Numerical results are listed in Table~\ref{tab:DeComparison} for $D$ as a function of $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case.
+The results in Table~\ref{tab:DeComparison} compare computations using our CLSVOF algorithm with corresponding results that were obtained with the VOF method used in \citet{LiRenRen00}.
 %
 \begin{table}[tbh]
-\caption{Comparison of the Taylor deformation parameter $D$ for a drop as a function 
-         of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$). In all cases, the domain 
-         size is $\lwh{8}{4}{8}$, where $R$ is the drop radius.
-         CLSVOF method computations used a two-level AMR computational domain 
-         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
-         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
-         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
+\caption{Comparison of the Taylor deformation parameter $D$ for a drop as a function of $Re$ ($Ca=0.3$, $\lambda = \eta = 1$).
+In all cases, the domain size is $\lwh{8}{4}{8}$, where $R$ is the drop radius.
+The CLSVOF method computations used a two-level AMR computational domain with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$ and a level-1 discretization $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 \label{tab:DeComparison}
@@
 %% Ohta
-Next, we examine the validation of our computational method in which we compare
-with the ``bubble deformation in simple linear shear flow'' results reported by
-\citet{MulTobDreFisWin08}.  \citet{MulTobDreFisWin08} experimentally inquired into the bubble
-deformation under the condition of $Re \approx 0$.  In our study, we computed
-the bubble deformation on a computational domain with dimensions
-$\lwh{12}{6}{6}$ and a computational grid in which the finest level grid size
-was $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
-Computations were performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$
-with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  $\lambda = 1.2 \times
-10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.  The parameters that we have
-prescribed are consistent with the experimental conditions by  \citet{MulTobDreFisWin08}.  
-Comparisons of our numerical results and
-previous experimental results (\citet{MulTobDreFisWin08}) are tabulated in
-Table~\ref{tab:DeComparisonRe=0}.  Additionally, in
-Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the
-condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by  \citet{RusMan02}. 
-These experimental values were obtained from the graph showing the relation of $D$ vs
-$Re$ (\citet{RusMan02}).  As is clear from Table~\ref{tab:DeComparisonRe=0}, our
-numerical results predicted larger values of $D$ than experimental ones
-reported by \citet{MulTobDreFisWin08}. Nevertheless, we
-found that our numerical results are very close to the experimental results by
-\citet{RusMan02}, which emphasizes the intrinsic difficulties
-associated with experimental investigations of bubble dynamics, even in simple
-linear shear flow.  These comparisons suggest that our computational method is
-effective and robust at reproducing bubble dynamics in simple linear shear
-flow.
-
+Next, we examine the validation of our computational method in which we compare with the ``bubble deformation in simple linear shear flow'' results reported by \citet{MulTobDreFisWin08}.
+\citet{MulTobDreFisWin08} experimentally inquired into the bubble deformation under the condition of $Re \approx 0$.
+In our study, we computed the bubble deformation on a computational domain with dimensions $\lwh{12}{6}{6}$ and a computational grid in which the finest level grid size was $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
+Computations were performed for the conditions of $Ca = 0.96$ and $Ca = 1.63$ with $Re \approx 0$ ($Re = 5.0 \times 10^{-4}$),  $\lambda = 1.2 \times 10^{-3}$ and  $\eta \leq 1.2 \times 10^{-6}$.
+The prescribed parameters are consistent with the experimental conditions by  \citet{MulTobDreFisWin08}.
+Comparisons of our numerical results and previous experimental results (\citet{MulTobDreFisWin08}) are tabulated in Table~\ref{tab:DeComparisonRe=0}.
+Additionally, in Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by  \citet{RusMan02}.
+These experimental values were obtained from the graph showing the relation of $D$ vs $Re$ (\citet{RusMan02}).
+As is clear from Table~\ref{tab:DeComparisonRe=0}, our numerical results predicted larger values of $D$ than experimental ones reported by \citet{MulTobDreFisWin08}.
+Nevertheless, our numerical results are very close to the experimental results by \citet{RusMan02}, which emphasizes the intrinsic difficulties associated with experimental investigations of bubble dynamics, even in simple linear shear flow.
+These comparisons suggest that our computational method is effective and robust at reproducing bubble dynamics in simple linear shear flow.
 %%
 \begin{table}[tbh]
-\caption{Comparison of  $D$ for a bubble as a function 
-         of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$). 
-	 In all cases, the domain 
-         size is $\lwh{12}{6}{6}$.
-         CLSVOF computations used a two-level AMR computational domain 
-         with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} 
-         = \Delta z^{\ell=0} = R/8$ and a level-1 discretization
-         $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
-
+\caption{Comparison of $D$ for a bubble as a function of $Ca$ ($Re \approx 0$, $\lambda \approx \eta \approx 0$).
+In all cases, the domain size is $\lwh{12}{6}{6}$.
+The CLSVOF computations used a two-level AMR computational domain with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$ and a level-1 discretization $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.}
 \label{tab:DeComparisonRe=0}
@@
   \includegraphics[scale=0.5]{Figure/2-DropBreakComparison}
-  \caption{Comparison with results reported 
-	in~\citet{RenCri01-2} 
-	(shown in boxes) 
-        for drop breakup in shear flow.  
-	In~\citet{RenCri01-2},
-	the computational domain
-        dimensions were 
-	$W=4R$, $H=8R$, and $L$ was varied depending 
-        on the $Re$ and $Ca$ conditions.  The
-	grid size 
-	in~\citet{RenCri01-2} 
-	was set to 
-        $\Delta x=\Delta y=\Delta z=R/8$.  
-	Reprinted with permission from 
-        reference~\citet{RenCri01-2}. 
+  \caption{Comparison with results reported in~\citet{RenCri01-2} (shown in bounding boxes) for drop breakup in shear flow.
+In~\citet{RenCri01-2}, the computational domain dimensions were $W=4R$, $H=8R$, and $L$ was varied depending on the $Re$ and $Ca$ conditions.
+The grid size in~\citet{RenCri01-2} was set to $\Delta x=\Delta y=\Delta z=R/8$.
+Reprinted with permission from reference~\citet{RenCri01-2}.
 Copyright 2001, AIP Publishing.
-	Results
-        obtained with our CLSVOF algorithm, corresponding to each case in
-        reference~\citet{RenCri01-2}, are shown outside boxes.  The
-        CLSVOF method used a two-level AMR computational domain 
-        with a level-0 discretization 
-	$\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$ 
-	and a level-1 discretization
-        $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$. 
-        The onset of drop breakup is demonstrated for (a) $Re=10$,
-        $Ca=0.16$, (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.
+The results obtained with our CLSVOF algorithm, corresponding to each case in reference~\citet{RenCri01-2}, are shown without the bounding boxes.
+The CLSVOF method used a two-level AMR computational domain with a level-0 discretization $\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$ and a level-1 discretization $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
+The onset of drop breakup is demonstrated for (a) $Re=10$, $Ca=0.16$, (b) $Re=12$, $Ca=0.1753$, and (c) $Re=15$, $Ca=0.196$.
 For all three $Re$ and $Ca$ conditions, $\lambda = \eta = 1$.}

### 2024-11-24 Revised-paper/Reply/Reply-Reviewer1.tex
Canedo et al

@@
 if we refine the grid one more time, the simulation time will be 
-lengthened by at least a factor 16! Why? (i) factor of 4 refinement 
+lengthened by at least a factor 16 due to the following reasons:
+(i) factor of 4 additional grid pointst 
 due to 4 times as many grid points in the ``interface zone''; (ii) factor of $2^{3/2}$
-refinement due to the surface tension stability time step constraint; (iii) factor of 2 refinement {\em OR MORE} because as one converges to the critical Reynolds number, the bubble oscillates, thus prolonging the ability to determine break-up versus no break-up.
+more time steps due to the surface tension stability time step constraint; (iii) factor of 2 or more time steps because as one converges to the critical Reynolds number, the bubble oscillates, thus prolonging the ability to determine break-up versus no break-up.
 Furthermore the bubble is longer at this critical juncture, thereby necessitating a longer and higher aspect ratio computational domain.

### 2024-11-24 Revised-paper/Paper/Bubble-deformation-Rev.tex
Canedo et al

@@
 Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.
-We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
+We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
 }
@@
 \textcolor{red} {
-This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, and low viscosity ratios.  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
+This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, low viscosity ratios, and zero buoyancy effects.  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
 }
@@
 We validate our numerical method by examining the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.
-An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify fluid physical properties and external properties (e.g.
+An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify bubble/drop shape initial conditions \cite{ohta2005computational}, fluid physical properties and external properties (e.g.
 we can easily modify the gravity force, in order to compare with the analogous drop case or compare with microgravity conditions) in order to isolate the sensitivity of deformation and breakup to physical parameters.
@@
 \par
-In previous studies on the motion of bubble deformation in a simple shear flow \cite{RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
+In previous studies on the motion of bubble deformation in a simple shear flow \cite{CanedoETAL,RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
 This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.
-In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.
+In the results reported in \cite{CanedoETAL}, the $x-z$ cross section of the deforming bubble was close to spherical in their experiments.
+This is expected since the experiments designed by \cite{CanedoETAL} closely followed the following basic assumptions: (i) ``steady creeping flow with negligible inertial effects,'' (ii) ``Incompressible Newtonian fluids,'' (iii) ``No buoyancy effects,'' (iv) ``No wall effects.''  In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.
 Additionally, our computational studies reveal characteristics that distinguish a drop's deformation and breakup processes versus those of a bubble.

### 2024-11-25 Revised-paper/Reply/Reply-Reviewer1.tex
working on the paper, forming an argument

--- 2024-11-16 Revised-paper/Reply/Reply-Reviewer1.tex
@@
 Response: \\
-In the section entitled ``Selecting the appropriate grid size,'' we 
-report results of a grid refinement study for our simulation results on
-the threshold Reynolds number required for bubble break-up.  Based on
-our grid refinement study, we claim that our results are within three
-percent of the ``exact threshold'' assuming that we had access to an
-infinite amount of computing power.  So, now the reviewer is asking for
-more resolution in which we assert the reviewer request is 
-unreasonable given the present state of technology.
+		There are two main problems identified from the referee: (a) the grid refinement study does not demonstrate enough convergence and (b) even if we could refine the grid an infinite number of times, our break-up model is insufficient and whatever findings that we have would be completely different than if we were able to model the break-up process with a molecular scale model.
+We disagree with the referee; we have added more references to our article in which the uncertainty in our article is smaller than that in the latest existing work.
+Also we note that existing articles on bubble and drop breakup due to shear do not take into account sub-scale models either and these articles demonstrate reasonable agreement with experiments (as does our submission).
+Note: if we were considering the merging of droplets in which bouncing versus merging can occur, then sub-scale drainage can be important to model.
+This issue is not relevent for our article though.
+We have added this discussion to the introduction.
 
-As mentioned in our initial submission, and further emphasized in the revision,
-if we refine the grid one more time, the simulation time will be 
-lengthened by at least a factor 16! Why? (i) factor of 4 refinement 
-due to 4 times as many grid points in the ``interface zone''; (ii) factor of $2^{3/2}$
-refinement due to the surface tension stability time step constraint; (iii) factor of 2 refinement {\em OR MORE} because as one converges to the critical Reynolds number, the bubble oscillates, thus prolonging the ability to determine break-up versus no break-up.
-Furthermore the bubble is longer at this critical juncture, thereby necessitating a longer and higher aspect ratio computational domain.
-Further important notes: (a) we cannot just do adaptivity at the regions of high curvature because the resulting speed-up by using less grid points is offset by the further ill-conditioning of the matrix system in not having the interface wholly contained on the finest level.
-As well, a sufficiently fine mesh is all around the gas-liquid interface in order to properly simulate the force exerted from the wall to the bubble.
-(b) The referee in his/her critism of our work did not mention alternate published work; and for good reason!
-Our work is the first of its kind!
-In the revised introduction, we make it clear that previous work on bubble deformation (just two papers) are based on the Lattice Boltzmann method which is an unacceptable method for measuring the tensile strength properties of a bubble.
-(c) in our revised introduction, we make it clear why the bubble deformation problem is so much more difficult than the drop deformation problem and why our work is the FIRST to report on
-tensile stress thresholding.
-We have added further references to the introduction which understate the importance of our research on the ``tensile strength'' properties of a bubble, and at the same time we have made it clear why both controlled experiments and numerical simulations are so difficult.
-In the Capillary and Reynolds number regime that we are interested in, experiments (which isolate the effect of density ratio) must be performed in microgravity, on the otherhand, computations are so much more difficult for the bubble case than the drop case because the density ratio is about
-1000 to one for the bubble case.
-
-Finally, we note that in the present study, the computation took more than one year for an experiment with $Re$ = 0.0 and $Ca$ = 1.63 
-(M\"{u}ller-Fischer et al. (2008)).
-A smaller tolerance would necessitate a larger supported Deformation parameter $D$, which would, in turn, necessitate a 
-higher aspect ratio computational domain, increased droplet surface area at break-up, increased number of time steps, and 
-higher resolution for representing the drop/bubble at its thinnest point. 
-All this translates to the simulation taking over 16 years on a refined mesh.
-\\
+Finally, we note that our simulations already take about one year.
+The bubble deformation case, is a much more challenging problem than the drop case due to the large density ratio.
+Anymore refinement would extend the time of simulation to 8 years using current technology.
+It is agreed though that speeding up the algorithm in order to run more efficiently would certainly reduce the uncertainty of our results even more.
+This is future work.
+%Muller-Fischer comparison
 

### 2024-11-25 Revised-paper/Paper/Bubble-deformation-Rev.tex
working on the paper, forming an argument

@@
 Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.
-We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
+We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, underwater projectiles, polyethylene devolatilization, microfluidics, food aeration, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL,GAO2022103212,WONG2012417,PolyethyleneDevo,FRENSE2024120579,lohse2018bubble,schluter2021small,SANOGO2023112478}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
 }
@@
 \textcolor{red} {
-This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than (terrestrial) experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, low viscosity ratios, and zero buoyancy effects.  The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most (terrestrial) studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
+	This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, low viscosity ratios, and zero buoyancy effects.  We remark that the majority of previous experimental studies on shear-driven bubble deformation are restricted to low Reynolds' number and large capillary number\cite{RusMan02,CanedoETAL}.
+One reason is that buoyancy effects are minimized in highly viscous liquids.
+On the other hand, many applications are characterized by liquids in the high Reynolds' number regime.
+The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
 }
@@
 In the results reported in \cite{CanedoETAL}, the $x-z$ cross section of the deforming bubble was close to spherical in their experiments.
+Also in the experiments in \cite{CanedoETAL}, the $x-z$ cross section shows minimal overall bubble rise speed in the (very) viscous fluid in comparison to the rate that the bubble deforms.
 This is expected since the experiments designed by \cite{CanedoETAL} closely followed the following basic assumptions: (i) ``steady creeping flow with negligible inertial effects,'' (ii) ``Incompressible Newtonian fluids,'' (iii) ``No buoyancy effects,'' (iv) ``No wall effects.''  In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.
@@
 \textcolor{red} {
-We remark that there have been a number of articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
+We remark that there have been a number of computational articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
 We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.
@@
 \textcolor{red} {
-To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop (for terrestrial experiments, when the density ratio of drop to matrix is very close to one!).
+To highlight the mechanisms of bubble deformation and breakup in a shear flow, we juxtapose the bubble results with those of a drop.
 We remark that while the study of critical tensile strength parameters for the bubble is sparse, there have been many studies for the simpler drop problem.
+This is because the density ratio for the drop deformation case is almost one so that it is not required that the continuous phase liquid be highly viscous in order to mitigate buoyancy effects.
 For completeness, we give a brief overview of previous ``tensile strength'' studies pertaining to drops.
@@
 In order to accurately compute the tensile strength of a bubble, one must resort to a combination of parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).
+These aspects of our algorithm allow one to accurately simulate the balance of the restoring bubble surface tension force against the driving wall shear force.
 }

### 2024-11-26 Revised-paper/Paper/Bubble-deformation-Rev.tex
more references

@@
 {
-Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow.
+For the first time, either experimentally or numerically, numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow in the low Capillary number, high Reynolds number regime.
 Numerical results are obtained using a projection method for incompressible two-phase flow.
@@
 \textcolor{red} {
-	This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low $Ca$ ($Ca=\mu_{m}U/\sigma$) conditions, low-density ratio, low viscosity ratios, and zero buoyancy effects.  We remark that the majority of previous experimental studies on shear-driven bubble deformation are restricted to low Reynolds' number and large capillary number\cite{RusMan02,CanedoETAL}.
+	This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low Capillary number ($Ca=\mu_{m}U/\sigma$) conditions, high Reynolds' number conditions ($Re=\rho_{m} R U/\mu_{m}$), low-density ratio, low viscosity ratios, and zero buoyancy effects.  We remark that previous controlled experimental studies on shear-driven bubble deformation are restricted to the low Reynolds' number and large capillary number regime\cite{RusMan02,CanedoETAL}.
 One reason is that buoyancy effects are minimized in highly viscous liquids.
@@
 We validate our numerical method by examining the sensitivity of the critical bubble deformation and break-up flow states with respect to the grid size.
-An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify bubble/drop shape initial conditions \cite{ohta2005computational}, fluid physical properties and external properties (e.g.
-we can easily modify the gravity force, in order to compare with the analogous drop case or compare with microgravity conditions) in order to isolate the sensitivity of deformation and breakup to physical parameters.
-In our computations, the time-evolution of the boundary between gas and liquid is tracked with a Coupled-Level-Set and Volume-Of-Fluid (CLSVOF) interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.
+We also compare with previous experimental results where the experimental data is available (the high Capillary number low Reynolds' number regime).
+An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify bubble/drop shape initial conditions \cite{ohta2005computational}, the gravity force term, fluid physical properties, and the geometry of the (virtual) apparatus.
+In our computations, the time-evolution of the boundary between gas and liquid is tracked with a Coupled-Level-Set and Volume-Of-Fluid (CLSVOF) sharp interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.
 The rationale for the CLSVOF method is that the hybrid method represents the (complex) gas-liquid interfaces with minimal volume loss (property of the Volume-Of-Fluid method) and minimal error in the approximation of the surface tension force (property of the Level-Set method).
+Our sharp interface approach\cite{SusSmiHusOhtZhi07,Sus03,KanFedLiu00} enables us to simulate multiphase flows without artificially giving the interface an empirical thickness.
 }
@@
 \par
-In previous studies on the motion of bubble deformation in a simple shear flow \cite{CanedoETAL,RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
+In previous experimental or computational studies on the motion of bubble deformation in a simple shear flow \cite{CanedoETAL,RusMan02, MulTobDreFisWin08}, only findings for bubble deformation under very low $Re$ number conditions ($Re \ll 1$) have been reported.
 This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.
 In the results reported in \cite{CanedoETAL}, the $x-z$ cross section of the deforming bubble was close to spherical in their experiments.
-Also in the experiments in \cite{CanedoETAL}, the $x-z$ cross section shows minimal overall bubble rise speed in the (very) viscous fluid in comparison to the rate that the bubble deforms.
+Also in the experiments in \cite{CanedoETAL}, the $x-z$ cross section shows minimal overall bubble rise speed in the (very) viscous fluid in comparison to the rate that the bubble deforms in the $y-z$ cross section.
 This is expected since the experiments designed by \cite{CanedoETAL} closely followed the following basic assumptions: (i) ``steady creeping flow with negligible inertial effects,'' (ii) ``Incompressible Newtonian fluids,'' (iii) ``No buoyancy effects,'' (iv) ``No wall effects.''  In this work, we determine, for the first time, the critical Reynolds number ($Re \gg 1$) that leads to bubble breakup.
@@
 For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.
-We contend that a projection method (e.g.
+We contend that a projection method (i.e.
 this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower) method for our study rather than the Lattice Boltzmann method.
@@
 The results that we present in this article (see e.g.
-section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data and grid refinement studies.
+section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data (where available) and grid refinement studies.
 Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.
-Finally, the larger the deformation parameter $D$, the longer we must make our computational domain (bigger domain aspect ratio!) thereby adversely effecting the condition number even more for carrying our the pressure projection.
+Finally, the larger the deformation parameter $D$, the longer one must make the computational domain (and thereby leading to larger domain aspect ratio) thereby adversely effecting the condition number even more for carrying our the pressure projection.
 }
@@
 In contrast, few studies have been conducted on bubble deformation and breakup.
+In the low Capillary number, high Reynolds' number regime, there are no controlled experiments or simulations.
 We reiterate why there have been few studies regarding the ``tensile strength'' of bubbles.
@@
 %
-$U$ is the velocity scale and $\sigma$ denotes the surface tension.
-For the problem of shear-induced drop deformation and breakup, the velocity is set to $U = \mathit{\Gamma} R$, where the shear-rate is $\mathit{\Gamma} = 2V/H$.
+$U$ is the velocity scale and $\sigma$ denotes the surface tension.  For the problem of shear-induced drop deformation and breakup, the velocity is set to,
+\begin{eqnarray*}
+U = \mathit{\Gamma} R, 
+\end{eqnarray*}
+where the shear-rate is,
+\begin{eqnarray*}
+\Gamma = 2V/H.  
+\end{eqnarray*}
 As mentioned in the introduction, most previous drop studies set $\eta = 1$ (e.g.
@@
 When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.
-Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
+Although the values of $Fr$ are not so large, the effect of gravity (inducing bubble rise motion) may not be completely negligible in terms of $Fr$.
 However, bubbles in our computations reach the breakup by way of deformation very quickly at $t$ = about 0.5 s.
-Accordingly, it is expected that the effect of gravity (bubble rise motion) can be small for the behavior of bubble deformation and breakup around critical $Re$ number conditions in our study.
+Accordingly, it is expected that the effect of gravity (inducing bubble rise motion) can be small for the behavior of bubble deformation and breakup around critical $Re$ number conditions in our study.
 }
@@
 \end{align}
+
+\textcolor{red}
+{
+	We remark that our method is a ``sharp interface method\cite{SusSmiHusOhtZhi07,Sus03,KanFedLiu00}.
+Thereby we do not need to specify an empirical interface thickness parameter\cite{SusSmeOsh94,SusPuc00}.
+}
+
 %
@@
 {
-The effectiveness of our computational method has been demonstrated for the complicated rising motion of single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19}.
+	The effectiveness of our sharp interface computational method has been demonstrated via grid refinement studies and comparison with experiments for the complicated rising motion of single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19,ohta2010sensitivity,stewart2008improved,SusSmiHusOhtZhi07}, the simulation of atomization in a realistic diesel injector\cite{arienti2013coupled}, and the simulation of bubble formation due to the injection of gas through a nozzle\cite{ohta2011robust}.
 In this section, the accuracy of our computational method will be verified for the problem of shear-induced deformation of a drop and bubble.

### 2024-11-27 Revised-paper/Paper/Bubble-deformation-Rev.tex
microgravity papers

@@
 {
-For the first time, either experimentally or numerically, numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow in the low Capillary number, high Reynolds number regime.
+Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow in a variety of regimes including the low Capillary number, high Reynolds number regime.
 Numerical results are obtained using a projection method for incompressible two-phase flow.
 The method represents interfaces using the sharp interface coupled level set and Volume-Of-Fluid (CLSVOF) method.
-To verify our numerical algorithm and provide a basis for comparison, we also present simulation results that compare with previous, more popular, drop deformation and rupture simulations.
+To verify the CLSVOF numerical algorithm and provide a basis for comparison, computational results are also presented that compare with previous, more popular, drop deformation and rupture simulations.
 The numerical results reveal that the shear-induced bubble deformation and breakup process differs significantly from that of the analogous drop system under similar flow conditions.
@@
 Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.
-We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, underwater projectiles, polyethylene devolatilization, microfluidics, food aeration, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL,GAO2022103212,WONG2012417,PolyethyleneDevo,FRENSE2024120579,lohse2018bubble,schluter2021small,SANOGO2023112478}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
+We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, underwater projectiles, polyethylene devolatilization, microfluidics, food aeration, passive cyclonic separators, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL,GAO2022103212,WONG2012417,PolyethyleneDevo,FRENSE2024120579,lohse2018bubble,schluter2021small,SANOGO2023112478,hoyt2013performance,sines2020study}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
 }
@@
 This is understandable since a low Reynolds number matrix fluid mitigates the effect of gravity on distorting the comparison with the drop case.
-In the results reported in \cite{CanedoETAL}, the $x-z$ cross section of the deforming bubble was close to spherical in their experiments.
+In the results reported in \cite{CanedoETAL}, the $x-z$ cross section of the deforming bubble was close to circular in their experiments.
 Also in the experiments in \cite{CanedoETAL}, the $x-z$ cross section shows minimal overall bubble rise speed in the (very) viscous fluid in comparison to the rate that the bubble deforms in the $y-z$ cross section.
@@
 If $0 < F < 1$, then a computational cell contains the gas-liquid interface.
-The VOF method has a great advantage over the LS method in that accurate algorithms for advecting $F$ can be applied so that mass/volume is conserved up to machine precision while still maintaining a sharp representation of the interface.
+The VOF method has an advantage over the LS method in that accurate algorithms for advecting $F$ can be applied so that mass/volume is conserved up to machine precision while still maintaining a sharp representation of the interface.
 On the other hand, the disadvantage of the VOF method in comparison to the LS method is that tangled and difficult reconstruction procedures are required for determining the slope of the piecewise linear VOF reconstructed interface.
@@
 
+\textcolor{red}
+{
+Remark 1: Due to time step stability constraints, the variable density pressure projection process, and computed bubble shapes with high aspect ratio, we find that our simulations can take over six months.
+We have experimented with (a) decreasing the ``error buffer'' parameter (radius of cells to be tagged when a given cell is tagged for adaptivity) and (b) relaxing the condition that the bubble-liquid interface be wholly contained on the finest adaptive level.
+Unfortunately we have found that these steps lead to poorer accuracy.
+This ``diminishing returns'' phenomena is expected for low Mach number flows in which the incompressible flow equations are characterized by non-local behavior.
+We refer the reader to the following research\cite{li2016high} in which it has been found through a systematic study that using an AMR grid can be less accurate than a case with a uniform fine grid (luckily that is not the case here).
+To summarize: we have found that each further refinement of the grid will multiply the simulation time by a factor of about eight (factor of 4 due to spatial refinement, factor of 2 due to temporal refinement).
+}
+
+\textcolor{red}
+{
+Remark 2: We believe that the inclusion of a special sub-scale model right at the point of bubble break-up is unnecessary because the driving shear force is temporally uniformly applied instead of impulsively applied.
+We are aware of research for predicting whether droplets merge or bounce\cite{Lewin-Jones_Lockerby_Sprittles_2024} but this research is not applicable in our case.
+We are not aware of previous studies on the shear flow driven breakup of bubble or drops that implement special subscale models.
+}
+
 \subsection{Validation of the numerical method}
@@
 
-Finally, we present a comparison with numerical results for drop breakup reported
-in~\citet{RenCri01-2}.  Figure~\ref{fig:DropBreakComp} demonstrates drop breakup
-with pinch-off behavior for three $Re$ and $Ca$ conditions and with constant
-values of $\lambda = \eta = 1$ for all cases.  The three cases that we consider
-correspond to (a) $Re = 10, \, Ca = 0.16$, (b) $Re = 12, \, Ca = 0.1753$, and
-(c) $Re = 15, \, Ca = 0.196$, and which are illustrated in
-Figures~\ref{fig:DropBreakComp}(a)-(c), respectively.  The results reported
-in~\citet{RenCri01-2}, which were obtained with a VOF method, are shown inside
-boxes while results obtained with our CLSVOF approach are displayed outside
-boxes.  In the computations presented in~\citet{RenCri01-2}, the dimensions
-$W=4R$ and $H=8R$ were fixed, while $L$ was changed depending on $Re$ and $Ca$
-conditions, and the grid size was set to $\Delta x=\Delta y=\Delta z=R/8$.  To
-compare with their results, we performed simulations with the CLSVOF method
-over a two-level AMR computational domain of the same dimensions and the same
-level-0 discretization: $\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta
-z^{\ell=0} = R/8$; we set the finer level-1 grid size $\Delta x^{\ell=1} =
-\Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.  The results shown in
-Figure~\ref{fig:DropBreakComp} verify that our numerical approach can reproduce
-the same drop breakup behavior presented in~\citet{RenCri01-2}.  Slight
-differences between the results can be attributed to the increased resolution
-used in our study in the level-1 grid around the elongated drop.
-
+Finally, we present a comparison with numerical results for drop breakup reported in~\citet{RenCri01-2}.
+Figure~\ref{fig:DropBreakComp} demonstrates drop breakup with pinch-off behavior for three $Re$ and $Ca$ conditions and with constant values of $\lambda = \eta = 1$ for all cases.
+The three cases that we consider correspond to (a) $Re = 10, \, Ca = 0.16$, (b) $Re = 12, \, Ca = 0.1753$, and (c) $Re = 15, \, Ca = 0.196$, and which are illustrated in Figures~\ref{fig:DropBreakComp}(a)-(c), respectively.
+The results reported in~\citet{RenCri01-2}, which were obtained with a VOF method, are shown inside boxes while results obtained with our CLSVOF approach are displayed outside boxes.
+In the computations presented in~\citet{RenCri01-2}, the dimensions $W=4R$ and $H=8R$ were fixed, while $L$ was changed depending on $Re$ and $Ca$ conditions, and the grid size was set to $\Delta x=\Delta y=\Delta z=R/8$.
+To compare with their results, we performed simulations with the CLSVOF method over a two-level AMR computational domain of the same dimensions and the same level-0 discretization: $\Delta x^{\ell=0} = \Delta y^{\ell=0} = \Delta z^{\ell=0} = R/8$; we set the finer level-1 grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
+The results shown in Figure~\ref{fig:DropBreakComp} verify that our numerical approach can reproduce the same drop breakup behavior presented in~\citet{RenCri01-2}.
+Slight differences between the results can be attributed to the increased resolution used in our study in the level-1 grid around the elongated drop.
+
+\textcolor{red}{
 The numerical validation studies performed in this section and the
@@
 analysis in this section and the following also demonstrate that the error is
-reduced by a factor of 2 each time the grid is refined by a factor of 2. Also,
-we refer the reader to \citet{ohta2011robust} in which we apply our CLSVOF
-method for bubble formation problems.
+reduced by a factor of 2 each time the grid is refined by a factor of 2.
+We reiterate that we have found at least a factor of 2 error reduction for each grid refinement in a number of multiphase flow problems involving complex interface deformation and breakup; see \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19,ohta2010sensitivity,stewart2008improved,SusSmiHusOhtZhi07,arienti2013coupled,ohta2011robust}.
+}
 
@@
 %  -----------------------------------------------------------------------------
-The bubble deformation and breakup process in simple linear shear flow liquid
-was explored numerically using the CLSVOF computational method.  In this study,
-the critical Reynolds number $Re_{\rm c}$, at which bubble breakup first occurs,
-was determined for several flow conditions, and the differences between bubble
-deformation and breakup were compared with the well-known analogous process of
-drop deformation and breakup.
-
-Numerical results revealed significant differences between bubble deformation
-and breakup and the corresponding drop dynamics.  For case of bubble, it was
-discovered that much stronger shear flows are necessary to induce interface
-breakup compared with a drop immersed in a similar flow field.  That is, a much
-larger Reynolds number flow is required in order to induce bubble breakup.  The
-behavior of bubble breakup was very similar through the $Ca$ number range
-considered in our computations: the bubble underwent a similar breakup
-mechanism in which rupture occurred at a thread-bridge part that followed a
-doglegged shape formation stage.  In bubble deformation without breakup, near
-$Re_{\rm c}$, the bubble did not maintain a stable deformed shape, in contrast to
-drop deformation near the critical Reynolds number.  The bubble exhibited
-pronounced underdamped behavior: the bubble oscillated between elongating and
-shrinking motions for non-rupturing flow conditions.
-\textcolor{red}
-{
-At the same time, bubble deformation under smaller $Re$ conditions ($< Re_{\rm c}$)
-becomes in a stable state.
-}
-We attribute the large differences in morphology for the bubble undergoing
-breakup, compared with the drop, to the density and viscosity ratio.  The
-density and viscosity ratio remarkably impacts on bubble/drop deformation and
-breakup.  The bubble deformation and breakup is subject to a synergistic
-coupling of the density and viscosity ratio, and whose effect will be examined
-separately in future work.
+\textcolor{red}{
+The bubble deformation and breakup process in liquid due to a driving simple linear shear flow was explored numerically using the CLSVOF computational method.
+In this study, the critical Reynolds number $Re_{\rm c}$, at which bubble breakup first occurs, was determined for several flow conditions, and the differences between the morphology of bubble deformation and breakup were compared with the analogous morphology of drop deformation and breakup.
+}
+
+\textcolor{red}{
+The numerical results revealed significant differences between bubble deformation and breakup and the corresponding drop dynamics.
+For the case of a bubble, it was discovered that much stronger shear flows are necessary in order to induce interface breakup compared with a drop immersed in a similar flow field.
+That is, a much larger Reynolds number flow is required in order to induce bubble breakup.
+The steps leading to bubble breakup were similar throughout the $Ca$ number range considered in our computations: the bubble underwent a similar breakup mechanism in which rupture occurred at a thread-bridge part that followed a doglegged shape formation stage.
+For bubble deformation without breakup, near $Re_{\rm c}$, the bubble did not maintain a stable deformed shape, in contrast to drop deformation near the critical Reynolds number.
+The bubble exhibited pronounced underdamped behavior: the bubble oscillated between elongating and shrinking motions for non-rupturing flow conditions.
+At the same time, bubble deformation under smaller $Re$ conditions ($< Re_{\rm c}$) led to a stable state.
+We attribute the large differences in morphology for the bubble undergoing breakup, compared with the drop, due to the density and viscosity ratio.
+}
+
+\textcolor{red}{
+There are a number of directions for future work.
+In the present work, we varied the Capillary number and Reynolds' number in studying bubble deformation and breakup morphology in the presence of a simple shear flow.
+For the future, one can also vary (i) the viscosity ratio, (ii) the effect of the initial shape of the bubble\cite{ohta2005computational}, (iii) the magnitude and direction of the gravitational force, (iv) the non-Newtonian properties of the ``matrix'' liquid, (v) bubble deformation and breakup due to a shear flow in a T junction\cite{FRENSE2024120579}, (vi) bubble deformation and breakup confined shear flow (see \cite{gupta2014deformation} for the drop case), and (vii) bubble deformation and breakup due to non-uniform shear flow (see \cite{chin1980studies} for the drop case).
+}
 

### 2024-11-28 Revised-paper/Paper/Bubble-deformation-Rev.tex
fixed all the grammar errors, hopefully

@@
 We also compare with previous experimental results where the experimental data is available (the high Capillary number low Reynolds' number regime).
-An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that we can easily modify bubble/drop shape initial conditions \cite{ohta2005computational}, the gravity force term, fluid physical properties, and the geometry of the (virtual) apparatus.
+An advantage of studying shear-driven bubble deformation and breakup computationally rather than experimentally is that one can easily modify bubble/drop shape initial conditions \cite{ohta2005computational}, the gravity force term\cite{hoyt2013performance}, fluid physical properties, and the geometry of the (virtual) apparatus\cite{FRENSE2024120579}.
 In our computations, the time-evolution of the boundary between gas and liquid is tracked with a Coupled-Level-Set and Volume-Of-Fluid (CLSVOF) sharp interface capturing algorithm \cite{SusPuc00,SusSmiHusOhtZhi07}.
@@
 	We remark that there have been a number of computational articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.
-We reiterate, though, that for bubble deformation and breakup in shear flows, only a few articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.
+We reiterate, though, that for bubble deformation and breakup in shear flows, only a few computational articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.
 These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.
@@
 In order to accurately compute the tensile strength of a bubble, one must resort to a combination of parallel computing, the multigrid preconditioned conjugate gradient method\cite{tatebe1993multigrid,SusSmiHusOhtZhi07} for poorly conditioned large sparse matrix systems, adaptive mesh refinement\cite{AMReX_JOSS,SusSmiHusOhtZhi07}, and a robust, volume preserving interface tracking method (we use the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}).
-These aspects of our algorithm allow one to accurately simulate the balance of the restoring bubble surface tension force against the driving wall shear force.
+These aspects of our algorithm allow one to accurately simulate the balance of the restoring bubble surface tension force against the driving wall shear force and at the same time, accurately simulate the evolution of the bubble shape to bubble-break-up if the given shear stress and physical properties permit it.
 }
@@
 {
-For readers’ reference, we describe the effect of gravity here.
-When we apply $g$ = 9.8 m/$s^{2}$,  $Fr$  can be $Fr$ = $1.7 \sim 1.9$ in our computations.
-Although the values of $Fr$ are not so large, the effect of gravity (inducing bubble rise motion) may not be completely negligible in terms of $Fr$.
+Remark: if we were to apply ``Earth'' gravity conditions in our simulations, then $g$ = 9.8 m/$s^{2}$,  and the Froude number ($Fr$) is in the range $Fr$ = $1.7 \sim 1.9$.
+Although these values of $Fr$ are not so large, the effect of gravity (inducing bubble rise motion) may not be completely negligible.
 However, bubbles in our computations reach the breakup by way of deformation very quickly at $t$ = about 0.5 s.
-Accordingly, it is expected that the effect of gravity (inducing bubble rise motion) can be small for the behavior of bubble deformation and breakup around critical $Re$ number conditions in our study.
-}
+Accordingly, it is expected that the effect of gravity (inducing bubble rise motion) can be small for the behavior of bubble deformation and breakup around the critical $Re$ number conditions determined in our study.
+}
+
 %  -----------------------------------------------------------------------------
@@
 $\bmu$ is the velocity vector, $t$ represents time, $p$ is the pressure, $\bmI$ is the unit tensor, $\bmD$ is the rate of deformation tensor ($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$ is the viscosity, $\kappa$ is the interfacial curvature, and the Heaviside function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$.
-The singular Heaviside gradient term in the right hand side of equation~\eqref{nseqn} is a body force representing the surface tension force and is equivalent to specifying that the jump in the normal stress is equal to $\sigma\kappa$ (\citet{TanguyEtAl2007}).
+The singular Heaviside gradient term in the right-hand side of equation~\eqref{nseqn} is a body force representing the surface tension force and is equivalent to specifying that the jump in the normal stress is equal to $\sigma\kappa$ (\citet{TanguyEtAl2007}).
 The surface tension force expressed by the singular Heaviside gradient term acts only on the gas-liquid interface.
@@
 \par
-The interfacial curvature $\kappa$ is computed with second order accuracy directly from the volume-of-fluid (VOF) function and the level set function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).
-We remark that we get the same results if we were to compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
-
+The interfacial curvature $\kappa$ is computed with second-order accuracy directly from the volume-of-fluid (VOF) function and the level set function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).
+We remark that we would get the same results if we compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
+\par
 Since $\rho$ and $\mu$ are taken to be constant in each fluid, with a jump at
@@
 %
-The subscripts ``b'' and ``m'' refer to ``drop or bubble'' and ``matrix fluid'', respectively.
-To represent the free surface with the CLSVOF method, we must evolve the solution to both the VOF equation for $F$ and the LS equation for $\phi$:
+The subscripts ``b'' and ``m'' refer to ``bubble'' (or drop) and ``matrix fluid.'' To represent the free surface with the CLSVOF method, we must evolve the solution to both the VOF equation for $F$ and the LS equation for $\phi$:
 %
@@
 %
-In all computations, the discretized variables $p$, $\phi$ and $F$ are located at the cell centers and the discrete velocity variable $\bmu$ is located at cell face centers.
+In all computations, the discretized variables $p$, $\phi$, and $F$ are located at the cell centers, and the discrete velocity variable $\bmu$ is located at the cell face centers.
 Our computations are performed using an overall second-order accurate hydrodynamic scheme.
@@
 \par
-The temporal discretization of our numerical method is an operator split
-projection method as described by \citet{SusSmiHusOhtZhi07}.  An outline of 
-our method is as follows (see \citet{SusSmiHusOhtZhi07}, section 4, for more 
-details):
+The temporal discretization of our numerical method is an operator split projection method as described by \citet{SusSmiHusOhtZhi07}.
+An outline of our method is as follows (see \citet{SusSmiHusOhtZhi07}, section 4, for more details):
 \begin{description}
@@
 Adaptive grids are dynamically adjusted based on the location of the deforming gas-liquid interface.
-In the AMR technique, the grid resolution is increased in regions near the interface while a coarser grid is used where the flow is relatively steady.
-The upper panel of Figure~\ref{fig:SchemAndGrid}(b) displays a schematic view of the hierarchical grid structure and the lower panel corresponds to an actual computational example corresponding to bubble deformation in simple linear shear flow.
+In the AMR technique, the grid resolution is increased in regions near the interface, while a coarser grid is used where the flow is relatively steady.
+The upper panel of Figure~\ref{fig:SchemAndGrid}(b) displays a schematic view of the hierarchical grid structure, and the lower panel corresponds to an actual computational example corresponding to bubble deformation in simple linear shear flow.
 In general, the mesh hierarchy is composed of different levels of refinement ranging from coarsest $\ell=0$ (``level-0") to finest $\ell=\ell_{\textrm{max}}$ (``level-$\ell_{\textrm{max}}$").
@@
 All computations in this study used an AMR system with a maximum prescribed level $\ell_{\textrm{max}} = 1$ (as illustrated in the upper panel of Figure~\ref{fig:SchemAndGrid}(b)).
-In our adaptive mesh refinement algorithm, the velocity in the coarse grid cells that neighbor fine grid cells is interpolated from the coarse grid using bilinear interpolation in order to initialize ``ghost'' fine cells.
-Thus, the bilinear interpolation procedure produces interpolated fine grid data as a linear combination of the coarse grid data.
-
+In our adaptive mesh refinement algorithm, the velocity in the coarse grid cells that neighbor fine grid cells are interpolated from the coarse grid using bilinear interpolation to initialize ``ghost'' fine cells.
+Thus, the bilinear interpolation procedure produces interpolated fine-grid data as a linear combination of the coarse-grid data.
+\par
 \textcolor{red}
@@
 Remark 1: Due to time step stability constraints, the variable density pressure projection process, and computed bubble shapes with high aspect ratio, we find that our simulations can take over six months.
-We have experimented with (a) decreasing the ``error buffer'' parameter (radius of cells to be tagged when a given cell is tagged for adaptivity) and (b) relaxing the condition that the bubble-liquid interface be wholly contained on the finest adaptive level.
-Unfortunately we have found that these steps lead to poorer accuracy.
-This ``diminishing returns'' phenomena is expected for low Mach number flows in which the incompressible flow equations are characterized by non-local behavior.
-We refer the reader to the following research\cite{li2016high} in which it has been found through a systematic study that using an AMR grid can be less accurate than a case with a uniform fine grid (luckily that is not the case here).
-To summarize: we have found that each further refinement of the grid will multiply the simulation time by a factor of about eight (factor of 4 due to spatial refinement, factor of 2 due to temporal refinement).
-}
-
-\textcolor{red}
-{
-Remark 2: We believe that the inclusion of a special sub-scale model right at the point of bubble break-up is unnecessary because the driving shear force is temporally uniformly applied instead of impulsively applied.
-We are aware of research for predicting whether droplets merge or bounce\cite{Lewin-Jones_Lockerby_Sprittles_2024} but this research is not applicable in our case.
-We are not aware of previous studies on the shear flow driven breakup of bubble or drops that implement special subscale models.
+We have experimented with (a) decreasing the ``error buffer'' parameter from two cells to one (radius of cells to be tagged when a given cell is tagged for adaptivity) and (b) relaxing the condition that the bubble-liquid interface be wholly contained on the finest adaptive level.
+Unfortunately, we have found that these steps lead to poorer accuracy.
+This ``diminishing returns'' phenomenon is expected for low Mach number flows in which the incompressible flow equations are characterized by non-local behavior.
+We refer the reader to the following research\cite{li2016high} in which it has been found through a systematic study that using an AMR grid can be less accurate than a case with a uniform fine grid (luckily, that is not the case here).
+To summarize, we have found that each further refinement of the grid will multiply the simulation time by about eight (a factor of 4 due to spatial refinement and a factor of 2 due to temporal refinement).
+}
+\par
+\textcolor{red}
+{
+Remark 2: We believe that including a customized sub-scale model right at the point of bubble break-up is unnecessary because the driving shear force is uniformly applied in the time variable instead of impulsively applied.
+We are aware of research for predicting whether droplets merge or bounce\cite{Lewin-Jones_Lockerby_Sprittles_2024} that necessitate the inclusion of a sub-scale model, but that research is not applicable in our case.
+Previous studies on the shear flow-driven breakup of bubbles or drops have not incorporated customized subscale models\cite{LiRenRen00,KomShaEskDer14,AmaBalCasOli19}.
 }
@@
 }
+\par
        First, we compare quantitatively against the steady-state drop deformation results reported by \citet{LiRenRen00}.
-The shape of a deformed drop in simple linear shear flow is described in terms of the Taylor deformation parameter $D$=$(a-b)/(a+b)$, where $a$ and $b$ are the major and minor axes of the deformed drop respectively.
+The shape of a deformed drop in simple linear shear flow is described in terms of the Taylor deformation parameter $D$=$(a-b)/(a+b)$, where $a$ and $b$ are the major and minor axes of the deformed drop, respectively.
 For consistency, we perform numerical simulations using CLSVOF over the same computational domain and grid size used in \citet{LiRenRen00}, which has dimensions $\lwh{8}{4}{8}$ (recall that $R$ is the bubble/drop radius) and a level-0 grid size $\Delta x=\Delta y=\Delta z=R/8$; our two-level AMR grid structure also uses a finer level-1 grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1} = \Delta z^{\ell=1} = R/16$.
 Numerical results are listed in Table~\ref{tab:DeComparison} for $D$ as a function of $Re$, with $Ca=0.3$ and $\lambda = \eta = 1$ fixed in every case.
-The results in Table~\ref{tab:DeComparison} compare computations using our CLSVOF algorithm with corresponding results that were obtained with the VOF method used in \citet{LiRenRen00}.
+The results in Table~\ref{tab:DeComparison} compare computations using our CLSVOF algorithm with corresponding results obtained with the VOF method used in \citet{LiRenRen00}.
 %
@@
 %% Ohta
-Next, we examine the validation of our computational method in which we compare with the ``bubble deformation in simple linear shear flow'' results reported by \citet{MulTobDreFisWin08}.
+Next, we report the results of validation tests conducted with our computational method; we compare our results with the ``bubble deformation in simple linear shear flow'' results reported by \citet{MulTobDreFisWin08}.
 \citet{MulTobDreFisWin08} experimentally inquired into the bubble deformation under the condition of $Re \approx 0$.
@@
 Comparisons of our numerical results and previous experimental results (\citet{MulTobDreFisWin08}) are tabulated in Table~\ref{tab:DeComparisonRe=0}.
-Additionally, in Table~\ref{tab:DeComparisonRe=0}, we also list experimental results with the condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by  \citet{RusMan02}.
+Additionally, in Table~\ref{tab:DeComparisonRe=0}, we list experimental results with the condition of $Re \approx 0$ and $\lambda \approx \eta \approx 0$ by  \citet{RusMan02}.
 These experimental values were obtained from the graph showing the relation of $D$ vs $Re$ (\citet{RusMan02}).
@@
 %
-
-Finally, we present a comparison with numerical results for drop breakup reported in~\citet{RenCri01-2}.
+Finally, we compare numerical results from our method with the numerical results for drop breakup reported in~\citet{RenCri01-2}.
 Figure~\ref{fig:DropBreakComp} demonstrates drop breakup with pinch-off behavior for three $Re$ and $Ca$ conditions and with constant values of $\lambda = \eta = 1$ for all cases.
@@
 \textcolor{red}{
-The numerical validation studies performed in this section and the
-following section demonstrate that our numerical method can reliably determine
-the transition regions at which shear-induced bubble or drop deformation leads
-to breakup.  We remark that in the next section, we demonstrate that we can
-expect an error of $3\%$ for predicting the transition to break-up.  The
-analysis in this section and the following also demonstrate that the error is
-reduced by a factor of 2 each time the grid is refined by a factor of 2.
-We reiterate that we have found at least a factor of 2 error reduction for each grid refinement in a number of multiphase flow problems involving complex interface deformation and breakup; see \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19,ohta2010sensitivity,stewart2008improved,SusSmiHusOhtZhi07,arienti2013coupled,ohta2011robust}.
+The numerical validation studies performed in this section and the following section demonstrate that our numerical method can reliably determine the transition regions at which shear-induced bubble or drop deformation leads to breakup.
+In the next section, we demonstrate that we can expect an error of $3\%$ for predicting the transition to break-up.
+The analysis in this section and the following also indicate that the error is reduced by a factor of 2 each time the grid is refined by a factor of 2.
+We reiterate that we have found at least a factor of 2 error reduction for each grid refinement in many multiphase flow problems involving complex interface deformation and breakup; see \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19,ohta2010sensitivity,stewart2008improved,SusSmiHusOhtZhi07,arienti2013coupled,ohta2011robust}.
 }
@@
 
-The computational domain size used in numerical studies can affect the behavior
-of drop deformation and breakup.  Referring to
-Figure~\ref{fig:SchemAndGrid}(a), with an appropriately large domain length $L$
-and a fixed width $W=4R$, the effect of the height $H$ on drop behavior was
-examined in~\citet{LiRenRen00} for Stokes flows and various $Ca$ conditions and
-in~\citet{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.  Other related studies
-investigated drop breakup sensitivity (\citet{RenCri01-1}) and drop deformation
-sensitivity (\citet{RenCriLi02}) with respect to the entire domain size.
+The computational domain size used in numerical studies can affect the behavior of drop deformation and breakup.
+Referring to Figure~\ref{fig:SchemAndGrid}(a), with an appropriately large domain length $L$ and a fixed width $W=4R$, the effect of the height $H$ on drop behavior was examined in~\citet{LiRenRen00} for Stokes flows and various $Ca$ conditions and in~\citet{KomShaEskDer14} for $Re=1$ and $Ca=0.27$.
+Other related studies investigated drop breakup sensitivity (\citet{RenCri01-1}) and drop deformation sensitivity (\citet{RenCriLi02}) with respect to the entire domain size.
 %
@@
 %
-
-Here we investigate the drop dynamics sensitivity to domain size around the
-critical Reynolds number $Re_{\rm c}=0.75$.  Specifically, we consider domain size
-sensitivity for the condition of $Re=0.75$, $Ca=0.3$, and $\lambda = \eta = 1$,
-which is a condition used in the comparison studies of the previous section.
-As shown in Table~\ref{tab:DeComparison}, the drop breaks up for the condition
-of $Re=0.75$ and $Ca=0.3$ with a domain size of $\lwh{8}{4}{8}$.  Results for
-domain size sensitivity for six domain systems, all of which use a level-1 grid
-size $\Delta x^{\ell=1} = \Delta y^{\ell=1}= \Delta z^{\ell=1} = R/16$, are
-tabulated in Table~\ref{tab:DomComparison}. Note that the domain size used in
-the comparison study (Table~\ref{tab:DeComparison}) corresponds to System 1.
-
-The results in Table~\ref{tab:DomComparison} suggest that drop deformation is
-promoted when we use a domain size with $W=4R$.  In contrast, the drop does not
-break up and becomes stable with a deformed shape if we set $L$ large enough
-and $W \geq 6R$ and $H \geq 6R$.  Since the value of $D$ for the domain size
-$\lwh{8}{6}{6}$ differs by only $1.3\%$ with the value for the domain size of
-$\lwh{8}{16}{16}$, in the results that follow we set the width to $W=6R$ and the
-height to $H=6R$ to minimize the number of computational grid nodes along those
-directions.  To determine the critical Reynolds number $Re_{\rm c}$ (with $Ca=0.3$),
-we consider a domain size of $\lwh{24}{6}{6}$, and we find that the drop
-reaches a stable state with deformation parameter $D$=0.549 for $Re=1.0$,
-while a value of $Re=1.1$ leads to drop breakup.
+Here, we investigate the drop dynamics sensitivity to domain size around the critical Reynolds number $Re_{\rm c}=0.75$.
+Specifically, we consider domain size sensitivity for the condition of $Re=0.75$, $Ca=0.3$, and $\lambda = \eta = 1$, a condition used in the comparison studies of the previous section.
+As shown in Table~\ref{tab:DeComparison}, the drop breaks up for the condition of $Re=0.75$ and $Ca=0.3$ with a domain size of $\lwh{8}{4}{8}$.
+Results for domain size sensitivity for six domain systems, all of which use a level-1 grid size $\Delta x^{\ell=1} = \Delta y^{\ell=1}= \Delta z^{\ell=1} = R/16$, are tabulated in Table~\ref{tab:DomComparison}.
+Note that the domain size used in the comparison study (Table~\ref{tab:DeComparison}) corresponds to System 1.
+
+The results in Table~\ref{tab:DomComparison} suggest that drop deformation is promoted when we use a domain size with $W=4R$.
+In contrast, the drop does not break up and becomes stable with a deformed shape if we set $L$ large enough and $W \geq 6R$ and $H \geq 6R$.
+Since the value of $D$ for the domain size $\lwh{8}{6}{6}$ differs by only $1.3\%$ with the value for the domain size of $\lwh{8}{16}{16}$, in the results that follow we set the width to $W=6R$ and the height to $H=6R$ to minimize the number of computational grid nodes along those directions.
+To determine the critical Reynolds number $Re_{\rm c}$ (with $Ca=0.3$), we consider a domain size of $\lwh{24}{6}{6}$, and we find that the drop reaches a stable state with deformation parameter $D$=0.549 for $Re=1.0$, while a value of $Re=1.1$ leads to drop breakup.
 % 
@@
 
-The grid size and adaptive meshing strategy that we adopt is chosen in order to
-answer the research question as to the conditions which determine whether a
-bubble in shear flow will break-up or not.  In such a case, we must accurately
-capture the balance of forces with respect to the (non-local) force exerted
-from the wall driven flow acting against the interfacial surface tension force.
-The accuracy of the ``Critical Reynolds Number'' depends on the largest Taylor
-Deformation parameter $D$ that is supported by the grid (see e.g. Figures
-\ref{fig:ShearStress} and \ref{fig:BubBrkCa0p8Re43}).  As we report here, we
-have found that as long as the grid size is fine enough to support a Taylor
-Deformation parameter $D<0.95$, then the transition region (i.e. ``Critical
-Reynolds number'') (see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit})
-will be captured with a tolerance of three percent.  The simulation time
-becomes impractical if we were to try to further improve the ``critical
-Reynolds number'' accuracy.  A smaller tolerance would necessitate a larger
-supported Deformation parameter $D$ which would in turn necessitate a higher
-aspect ratio computational domain, increased droplet surface area at break-up,
-increased number of time steps, and higher resolution for representing the
-drop/bubble at its thinnest point.
-
-We make the distinction between our present research, and the research found in
-the work of  \citet{zhang2021three,zhang2022three} on
-predicting the conditions for bubble mergers.  Even in the most extreme cases
-for mergers, the largest Deformation parameter never exceeds $0.4$ in
-\citet{zhang2021three}.  In summary, our gridding requirements necessitate grid
-points distributed relatively evenly throughout the computational domain when a
-bubble is stretched to a $D=0.9$ Deformation, whereas in \citet{zhang2021three}
-the gridding strategy necessitates a more localized strategy.
-
-The numerical results presented in this and the previous section used a
-finest-level grid size set to $\Delta x^{\ell=1}(= \Delta y^{\ell=1}= \Delta
-z^{\ell=1})=R/16$. To verify the adequacy of this grid resolution, we present
-rid refinement results for a bubble breakup simulation with $Ca=1.0$, which
-corresponds to the most deformable and stretchable bubble case considered in
-our numerical studies. We use three different grid systems, (i) $\Delta
-x^{\ell=1}=R/8$, (ii) $\Delta x^{\ell=1}=R/16$, and (iii) $\Delta
-x^{\ell=1}=R/24$, in order to determine $Re_{\rm c}$.
-Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation
-parameter $D$ over time for the three grid systems; the $x$-axis is a
-dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $D$.
-The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid
-system with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with
-$\Delta x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.  For
-the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is
-too coarse in order to capture the proper break-up time, albeit the critical
-Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid
-resolution cases.  Note that although the time evolution of $D$ for the two
-finer resolution systems ($R/16$ and $R/24$) is consistent between the two,
-(the predicted critical Reynolds numbers differ by $\sim 3\%$), the
-computational time using the grid system with $\Delta x^{\ell=1}=R/24$ was more
-than 6 times longer than the one based on the coarser system with $\Delta
-x^{\ell=1}=R/16$.  We remark that in our search for $Re_{\rm c}$, we considered
-a wide range of values of $Ca$ and we found it necessary to use a large $L$
-($\sim 24R$) since for certain shear flows the bubble can stretch significantly
-without breaking up.  Nevertheless, for the conditions presented in this
-section, the results indicate that our numerical approach, even with a
-finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of
-accurately reproducing bubble deformation and breakup without sacrificing any
-essential dynamical features.
+The grid size and adaptive meshing strategy we adopt are chosen to answer the research question as to the conditions that determine whether a bubble in shear flow will break up.  In such a case, we must accurately capture the balance of forces between the (non-local) force exerted from the wall-driven flow acting against the interfacial surface tension force.  The accuracy of the ``Critical Reynolds Number'' depends on the largest Taylor Deformation parameter $D$ that is supported by the grid (see e.g., Figures \ref{fig:ShearStress} and \ref{fig:BubBrkCa0p8Re43}).  As we report here, we have found that as long as the grid size is fine enough to support a Taylor Deformation parameter $D<0.95$, then the transition region (i.e.
+``Critical Reynolds number'') (see Figures \ref{fig:DeEvolution} and \ref{fig:CaRecFit}) will be captured with a tolerance of three percent.  The simulation time would become impractical if we were to try further to improve the accuracy of the ``critical Reynolds number''.  A smaller tolerance would necessitate a larger supported Deformation parameter $D$, which would in turn, necessitate a higher aspect ratio computational domain, increased droplet surface area at break-up, increased number of time steps, and higher resolution for representing the drop/bubble at its thinnest point.
+
+We distinguish between our present research and the research found in the work of \citet{zhang2021three,zhang2022three} on predicting the conditions for bubble mergers.  Even in the most extreme cases for mergers, the largest Deformation parameter never exceeds $0.4$ in \citet{zhang2021three}.  In summary, our gridding requirements necessitate grid points distributed relatively evenly throughout the computational domain when a bubble is stretched to a $D=0.9$ Deformation, whereas in \citet{zhang2021three}, the gridding strategy necessitates a more localized approach.
+
+The numerical results presented in this and the previous section used a finest-level grid size set to $\Delta x^{\ell=1}(= \Delta y^{\ell=1}= \Delta z^{\ell=1})=R/16$.
+To verify the adequacy of this grid resolution, we present rid refinement results for a bubble breakup simulation with $Ca=1.0$, which corresponds to the most deformable and stretchable bubble case considered in our numerical studies.
+We use three different grid systems, (i) $\Delta x^{\ell=1}=R/8$, (ii) $\Delta x^{\ell=1}=R/16$, and (iii) $\Delta x^{\ell=1}=R/24$, in order to determine $Re_{\rm c}$.
+Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation parameter $D$ over time for the three grid systems; the $x$-axis is a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $D$.
+The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.
+For the $\Delta x^{\ell=1}=R/8$ results, it is clear that the $R/8$ resolution is too coarse to capture the proper break-up time, albeit the critical Reynolds' number, $Re_{\rm c}$ = 33, was still close to the finer grid resolution cases.
+Note that although the time evolution of $D$ for the two finer resolution systems ($R/16$ and $R/24$) is consistent between the two (the predicted critical Reynolds numbers differ by $\sim 3\%$), the computational time using the grid system with $\Delta x^{\ell=1}=R/24$ was more than 6 times longer than the one based on the coarser system with $\Delta x^{\ell=1}=R/16$.
+We remark that in our search for $Re_{\rm c}$, we considered a wide range of values of $Ca$, and we found it necessary to use a large $L$ ($\sim 24R$) since for certain shear flows the bubble can stretch significantly without breaking up.
+Nevertheless, for the conditions presented in this section, the results indicate that our numerical approach, even with a finest-level resolution set to $\Delta x^{\ell=1}=R/16$, is capable of accurately reproducing bubble deformation and breakup without sacrificing any essential dynamical features.
 
@@
 %
-To illustrate the differences in deformation and breakup between a drop and a
-bubble around critical conditions, we first present numerical results for drop
-deformation.  The time evolution of drop deformation and breakup in simple
-linear shear flow for two conditions is shown in Figure 4;
-%~\ref{fig:DropBreak};
-the first case, shown in Figure 4(a),
-%~\ref{fig:DropBreak}(a)
-uses $Ca=0.3$ and $Re=1.0$, while the second case, depicted in Figure 4(b),
-%~\ref{fig:DropBreak}(b),
-uses $Ca=0.3$ and $Re=1.1$.  Using a domain size of $\lwh{24}{6}{6}$, in the
-case with $Re=1.0$, the drop gradually deforms and finally attains a stable
-deformed state. 
+To illustrate the differences in deformation and breakup between a drop and a bubble around critical conditions, we first present numerical results for drop deformation.
+The time evolution of drop deformation and breakup in simple linear shear flow for two conditions is shown in Figure \ref{fig:DropBreak}; the first case, shown in Figure ~\ref{fig:DropBreak}(a), uses $Ca=0.3$ and $Re=1.0$, while the second case, depicted in Figure ~\ref{fig:DropBreak}(b), uses $Ca=0.3$ and $Re=1.1$.
+Using a domain size of $\lwh{24}{6}{6}$, in the case with $Re=1.0$, the drop gradually deforms and finally attains a stable deformed state.
+
 \textcolor{red}
@@
 After $T$ = 35.0, the drop remains a stable deformed state with $D$= 0.549.
-}
-Over the same domain, for the case with
-$Re=1.1$, the ``mother'' drop elongates over time and the volume at the ends of
-the deforming drop expands; that is, both ends of the drop become bulb-shaped.
-As time progresses, particularly over the time interval $48.4 \leq T \leq
-55.2$, a thread-bridge forms between the bulbous ends and the thread-bridge
-becomes thinner.  Finally, at around the dimensionless time $T\sim 56.7$, the
-mother drop breaks up, forming two ``daughter'' drops through the pinch off;
-one satellite drop is also generated between the pinched off daughter drops.
+Over the same domain, for the case with $Re=1.1$, the ``mother'' drop elongates over time, and the volume at the ends of the deforming drop expands; both ends become bulb-shaped.
+As time progresses, particularly over the time interval $48.4 \leq T \leq 55.2$, a thread-bridge forms between the bulbous ends, and the thread-bridge becomes thinner.
+Finally, at around the dimensionless time $T\sim 56.7$, the mother drop breaks up, forming two ``daughter'' drops through the pinch-off; one satellite drop is also generated between the pinched-off daughter drops.
+}
 
@@
 %
-Next we present numerical results that illustrate the conditions that lead to
-bubble deformation without breakup as well as conditions where the bubble
-deforms and ultimately breaks up.  The time evolution of shear-induced bubble
-deformation without breakup at the condition of $Ca=0.3$ and $Re=92$ is
-depicted in Figure~\ref{fig:BubbleBreakCa0p3Re92} and the bubble breakup
-process with flow condition of $Ca=0.3$ and $Re=93$ is illustrated in
-Figure~\ref{fig:BubbleBreakCa0p3Re93}.  The results indicate that the critical
-Reynolds number is approximately $Re_{\rm c}$ = 93 (with $Ca=0.3$).  A comparison
-with the drop breakup dynamics presented in Section~\ref{sec:DropBreak} and the
-corresponding processes for bubble deformation and breakup exhibit very
-distinct features.  First, we note that a relatively large shear force
-magnitude is required for bubble breakup 
-($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) 
-compared with the case of the drop ($\lambda$ = $\eta$ = 1). Then,
-for the same value of $Ca=0.3$, the critical Reynolds number for the bubble is
-around 85 times larger than that for the drop.  Focusing on the bubble dynamics
-with no-breakup (Figure~\ref{fig:BubbleBreakCa0p3Re92}), the results show that
-the bubble is largely elongated in the $x$-direction at the early stages ($T
-\leq 24.3$) of bubble deformation, but the bubble does not develop the
-bulb-like shape (large volume areas) at both ends present in the drop
-deformation process.  It is also evident that the ends of the deforming bubble
-develop cusped shapes under the influence of the strong shear flow.
-\textcolor{red}
-{
-In providing a more detailed description, very large shear forces are required to deform the bubble 
-because $\lambda \simeq 0$ and $\eta \simeq 0$.
-Thus, the bubble undergoing large shear forces at $T > 0$ is largely stretched long the shear flow direction, 
-and the very long elongated bubble with cusped shapes is formed. 
-Accordingly, the bubble finally breaks up through f the elongated shape without forming a bulb-like shape.
-}
-A noteworthy feature for the non-breaking bubble is that it does not settle into
-a deformed stable state as in the case of drop deformation presented in
-Figure~\ref{fig:DropBreak}(a).  After an initial elongation process, the bubble
-enters a shrinking phase ($T = 27.8$) where the doglegged shape formed at the
-center of the bubble returns to a smaller deformed shape ($T = 34.4$) that is
-similar to its earlier shape ($T=3.47$).  However, when we compare the early
-deformed bubble shape at $T = 3.47$ with the shape at $T = 34.4$, it is clear
-that the shapes are not identical.  Following the shrinking phase, the bubble
-begins to stretch again ($T = 38.2$) and the bubble oscillates between its
-elongated shape and shortened geometry.
+Next, we present numerical results that illustrate the conditions that lead to bubble deformation without breakup and conditions where the bubble deforms and ultimately breaks up.
+The time evolution of shear-induced bubble deformation without breakup at the condition of $Ca=0.3$ and $Re=92$ is depicted in Figure~\ref{fig:BubbleBreakCa0p3Re92} and the bubble breakup process with flow condition of $Ca=0.3$ and $Re=93$ is illustrated in Figure~\ref{fig:BubbleBreakCa0p3Re93}.
+The results indicate that the critical Reynolds number is approximately $Re_{\rm c}$ = 93 (with $Ca=0.3$).
+A comparison with the drop breakup dynamics presented in Section~\ref{sec:DropBreak} and the corresponding processes for bubble deformation and breakup exhibit very distinct features.
+First, we note that a relatively large shear force magnitude is required for bubble breakup ($\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$) compared with the case of the drop ($\lambda$ = $\eta$ = 1).
+Then, for the same value of $Ca=0.3$, the critical Reynolds number for the bubble is around 85 times larger than that for the drop.
+Focusing on the bubble dynamics with no-breakup (Figure~\ref{fig:BubbleBreakCa0p3Re92}), the results show that the bubble is noticeably elongated in the $x$-direction at the early stages ($T \leq 24.3$) of bubble deformation, but the bubble does not develop the bulb-like shape (large volume areas) at both ends as observed in the drop deformation process.
+It is also evident that the ends of the deforming bubble develop cusped shapes under the influence of the strong shear flow.
+
+\textcolor{red}
+{
+In providing a more detailed description, very large shear forces are required to deform the bubble because $\lambda \simeq 0$ and $\eta \simeq 0$.  Thus, the bubble undergoing large shear forces at $T > 0$ is largely stretched along the shear flow direction, and the very long elongated bubble with cusped shapes is formed.  Accordingly, the bubble finally breaks up through the elongated shape without forming a bulb-like shape.  A noteworthy feature of the non-breaking bubble is that it does not settle into a deformed stable state as in the case of drop deformation presented in Figure~\ref{fig:DropBreak}(a).  After an initial elongation process, the bubble enters a shrinking phase ($T = 27.8$) where the doglegged shape formed at the center of the bubble returns to a smaller deformed shape ($T = 34.4$) that is similar to its earlier shape ($T=3.47$).  However, when we compare the early deformed bubble shape at $T = 3.47$ with the shape at $T = 34.4$, it is clear that the shapes are not identical.  Following the shrinking phase, the bubble stretches again ($T = 38.2$) and oscillates between its elongated shape and shortened geometry.
+}
 
@@
 %
-For the case of bubble breakup (Figure~\ref{fig:BubbleBreakCa0p3Re93}), we
-observe that the deformation process is almost the same as the no-breakup case
-until the doglegged shape is formed at $T \sim 27.4$. The bubble finally breaks
-during the time interval $27.7 \leq T \leq 29.5$.  For a closer examination of
-the bubble breakup process, a detailed panel of cross-sectional slices in the
-$xz$-plane through the bubble shape center is presented in
-Figure~\ref{fig:BubBreakCa0p3Re93Detail}.  The images displayed in
-Figure~\ref{fig:BubBreakCa0p3Re93Detail}, which are taken at shorter time
-intervals than those shown in Fig.~\ref{fig:BubbleBreakCa0p3Re93}, reveal that
-the bubble breaks up into two daughter bubbles due to the pinch off at the
-thread-bridge part of the doglegged shape during the shrinking process ($T =
-28.5 \sim 28.8$).  After breaking up, the two daughter bubbles migrate to the
-center: the left daughter bubble moves toward the right-side of the domain and
-the right daughter bubble moves to the left side (see results for $T = 29.5
-\sim 35.1$ in Figure~\ref{fig:BubbleBreakCa0p3Re93} and for $T = 28.8 \sim
-30.9$ in Figure~\ref{fig:BubBreakCa0p3Re93Detail}).  The two daughter bubbles
-then momentarily congregate near the domain center ($T = 35.1$ in
-Figure~\ref{fig:BubbleBreakCa0p3Re93}), before they slowly start to separate:
-the left daughter bubble moves to the left and the right daughter bubble moves
-to the right ($T = 46.2$ in Figure~\ref{fig:BubbleBreakCa0p3Re93}).  The
-results clearly demonstrate that the bubble breakup process is markedly
-different from the analogous drop breakup process 
-\textcolor{red}
-{
-with $\lambda = 1$ and $\eta =1$. Note that the appearance of deformation and breakup of the drop
-will largely depend on the viscosity ratios.
+\textcolor{red}
+{
+For the case of bubble breakup (Figure~\ref{fig:BubbleBreakCa0p3Re93}), we observe that the deformation process is almost the same as the no-breakup case until the doglegged shape is formed at $T \sim 27.4$.
+The bubble finally breaks during the time interval $27.7 \leq T \leq 29.5$.  For a closer examination of the bubble breakup process, a detailed panel of cross-sectional slices in the $xz$-plane through the bubble shape center is presented in Figure~\ref{fig:BubBreakCa0p3Re93Detail}.  The images displayed in Figure~\ref{fig:BubBreakCa0p3Re93Detail}, which are taken at shorter time intervals than those shown in Fig.~\ref{fig:BubbleBreakCa0p3Re93}, reveal that the bubble breaks up into two daughter bubbles due to the pinch off at the thread-bridge part of the doglegged shape during the shrinking process ($T = 28.5 \sim 28.8$).  After breaking up, the two daughter bubbles migrate to the center: the left daughter bubble moves toward the right side of the domain and the right daughter bubble moves to the left side (see results for $T = 29.5 \sim 35.1$ in Figure~\ref{fig:BubbleBreakCa0p3Re93} and for $T = 28.8 \sim 30.9$ in Figure~\ref{fig:BubBreakCa0p3Re93Detail}).  The two daughter bubbles then momentarily congregate near the domain center ($T = 35.1$ in Figure~\ref{fig:BubbleBreakCa0p3Re93}), before they slowly start to separate: the left daughter bubble moves to the left, and the right daughter bubble moves to the right ($T = 46.2$ in Figure~\ref{fig:BubbleBreakCa0p3Re93}).  The results demonstrate that the bubble breakup process is markedly different from the analogous drop breakup process with $\lambda = 1$ and $\eta =1$.
+Note that the appearance of deformation and breakup of the drop will largely depend on the viscosity ratios.
 }
@@
 %
-In the previous section, the appearance of bubble deformation and breakup was
-discussed. It is expected that a large deformation and breakup of the bubble
-are closely related to the state of shear stress acting on the bubble.
-Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble for
-two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds number equal
-to 50 and 93.  The shear stress profile on the left corresponds to the case of
-$Re = 50$ and the right side shows the shear stress profile for the case of $Re
-= 93$.  The normalized shear stress, $\tau^{\ast} = \tau / \tau_{0}$, is
-defined as a ratio of the local shear stress $\tau = \mu_{\rm
-m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress $\tau_{0} = \mu_{\rm
-m}$$\mathit{\Gamma}$.  In this study, for a given $Ca$ condition, the same
-value of $\tau_{0}$ is used regardless of $Re$. 
-%\par\noindent
-For the case of $Re = 50$, the bubble reached a deformed stable state,
-%\par\noindent
-\textcolor{red}
-{
-and the shear stress profile around the bubble was drawn after the bubble attained a stable deformed state.
-}
-As observed in previous sections, when the value of $Re$ is slightly below the 
-critical $Re$ condition, the bubble does not settle into a deformed stable state but instead alternates in an elongation and 
-contraction process.  
-\textcolor{red}
-{
+
+\textcolor{red}
+{
+The previous section discussed bubble deformation and breakup.
+Large deformation and breakup of the bubble are expected to be closely related to the state of shear stress acting on the bubble.
+Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds number equal to 50 and 93.
+The shear stress profile on the left corresponds to the case of $Re = 50$, and the right side shows the shear stress profile for the case of $Re = 93$.
+The normalized shear stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a ratio of the local shear stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress $\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.
+In this study, for a given $Ca$ condition, the same value of $\tau_{0}$ is used regardless of $Re$.
+For the case of $Re = 50$, the bubble reached a deformed stable state, and the shear stress profile around the bubble was drawn after the bubble attained a stable deformed state.
+As observed in previous sections, when the value of $Re$ is slightly below the critical $Re$ condition, the bubble does not settle into a deformed stable state.
+Instead, it alternates in an elongation and contraction process.
 The shear stress profile for the case of $Re$ = 93 was depicted when the bubble sufficiently elongated ($T$ = 14.9).
-}
-In comparison to the $Re=50$ case on the left, the right image in Fig.~\ref{fig:ShearStress} ($Re=93$) shows a higher 
-shear stress profile near the bubble endpoints as it undergoes an elongation
-state in the process toward breakup.
-The value of the maximum shear stress for the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ 
-and the maximum shear stress for the case of $Re = 93$ at the moment 
-shown in Fig.~\ref{fig:ShearStress} has the value of $\tau ^{\ast} \approx 8$.  
-The shear stress profile in Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from 
-$\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions
-with $\tau ^{\ast} \geqq 6$ are illustrated in red.  
-As can be seen in the figure, the strongest shear stresses are concentrated on the 
-ends of the bubble for both $Re$ conditions.  
-This indicates that the strong shear stresses acting on the ends of the bubble are responsible 
-for much of the bubble stretching.
-It is important to note that the magnitude of the shear stress acting on the
-ends of the bubble for the case of $Re = 93$ is much larger than that for the
-case of $Re = 50$.
-
-We also observe that the shear stress inside the bubble was very small
-relative to that of the matrix fluid due to very small density and viscosity of
-the bubble.  Since the force of strong shear stresses acting on the ends of the
-bubble is difficult to transfer across the interface, as a consequence, a
-sufficiently large $Re$ condition is required for large bubble deformations.  
+In comparison to the $Re=50$ case on the left, the right image in Fig.~\ref{fig:ShearStress} ($Re=93$) shows a higher shear stress profile near the bubble endpoints as it undergoes an elongation state in the process toward breakup.
+The value of the maximum shear stress for the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ and the maximum shear stress for the case of $Re = 93$ at the moment shown in Fig.~\ref{fig:ShearStress} has the value of $\tau ^{\ast} \approx 8$.
+The shear stress profile in Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from $\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions with $\tau ^{\ast} \geqq 6$ are illustrated in red.
+As shown in the figure, the strongest shear stresses are concentrated on the ends of the bubble for both $Re$ conditions.
+This indicates that the strong shear stresses acting on the ends of the bubble are responsible for much of the bubble stretching.
+It is important to note that the magnitude of the shear stress acting on the ends of the bubble for the case of $Re = 93$ is much larger than that for the case of $Re = 50$.
+}
+
+We also observed that the shear stress inside the bubble was very small relative to that of the matrix fluid due to the bubble's very small density and viscosity.
+Since the force of strong shear stresses acting on the ends of the bubble is difficult to transfer across the interface, a sufficiently large $Re$ condition is required for large bubble deformations.
+
 \par\noindent
-In summary, what we discover is that for the Reynolds
-number sufficiently below the critical value, a relatively quick
-unsteady elongation period gives way to a steady state (with no
-break up).  On the other hand for Reynolds number close to the critical Reynolds
-number, there is a prolonged, unsteady, elongation period, in which
-periodic motion is observed and the deformation parameter $D$ is close 
-to one.  The ``vacillating'' behavior cannot last forever, ultimately (perhaps stochastically!),
-the bubble will either settle down or break.  We assert that regardless
-of the outcome, this vacillating behaviour will always occur
-in close proximity to the critical Reynolds' number.  In other words,
-regardless of the outcome, we claim, using the grid resolution of
-$R/16$, that one is assured of being within 
-3 percent of the critical Reynolds number (see Figure \ref{fig:DeEvolution}).  
-In fact,
-we hypothesize that there will always be ``vacillating'' behavior
-if one is sufficiently close to the critical Reynolds number.  i.e.
-given an almost infinite supply of computational resources, as one hones
-in closer and closer to the critical Reynolds number, a ``tug of war''
-will be observed between the surface tension force trying to pull the
-bubble together versus the wall driven shear stress trying to pull the
-bubble apart.
+
+In summary, we discover that for the Reynolds number sufficiently below the critical value, a relatively quick, unsteady elongation period gives way to a steady state (with no break up).
+On the other hand, for the Reynolds number close to the critical Reynolds number, there is a prolonged, unsteady elongation period in which periodic motion is observed, and the deformation parameter $D$ is close to one.
+The ``vacillating'' behavior cannot last forever; ultimately (perhaps stochastically!), the bubble will either settle down or break.
+Regardless of the outcome, this vacillating behavior will always occur near the critical Reynolds number.
+In other words, irrespective of the result, we claim, using the grid resolution of $R/16$, that one is assured of being within 3 percent of the critical Reynolds number (see Figure \ref{fig:DeEvolution}).
+We hypothesize that there will always be ``vacillating'' behavior if one is sufficiently close to the critical Reynolds number.
+In other words, given an almost infinite supply of computational resources, as one hones in closer and closer to the critical Reynolds number, a ``tug of war'' will be observed between the surface tension force trying to pull the bubble together versus the wall driven shear stress trying to pull the bubble apart.
 
@@
 %
-In this section, we consider the fluid flow velocity field outside and inside
-the bubble during the shear-induced breakup process.
-\textcolor{red}
-{
-Detailed velocity fields of the deforming and breaking drop have already been presented in 
-some references (\citet{LiRenRen00, RenCri01-1}).
-The velocity fields for the drop and the bubble will be influenced by the behavior of the 
-breakup process, so the velocity fields for the drop and the bubble are not similar
-}
-Figure~\ref{fig:BubbleFieldCa0p3Re93} shows the velocity fields outside and
-inside the bubble at cross-sectional slices in the $xz$-plane for a flow
-condition of $Ca = 0.3$ and $Re = 93$.  Regions around the bubble where there
-is a higher density of velocity vectors correspond to the level-1 grid portion
-of the AMR structure.  The simulation results show that the velocity field
-inside the bubble is particularly distinct from the surrounding flow field in
-the exterior of the bubble.  The cross-sections at $T=12.2$ and $T=18.1$, taken
-during the elongation phase, show how shear forces at the lower and upper
-halves of the bubble act along the bottom and top surfaces, respectively, to
-deform the interface.  Near the left and right edges of the bubble, inward
-interior flows (that point toward the bubble center) begin to develop.  Strong
-shearing forces in the exterior near the bottom-left-end and top-right-end of
-the bubble interact with the interior flow field through the boundary to create
-cusped shapes at the bottom-left and top-right ends of the bubble while the
-interface is laterally elongated in the $x$-direction.  During the shrinking
-process, which occurs for $23.6 \leq T \leq 27.8$, inward flows within the
-bubble extend over a wider region and are no longer localized near the bubble
-edges.  Then, we observe that circulating flows form at the thread-bridge part
-of the doglegged bubble shape over the time interval $[25.7, 27.8]$.  During
-the breakup process ($T \sim 28.8$), higher-intensity inward flows are formed
-inside the bubble, near the pinch off region, that are naturally larger than
-the surrounding interior flows and which are inextricably associated with the
-bubble migration illustrated in Figs.~\ref{fig:BubbleBreakCa0p3Re93}
-and~\ref{fig:BubBreakCa0p3Re93Detail}.  As time proceeds further ($T =  46.2$),
-distinct inward flows are formed inside the daughter bubbles; the bubbles then
-begin their migration toward the side walls.  Considering the left daughter
-bubble, for example, we see that the mechanism responsible for this movement
-results from larger shear forces acting on the bottom-left end than those in
-the top-left end.
+\textcolor{red}
+{
+This section considers the fluid flow velocity field outside and inside the bubble during the shear-induced breakup process.  Detailed velocity fields of the deforming and breaking drop have already been presented in a few references (\citet{LiRenRen00, RenCri01-1}).  The behavior of the breakup process will influence the velocity fields for the drop and the bubble, so the velocity fields for the drop and the bubble are not similar.  Figure~\ref{fig:BubbleFieldCa0p3Re93} shows the velocity fields outside and inside the bubble at cross-sectional slices in the $xz$-plane for a flow condition of $Ca = 0.3$ and $Re = 93$.  Regions around the bubble with a higher density of velocity vectors correspond to the level-1 grid portion of the AMR structure.  The simulation results show that the velocity field inside the bubble is notably distinct from the surrounding flow field on the bubble's exterior.  The cross-sections at $T=12.2$ and $T=18.1$, taken during the elongation phase, show how shear forces at the lower and upper halves of the bubble act along the bottom and top surfaces, respectively, to deform the interface.  Near the left and right edges of the bubble, inward interior flows (that point toward the bubble center) begin to develop.  Strong shearing forces in the exterior near the bottom-left-end and top-right-end of the bubble interact with the interior flow field through the boundary to create cusped shapes at the bottom-left and top-right ends of the bubble.
+At the same time, the interface is laterally elongated in the $x$-direction.  During the shrinking process, which occurs for $23.6 \leq T \leq 27.8$, inward flows within the bubble extend over a wider region and are no longer localized near the bubble edges.  Then, we observe that circulating flows form at the thread-bridge part of the doglegged bubble shape over the time interval $[25.7, 27.8]$.  During the breakup process ($T \sim 28.8$), higher-intensity inward flows are formed inside the bubble, near the pinch-off region, that are naturally larger than the surrounding interior flows and which are inextricably associated with the bubble migration illustrated in Figs.~\ref{fig:BubbleBreakCa0p3Re93} and~\ref{fig:BubBreakCa0p3Re93Detail}.  As time proceeds further ($T =  46.2$), distinct inward flows are formed inside the daughter bubbles; the bubbles then migrate toward the side walls.  For example, considering the left daughter bubble, we see that the mechanism responsible for this movement results from larger shear forces acting on the bottom-left end than those in the top-left end.
+}
 
@@
 %
-In previous sections, we considered numerical simulations of bubble deformation
-and breakup with a capillary number $Ca = 0.3$.  Here, we examine similar
-bubble dynamics with $Ca = 0.8$ and we also investigate the effect of
-interfacial tension on bubble deformation and breakup.  Using $Ca=0.8$ for both
-cases, Figures~\ref{fig:BubDefCa0p8Re42} and~\ref{fig:BubBrkCa0p8Re43} present
-the time evolution of shear-induced bubble deformation and breakup with $Re=42$
-and $Re=43$, respectively.  We note that the bubble critical Reynolds number is
-around $Re_{\rm c} \approx 43$, whereas $Re_{\rm c} \approx 0$ for the corresponding
-case of the drop with 
-$\lambda$ = $\eta$ = 1 (see e.g.~\citet{LiRenRen00}).
-Note that $Re_{\rm c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca
-= 0.3$ since the bubble at $Ca = 0.8$ is more elastic due to the weaker effect
-of surface tension in this case.  The results shown in
-Figs.~\ref{fig:BubDefCa0p8Re42} and~\ref{fig:BubBrkCa0p8Re43} indicate that the
-bubble deformation and breakup process for the condition of $Ca = 0.8$ is
-analogous to that for $Ca = 0.3$.  For the case of bubble deformation without
-breakup (Fig.~\ref{fig:BubDefCa0p8Re42}), the bubble initially assumes a long
-elongated shape along the $x$-direction at around $T=17.0$. The bubble then
-enters a compression stage over the time interval $[31.3,41.2]$ and
-subsequently starts to elongate again at $T = 45.8$.  On the other hand, for
-the case of bubble breakup (Fig.~\ref{fig:BubBrkCa0p8Re43}), an initial
-elongation phase is followed by a doglegged shape formation at $T=33.7$.  After
-that, the bubble ruptures from the thread-bridge part of the doglegged shape
-and two daughter bubbles are produced ($T = 35.8$).  The two daughter bubbles
-formed after breakup move to the central area ($T = 49.7$) as in the case of
-$Ca = 0.8$ and $Re = 93$, but the two bubbles eventually coalesce in a region
-approximately centered in the computational domain ($T = 55.6$).  We note that
-in a real experimental setting, bubbles may coalesce after breaking up due to
-slight deviations of flow conditions and states.  Although the process of
-bubble deformation and breakup for flow conditions with $Ca = 0.3$ and $Ca =
-0.8$ are similar, a pronounced difference is that the bubble for $Ca = 0.8$ is
-more elongated and slender than that for $Ca = 0.3$ due to the smaller effect
-of surface tension for $Ca = 0.8$.
-
-Table~\ref{tab:CaRecComparison} lists, for representative $Ca$ values, the
-corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced bubble
-breakup.  The data in Table~\ref{tab:CaRecComparison} corresponds to $\lambda =
-1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and the
-initial/boundary conditions are given by (\ref{IC_BC}).  The results in
-Table~\ref{tab:CaRecComparison} indicate that sufficiently large shear forces
-are required for bubble breakup even for large capillary numbers.  In
-Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in
-Table~\ref{tab:CaRecComparison} and make the hypothesis that given a new data
-point, $(Ca,Re)$,  shear induced bubble break up will occur if the point
-$(Ca,Re)$ is above the given critical curve, and the bubble will not break if
-the $(Ca,Re)$ pair is below the critical curve.  For comparison,
-a critical curve for the drop with $\lambda =\eta = 1$ is also indicated in
-Fig.~\ref{fig:CaRecFit}.  The inclusion of breakup and no-breakup critical
-curves, for both the drop and the bubble, will facilitate future identification
-of $Re_{\rm c}$ numbers---and thus a more complete general critical curve---for
-a wide range of high $Ca$ numbers.
+In previous sections, we considered numerical simulations of bubble deformation and breakup with a capillary number $Ca = 0.3$.  In this section, we examine the case of $Ca=0.8$.    We investigate the effect of interfacial tension on bubble deformation and breakup.  Using $Ca=0.8$ for both cases, Figures~\ref{fig:BubDefCa0p8Re42} and~\ref{fig:BubBrkCa0p8Re43} present the time evolution of shear-induced bubble deformation and breakup with $Re=42$ and $Re=43$, respectively.  We note that the bubble critical Reynolds number is around $Re_{\rm c} \approx 43$, whereas $Re_{\rm c} \approx 0$ for the corresponding case of the drop with $\lambda$ = $\eta$ = 1 (see e.g.~\citet{LiRenRen00}).  Note that $Re_{\rm c}$ for $Ca = 0.8$ is smaller than that for the condition of $Ca = 0.3$ since the bubble at $Ca = 0.8$ is more elastic due to the weaker effect of surface tension in this case.  The results shown in Figs.~\ref{fig:BubDefCa0p8Re42} and~\ref{fig:BubBrkCa0p8Re43} indicate that the bubble deformation and breakup process for the condition of $Ca = 0.8$ is analogous to that for $Ca = 0.3$.  For the case of bubble deformation without breakup (Fig.~\ref{fig:BubDefCa0p8Re42}), the bubble initially assumes a long elongated shape along the $x$-direction at around $T=17.0$.
+The bubble then enters a compression stage over the time interval $[31.3,41.2]$ and then elongates again at $T = 45.8$.  On the other hand, for the case of bubble breakup (Fig.~\ref{fig:BubBrkCa0p8Re43}), an initial elongation phase is followed by a doglegged shape formation at $T=33.7$.  After that, the bubble ruptures from the thread-bridge part of the doglegged shape, producing two daughter bubbles ($T = 35.8$).  The two daughter bubbles formed after the breakup move to the central area ($T = 49.7$) as in the case of $Ca = 0.8$ and $Re = 93$.
+Still, the two bubbles eventually coalesce in a region approximately centered in the computational domain ($T = 55.6$).  We note that bubbles may coalesce after breaking up in a real experimental setting due to slight deviations in flow conditions and states.  Although the process of bubble deformation and breakup for flow conditions with $Ca = 0.3$ and $Ca = 0.8$ are similar, a pronounced difference is that the bubble for $Ca = 0.8$ is more elongated and slender than that for $Ca = 0.3$ due to the smaller effect of surface tension for $Ca = 0.8$.
+
+Table~\ref{tab:CaRecComparison} lists, for representative $Ca$ values, the corresponding critical Reynolds number, $Re_{\rm c}$, for shear-induced bubble breakup.  The data in Table~\ref{tab:CaRecComparison} corresponds to $\lambda = 1.2 \times 10^{-3}$, $\eta < 1.0 \times 10^{-3}$, $0.3<Ca<1$, and the initial/boundary conditions are given by (\ref{IC_BC}).  The results in Table~\ref{tab:CaRecComparison} indicate that sufficiently large shear forces are required for bubble breakup, even for large capillary numbers.  In Figure~\ref{fig:CaRecFit} we plot the smooth interpolant of the data given in Table~\ref{tab:CaRecComparison} and make the hypothesis that given a new data point, $(Ca,Re)$, shear-induced bubble break up will occur if the point $(Ca,Re)$ is above the given critical curve, and the bubble will not break if the $(Ca,Re)$ pair is below the critical curve.  For comparison, a critical curve for the drop with $\lambda =\eta = 1$ is also indicated in Fig.~\ref{fig:CaRecFit}.  Including breakup and no-breakup critical curves for both the drop and the bubble will facilitate future identification of $Re_{\rm c}$ numbers and, thus, a complete general critical curve for a wide range of $Ca$ numbers.
+
 %{\color{red} it seems like the above passage is still a work in progress?}
@@
 \textcolor{red}{
-The numerical results revealed significant differences between bubble deformation and breakup and the corresponding drop dynamics.
-For the case of a bubble, it was discovered that much stronger shear flows are necessary in order to induce interface breakup compared with a drop immersed in a similar flow field.
-That is, a much larger Reynolds number flow is required in order to induce bubble breakup.
-The steps leading to bubble breakup were similar throughout the $Ca$ number range considered in our computations: the bubble underwent a similar breakup mechanism in which rupture occurred at a thread-bridge part that followed a doglegged shape formation stage.
-For bubble deformation without breakup, near $Re_{\rm c}$, the bubble did not maintain a stable deformed shape, in contrast to drop deformation near the critical Reynolds number.
-The bubble exhibited pronounced underdamped behavior: the bubble oscillated between elongating and shrinking motions for non-rupturing flow conditions.
-At the same time, bubble deformation under smaller $Re$ conditions ($< Re_{\rm c}$) led to a stable state.
-We attribute the large differences in morphology for the bubble undergoing breakup, compared with the drop, due to the density and viscosity ratio.
+The numerical results revealed significant differences between bubble deformation and breakup and the corresponding drop dynamics.  For the case of a bubble, it was discovered that much stronger shear flows are necessary to induce interface breakup compared with a drop immersed in a similar flow field.  That is, a much larger Reynolds number flow is required to induce bubble breakup.  The steps leading to bubble breakup were similar throughout the $Ca$ number range considered in our computations: the bubble underwent a similar breakup mechanism in which rupture occurred at a thread-bridge part that followed a doglegged shape formation stage.  For bubble deformation without breakup, near $Re_{\rm c}$, the bubble did not maintain a stable deformed shape, unlike drop deformation near the critical Reynolds number.  The bubble exhibited pronounced underdamped behavior: the bubble oscillated between elongating and shrinking motions for non-rupturing flow conditions.  At the same time, bubble deformation under smaller $Re$ conditions ($< Re_{\rm c}$) led to a stable state.  Compared with the drop, we attribute the significant differences in morphology for the bubble undergoing breakup to the density and viscosity ratio.  Due to the bubble's very small density and viscosity, it is comparatively difficult to transfer the shear stresses acting on the ends of the bubble across the interface.
 }
@@
 \textcolor{red}{
-There are a number of directions for future work.
-In the present work, we varied the Capillary number and Reynolds' number in studying bubble deformation and breakup morphology in the presence of a simple shear flow.
+There are several directions for future work.
+In the present work, we varied the capillary number and Reynolds number to study bubble deformation and breakup morphology in the presence of a simple shear flow.
 For the future, one can also vary (i) the viscosity ratio, (ii) the effect of the initial shape of the bubble\cite{ohta2005computational}, (iii) the magnitude and direction of the gravitational force, (iv) the non-Newtonian properties of the ``matrix'' liquid, (v) bubble deformation and breakup due to a shear flow in a T junction\cite{FRENSE2024120579}, (vi) bubble deformation and breakup confined shear flow (see \cite{gupta2014deformation} for the drop case), and (vii) bubble deformation and breakup due to non-uniform shear flow (see \cite{chin1980studies} for the drop case).

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer1.tex
working on the replies

@@
 Response: \\
-		There are two main problems identified from the referee: (a) the grid refinement study does not demonstrate enough convergence and (b) even if we could refine the grid an infinite number of times, our break-up model is insufficient and whatever findings that we have would be completely different than if we were able to model the break-up process with a molecular scale model.
-We disagree with the referee; we have added more references to our article in which the uncertainty in our article is smaller than that in the latest existing work.
-Also we note that existing articles on bubble and drop breakup due to shear do not take into account sub-scale models either and these articles demonstrate reasonable agreement with experiments (as does our submission).
-Note: if we were considering the merging of droplets in which bouncing versus merging can occur, then sub-scale drainage can be important to model.
-This issue is not relevent for our article though.
-We have added this discussion to the introduction.
+In addition to the previous verification and validation tests (Tables I and II, Figure 3), we now list a number of references (top of section 3.2) involving bubbles and drops with severe deformation in which our method is validated by way of grid refinement studies and comparison with experiments.
 
-Finally, we note that our simulations already take about one year.
-The bubble deformation case, is a much more challenging problem than the drop case due to the large density ratio.
-Anymore refinement would extend the time of simulation to 8 years using current technology.
-It is agreed though that speeding up the algorithm in order to run more efficiently would certainly reduce the uncertainty of our results even more.
-This is future work.
-%Muller-Fischer comparison
+In light of all the previous tests that we have already done, with satisfactory results, it is grossly unfair to require us to do a further grid refinement which would force us to wait another four years for the results; please see Remark 1 in section 3.1.
+It is also very unfair to ask us to test a subgrid scale model which is very unnecessary for our problem; please see Remark 2 in section 3.1.
+As explained throughout our article, our results fulfill a unique niche in bubble dynamics (low Capillary number, high Reynolds number),  that is on the one hand important in many applications (see first paragraph in the introduction, we have added many new references) and yet impossible to do controlled experiments unless one is in a microgravity environment.
+If our paper is rejected because of this, it is most certain that someone else will publish similar findings later on, which is terribly unfair to us.
+As we now mention in the conclusion, we expect many follow-on articles should our article be accepted;  For example bubble deformation with non-Newtonian matrix fluids, experimenting with a non-spherical initial condition (your recommendation), bubble deformation in complex geometry, etc.
 
@@
 Response: \\
-As in our response to the previous comment, we believe it is unreasonable to report more results; specifically each new data point requires an additional year, and additional computers.
-As also mentioned in our response to point 2 above, and hilighted in our revised introduction,
-our work as it stands now is significant and novel.  We take the referee comments on as a challenge for future work.
+As in our response to the previous comment, we believe it is unfair to ask us to  report more results; each new data point requires an additional 6 months, and additional computers.
+As also mentioned in our response to point 2 above, and hilighted in our revised introduction, our work as it stands now is significant and novel.
+We take the referee comments on as a challenge for future work.
+Please refer to the revised conclusions section in which we report on potential future work.
 
-We remark that the significance of our article is the fact that we have 
-reported for the first time controlled tensile strength properties for a bubble in shear flow.  In addition, we have made the following noteworthy discoveries along the way:
+The reviewer says ``Mostly just pictures are shown from which little is to be learned,''  but yet it is clearly mentioned that the shear force necessary to deform a bubble is noticeably larger than that for the drop, all other factors being equal, and from the results (figures and tables) we deduce for the first time the mechanisms for why the bubble requires a larger shearing force; please see section 4.3 second to last paragraph.
+
+Just in case the reviewer overlooked these additional points of significance and novelty:
 \begin{enumerate}
@@
 combinations of $\lambda$ and $\eta$:
-
 \begin{tabbing}

### 2024-11-29 Revised-paper/Paper/Bubble-deformation-Rev.tex
working on the replies

@@
 \cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
+\begin{comment} 
 \affiliation[1]{
@@
   country={Japan}}
+\end{comment}
 
@@
 
+\begin{comment} 
 \affiliation[3]{
@@
 \author[4]{Edwin Jimenez}  
+\begin{comment} 
 \affiliation[4]{
@@
   country={USA}}
+\end{comment}
 
 \author[5]{Mark Sussman}  
+\begin{comment} 
 \affiliation[5]{
@@
   country={USA}}
+\end{comment}
 
@@
 section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data (where available) and grid refinement studies.
-Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.
+Each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$), oscillatory behaviour is observed delaying the determination of breakup or not.
 Finally, the larger the deformation parameter $D$, the longer one must make the computational domain (and thereby leading to larger domain aspect ratio) thereby adversely effecting the condition number even more for carrying our the pressure projection.
@@
 {
-	We remark that our method is a ``sharp interface method\cite{SusSmiHusOhtZhi07,Sus03,KanFedLiu00}.
+	We note that our method is a ``sharp interface method\cite{SusSmiHusOhtZhi07,Sus03,KanFedLiu00}.
 Thereby we do not need to specify an empirical interface thickness parameter\cite{SusSmeOsh94,SusPuc00}.
@@
 The interfacial curvature $\kappa$ is computed with second-order accuracy directly from the volume-of-fluid (VOF) function and the level set function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).
-We remark that we would get the same results if we compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
+We note that we would get the same results if we compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
 \par
@@
 }
-
+\par
+\textcolor{red}
+{
 We also observed that the shear stress inside the bubble was very small relative to that of the matrix fluid due to the bubble's very small density and viscosity.
 Since the force of strong shear stresses acting on the ends of the bubble is difficult to transfer across the interface, a sufficiently large $Re$ condition is required for large bubble deformations.
+}
 

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer1.tex
replies

--- 2024-11-25 Revised-paper/Reply/Reply-Reviewer1.tex
@@
 Response: \\
-In the revision, we made many improvements to the grammar and structure so that the reader can follow in a much more efficient manner. \\
+We have gone through the whole paper fixing the grammar and structure.  We believe the message is very clear now. \\
 \\
@@
 Response: \\
-		There are two main problems identified from the referee: (a) the grid refinement study does not demonstrate enough convergence and (b) even if we could refine the grid an infinite number of times, our break-up model is insufficient and whatever findings that we have would be completely different than if we were able to model the break-up process with a molecular scale model.
-We disagree with the referee; we have added more references to our article in which the uncertainty in our article is smaller than that in the latest existing work.
-Also we note that existing articles on bubble and drop breakup due to shear do not take into account sub-scale models either and these articles demonstrate reasonable agreement with experiments (as does our submission).
-Note: if we were considering the merging of droplets in which bouncing versus merging can occur, then sub-scale drainage can be important to model.
-This issue is not relevent for our article though.
-We have added this discussion to the introduction.
+We totally disagree with the referee here.
+The resolution used for our results is enough.
+The results shown in Figure 3 are very convincing in that if we refined the grid more, the results would hardly change.
+In addition, we have the results in Tables I and II which compare our results to other researchers' simulations and experiments for bubble/drop deformation in shear flows.
+Finally, at the top of section 3.2, we now list a number of references involving bubbles and drops with severe deformation in which our method was validated by way of grid refinement studies and comparison with experiments.
 
-Finally, we note that our simulations already take about one year.
-The bubble deformation case, is a much more challenging problem than the drop case due to the large density ratio.
-Anymore refinement would extend the time of simulation to 8 years using current technology.
-It is agreed though that speeding up the algorithm in order to run more efficiently would certainly reduce the uncertainty of our results even more.
-This is future work.
-%Muller-Fischer comparison
+There is a big gaping hole in the research in which our results fit in: this is the low Capillary number, Moderate to High Reynolds number regime.
+In this void, it is impossible to do experiments unless one is in a microgravity environment.
+At the same time, numerical algorithms must be designed in order to robustly and accurately predict the tensile strength of a bubble in the low capillary, moderate to high Reynolds number regime, in which ours is the first.
+We believe that the results as currently presented, fill the void and that they should be reported now rather than waiting another year.
+
+Perhaps in future work, in which we have more computing power available to us, we can try an extra refinement, albeit, the results are most likely a foregone conclusion in that they will be in close agreement with the results that we already have.
+Also as future work, it is inevitable that researchers will be able to run experiments on the space station which corroborate the results of our simulations that we have now.
+
+We have also added ``Remark 1'' and ``Remark 2'' in section 3.1 which makes it clear why adding another level of refinement would delay the publication of our work by another four years, and why sub-scale models are unnnecessary at pinch off for the bubble deformation under simple shear flow problem.
+Again, the results that we have now are publishable and will make an impact, it would be fruitless to wait another 4 years.
 
@@
 Response: \\
-As in our response to the previous comment, we believe it is unreasonable to report more results; specifically each new data point requires an additional year, and additional computers.
-As also mentioned in our response to point 2 above, and hilighted in our revised introduction,
-our work as it stands now is significant and novel.  We take the referee comments on as a challenge for future work.
-
-We remark that the significance of our article is the fact that we have 
-reported for the first time controlled tensile strength properties for a bubble in shear flow.  In addition, we have made the following noteworthy discoveries along the way:
-\begin{enumerate}
-\item The behavior of the bubble deformation process around critical $Re$ conditions with $Ca$ = 0.3  $\sim$ 1.0 has been presented for the first time.
-\item The behavior of the bubble breakup process at critical $Re$ conditions with $Ca$ = 0.3  $\sim$ 1.0 has been presented for the first time.
-\item The value of critical $Re$ numbers was found for $Ca$ = 0.3  $\sim$ 1.0 for the first time.
-\item  We showed that most previous computational studies overestimated drop deformation and breakup because most previous studies used a domain size with $W$ (width ($y$directional length)) =4$R$.
-Drop deformation is promoted when using a domain size with $W=4R$.
-\item The difference in the deformation and breakup between the bubble ($\lambda<<1$) and the drop ($\lambda = 1$ and $\eta = 1$) was clearly shown.
-\item Shear-induced bubble/drop breakup critical curves were obtained. 
-\end{enumerate}
-
-Regarding the effect of $\lambda$ and $\eta$, ongoingly we are examining the effect of $\lambda$ and $\eta$ on drop breakup for following 
-combinations of $\lambda$ and $\eta$:
-
-\begin{tabbing}
- \hspace{55mm} \= \hspace{10mm} \kill
- \hspace{5mm} 1. $\lambda$ = 1.0, $\eta$ =1.0 (done) \> 2. $\lambda \simeq 0.0$, $\eta \simeq 0.0$ (this study) \\ 
- \hspace{5mm} 3. $\lambda$ = 1.0, $\eta \simeq 0.0$ (done) \> 4. $\lambda$ = 1.0, $\eta$ =0.01 \\
- \hspace{5mm} 5. $\lambda$ = 1.0, $\eta \simeq 0.1$ \> 6. $\lambda$ = 0.1, $\eta \simeq 0.0$ (done) \\
- \hspace{5mm} 7. $\lambda$ = 0.1, $\eta$ =0.01 \> 8. $\lambda = 0.1$, $\eta$ =0.1  \\
- \hspace{5mm} 9. $\lambda$ = 0.1, $\eta$ =1.0 (done) \> 10. $\lambda$ = 1.0, $\eta$ =10  \\
- \hspace{5mm} 11. $\lambda$ = 1.0, $\eta$ =100 \> 12. $\lambda$ = 1.0, $\eta$ =1000 \\
-\end{tabbing}
-
-Since it takes a very long computational time to obtain results for the effect of $\lambda$ and $\eta$ on drop deformation and breakup, 
-all computations for these conditions have not been finished. We will also present the fruits of research on the effect of density and 
-viscosity ratios in the next papers. \\
-\\
+We totally disagree with this comment too.
+We already report many novel and significant results and sufficiently analyze the data both with strategic plots and quantitative tables.
+Adding more would only needlessly delay the paper another year.
+\par
+We do agree with the referee in that the recommended new simulations would be an excellent inclusion in future papers.  Please see our modified conclusion, last paragraph.
 
@@
 Response: \\
-In our computations, we set $g = 0$ because we wanted to clearly isolate only the effects of the density and viscosity ratios and 
-wanted to compare with previous studies dealing with the deformation and breakup of a drop with $\lambda =1$ and $\eta = 1$.
-When the gravity is considered, we obtain $Fr$ (Froude number) $\left(= \frac{{\it \Gamma}R}{\sqrt {gR}} \right)$ = 1.7 ($Re$ = 93 and $Ca$ = 0.3) 
-and 1.9 ($Re = 43$ and $Ca$ = 0.8). \\
-Although the values of $Fr$ are not so large, the effect of gravity (bubble rise motion) may not be completely negligible in terms of $Fr$.
-However, bubbles for both conditions reach the breakup at $t$ = about 0.5 s. 
-($V$ (moving wall speed) had about 1.1 $\sim$ 1.3 m/s for the range of $Ca$ and $Re$ in our computaions.)
-Therefore, the effect of gravity (bubble rise motion) is expected to be negligible when juxtaposed with the measured tensile strength properties of bubble deformation and breakup 
-around the critical $Re$ number conditions.
-Contrary to what the reviewer suggests, we believe that our computational results in which we only focus on the force balance between the driving shear flow and the bubble surface tension will provide fundamental knowledge and findings for practical applications.
-In the revised paper, we have described these explanations.\\
-\\
-Please see lines 133 to 139.
+We totally disagree that not including gravity ``obliterates'' the results.
+
+At the least, there are a host of strictly microgravity applications in which our research will be of great help.
+We list many new applications, including the microgravity applications, in the revised version: please see the first paragraph in the introduction.
+All these applications that we list will significantly benefit from our article.
+
+We have also added a discussion at the end of section 2 (see the ``Remark'') in which we make some predictions as to how the inclusion of gravity would change the results.
+
+Having said that, we do agree that taking into account the gravity effects and initial condition effects will make good material for future work.
+Please see the last paragraph in our modified conclusion.
+
 \\
@@
 Response: \\
-We carefully checked the paper and modified poor English writing, expressions, etc.\\
+We have fixed these items.  Also, we have made many complete ``run-throughs'' of our paper in order to remove all mistakes and awkward sentences.
 

### 2024-11-29 Revised-paper/Paper/Bubble-deformation-Rev.tex
replies

@@
 {
-Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow in a variety of regimes including the low Capillary number, high Reynolds number regime.
+Numerical simulations are presented for the deformation and breakup of a bubble in liquids undergoing simple linear shear flow in a variety of regimes including the low Capillary number, moderate/high Reynolds number regime.
 Numerical results are obtained using a projection method for incompressible two-phase flow.
@@
 \textcolor{red} {
-	This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low Capillary number ($Ca=\mu_{m}U/\sigma$) conditions, high Reynolds' number conditions ($Re=\rho_{m} R U/\mu_{m}$), low-density ratio, low viscosity ratios, and zero buoyancy effects.  We remark that previous controlled experimental studies on shear-driven bubble deformation are restricted to the low Reynolds' number and large capillary number regime\cite{RusMan02,CanedoETAL}.
+	At the present, there is a large hole in the research concerning fundamental bubble dynamics in a simple shear flow.
+There are no results, either experimentally or numerically, in the low Capillary number ($Ca=\mu_{m}U/\sigma$), moderate/high Reynolds number ($Re=\rho_{m} R U/\mu_{m}$) regimes.
+In this void, it is impossible to do experiments unless one is in a microgravity environment.
+At the same time, numerical algorithms must be designed in order to robustly and accurately predict the tensile strength of a bubble in the low capillary, moderate to high Reynolds number regime, in which ours is the first to be reliably used for such a purpose.
+}
+\par
+\textcolor{red} {
+	This article presents computational studies of shear-driven deformation and breakup of a bubble in insoluble viscous liquids.  Studying bubble break-up, in which we focus only on the balance of the wall driving force and bubble surface tension force, via computation rather than experiments simplifies the process of setting a combination of precise, simple shear flow conditions, low Capillary number ($Ca=\mu_{m}U/\sigma$) conditions, moderate/high Reynolds' number conditions ($Re=\rho_{m} R U/\mu_{m}$), low-density ratio, low viscosity ratios, and zero buoyancy effects.  We remark that previous controlled experimental studies on shear-driven bubble deformation are restricted to the low Reynolds' number and large capillary number regime\cite{RusMan02,CanedoETAL}.
 One reason is that buoyancy effects are minimized in highly viscous liquids.
-On the other hand, many applications are characterized by liquids in the high Reynolds' number regime.
+On the other hand, many applications are characterized by liquids in the moderate/high Reynolds' number regime.
 The physical properties that distinguish bubble and drop studies are expressed in terms of the density ratio $\lambda = \rho_{\rm b} / \rho_{\rm m}$ and the viscosity ratio $\eta = \mu_{\rm b} / \mu_{\rm m}$, where $\rho$ is the fluid density, $\mu$ is the viscosity and the subscripts ``b'' and ``m'' denote the ``bubble'' or ``drop'' and the ``matrix fluid'', respectively.  For a bubble in an insoluble, viscous liquid, $\lambda \simeq 0$ and $\eta \simeq 0$, whereas most studies dealing with a drop in an immiscible viscous liquid take $\lambda =1$ and $\eta \simeq 1$.
@@
 In contrast, few studies have been conducted on bubble deformation and breakup.
-In the low Capillary number, high Reynolds' number regime, there are no controlled experiments or simulations.
+In the low Capillary number, moderate/high Reynolds' number regime, there are no controlled experiments or simulations.
 We reiterate why there have been few studies regarding the ``tensile strength'' of bubbles.
@@
 {
-	The effectiveness of our sharp interface computational method has been demonstrated via grid refinement studies and comparison with experiments for the complicated rising motion of single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19,ohta2010sensitivity,stewart2008improved,SusSmiHusOhtZhi07}, the simulation of atomization in a realistic diesel injector\cite{arienti2013coupled}, and the simulation of bubble formation due to the injection of gas through a nozzle\cite{ohta2011robust}.
+	The effectiveness of our sharp interface computational method has been demonstrated via grid refinement studies and comparison with experiments for the complicated rising motion of single bubbles and drops in viscous liquids \citet{OhtSus12, OhtAkaYosSus14, OhtFurYosSus19,ohta2010sensitivity,stewart2008improved,SusSmiHusOhtZhi07,sussman2009stable}, the simulation of atomization in a realistic diesel injector\cite{arienti2013coupled}, and the simulation of bubble formation due to the injection of gas through a nozzle\cite{ohta2011robust}.
 In this section, the accuracy of our computational method will be verified for the problem of shear-induced deformation of a drop and bubble.

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer1.tex
hand off back to Mitsuhiro

@@
 Response: \\
-We have gone through the whole paper fixing the grammar and structure.  We believe the message is very clear now. \\
+We have gone through the whole paper fixing the grammar and the organization.  We believe the message is very clear now. \\
 \\
@@
 Response: \\
-We totally disagree with the referee here.
+We disagree with the referee here.
 The resolution used for our results is enough.
@@
 
-There is a big gaping hole in the research in which our results fit in: this is the low Capillary number, Moderate to High Reynolds number regime.
+There is a large hole in the research in which our results fit in: this is the low Capillary number, Moderate to High Reynolds number regime.
 In this void, it is impossible to do experiments unless one is in a microgravity environment.
@@
 
-We have also added ``Remark 1'' and ``Remark 2'' in section 3.1 which makes it clear why adding another level of refinement would delay the publication of our work by another four years, and why sub-scale models are unnnecessary at pinch off for the bubble deformation under simple shear flow problem.
+We have added ``Remark 1'' and ``Remark 2'' in section 3.1 which makes it clear why adding another level of refinement would delay the publication of our work by another four years, and why sub-scale models are unnnecessary at pinch off for the bubble deformation under simple shear flow problem.
 Again, the results that we have now are publishable and will make an impact, it would be fruitless to wait another 4 years.
@@
 Response: \\
-We totally disagree with this comment too.
+We have added more snapshots to Figure 4, plotted the velocity field in Figure 9,  and added appropriate accompanying analysis to the text (in response to reviewer 2), but otherwise, we disagree with this comment.
 We already report many novel and significant results and sufficiently analyze the data both with strategic plots and quantitative tables.
-Adding more would only needlessly delay the paper another year.
+Adding more results would only needlessly delay the paper another year.
 \par
@@
 Response: \\
-We totally disagree that not including gravity ``obliterates'' the results.
+We disagree that not including gravity ``obliterates'' the results.
 
@@
 Please see the last paragraph in our modified conclusion.
-
 \\

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer2.tex
hand off back to Mitsuhiro

@@
 Response: \\
-The italic format was used to emphasize words, But the italic format was removed in the revised 
-paper because words in italic format are confusing expressions.\\
+The italic format was used to emphasize certain passages, but in retrospect, we agree that which passages deserve italics and which passages don't is open to discretion.
+So we have removed all the italics.
+\\
 
@@
 Response: \\
-We appreciate the reviewer's suggestion. The description of the applicable part disappeared 
-in the revised paper because we have completely modified the ``Introduction".\\
-\\
-Please see the ``Introduction".
+We have corrected this mistake.  Also we have made complete run-throughs of the  paper checking for grammar errors and awkward sentences. \\
 \\
@@
 Response: \\
-The level set method, by itself, is not designed to directly conserve the
-volume of materials.
-The error is especially large at regions of high curvature.
-The lack of volume conservation can significantly alter the numerical predictions.
-On the other hand, the volume of fluid method, by itself, is not designed to accurately and robustly approximate the interface curvature.
-The surface tension force will be incorrectly calculated if the curvature is not accurately approximated.
-We have found that the CLSVOF method on the otherhand, in which we couple the two methods, is the optimal method.
-We have added further discussion to the paper.
-
-\\
+We have improved the introduction and section 3.1 in order to make it more clear about our rationale for using the CLSVOF method to capture complex deforming boundaries and also why we represent the gas-liquid interface as ideally sharp.
+Also, we have already applied the CLSVOF method in past work to many multiphase flow problems with complex interface deformations.
+Please see the top of section 3.2 in which we list past research in which we have obtained nice results for hard multiphase flow problems using the CLSVOF method.
 \\
@@
 Also, in the revised paper, a brief discussion of the potential influence of gravity (Froude number) on bubble breakup dynamics 
-has been added according to another reviewer's suggestion.\\
-\\
-Please see lines 133 to 139.
-\\
+has been added according to another reviewer's suggestion.\\ \\
+Please see the remark in section 2.  \\
 
@@
 Interface Science, Vol. 249, 476– 480 2002). For your reference, computations for bubble deformation with the condition of $Re \simeq 0$ 
-were hard tasks and a very long computational time (one year) was needed. \\
-\\
+were hard tasks and a very long computational time (one year) was needed. \\ \\
 
@@
 Response: \\
-$T$ is the dimensionless time defined by $T$ =$\mathit{\Gamma} t$. \\
-\\
-Please confirm line 354.
+$T$ is the dimensionless time defined by $T$ =$\mathit{\Gamma} t$.  Please see
+equation (8) in the revision. \\
 \\
@@
 Response: \\
-We agree with the reviewer's suggestion. We added results at $T$ = 40.1, 50.0, and 56.7 to the drop status for $Re$ = 1.0 in Fig. 4.
-As can be seen from new Fig. 4, a drop remains a stable deformed state after $T$ = 35.0. In the revised paper, such a comment was added.\\
-\\
-Please confirm lines 380 to 381.
+We agree with the reviewer's suggestion.
+We added results at $T$ = 40.1, 50.0, and 56.7 to the drop case for $Re$ = 1.0 in Fig.
+4.
+As can be seen from the new Fig.
+4, a drop remains a stable deformed state after $T$ = 35.0.
+In the revised paper, such a comment was added.\\
 \\
@@
 \\
-Please see lines 408 to 413.
-\\
 
@@
 \\
-Please see lines 440 to 442.
-\\
 
@@
 In the revised paper, we added these explanations.  \\
-\\
-Please see lines 497 to 501.
 \\

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer3.tex
hand off back to Mitsuhiro

@@
 Response: \\
-We carefully checked English writing and grammar.\\
+We carefully made multiple run-throughs of our paper fixing all English errors and awkward constructs.\\
 
@@
 Response: \\
-We have referred to and explained previous studies about bubble deformation and breakup in the ``Introduction".
+We have completely rewritten the introduction in order to make our message very clear.
+\par
+To summarize: \\
+We have referred to and explained previous studies about bubble deformation and breakup in the ``Introduction.''
 Besides, we have stated the novelty of this study and the difference between this study and previous studies.
@@
 \\
-Please see the ``Introduction".
+Again, please see the revised ``Introduction.''  The Introduction is better now.
 \\
@@
 Response: \\
-We carefully checked The ``Conclusions", and believe the results and discussion properly support our conclusions.\\
-We have made a minor alteration to the  ``Conclusions".\\
+We carefully checked the ``Conclusions,'' and believe the results and discussion properly support our conclusions.\\
+We have made some minor alterations to the ``Conclusions.'' Also, we have added an additional paragraph which gives suggestions for future research. \\
 \\
-Please see the ``Conclusions".
+Please see the improved ``Conclusions.'' 
 \\

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer4.tex
hand off back to Mitsuhiro

@@
 Response: \\
-Thank you for your kind comments. 
-In the revised paper, we have completely modified the ``Introduction" and stated the target and applicable processes of this study.\\
-\\
-Please see the ``Introduction".
+Thank you for your kind comments.  In the revised paper, we have completely modified the ``Introduction'' and improved the motivation for our research.\\
 \\
@@
 Response: \\
-Thank you very much for your suggestions.  We have additionally referred to our papers (following three papers) 
-performed based on the computational code with the same algorithm.
-
-\begin{enumerate}
-\item [1.] M. Ohta, T. Furukawa, Y. Yoshida, M. Sussman,\\
-A Three-Dimensional Numerical Study on the Dynamics and Deformation of a Bubble Rising in a Hybrid Carreau and FENE-CR Modeled Polymeric Liquid, 
-Journal of Non-Newtonian Fluid Mechanics, Vol.265, pp.66-78 (2019).\\
-\item [2.] M. Ohta, Y. Akama, Y. Yoshida, \\
-M. Sussman, Influence of the Viscosity Ratio on Drop Dynamics and Breakup for a Drop Rising in an Immiscible Low-Viscous Liquid,\\
-Journal of Fluid Mechanics, Vol.752, pp.383-409 (2014).\\
-\item [3.]  M. Ohta, M. Sussman, \\
-The Buoyancy-Driven Motion of a Single Skirted Bubble or Drop Rising through a Viscous Liquid, \\
-Physics of Fluids, Vol.24, 112101 (18pp) (2012).\\
-\end{enumerate}
-Please see lines 223 to 227.
+Thank you very much for your suggestions.  Please see the top of section 3.2 which now references our past work on the algorithm that is employed in this paper.
 \\
@@
 We have added the range of $\mu_{\rm m}$ and $V$ used in this study.\\
-\\
-Please see lines 119 to 120.
 \\
@@
 \\
-Please see line 95 (the definiton of $Fr$) and lines 123 to 130.
+Please see line 181 in section 2 (the definiton of $Fr$) and the remark in section 2.
 \\

### 2024-11-29 Revised-paper/Paper/Bubble-deformation-Rev.tex
hand off back to Mitsuhiro

@@
 \usepackage{bm}% bold math
-%\usepackage{comment}
 \usepackage{color}
@@
 \cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
-\begin{comment} 
+%\begin{comment} 
 \affiliation[1]{
@@
   country={Japan}}
-\end{comment}
+%\end{comment}
 
@@
 
-\begin{comment} 
+%\begin{comment} 
 \affiliation[3]{
@@
 \author[4]{Edwin Jimenez}  
-\begin{comment} 
+%\begin{comment} 
 \affiliation[4]{
@@
   country={USA}}
-\end{comment}
+%\end{comment}
 
 \author[5]{Mark Sussman}  
-\begin{comment} 
+%\begin{comment} 
 \affiliation[5]{
@@
   country={USA}}
-\end{comment}
+%\end{comment}
 
@@
 \textcolor{red} {
-Bubble dynamics in shear flow, including breakup, is critically important for various \textcolor{blue} {gas-liquid} scientific and engineering processes.
+Bubble dynamics in shear flow, including breakup, is critically important for various gas-liquid scientific and engineering processes.
 We refer the reader to the following experimental studies relating to bubble deformation in foaming processes, microfluidic devices, microbubbles in the blood circulation system, materials processing, pharmaceuticals, minerals engineering, bubble column reactor, underwater projectiles, polyethylene devolatilization, microfluidics, food aeration, passive cyclonic separators, and cosmetics\cite{ChuFinBouAtaHamPug19,MulTobDreFisWin08,BenRodFauPinFerPerGarMirLim18,DreSai15,EFTEKHARI2021837,WANG2023108105,doi:10.1021/acs.langmuir.1c01814,yoshikawa2010bubble,CanedoETAL,GAO2022103212,WONG2012417,PolyethyleneDevo,FRENSE2024120579,lohse2018bubble,schluter2021small,SANOGO2023112478,hoyt2013performance,sines2020study}.  In particular, it is the study of bubble deformation as it pertains to high-performance plastics applications that motivate this work.
@@
 \par
-\textcolor{blue} 
+\textcolor{red} 
 { Thus, a lot of studies about the deformation and breakup of a drop in simple linear shear have been presented so far.
@@
 We use three different grid systems, (i) $\Delta x^{\ell=1}=R/8$, (ii) $\Delta x^{\ell=1}=R/16$, and (iii) $\Delta x^{\ell=1}=R/24$, in order to determine $Re_{\rm c}$.
-Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation parameter $D$ over time for the three grid systems; the $x$-axis is a dimensionless time defined by $T=\mathit{\Gamma} t$ and the $y$-axis is $D$.
+Figure~\ref{fig:DeEvolution} shows the time evolution of the deformation parameter $D$ over time for the three grid systems; the $x$-axis is a dimensionless time defined by,
+\textcolor{red}{
+\begin{eqnarray}
+T=\Gamma t,
+\end{eqnarray}
+}
+and the $y$-axis is $D$.
 The results show that bubble breakup occurs at $Re_{\rm c}$ = 35 for the grid system with $\Delta x^{\ell=1}=R/16$, while the finer computational grid with $\Delta x^{\ell=1}=R/24$ predicts a critical value of $Re_{\rm c}$ = 34.
@@
 	   $1.0<Re_{\rm c}<1.1$.
-	   ($\lambda$ = $\eta$ = 1.0)}
- }
-  \label{fig:DropBreak}
+	   ($\lambda$ = $\eta$ = 1.0) \label{fig:DropBreak} }
+ }
+
 \end{figure}
